### 2022-11-15 scripts/00_eda.qmd
first commit

---
title: "MEPS"
format: html
editor: visual
execute:
  echo: false
  include: false
---

Notes:
- Only have US Born data from 2002 - 2003, then 2007 - 2013

```{r}
# Libraries
library(tidyverse)
library(haven)

# Read in data
# For the time being, just going to work with 2001 - 2006 to recreate table
# in that paper
dat_files <- list.files(path = 'data', pattern = 'meps', full.names = TRUE)
dat_names <- map_chr(dat_files, ~str_extract(.x, 'meps[0-9]{4}'))
# 
readAndSelect <- function(data_path, data_year) {
  yr <- substr(data_year, 7, 8)
  eye_var <- paste0('DSEY', yr, '53')
  chol_var <- paste0('DSCH', yr, '53')
  feet_var <- paste0('DSFT', yr, '53')
  flu_var <- paste0('DSFL', yr, '53')
  if (str_ends(data_path, '[sSpP]{3}') == TRUE) {
    temp <- read_xpt(data_path)

  } else {
    temp <- read_sas(data_path)

  }
  if (yr == '01') {
    temp <- temp %>% 
      mutate(RACEX = recode_factor(
        RACEX,
        `1` = 'American Indian',
        `2` = 'Aleut, Eskimo',
        `3` = 'Asian or Pacific Islander',
        `4` = 'Black',
        `5` = 'White'
      ))
  }

  temp %>% 
    mutate(across(starts_with('RACE'), ~as.factor(.x))) %>% 
    select(starts_with('DOB'),
           starts_with('DUPERSID'),
           starts_with('USBORN'),
           starts_with('BORN'), # Two different born in USA variables used in different years
           starts_with('AGE'),
           starts_with('RACE'),
           starts_with('SEX'),
           starts_with('VARPSU'), # PSU
           starts_with('VARSTR'), # Strata
          # starts_with('INSCOV'), # Insurance coverage variable
           starts_with('HIDEG'), # Highest degree - want only HIDEGYR and HIDEG
           starts_with('HIDEG'), # Highest degree when first entered MEPS
           starts_with('TTLP'), # Total income
           starts_with('POVCAT'), # Categorical poverty status
           #starts_with('POVLEV'), # Continuous poverty status
           #starts_with('REGION'),
           starts_with('DENTCK53'), # Dental checkup, only 2000 - 2016,
           matches('DVTOT[0-9]{2}'), # # of dental care visits in YYYY        
           starts_with('CHOLCK'), # Cholesterol check, only 2000 - 2016,
           starts_with('CHECK53'), # Routine check up, only 2000 - 2016,
           starts_with('FLUSHT'), # Flu shot. only 2000 - 2016
           starts_with('DSFL'),
           starts_with('DIAB'), # 3 different variable names for diabetes, all start with DIABDX. this should also grab the DAIBW weight variables
           starts_with(!!eye_var), # Get only the eye variable for each year
           starts_with(!!flu_var),
           starts_with(!!chol_var),
           starts_with(!!feet_var),
           starts_with('DSEYE53'), # Have to get the 2001 eye check variable too
           starts_with('DSA1'), # A1C test,
           starts_with('DSCKFT'), # Feet check, only 2001 - 2007
          -starts_with('DSEB'), # Remove the eye test in year before columns
          -contains('AGE31X'),
          -contains('AGE42X'),
          -contains('AGE53x'), # Remove some of the extra age variables
           starts_with('PERWT'), # Person weight level. Not sure I need this, since just working with DCS variables
           starts_with('INSCOP') # Inscope, again not sure if needed but putting here anyway for now
           )
}
safeReadAndSelect <- safely(readAndSelect)
dat_list <- map2(dat_files, dat_names, ~readAndSelect(.x, .y))
names(dat_list) <- dat_names

# Check number of columns
map(dat_list, ~ncol(.x))

```
# To do for 11/4 or 11/7: Figure out how to actually recode DSEYE53.

```{r}
dat <- bind_rows(dat_list, .id = 'year')
# Do some type conversions
dat <- dat %>%
  mutate(
    DSEY0153 = case_when(
      DSEYE53 == 2 ~ 1,
      DSEYE53 %in% c(1, 3, 4, 5) ~ 2,
      DSEYE53 == -9 ~ -9,
      DSEYE53 == -8 ~ -8,
      DSEYE53 == -1 ~ -1,
      TRUE ~ as.numeric(DSEYE53)
    ),
    DSA1C53 = as.factor(
      case_when(
        DSA1C53 == -1 ~ 'Inapplicable',
        DSA1C53 == -7 ~ 'Refused',
        DSA1C53 == -8 ~ 'DK',
        DSA1C53 == -9 ~ 'Not ascertained',
        DSA1C53 == -15 ~ 'Cannot be computed',
        DSA1C53 %in% c(0, 1, 96) ~ 'Less than 2 or more A1C tests in a year',
        DSA1C53 >= 2 ~ '2 or more A1C tests in a year',
        TRUE ~ as.character(DSA1C53)
      )
    ),

    DSCKFT53 = as.factor(
      case_when(
        DSCKFT53 >= 1 ~ 'Within last year',
        DSCKFT53 == 0 ~ 'No foot examinations in a year',
        DSCKFT53 == -1 ~ 'Inapplicable',
        DSCKFT53 == -7 ~ 'Refused',
        DSCKFT53 == -8 ~ 'DK',
        DSCKFT53 == -9 ~ 'Not ascertained'
      )
    )
  ) %>%
  select(-DSEYE53) %>% # Remove the 2001 eye variable that we recoded
  mutate(
    across(
      c(
        starts_with('DS'),
        CHOLCK53,
        CHECK53,
        FLUSHT53,
        HIDEGYR,
        HIDEG,
        RACEX,
        RACETHNX,
        USBORN42
      ),
      ~ as.factor(.x)
    )
  )

# Recode factors to facilitate working with them
dat <- dat %>%
  mutate(
    across(
      intersect(starts_with('DSEY'),
                ends_with('53')),
      ~ recode_factor(
        .x,
        `-9` = 'Not ascertained',
        `-8` = 'DK',
        `-1` = 'Inapplicable',
        `1` = 'YES',
        `2` = 'NO'
      )
    ),
    across(
      intersect(starts_with('DSCH'),
                ends_with('53')),
      ~ recode_factor(
        .x,
        `-9` = 'Not ascertained',
        `-8` = 'DK',
        `-1` = 'Inapplicable',
        `1` = 'Within last year',
        `2` = 'NO'
      )
    ),
    across(
      intersect(starts_with('DSFL'),
                ends_with('53')),
      ~ recode_factor(
        .x,
        `-9` = 'Not ascertained',
        `-8` = 'DK',
        `-1` = 'Inapplicable',
        `1` = 'Within last year',
        `2` = 'NO'
      )
    ),
    across(
      intersect(starts_with('DSFT'),
                ends_with('53')),
      ~ recode_factor(
        .x,
        `-9` = 'Not ascertained',
        `-8` = 'DK',
        `-1` = 'Inapplicable',
        `1` = 'Within last year',
        `2` = 'NO'
      )
    ), 
    across(
      starts_with('DVTOT'),
      ~ as.factor(case_when(.x >= 1 ~ 1,
                            TRUE ~ 0)) %>%
      recode_factor(`1` = 'Once a year',
                    `0` = 'Less than once a year')
    ), 
    across(
      starts_with('HIDE'),
      ~ recode_factor(
        .x,
        `-9` = 'Not ascertained',
        `-8` = 'DK',
        `-7` = 'Refused',
        `1` = 'No Degree',
        `2` = 'GED',
        `3` = 'HS',
        `4` = 'Bachelor',
        `5` = 'Masters',
        `6` = 'Doctorate',
        `7` = 'Other',
        `8` = 'Under 16, inapplicable'
      ) %>%
        fct_collapse(
          `Less than high school` = c('No Degree', 'GED', 'Under 16, inapplicable'),
          `High school` = c('HS'),
          `Greater than HS` = c('Bachelor', 'Masters', 'Doctorate', 'Other'),
          `Not available` = c('Not ascertained', 'DK', 'Refused', '-1', '-15')
        )
    ),
    across(
      c(RACEX, RACEV1X),
      ~ recode_factor(
        .x,
        `1` = 'White',
        `2` = 'Black',
        `3` = 'Amer Indian/Alaska Native',
        `4` = 'Asian',
        `5` = 'Native Hawiian/Pacific Islander',
        `6` = 'Multiple races reported',
        `-9` = 'Not ascertained',
        `-8` = 'DK',
        `-7` = 'Refused'
      )
    ),
    RACETHNX = recode_factor(
      RACETHNX,
      `1` = 'Hispanic',
      `2` = 'Black/Not Hispanic',
      `3` = 'Asian/Not Hispanic',
      `4` = 'Other Race/Not Hispanic',
    ) %>% fct_expand('White/Not Hispanic'),
    RACETHX = recode_factor(
      RACETHX,
      `1` = 'Hispanic',
      `2` = 'White/Not Hispanic',
      `3` = 'Black/Not Hispanic',
      `4` = 'Asian/Not Hispanic',
      `5` = 'Other Race/Not Hispanic',
    ),
    USBORN42 = recode_factor(
      USBORN42,
      `-9` = 'Not ascertained',
      `-8` = 'DK',
      `-7` = 'Refused',
      `-1` = 'Inapplicable',
      `1` = 'Yes',
      `2` = 'No'
    ),
    BORNUSA = recode_factor(
      BORNUSA,
      `-15` = 'Cannot be computed',
      `-9` = 'Not ascertained',
      `-8` = 'DK',
      `-7` = 'Refused',
      `-1` = 'Inapplicable',
      `1` = 'Yes',
      `2` = 'No'
    ),
    across(
      c(CHOLCK53, CHECK53, FLUSHT53),
      ~ recode_factor(
        .x,
        `-9` = 'Not ascertained',
        `-8` = 'DK',
        `-7` = 'Refused',
        `-1` = 'Inapplicable',
        `1` = 'Within last year',
        `2` = 'Within past 2 years',
        `3` = 'Within past 3 years',
        `4` = 'Within past 5 years',
        `5` = 'More than 5 years',
        `6` = 'Never'
      ) %>%
        fct_collapse(
          `Within last 2 more more years` = c(
            'Within past 2 years',
            'Within past 3 years',
            'Within past 5 years',
            'More than 5 years',
            'Never'
          ),
          `Not available` = c(
            'Not ascertained',
            'DK',
            'Refused',
            'Inapplicable'
          )
        )
    ),
    DENTCK53 = recode_factor(
      DENTCK53,
      `-9` = 'Not ascertained',
      `-8` = 'DK',
      `-7` = 'Refused',
      `-1` = 'Inapplicable',
      `1` = 'Twice a year or more',
      `2` = 'Once a year',
      `3` = 'Less than once a year',
      `4` = 'Never go to dentist'
    ),
    SEX = recode_factor(SEX,
                        `1` = 'Male',
                        `2` = 'Female')

  )

dat$RACETHNX[dat$RACEX == 'White'] <- 'White/Not Hispanic'

# Need to coalesce the eye exam columns into a single column for a Y/N eye exam

```

Clean data. Here's some relevant coding information:
DSEYE53: 1 - 4 can be considered yes for eye exam, 5 is never. -1 Inapplicable, -8 DK (?), -9 Not ascertained (2001 only)
DSEY0353: Eye exam in 2003: 1 YES, 2 NO
DSEY0253: Eye exam in 2002: 1 YES, 2 NO
DSEY0153: Eye exam in 2001: 1 YES, 2 NO
DSEY0453: Eye exam in 2004: 1 YES, 2 NO
DSEY0553: Eye exam in 2005: 1 YES, 2 NO
DSEY0654: Eye exam in 2006: 1 YES, 2 NO
DSEY0754: Eye exam in 2007: 1 YES, 2 NO
DSEB0153: Eye exam before 2001: 1 YES, 2 NO
DSEB0253: Eye exam before 2002: 1 YES, 2 NO
DSEB0353: Eye exam before 2003: 1 YES, 2 NO
DSEB0453: Eye exam before 2004, 1 YES, 2 NO
DSEB0553: Eye exam before 2005, 1 YES, 2 NO
DSEYNV53: Never had eye exam: 1 YES, 2 NO
DSEYPR53: Has diabetes caused eye problems: 1 YES, 2 NO
RACEX: Race: 1 White (no other reported), 2 Black (nor), 3 Amer Indian (nor), 4 Asian (nor), 5 Native hawaiian (nor), 6 Multiple races reported
RACETHNX: Race/Ethnicity: 1 - Hispanic, 2 - Black/No other race/not hispanic, 3 - Asian/No other race/not hispanic, 4 - Other race/not hispanic
HIDEGYR/HIDEG: Highest degree when first entered MIPS: 1 - No Degree, 2 - GED, 3 - High School Diploma, 4 - Bacehlor's Degree, 5 - MS, 6 - Doctorate, 7 - Other, 8 - Under 16, inapplicable
CHOLCK53: How long since last cholesterol check? (only available 2000 - 2016).

```{r}
# Three columns denote the DIAB diagnosis based on different years. I coalesce them
# to create a single column, which we can then filter on.
# Coding appears the same for all variables. 1 is diagnosed with diabetes, 2 is not. Other numbers
# are variations on missing or non-response
dat$DIABDX_all <- coalesce(dat$DIABDX53, dat$DIABDX_M18) # When using full data, add dat$DIABDX_M18,

# Variable to coallesce
# HIDEGYR/HIDEG
# POVCAT
# DIABW variables
dat <- dat %>%
  mutate(
    DSEY_all = coalesce(!!!select(., starts_with('DSEY'))),
    HIDEG_all = coalesce(!!!select(., starts_with('HIDEG'))),
    DIABW = coalesce(!!!select(., starts_with('DIABW'))),
    POVCAT_all = coalesce(!!!select(., starts_with('POVCAT'))),
    USBORN_all = coalesce(!!!select(., contains('BORN'))),
    VARPSU_all = coalesce(!!!select(., starts_with('VARPSU'))),
    VARSTR_all = coalesce(!!!select(., starts_with('VARSTR'))),
    AGE_all = coalesce(!!!select(., starts_with('AGE'))),
    RACE_all = coalesce(!!!select(., RACETHNX, RACETHX)),
    CHOL_all = coalesce(!!!select(., CHOLCK53, starts_with('DSCH'))),
    FLU_all = coalesce(!!!select(., FLUSHT53, starts_with('DSFL'))),
    DENT_all = coalesce(!!!select(., DENTCK53, num_range('DVTOT', 17:20))),
    FEET_all = coalesce(!!!select(., DSCKFT53, starts_with('DSFT'))),

  ) %>% 
  mutate(
    AGE_all = as.factor(case_when(
      AGE_all == -1 ~ NA_character_,
      AGE_all < 18 & AGE_all > -1 ~ NA_character_,
      AGE_all >= 18 & AGE_all <= 44 ~ '18 to 44',
      AGE_all >= 45 & AGE_all <= 64 ~ '45 to 64',
      AGE_all >= 65 & AGE_all <= 74 ~ '65 to 74',
      AGE_all >= 75 ~ '75+',
      TRUE ~ as.character(AGE_all)
    ))
  )
# Get just data for people with diabetes
# Get just the variables I want
diab_dat <- dat %>% 
  select(year, DUPERSID, SEX, DIABW, ends_with('_all'),
         CHOLCK53, FLUSHT53, CHECK53, DENTCK53, DSA1C53, DSCKFT53)

```

```{r}
library(sitrep)
library(gtsummary)
library(srvyr)

diab_list <- group_split(diab_dat, year)
diab_svy <- diab_list[[17]] %>%
  as_survey_design(ids = VARPSU_all, weights = DIABW, strata = VARSTR_all, nest = TRUE)
diab_only <- subset(diab_svy, DIABW != 0)
#svytable(~SEX, design = diab_only)
#test <-svytable(~CHOLCK53 + USBORN_all, design = diab_only, Ntotal = 100)

test <- diab_svy %>%
  tab_survey(
    #CHOL_all,
    #FLU_all,
    #DENT_all,
    #DSA1C53,
    DSEY_all,
    #FEET_all,
    pretty = FALSE,
    strata = 'AGE_all',
    wide = FALSE,
    method = 'mean',
    #drop = c('Not ascertained', 'DK', 'Refused', 'Inapplicable'),
    keep = c(
      'Within last year',
      '2 or more A1C tests in a year',
      '1 or more foot examinations in a year',
      'Once a year',
      #Dental checkups
      'YES' # eye exam
    )
  )
```

```{r}
diab_list <- group_split(diab_dat, year)
diab_svy <- diab_list[[8]] %>% 
  as_survey_design(ids = VARPSU_all, weights = DIABW, strata = VARSTR_all, nest = TRUE)
diab_only <- subset(diab_svy, DIABDX_all == 1)
calcProp <- function(data, year, variable) {
  if (is.character(variable)) {
    vari <- enquo(variable)
    diab_svy <- data %>%
    as_survey_design(
      ids = VARPSU_all,
      weights = DIABW,
      strata = VARSTR_all,
      nest = TRUE
    )
  diab_svy %>%
    tab_survey(
      CHOL_all, FLU_all, DENT_all, DSA1C53, DSEY_all, FEET_all, #CHECK53 - not in all years
      pretty = FALSE,
      strata = !!vari,
      wide = FALSE,
      method = 'mean'
      #drop = c('Not ascertained', 'DK', 'Refused', 'Inapplicable'),
      # keep = c(
      #   'Within last year',
      #   '2 or more A1C tests in a year',
      #   '1 or more foot examinations in a year',
      #   'Once a year',
      #   #Dental checkups
      #   'YES' # eye exam
      # )
    ) %>%
    mutate(year = year)
  } else {
    vari <- variable
    diab_svy <- data %>%
    as_survey_design(
      ids = VARPSU_all,
      weights = DIABW,
      strata = VARSTR_all,
      nest = TRUE
    )
  diab_svy %>%
    tab_survey(
      CHOL_all, FLU_all, DENT_all, DSA1C53, DSEY_all, FEET_all, #CHECK53 - not in all years
      pretty = FALSE,
      strata = vari,
      wide = FALSE,
      method = 'mean'
      #drop = c('Not ascertained', 'DK', 'Refused', 'Inapplicable'),
      # keep = c(
      #   'Within last year',
      #   '2 or more A1C tests in a year',
      #   '1 or more foot examinations in a year',
      #   'Once a year',
      #   #Dental checkups
      #   'YES' # eye exam
      # )
    ) %>%
    mutate(year = year)
  }

}
safelyCalcProp <- safely(calcProp)
possiblyCalcProp <- possibly(calcProp, otherwise = NULL)
library(furrr)
future::plan(multisession, workers = 3)
overall <- future_map2(diab_list, 2001:2020, ~safelyCalcProp(.x, .y, NULL))
sex <- future_map2(diab_list, 2001:2020,  ~possiblyCalcProp(.x, .y, 'SEX'))
race <- future_map2(diab_list, 2001:2020, ~possiblyCalcProp(.x, .y, 'RACE_all'))
edu <- future_map2(diab_list, 2001:2020,  ~possiblyCalcProp(.x, .y, 'HIDEG_all'))
age <- future_map2(diab_list, 2001:2020,  ~safelyCalcProp(.x, .y, 'AGE_all'))
future::plan(sequential)

```

```{r}
race_df <- compact(race) %>% 
  bind_rows(.)
sex_df <- compact(sex) %>% 
  bind_rows(.)
edu_df <- compact(edu) %>% 
  bind_rows(.)
overall_df <- compact(overall) %>% 
  bind_rows(.)

ggplot(race_df, aes(x = year, y = proportion, group = RACE_all, colour = RACE_all)) +
  geom_line() +
  facet_wrap(~variable)

ggplot(sex_df, aes(x = year, y = proportion, group = SEX, colour = SEX)) +
  geom_line() +
  facet_wrap(~variable)

ggplot(edu_df, aes(x = year, y = proportion, group = HIDEG_all, colour = HIDEG_all)) +
  geom_line() +
  facet_wrap(~variable)

ggplot(overall_df, aes(x = year, y = proportion)) +
  geom_line() +
  facet_wrap(~variable)

```

# Get the dashboard medians
```{r}
dash_files <- list.files(here::here('data', 'dashboard'), full.names = TRUE)
dash_file_names <- str_extract(list.files(here::here('data', 'dashboard')), '^([^.])+')
dash_list <-
  map(dash_files,
      ~ read_csv(
        .x,
        skip = 2,
        col_names = TRUE,
        n_max = 21,
        col_types = c('dcddd'),
        na = c('Suppressed', 'No Data')
      ))
names(dash_list) <- dash_file_names
dash_dat <- bind_rows(dash_list, .id = 'file_name')%>% 
  separate(file_name, into = c('indicator', 'stratifier', 'strata'), sep = "_") %>% 
  janitor::clean_names() %>% 
  mutate(across(percentage:upper_limit, ~.x/100))

overall_indicator <- overall_df %>%
  mutate(
    variable = case_when(
      variable == 'FLU_all' ~ 'flu',
      variable == 'DSEY_all' ~ 'eye-exam',
      variable == 'DSA1C53' ~ 'a1c',
      variable == 'FEET_all' ~ 'foot',
      TRUE ~ variable
    )
  ) %>%
  left_join(
    .,
    filter(dash_dat, stratifier == 'total'),
    by = c('year', 'variable' = 'indicator')
  )

sex_indicator <- sex_df %>%
  mutate(
    variable = case_when(
      variable == 'FLU_all' ~ 'flu',
      variable == 'DSEY_all' ~ 'eye-exam',
      variable == 'DSA1C53' ~ 'a1c',
      variable == 'FEET_all' ~ 'foot',
      TRUE ~ variable
    ),
    SEX = case_when(SEX == 'Male' ~ 'M',
                    SEX == 'Female' ~ 'F')
  ) %>%
    left_join(
    .,
    filter(dash_dat, stratifier == 'gender'),
    by = c('year', 'variable' = 'indicator', 'SEX' = 'strata')
  )

race_indicator <- race_df %>%
  mutate(
    variable = case_when(
      variable == 'FLU_all' ~ 'flu',
      variable == 'DSEY_all' ~ 'eye-exam',
      variable == 'DSA1C53' ~ 'a1c',
      variable == 'FEET_all' ~ 'foot',
      TRUE ~ variable
    ),
    RACE_all = case_when(
      RACE_all == 'Hispanic' ~ 'hispanic',
      RACE_all == 'Black/Not Hispanic' ~ 'black',
      RACE_all == 'White/Not Hispanic' ~ 'white',
      RACE_all == 'Asian/Not Hispanic' ~ 'asian',
      TRUE ~ as.character(RACE_all)
    )
  ) %>%
    left_join(
    .,
    filter(dash_dat, stratifier == 'race'),
    by = c('year', 'variable' = 'indicator', 'RACE_all' = 'strata')
  )

edu_indicator <- edu_df %>%
  mutate(
    variable = case_when(
      variable == 'FLU_all' ~ 'flu',
      variable == 'DSEY_all' ~ 'eye-exam',
      variable == 'DSA1C53' ~ 'a1c',
      variable == 'FEET_all' ~ 'foot',
      TRUE ~ variable
    ),
    HIDEG_all = case_when(
      HIDEG_all == 'Greater than HS' ~ 'greater-than-HS',
      HIDEG_all == 'Less than high school' ~ 'less-than-HS',
      HIDEG_all == 'High school' ~ 'HS',
      TRUE ~ as.character(HIDEG_all)
    )
  ) %>%
    left_join(
    .,
    filter(dash_dat, stratifier == 'edu'),
    by = c('year', 'variable' = 'indicator', 'HIDEG_all' = 'strata')
  )

```

```{r}
overall_indicator %>%
  filter(variable %in% c('a1c', 'eye-exam', 'flu', 'foot')) %>%
  ggplot() +
  geom_line(aes(x = year, y = proportion, group = variable, linetype = 'MEPS')) +
  geom_line(aes(x = year, y = percentage, group = variable, linetype = 'Dashboard')) +
  facet_wrap( ~ variable) +
  theme_bw()

sex_indicator %>%
  filter(variable %in% c('a1c', 'eye-exam', 'flu', 'foot')) %>%
  ggplot() +
  geom_line(aes(x = year, y = proportion, group = SEX, color = SEX, linetype = 'MEPS') ) +
  geom_line(aes(x = year, y = percentage, group = SEX, color = SEX, linetype = 'Dashboard')) +
  facet_wrap( ~ variable) +
  scale_linetype_manual(labels = c('Dashboard', 'MEPS'),
                        values = c('solid', 'dashed')) +
  theme_bw()

race_indicator %>%
  filter(variable %in% c('a1c', 'eye-exam', 'flu', 'foot')) %>%
  ggplot() +
  geom_line(aes(
    x = year,
    y = proportion,
    group = RACE_all,
    color = RACE_all,
    linetype = 'MEPS'
  )) +
  geom_line(aes(
    x = year,
    y = percentage,
    group = RACE_all,
    color = RACE_all,
    linetype = 'Dashboard'
  )) +
  facet_wrap(~ variable) +
  scale_linetype_manual(labels = c('Dashboard', 'MEPS'),
                        values = c('solid', 'dashed')) +
  theme_bw()

edu_indicator %>%
  filter(variable %in% c('a1c', 'eye-exam', 'flu', 'foot')) %>%
  ggplot() +
  geom_line(aes(
    x = year,
    y = proportion,
    group = HIDEG_all,
    color = HIDEG_all,
    linetype = 'MEPS'
  )) +
  geom_line(aes(
    x = year,
    y = percentage,
    group = HIDEG_all,
    color = HIDEG_all,
    linetype = 'Dashboard'
  )) +
  facet_wrap(~ variable) +
  scale_linetype_manual(labels = c('Dashboard', 'MEPS'),
                        values = c('solid', 'dashed')) +
  theme_bw()

```

### 2022-11-15 _targets.R

@@ -1,0 +1,103 @@
+# Created by use_targets().
+# Follow the comments below to fill in this target script.
+# Then follow the manual to check and run the pipeline:
+#   https://books.ropensci.org/targets/walkthrough.html#inspect-the-pipeline # nolint
+
+# Load packages required to define the pipeline:
+library(targets)
+library(future)
+library(future.callr)
+library(tarchetypes)
+# Set up future
+plan(callr)
+
+# Set target options:
+tar_option_set(
+  packages = c("tidyverse", "haven", 'sitrep', 'gtsummary', 'srvyr'), # packages that your targets need to run
+  format = "rds" # default storage format
+  # Set other options as needed.
+)
+
+# Run the R scripts in the R/ folder with your custom functions:
+tar_source('scripts/functions.R')
+# source("other_functions.R") # Source other scripts as needed. # nolint
+
+# Replace the target list below with your own:
+list(
+  # tar_target(
+  #   name = grasp_form_data_input,
+  #   command = "//cdc.gov/locker/CCHP_NCCD_DDT_Data1/epistat/Surveillance/Surveillance and Trends Reporting System/GRASP/NEW_Jan2018/Datasets/consol_dat_2022_1014.sas7bdat",
+  #   format = 'file'
+  # ),
+  # tar_target(
+  #   name = grasp_form_data,
+  #   command = readGraspData(grasp_form_data_input),
+  #   format = 'feather'
+  # ),
+  # Get MEPS files
+  tar_target(
+    name = dat_files,
+    command = list.files(path = 'data', pattern = 'meps', full.names = TRUE)
+  ),
+  tar_target(
+    dat_names,
+    map_chr(dat_files, ~str_extract(.x, 'meps[0-9]{4}'))
+  ),
+  tar_target(
+    dat_list,
+    map2(dat_files, dat_names, ~readAndSelect(.x, .y)) %>%
+      setNames(dat_names)
+  ),
+  tar_target(
+    dat,
+    bind_rows(dat_list, .id = 'year')
+  ),
+  # Clean data
+  tar_target(
+    cleaned_dat,
+    cleanMepsData(dat)
+  ),
+  tar_target(
+    combined_dat,
+    coalesceData(cleaned_dat)
+  ),
+  # Get down to just the columns we want
+  tar_target(
+    diab_dat,
[…]

### 2022-11-15 scripts/00_GRASP_formatted.R

@@ -1,0 +1,3 @@
+library(targets)
+file_path <- "//cdc.gov/locker/CCHP_NCCD_DDT_Data1/epistat/Surveillance/Surveillance and Trends Reporting System/GRASP/NEW_Jan2018/Datasets/consol_dat_2022_1014.sas7bdat"
+test <- read_sas(file_path)

### 2022-11-15 scripts/functions.R

@@ -1,0 +1,416 @@
+
+library(tidyverse)
+library(haven)
+
+readGraspData <- function(filepath) {
+  if (file.exists(filepath)) {
+  haven::read_sas(filepath)
+  } else {
+    print('File not found')
+  }
+}
+
+
+# Read in data
+readAndSelect <- function(data_path, data_year) {
+  yr <- substr(data_year, 7, 8)
+  eye_var <- paste0('DSEY', yr, '53')
+  chol_var <- paste0('DSCH', yr, '53')
+  feet_var <- paste0('DSFT', yr, '53')
+  flu_var <- paste0('DSFL', yr, '53')
+  if (str_ends(data_path, '[sSpP]{3}') == TRUE) {
+    temp <- read_xpt(data_path)
+
+  } else {
+    temp <- read_sas(data_path)
+
+  }
+  if (yr == '01') {
+    temp <- temp %>%
+      mutate(RACEX = recode_factor(
+        RACEX,
+        `1` = 'American Indian',
+        `2` = 'Aleut, Eskimo',
+        `3` = 'Asian or Pacific Islander',
+        `4` = 'Black',
+        `5` = 'White'
+      ))
+  }
+
+  temp %>%
+    mutate(across(starts_with('RACE'), ~as.factor(.x))) %>%
+    select(starts_with('DOB'),
+           starts_with('DUPERSID'),
+           starts_with('USBORN'),
+           starts_with('BORN'), # Two different born in USA variables used in different years
+           starts_with('AGE'),
+           starts_with('RACE'),
+           starts_with('SEX'),
+           starts_with('VARPSU'), # PSU
+           starts_with('VARSTR'), # Strata
+           # starts_with('INSCOV'), # Insurance coverage variable
+           starts_with('HIDEG'), # Highest degree - want only HIDEGYR and HIDEG
+           starts_with('HIDEG'), # Highest degree when first entered MEPS
+           starts_with('TTLP'), # Total income
+           starts_with('POVCAT'), # Categorical poverty status
+           #starts_with('POVLEV'), # Continuous poverty status
+           #starts_with('REGION'),
+           starts_with('DENTCK53'), # Dental checkup, only 2000 - 2016,
+           matches('DVTOT[0-9]{2}'), # # of dental care visits in YYYY
+           starts_with('CHOLCK'), # Cholesterol check, only 2000 - 2016,
[…]

### 2022-11-29 scripts/00_eda.qmd
Implemented suppression flowchart

@@
 
-Notes:
-- Only have US Born data from 2002 - 2003, then 2007 - 2013
+Notes: - Only have US Born data from 2002 - 2003, then 2007 - 2013
 
@@
 library(haven)
+library(targets)
 
-# Read in data
-# For the time being, just going to work with 2001 - 2006 to recreate table
-# in that paper
-dat_files <- list.files(path = 'data', pattern = 'meps', full.names = TRUE)
-dat_names <- map_chr(dat_files, ~str_extract(.x, 'meps[0-9]{4}'))
-# 
-readAndSelect <- function(data_path, data_year) {
-  yr <- substr(data_year, 7, 8)
-  eye_var <- paste0('DSEY', yr, '53')
-  chol_var <- paste0('DSCH', yr, '53')
-  feet_var <- paste0('DSFT', yr, '53')
-  flu_var <- paste0('DSFL', yr, '53')
-  if (str_ends(data_path, '[sSpP]{3}') == TRUE) {
-    temp <- read_xpt(data_path)
-
-  } else {
-    temp <- read_sas(data_path)
-
-  }
-  if (yr == '01') {
-    temp <- temp %>% 
-      mutate(RACEX = recode_factor(
-        RACEX,
-        `1` = 'American Indian',
-        `2` = 'Aleut, Eskimo',
-        `3` = 'Asian or Pacific Islander',
-        `4` = 'Black',
-        `5` = 'White'
-      ))
-  }
-
-  temp %>% 
-    mutate(across(starts_with('RACE'), ~as.factor(.x))) %>% 
-    select(starts_with('DOB'),
-           starts_with('DUPERSID'),
-           starts_with('USBORN'),
-           starts_with('BORN'), # Two different born in USA variables used in different years
-           starts_with('AGE'),
-           starts_with('RACE'),
-           starts_with('SEX'),
-           starts_with('VARPSU'), # PSU
-           starts_with('VARSTR'), # Strata
-          # starts_with('INSCOV'), # Insurance coverage variable
-           starts_with('HIDEG'), # Highest degree - want only HIDEGYR and HIDEG
-           starts_with('HIDEG'), # Highest degree when first entered MEPS
-           starts_with('TTLP'), # Total income
-           starts_with('POVCAT'), # Categorical poverty status
-           #starts_with('POVLEV'), # Continuous poverty status
-           #starts_with('REGION'),
-           starts_with('DENTCK53'), # Dental checkup, only 2000 - 2016,
-           matches('DVTOT[0-9]{2}'), # # of dental care visits in YYYY        
-           starts_with('CHOLCK'), # Cholesterol check, only 2000 - 2016,
-           starts_with('CHECK53'), # Routine check up, only 2000 - 2016,
-           starts_with('FLUSHT'), # Flu shot. only 2000 - 2016
-           starts_with('DSFL'),
-           starts_with('DIAB'), # 3 different variable names for diabetes, all start with DIABDX. this should also grab the DAIBW weight variables
-           starts_with(!!eye_var), # Get only the eye variable for each year
-           starts_with(!!flu_var),
-           starts_with(!!chol_var),
-           starts_with(!!feet_var),
-           starts_with('DSEYE53'), # Have to get the 2001 eye check variable too
-           starts_with('DSA1'), # A1C test,
-           starts_with('DSCKFT'), # Feet check, only 2001 - 2007
-          -starts_with('DSEB'), # Remove the eye test in year before columns
-          -contains('AGE31X'),
-          -contains('AGE42X'),
-          -contains('AGE53x'), # Remove some of the extra age variables
-           starts_with('PERWT'), # Person weight level. Not sure I need this, since just working with DCS variables
-           starts_with('INSCOP') # Inscope, again not sure if needed but putting here anyway for now
-           )
-}
-safeReadAndSelect <- safely(readAndSelect)
-dat_list <- map2(dat_files, dat_names, ~readAndSelect(.x, .y))
-names(dat_list) <- dat_names
-
-# Check number of columns
-map(dat_list, ~ncol(.x))
+tar_load(dat_list)
 
 ```
+
 # To do for 11/4 or 11/7: Figure out how to actually recode DSEYE53.
@@
 ```{r}
-dat <- bind_rows(dat_list, .id = 'year')
-# Do some type conversions
-dat <- dat %>%
-  mutate(
-    DSEY0153 = case_when(
-      DSEYE53 == 2 ~ 1,
-      DSEYE53 %in% c(1, 3, 4, 5) ~ 2,
-      DSEYE53 == -9 ~ -9,
-      DSEYE53 == -8 ~ -8,
-      DSEYE53 == -1 ~ -1,
-      TRUE ~ as.numeric(DSEYE53)
-    ),
-    DSA1C53 = as.factor(
-      case_when(
-        DSA1C53 == -1 ~ 'Inapplicable',
-        DSA1C53 == -7 ~ 'Refused',
-        DSA1C53 == -8 ~ 'DK',
-        DSA1C53 == -9 ~ 'Not ascertained',
-        DSA1C53 == -15 ~ 'Cannot be computed',
-        DSA1C53 %in% c(0, 1, 96) ~ 'Less than 2 or more A1C tests in a year',
-        DSA1C53 >= 2 ~ '2 or more A1C tests in a year',
-        TRUE ~ as.character(DSA1C53)
-      )
-    ),
-
-    DSCKFT53 = as.factor(
-      case_when(
-        DSCKFT53 >= 1 ~ 'Within last year',
-        DSCKFT53 == 0 ~ 'No foot examinations in a year',
-        DSCKFT53 == -1 ~ 'Inapplicable',
-        DSCKFT53 == -7 ~ 'Refused',
-        DSCKFT53 == -8 ~ 'DK',
-        DSCKFT53 == -9 ~ 'Not ascertained'
-      )
-    )
-  ) %>%
-  select(-DSEYE53) %>% # Remove the 2001 eye variable that we recoded
-  mutate(
-    across(
-      c(
-        starts_with('DS'),
-        CHOLCK53,
-        CHECK53,
-        FLUSHT53,
-        HIDEGYR,
-        HIDEG,
-        RACEX,
-        RACETHNX,
-        USBORN42
-      ),
-      ~ as.factor(.x)
-    )
-  )
-
-# Recode factors to facilitate working with them
-dat <- dat %>%
-  mutate(
-    across(
-      intersect(starts_with('DSEY'),
-                ends_with('53')),
-      ~ recode_factor(
-        .x,
-        `-9` = 'Not ascertained',
-        `-8` = 'DK',
-        `-1` = 'Inapplicable',
-        `1` = 'YES',
-        `2` = 'NO'
-      )
-    ),
-    across(
-      intersect(starts_with('DSCH'),
-                ends_with('53')),
-      ~ recode_factor(
-        .x,
-        `-9` = 'Not ascertained',
-        `-8` = 'DK',
-        `-1` = 'Inapplicable',
-        `1` = 'Within last year',
-        `2` = 'NO'
-      )
-    ),
-    across(
-      intersect(starts_with('DSFL'),
-                ends_with('53')),
-      ~ recode_factor(
-        .x,
-        `-9` = 'Not ascertained',
-        `-8` = 'DK',
-        `-1` = 'Inapplicable',
-        `1` = 'Within last year',
-        `2` = 'NO'
-      )
-    ),
-    across(
-      intersect(starts_with('DSFT'),
-                ends_with('53')),
-      ~ recode_factor(
-        .x,
-        `-9` = 'Not ascertained',
-        `-8` = 'DK',
-        `-1` = 'Inapplicable',
-        `1` = 'Within last year',
-        `2` = 'NO'
-      )
-    ), 
-    across(
-      starts_with('DVTOT'),
-      ~ as.factor(case_when(.x >= 1 ~ 1,
-                            TRUE ~ 0)) %>%
-      recode_factor(`1` = 'Once a year',
-                    `0` = 'Less than once a year')
-    ), 
-    across(
-      starts_with('HIDE'),
-      ~ recode_factor(
-        .x,
-        `-9` = 'Not ascertained',
-        `-8` = 'DK',
-        `-7` = 'Refused',
-        `1` = 'No Degree',
-        `2` = 'GED',
-        `3` = 'HS',
-        `4` = 'Bachelor',
-        `5` = 'Masters',
-        `6` = 'Doctorate',
-        `7` = 'Other',
-        `8` = 'Under 16, inapplicable'
-      ) %>%
-        fct_collapse(
-          `Less than high school` = c('No Degree', 'GED', 'Under 16, inapplicable'),
-          `High school` = c('HS'),
-          `Greater than HS` = c('Bachelor', 'Masters', 'Doctorate', 'Other'),
-          `Not available` = c('Not ascertained', 'DK', 'Refused', '-1', '-15')
-        )
-    ),
-    across(
-      c(RACEX, RACEV1X),
-      ~ recode_factor(
-        .x,
-        `1` = 'White',
-        `2` = 'Black',
-        `3` = 'Amer Indian/Alaska Native',
-        `4` = 'Asian',
-        `5` = 'Native Hawiian/Pacific Islander',
-        `6` = 'Multiple races reported',
-        `-9` = 'Not ascertained',
-        `-8` = 'DK',
-        `-7` = 'Refused'
-      )
-    ),
-    RACETHNX = recode_factor(
-      RACETHNX,
-      `1` = 'Hispanic',
-      `2` = 'Black/Not Hispanic',
-      `3` = 'Asian/Not Hispanic',
-      `4` = 'Other Race/Not Hispanic',
-    ) %>% fct_expand('White/Not Hispanic'),
-    RACETHX = recode_factor(
-      RACETHX,
-      `1` = 'Hispanic',
-      `2` = 'White/Not Hispanic',
-      `3` = 'Black/Not Hispanic',
-      `4` = 'Asian/Not Hispanic',
-      `5` = 'Other Race/Not Hispanic',
-    ),
-    USBORN42 = recode_factor(
-      USBORN42,
-      `-9` = 'Not ascertained',
-      `-8` = 'DK',
-      `-7` = 'Refused',
-      `-1` = 'Inapplicable',
-      `1` = 'Yes',
-      `2` = 'No'
-    ),
-    BORNUSA = recode_factor(
-      BORNUSA,
-      `-15` = 'Cannot be computed',
-      `-9` = 'Not ascertained',
-      `-8` = 'DK',
-      `-7` = 'Refused',
-      `-1` = 'Inapplicable',
-      `1` = 'Yes',
-      `2` = 'No'
-    ),
-    across(
-      c(CHOLCK53, CHECK53, FLUSHT53),
-      ~ recode_factor(
-        .x,
-        `-9` = 'Not ascertained',
-        `-8` = 'DK',
-        `-7` = 'Refused',
-        `-1` = 'Inapplicable',
-        `1` = 'Within last year',
-        `2` = 'Within past 2 years',
-        `3` = 'Within past 3 years',
-        `4` = 'Within past 5 years',
-        `5` = 'More than 5 years',
-        `6` = 'Never'
-      ) %>%
-        fct_collapse(
-          `Within last 2 more more years` = c(
-            'Within past 2 years',
-            'Within past 3 years',
-            'Within past 5 years',
-            'More than 5 years',
-            'Never'
-          ),
-          `Not available` = c(
-            'Not ascertained',
-            'DK',
-            'Refused',
-            'Inapplicable'
-          )
-        )
-    ),
-    DENTCK53 = recode_factor(
-      DENTCK53,
-      `-9` = 'Not ascertained',
-      `-8` = 'DK',
-      `-7` = 'Refused',
-      `-1` = 'Inapplicable',
-      `1` = 'Twice a year or more',
-      `2` = 'Once a year',
-      `3` = 'Less than once a year',
-      `4` = 'Never go to dentist'
-    ),
-    SEX = recode_factor(SEX,
-                        `1` = 'Male',
-                        `2` = 'Female')
-
-  )
-
-dat$RACETHNX[dat$RACEX == 'White'] <- 'White/Not Hispanic'
-
-# Need to coalesce the eye exam columns into a single column for a Y/N eye exam
-
+tar_load(cleaned_dat)
 ```
 
-Clean data. Here's some relevant coding information:
-DSEYE53: 1 - 4 can be considered yes for eye exam, 5 is never. -1 Inapplicable, -8 DK (?), -9 Not ascertained (2001 only)
-DSEY0353: Eye exam in 2003: 1 YES, 2 NO
-DSEY0253: Eye exam in 2002: 1 YES, 2 NO
-DSEY0153: Eye exam in 2001: 1 YES, 2 NO
-DSEY0453: Eye exam in 2004: 1 YES, 2 NO
-DSEY0553: Eye exam in 2005: 1 YES, 2 NO
-DSEY0654: Eye exam in 2006: 1 YES, 2 NO
-DSEY0754: Eye exam in 2007: 1 YES, 2 NO
-DSEB0153: Eye exam before 2001: 1 YES, 2 NO
-DSEB0253: Eye exam before 2002: 1 YES, 2 NO
-DSEB0353: Eye exam before 2003: 1 YES, 2 NO
-DSEB0453: Eye exam before 2004, 1 YES, 2 NO
-DSEB0553: Eye exam before 2005, 1 YES, 2 NO
-DSEYNV53: Never had eye exam: 1 YES, 2 NO
-DSEYPR53: Has diabetes caused eye problems: 1 YES, 2 NO
-RACEX: Race: 1 White (no other reported), 2 Black (nor), 3 Amer Indian (nor), 4 Asian (nor), 5 Native hawaiian (nor), 6 Multiple races reported
-RACETHNX: Race/Ethnicity: 1 - Hispanic, 2 - Black/No other race/not hispanic, 3 - Asian/No other race/not hispanic, 4 - Other race/not hispanic
-HIDEGYR/HIDEG: Highest degree when first entered MIPS: 1 - No Degree, 2 - GED, 3 - High School Diploma, 4 - Bacehlor's Degree, 5 - MS, 6 - Doctorate, 7 - Other, 8 - Under 16, inapplicable
-CHOLCK53: How long since last cholesterol check? (only available 2000 - 2016).
+Clean data.
+Here's some relevant coding information: DSEYE53: 1 - 4 can be considered yes for eye exam, 5 is never.
+-1 Inapplicable, -8 DK (?), -9 Not ascertained (2001 only) DSEY0353: Eye exam in 2003: 1 YES, 2 NO DSEY0253: Eye exam in 2002: 1 YES, 2 NO DSEY0153: Eye exam in 2001: 1 YES, 2 NO DSEY0453: Eye exam in 2004: 1 YES, 2 NO DSEY0553: Eye exam in 2005: 1 YES, 2 NO DSEY0654: Eye exam in 2006: 1 YES, 2 NO DSEY0754: Eye exam in 2007: 1 YES, 2 NO DSEB0153: Eye exam before 2001: 1 YES, 2 NO DSEB0253: Eye exam before 2002: 1 YES, 2 NO DSEB0353: Eye exam before 2003: 1 YES, 2 NO DSEB0453: Eye exam before 2004, 1 YES, 2 NO DSEB0553: Eye exam before 2005, 1 YES, 2 NO DSEYNV53: Never had eye exam: 1 YES, 2 NO DSEYPR53: Has diabetes caused eye problems: 1 YES, 2 NO RACEX: Race: 1 White (no other reported), 2 Black (nor), 3 Amer Indian (nor), 4 Asian (nor), 5 Native hawaiian (nor), 6 Multiple races reported RACETHNX: Race/Ethnicity: 1 - Hispanic, 2 - Black/No other race/not hispanic, 3 - Asian/No other race/not hispanic, 4 - Other race/not hispanic HIDEGYR/HIDEG: Highest degree when first entered MIPS: 1 - No Degree, 2 - GED, 3 - High School Diploma, 4 - Bacehlor's Degree, 5 - MS, 6 - Doctorate, 7 - Other, 8 - Under 16, inapplicable CHOLCK53: How long since last cholesterol check?
+(only available 2000 - 2016).
 
 ```{r}
-# Three columns denote the DIAB diagnosis based on different years. I coalesce them
-# to create a single column, which we can then filter on.
-# Coding appears the same for all variables. 1 is diagnosed with diabetes, 2 is not. Other numbers
-# are variations on missing or non-response
-dat$DIABDX_all <- coalesce(dat$DIABDX53, dat$DIABDX_M18) # When using full data, add dat$DIABDX_M18,
+tar_load(diab_dat)
 
-# Variable to coallesce
-# HIDEGYR/HIDEG
-# POVCAT
-# DIABW variables
-dat <- dat %>%
-  mutate(
-    DSEY_all = coalesce(!!!select(., starts_with('DSEY'))),
-    HIDEG_all = coalesce(!!!select(., starts_with('HIDEG'))),
-    DIABW = coalesce(!!!select(., starts_with('DIABW'))),
-    POVCAT_all = coalesce(!!!select(., starts_with('POVCAT'))),
-    USBORN_all = coalesce(!!!select(., contains('BORN'))),
-    VARPSU_all = coalesce(!!!select(., starts_with('VARPSU'))),
-    VARSTR_all = coalesce(!!!select(., starts_with('VARSTR'))),
-    AGE_all = coalesce(!!!select(., starts_with('AGE'))),
-    RACE_all = coalesce(!!!select(., RACETHNX, RACETHX)),
-    CHOL_all = coalesce(!!!select(., CHOLCK53, starts_with('DSCH'))),
-    FLU_all = coalesce(!!!select(., FLUSHT53, starts_with('DSFL'))),
-    DENT_all = coalesce(!!!select(., DENTCK53, num_range('DVTOT', 17:20))),
-    FEET_all = coalesce(!!!select(., DSCKFT53, starts_with('DSFT'))),
-
-  ) %>% 
-  mutate(
-    AGE_all = as.factor(case_when(
-      AGE_all == -1 ~ NA_character_,
-      AGE_all < 18 & AGE_all > -1 ~ NA_character_,
-      AGE_all >= 18 & AGE_all <= 44 ~ '18 to 44',
-      AGE_all >= 45 & AGE_all <= 64 ~ '45 to 64',
-      AGE_all >= 65 & AGE_all <= 74 ~ '65 to 74',
-      AGE_all >= 75 ~ '75+',
-      TRUE ~ as.character(AGE_all)
-    ))
-  )
-# Get just data for people with diabetes
-# Get just the variables I want
-diab_dat <- dat %>% 
-  select(year, DUPERSID, SEX, DIABW, ends_with('_all'),
-         CHOLCK53, FLUSHT53, CHECK53, DENTCK53, DSA1C53, DSCKFT53)
+ggplot(dplyr::filter(sex_indicator, variable == 'eye-exam', value %in% c(
+    'Within last year',
+    '2 or more A1C tests in a year',
+    '1 or more foot examinations in a year',
+    'Once a year',
+    #Dental checkups
+    'YES'  ))) + geom_line(aes(x = year, y = proportion, group = SEX))
 
@@
 ```{r}
+library(survey)
 library(sitrep)
@@
 diab_list <- group_split(diab_dat, year)
+diab_all_svy <- diab_dat %>% 
+  as_survey_design(ids = VARPSU_all, weights = DIABW, strata = VARSTR_all, nest = TRUE)
 diab_svy <- diab_list[[17]] %>%
@@
 #test <-svytable(~CHOLCK53 + USBORN_all, design = diab_only, Ntotal = 100)
+
+tbl_svysummary(
+  diab_all_srvy,
+  by = year,
+  include = c(#CHOL_all,
+              # FLU_all,
+              # DENT_all,
+              DSA1C53
+              # DSEY_all,
+              # FEET_all
+              ),
+  statistic = list(all_categorical() ~ "{n}")
+)
+tbl_svysummary(diab_svy)
 
@@
     wide = FALSE,
+    statistic = list(DSEY_all ~ "{n}"),
     method = 'mean',
@@
 # Get the dashboard medians
+
 ```{r}
@@
 ```
+
+```{r}
+
+```

### 2022-11-29 _targets.R

@@ -9,11 +9,13 @@ library(future)
 library(future.callr)
 library(tarchetypes)
 # Set up future
-plan(callr)
+#plan(callr)
+options(clustermq.scheduler = 'multiprocess')
 
 # Set target options:
 tar_option_set(
-  packages = c("tidyverse", "haven", 'sitrep', 'gtsummary', 'srvyr'), # packages that your targets need to run
+  packages = c("tidyverse", "haven", 'sitrep', 'gtsummary', 'srvyr'),
+  # packages that your targets need to run
   format = "rds" # default storage format
   # Set other options as needed.
 )
@@ -24,80 +26,324 @@ tar_source('scripts/functions.R')
 
 # Replace the target list below with your own:
 list(
-  # tar_target(
-  #   name = grasp_form_data_input,
-  #   command = "//cdc.gov/locker/CCHP_NCCD_DDT_Data1/epistat/Surveillance/Surveillance and Trends Reporting System/GRASP/NEW_Jan2018/Datasets/consol_dat_2022_1014.sas7bdat",
-  #   format = 'file'
-  # ),
-  # tar_target(
-  #   name = grasp_form_data,
-  #   command = readGraspData(grasp_form_data_input),
-  #   format = 'feather'
-  # ),
+
   # Get MEPS files
   tar_target(
     name = dat_files,
-    command = list.files(path = 'data', pattern = 'meps', full.names = TRUE)
+    command = list.files(
+      path = 'data',
+      pattern = 'meps',
+      full.names = TRUE
+    )
   ),
-  tar_target(
-    dat_names,
-    map_chr(dat_files, ~str_extract(.x, 'meps[0-9]{4}'))
-  ),
+  tar_target(dat_names,
+             map_chr(
+               dat_files, ~ str_extract(.x, 'meps[0-9]{4}')
+             )),
   tar_target(
     dat_list,
-    map2(dat_files, dat_names, ~readAndSelect(.x, .y)) %>%
+    map2(dat_files, dat_names, ~ readAndSelect(.x, .y)) %>%
       setNames(dat_names)
   ),
-  tar_target(
-    dat,
-    bind_rows(dat_list, .id = 'year')
-  ),
+  tar_target(dat,
+             bind_rows(dat_list, .id = 'year')),
   # Clean data
-  tar_target(
-    cleaned_dat,
-    cleanMepsData(dat)
-  ),
-  tar_target(
-    combined_dat,
[…]

### 2022-11-29 scripts/functions.R

@@ -2,15 +2,6 @@
 library(tidyverse)
 library(haven)
 
-readGraspData <- function(filepath) {
-  if (file.exists(filepath)) {
-  haven::read_sas(filepath)
-  } else {
-    print('File not found')
-  }
-}
-
-
 # Read in data
 readAndSelect <- function(data_path, data_year) {
   yr <- substr(data_year, 7, 8)
@@ -50,7 +41,7 @@ readAndSelect <- function(data_path, data_year) {
            starts_with('VARSTR'), # Strata
            # starts_with('INSCOV'), # Insurance coverage variable
            starts_with('HIDEG'), # Highest degree - want only HIDEGYR and HIDEG
-           starts_with('HIDEG'), # Highest degree when first entered MEPS
+           starts_with('EDUYRDG'), #
            starts_with('TTLP'), # Total income
            starts_with('POVCAT'), # Categorical poverty status
            #starts_with('POVLEV'), # Continuous poverty status
@@ -73,6 +64,7 @@ readAndSelect <- function(data_path, data_year) {
            -contains('AGE31X'),
            -contains('AGE42X'),
            -contains('AGE53x'), # Remove some of the extra age variables
+           -contains('DSFLNV'), # Remove the never had flu shot
            starts_with('PERWT'), # Person weight level. Not sure I need this, since just working with DCS variables
            starts_with('INSCOP') # Inscope, again not sure if needed but putting here anyway for now
     )
@@ -94,7 +86,7 @@ cleanMepsData <- function(dat) {
         case_when(
           DSA1C53 == -1 ~ 'Inapplicable',
           DSA1C53 == -7 ~ 'Refused',
-          DSA1C53 == -8 ~ 'DK',
+          DSA1C53 == -8 ~ 'Do not know',
           DSA1C53 == -9 ~ 'Not ascertained',
           DSA1C53 == -15 ~ 'Cannot be computed',
           DSA1C53 %in% c(0, 1, 96) ~ 'Less than 2 or more A1C tests in a year',
@@ -105,12 +97,13 @@ cleanMepsData <- function(dat) {
 
       DSCKFT53 = as.factor(
         case_when(
-          DSCKFT53 >= 1 ~ 'Within last year',
-          DSCKFT53 == 0 ~ 'No foot examinations in a year',
+          DSCKFT53 >= 1 ~ 'YES',
+          DSCKFT53 == 0 ~ 'NO',
[…]

### 2022-12-16 scripts/00_eda.qmd
Age adjusted cumulative prevalence practices

@@
   as_survey_design(ids = VARPSU_all, weights = DIABW, strata = VARSTR_all, nest = TRUE)
-diab_svy <- diab_list[[17]] %>%
-  as_survey_design(ids = VARPSU_all, weights = DIABW, strata = VARSTR_all, nest = TRUE)
+diab_svy <- diab_list[[13]] %>%
+  as_survey_design(ids = VARPSU_all, weights = PERWT, strata = VARSTR_all, nest = TRUE)
 diab_only <- subset(diab_svy, DIABW != 0)
@@
     #DSA1C53,
-    DSEY_all,
+    RACE_all,
+    #DIABDX_all,
+    #DSEY_all,
     #FEET_all,
     pretty = FALSE,
-    strata = 'AGE_all',
+    #strata = 'AGE_all',
     wide = FALSE,
-    statistic = list(DSEY_all ~ "{n}"),
+    #statistic = list(DSEY_all ~ "{n}"),
     method = 'mean',
     #drop = c('Not ascertained', 'DK', 'Refused', 'Inapplicable'),
-    keep = c(
-      'Within last year',
-      '2 or more A1C tests in a year',
-      '1 or more foot examinations in a year',
-      'Once a year',
-      #Dental checkups
-      'YES' # eye exam
+    # keep = c(
+    #   'Within last year',
+    #   '2 or more A1C tests in a year',
+    #   '1 or more foot examinations in a year',
+    #   'Once a year',
+    #   #Dental checkups
+    #   'YES' # eye exam
+    # )
   )
+set.seed(123)
+test_table <- diab_dat %>% 
+  filter(year %in% 2008:2010) %>% 
+  filter(FLU_all %in% c('Within last year')) %>% 
+  mutate(FLU_all = fct_drop(FLU_all),
+         FLU_all = ifelse(FLU_all == 'Within last year', 'Flu vaccine within last year', FLU_all)) %>% 
+  as_survey_design(ids = VARPSU_all, weights = DIABW, strata = VARSTR_all, nest = TRUE) %>% 
+  select(FLU_all,
+         Race = RACE_all,
+         Education = HIDEG_all,
+         Gender = SEX,
+         Age = AGE_all,
+         Region = REGION_all,
+         Insurance = INSCOV_all,
+         Poverty = POVCAT_all,
+         year) %>%
+  select(order(colnames(.))) %>% 
+  tbl_strata(
+    strata = c(year),
+    ~.x %>%  
+      select(-year) %>% 
+      tbl_svysummary(by = FLU_all,
+                     statistic = list(all_categorical() ~ '{p}%'))
+  ) %>% 
+  modify_header(label = "**Flu vaccine within last year**",
+                all_stat_cols() ~ "")
+
+test_table2 <- diab_dat %>% 
+  #filter(year %in% 2008:2011) %>% 
+  filter(DSA1C53 %in% c('2 or more A1C tests in a year')) %>% 
+  mutate(DSA1C53 = fct_drop(DSA1C53)) %>% 
+  as_survey_design(ids = VARPSU_all, weights = DIABW, strata = VARSTR_all, nest = TRUE) %>% 
+  select(DSA1C53,
+         Race = RACE_all,
+         Education = HIDEG_all,
+         Gender = SEX,
+         Age = AGE_all,
+         Region = REGION_all,
+         Insurance = INSCOV_all,
+         Poverty = POVCAT_all,
+         year) %>%
+  select(order(colnames(.))) %>% 
+  tbl_svysummary(
+    by = DSA1C53
   )
+
+  tbl_strata(
+    strata = c(year),
+    ~.x %>%  
+      select(-year) %>% 
+      tbl_svysummary(by = DSA1C53,
+                     statistic = list(all_categorical() ~ '{p}%'))
+  ) %>% 
+  modify_header(label = "**2 or more A1C tests in a year**",
+                all_stat_cols() ~ "")
+
 ```
@@
 ```{r}
+tar_load(contains('focus'))
+dats <- list(overall = overall_focus, edu = edu_focus, race = race_focus, sex = sex_focus, age = age_focus)
+test <- bind_rows(dats, .id = 'stratifying_variable')
+test2 <- test %>%
+  filter(variable != 'DENT_all') %>% 
+  mutate(strata = as.character(coalesce(HIDEG_all, RACE_all, SEX, AGE_all))) %>%
+  select(-HIDEG_all,-RACE_all,-SEX,-AGE_all) %>%
+  mutate(strata = case_when(is.na(strata) ~ 'Overall',
+                            TRUE ~ strata))
 
+test3 <-  test2 %>%
+  filter(value %in% c(c(
+                      'Within last year',
+                      '2 or more A1C tests in a year',
+                      '1 or more foot examinations in a year',
+                      'Once a year',
+                      'YES'
+                    ))) %>% 
+  filter(strata != 'Total') %>%
+  filter(strata != 'Not available') %>% 
+  group_split(stratifying_variable) 
+plots <- test3 %>% 
+   map(
+    ~ ggplot(.x, aes(
+      x = year,
+      y = proportion * 100,
+      group = strata,
+      color = strata
+    )) +
+      geom_line() +
+      facet_wrap( ~ variable, ncol = 5) +
+      theme_classic() +
+      scale_y_continuous(
+        limits = c(25, 100),
+        breaks = seq(25, 100, 25),
+        labels = seq(25, 100, 25)
+      ) +
+      scale_x_continuous(
+        limits = c(2008, 2020),
+        breaks = seq(2008, 2020, 2),
+        labels = seq(2008, 2020, 2)
+      ) +
+      theme(axis.text = element_text(color = 'black'),
+            axis.text.x = element_text(angle = 45, hjust = 0.9, vjust = 0.95)) +
+      labs(x = 'Year', y = 'Percentage')
+  )
+plots[[1]] <- plots[[1]] + labs(color = 'Age (grouped)')
+plots[[2]] <- plots[[2]] + labs(color = 'Highest degree \nobtained')
+plots[[3]] <- plots[[3]] + labs(color = "")
+plots[[4]] <- plots[[4]] + labs(color = 'Race/Ethnicity')
+plots[[5]] <- plots[[5]] + labs(color = 'Gender')
+plots <- list(
+  plots[[3]],
+  plots[[1]],
+  plots[[2]],
+  plots[[4]],
+  plots[[5]]
+)
+plots %>% 
+  wrap_plots(nrow = 5)
 ```

### 2022-12-16 scripts/manuscript/manuscript_draft.qmd
Age adjusted cumulative prevalence practices

---
title: "Trends in Preventive Care Practices among US Adults with Diabetes, 2008-2020 "
format: docx
editor: visual
bibliography: references.bib
csl: ama.csl
---
```{r}
library(gtsummary)
library(tidyverse)
library(patchwork)
library(targets)
library(gt)

```

**Trends in Preventive Care Practices among US Adults with Diabetes, 2008-2020**

Jacob T. Wittman, PhD
Kai M. Bullard
Stephen R. Benoit

CDC Affiliation

\pagebreak

# Abstract

\pagebreak

# Introduction

- Diabetes affects a lot of people
  - Kills people, makes them sick, reduces quality of life
  - Cost of management is high and increasing
- Advances in diabetes management
  - Patients with diabetes must actually receive this care
- Present trends in self-reported receipt of preventive care practices according to MEPS from 2008 - 2020.

Diabetes is a chronic disease that affects XX people in the USA.

# Methods

## Data Source

We used data from the Medical Expenditure Panel Survey (MEPS) from years 2008 - 2020. Participants in this survey are a subsample of households that participate in the National Health Interview Survey (NHIS). The MEP survey targets the civilian noninstitutionalized population in the US and provides national and regional estimates of health care use, expenditures, sources of payment and health insurance coverage. This survey also contains information on patient demographics, socioeconomics, and via the Diabetes Care Survey (DCS), information on diabetes preventive care practices. The DCS is a self-administered paper-and-pencil questionnaire that is provided to MEPS respondents who indicate that they have been told by a doctor or health professional that they have diabetes.

The data we used comes from the full-year consolidated file from MEPS for the 12 year time span. Our analysis is adjusted for the complex survey design

# Results

# Discussion

# References

::: {#refs}
:::

# Tables
```{r}
# tar_load(age_adjusted_stats)
# age_adjusted_stats %>% 
#   #filter(stratifier != 'age') %>% 
#   mutate(age_adjusted_prop = age_adjusted_prop * 100) %>% 
#   pivot_wider(
#     id_cols = c(stratifier, variable, var_label, strata),
#     names_from = year,
#     values_from = age_adjusted_prop
#   ) %>% 
#   group_by(stratifier, strata) %>%
#   select(stratifier, var_label, `2008`:`2020`) %>%
#   gt() %>% 
#   fmt_number(columns = `2008`:`2020`, decimals = 1) %>% 
#   gtsave('table_one.docx')
```

```{r}
tar_load(age_adjusted_preventive)
age_adjusted_preventive %>% 
  filter(label == 'Three preventive practices followed') %>% 
  mutate(age_adjusted_prop = age_adjusted_prop * 100) %>% 
  pivot_wider(
    id_cols = c(stratifier, variable, label, strata),
    names_from = year,
    values_from = age_adjusted_prop
  ) %>% 
  group_by(stratifier, strata) %>%
  select(stratifier, label, `2008`:`2020`) %>%
  gt() %>% 
  fmt_number(columns = `2008`:`2020`, decimals = 1) %>% 
  gtsave('preventive_practices.docx')
```

# Figures

```{r}
tar_load(age_adjusted_stats)

stats_table_plot_dat <- age_adjusted_stats %>% 
  filter(strata != 'Total') %>%
  filter(strata != 'Not available') %>% 
  filter(strata != 'Other Race/Not Hispanic') %>% 
  mutate(variable_text = case_when(variable == 'a1c' ~ '2 or more A1C tests',
                                   variable == 'CHOL_all' ~ 'Cholesterol tested',
                                   variable == 'DENT_all' ~ '1 or more dentist visits',
                                   variable == 'eye-exam' ~ 'Eye exam with dilation',
                                   variable == 'flu' ~ 'Received flu vaccine',
                                   variable == 'foot' ~ 'Foot examination'),
         strata = case_when(strata == 'stat_0' ~ 'Overall',
                            TRUE ~ strata)) %>% 
  mutate(strata = as.factor(strata)) %>% 
  split(., f = .$stratifier)

stats_table_plot_dat <- map(stats_table_plot_dat, function(.x) {
  .x %>% 
    mutate(strata = fct_drop(strata))
})

overall_data <- stats_table_plot_dat$overall
# Remove the overall data from the list
stats_table_plot_dat <- stats_table_plot_dat[-4]
# Relevel the poverty factors
stats_table_plot_dat$poverty$strata <- factor(stats_table_plot_dat$poverty$strata, levels = c('High income', 'Middle income', 'Low income', 'Poor/Negative'))
test_plots <- stats_table_plot_dat %>% 
   map(
    ~ ggplot(filter(.x, variable %in% c('a1c', 'CHOL_all', 'flu')),
             aes(
      x = year,
      y = age_adjusted_prop * 100,
      group = strata,
      color = strata
    )) +
      #geom_point() +
      geom_smooth( se = FALSE) +
      geom_smooth(data = filter(overall_data, variable %in% c('a1c', 'CHOL_all', 'flu')),
                  aes(x = year, y = age_adjusted_prop * 100),
                  color = 'black',
                  se = FALSE,
                  linetype = 'dashed') +
      facet_wrap( ~ variable_text, ncol = 3) +
      theme_classic() +
      scale_y_continuous(
        limits = c(00, 100),
        breaks = seq(0, 100, 25),
        labels = seq(0, 100, 25)
      ) +
      scale_x_continuous(
        limits = c(2008, 2020),
        breaks = seq(2008, 2020, 2),
        labels = seq(2008, 2020, 2)
      ) +
      scale_color_brewer(type = 'qual', palette = 'Set2') +
      theme(axis.text = element_text(color = 'black'),
            axis.text.x = element_text(angle = 45, hjust = 0.9, vjust = 0.95)) +
      labs(x = 'Year', y = 'Percentage')
  )

test_plots[[1]] <- test_plots[[1]] + labs(color = 'Age (grouped)') 
test_plots[[2]] <- test_plots[[2]] + labs(color = 'Highest degree \nobtained') + theme(strip.background =  element_blank(),
                                                                          strip.text = element_blank())
test_plots[[3]] <- test_plots[[3]] + labs(color = "Insurance") + theme(strip.background =  element_blank(),
                                                                            strip.text = element_blank())
test_plots[[4]] <- test_plots[[4]] + labs(color = 'Poverty') + theme(strip.background =  element_blank(),
                                                                            strip.text = element_blank())
test_plots[[5]] <- test_plots[[5]] + labs(color = 'Race/Ethnicity') + theme(strip.background =  element_blank(),
                                                                             strip.text = element_blank())
test_plots[[6]] <- test_plots[[6]] + labs(color = 'Sex') + theme(strip.background =  element_blank(),
                                                                          strip.text = element_blank())
test_plots <- list(
  test_plots[[1]],
  test_plots[[6]],
  test_plots[[5]],
  test_plots[[2]],
  test_plots[[3]],
  test_plots[[4]]
)

exam_plots <- stats_table_plot_dat %>% 
   map(
    ~ ggplot(filter(.x, variable %!in% c('a1c', 'CHOL_all', 'flu')),
             aes(
      x = year,
      y = age_adjusted_prop * 100,
      group = strata,
      color = strata
    )) +
      #geom_point() +
      geom_smooth(se = FALSE) +
      geom_smooth(data = filter(overall_data, variable %!in% c('a1c', 'CHOL_all', 'flu')),
                  aes(x = year, y = age_adjusted_prop * 100),
                  color = 'black',
                  se = FALSE,
                  linetype = 'dashed') +
      facet_wrap( ~ variable_text, ncol = 3) +
      theme_classic() +
      scale_y_continuous(
        limits = c(  0, 100),
        breaks = seq(0, 100, 25),
        labels = seq(0, 100, 25)
      ) +
      scale_x_continuous(
        limits = c(2008, 2020),
        breaks = seq(2008, 2020, 2),
        labels = seq(2008, 2020, 2)
      ) +
      scale_color_brewer(type = 'qual', palette = 'Set2') +
      theme(axis.text = element_text(color = 'black'),
            axis.text.x = element_text(angle = 45, hjust = 0.9, vjust = 0.95)) +
      labs(x = 'Year', y = 'Percentage')
  )

exam_plots[[1]] <- exam_plots[[1]] + labs(color = 'Age (grouped)')
exam_plots[[2]] <- exam_plots[[2]] + labs(color = 'Highest degree \nobtained') + theme(strip.background =  element_blank(),
                                                                          strip.text = element_blank())
exam_plots[[3]] <- exam_plots[[3]] + labs(color = "Insurance") + theme(strip.background =  element_blank(),
                                                                            strip.text = element_blank())
exam_plots[[4]] <- exam_plots[[4]] + labs(color = 'Poverty') + theme(strip.background =  element_blank(),
                                                                            strip.text = element_blank())
exam_plots[[5]] <- exam_plots[[5]] + labs(color = 'Race/Ethnicity') + theme(strip.background =  element_blank(),
                                                                             strip.text = element_blank())
exam_plots[[6]] <- exam_plots[[6]] + labs(color = 'Sex') + theme(strip.background =  element_blank(),
                                                                          strip.text = element_blank())
exam_plots <- list(
  exam_plots[[1]],
  exam_plots[[6]],
  exam_plots[[5]],
  exam_plots[[2]],
  exam_plots[[3]],
  exam_plots[[4]]
)
(all_exam_plots <- exam_plots %>% 
  wrap_plots(nrow = 6) &
  theme(plot.margin = margin(0.5, 0.5, 0.5, 0.5, 'pt')))
(all_test_plots <- test_plots %>% 
  wrap_plots(nrow = 6) &
  theme(plot.margin = margin(0.5, 0.5, 0.5, 0.5, 'pt')))
ggsave(plot = all_exam_plots,
       filename = 'figures/all_exam_plots.tiff',
       dpi = 200)
ggsave(plot = all_test_plots,
       filename = 'figures/all_test_plots.tiff',
       dpi = 200)
```

### 2022-12-16 _targets.R

@@ -14,7 +14,7 @@ options(clustermq.scheduler = 'multiprocess')
 
 # Set target options:
 tar_option_set(
-  packages = c("tidyverse", "haven", 'sitrep', 'gtsummary', 'srvyr'),
+  packages = c("tidyverse", "haven", 'sitrep', 'gtsummary', 'srvyr', 'dtplyr'),
   # packages that your targets need to run
   format = "rds" # default storage format
   # Set other options as needed.
@@ -26,6 +26,9 @@ tar_source('scripts/functions.R')
 
 # Replace the target list below with your own:
 list(
+
+# Set up data -------------------------------------------------------------
+
 
   # Get MEPS files
   tar_target(
@@ -46,17 +49,21 @@ list(
       setNames(dat_names)
   ),
   tar_target(dat,
-             bind_rows(dat_list, .id = 'year')),
+             bind_rows(dat_list, .id = 'year'),
+             format = 'parquet'),
   # Clean data
   tar_target(cleaned_dat,
-             cleanMepsData(dat)),
+             cleanMepsData(dat),
+             format = 'parquet'),
   tar_target(combined_dat,
-             coalesceData(cleaned_dat)),
+             coalesceData(cleaned_dat),
+             format = 'parquet'),
   tar_target(releveled_dat,
-             relevelFactors(combined_dat)),
+             relevelFactors(combined_dat),
+             format = 'parquet'),
   # Get down to just the columns we want
   tar_target(
-    diab_dat,
+    diab_dat_sub,
     select(
       releveled_dat,
       year,
@@ -67,16 +74,26 @@ list(
       CHOLCK53,
       FLUSHT53,
       CHECK53,
-      DENTCK53,
       DSA1C53,
-      DSCKFT53
+      DSCKFT53,
+      PERWT,
     ) %>%
-      mutate(year = str_extract(year, '[0-9]{4}'))
+      mutate(year = as.numeric(str_extract(year, '[0-9]{4}'))) %>%
+      filter(year >= 2008),
+    format = 'parquet'
+  ),
+  tar_target(
+    diab_dat,
+    cumulativePractices(diab_dat_sub)
   ),
   tar_target(diab_list,
              diab_dat %>% group_split(year),
              iteration = 'list'),
-  tar_target(years, as.list(2001:2020)),
+  tar_target(years, as.list(2008:2020)),
+
[…]

### 2022-12-16 scripts/functions.R

@@ -1,6 +1,7 @@
 
 library(tidyverse)
 library(haven)
+`%!in%` <- Negate(`%in%`)
 
 # Read in data
 readAndSelect <- function(data_path, data_year) {
@@ -29,23 +30,22 @@ readAndSelect <- function(data_path, data_year) {
   }
 
   temp %>%
+    lazy_dt() %>%
     mutate(across(starts_with('RACE'), ~as.factor(.x))) %>%
     select(starts_with('DOB'),
            starts_with('DUPERSID'),
-           starts_with('USBORN'),
-           starts_with('BORN'), # Two different born in USA variables used in different years
            starts_with('AGE'),
            starts_with('RACE'),
            starts_with('SEX'),
            starts_with('VARPSU'), # PSU
            starts_with('VARSTR'), # Strata
-           # starts_with('INSCOV'), # Insurance coverage variable
+           starts_with('INSCOV'), # Insurance coverage variable
            starts_with('HIDEG'), # Highest degree - want only HIDEGYR and HIDEG
            starts_with('EDUYRDG'), #
            starts_with('TTLP'), # Total income
            starts_with('POVCAT'), # Categorical poverty status
            #starts_with('POVLEV'), # Continuous poverty status
-           #starts_with('REGION'),
+           starts_with('REGION'),
            starts_with('DENTCK53'), # Dental checkup, only 2000 - 2016,
            matches('DVTOT[0-9]{2}'), # # of dental care visits in YYYY
            starts_with('CHOLCK'), # Cholesterol check, only 2000 - 2016,
@@ -60,14 +60,20 @@ readAndSelect <- function(data_path, data_year) {
            starts_with('DSEYE53'), # Have to get the 2001 eye check variable too
            starts_with('DSA1'), # A1C test,
            starts_with('DSCKFT'), # Feet check, only 2001 - 2007
+           starts_with('DSDIA'), # Diagnosed with diabetes by a physician
+           starts_with('DIABDX'), # Diabetes diagnosis
            -starts_with('DSEB'), # Remove the eye test in year before columns
            -contains('AGE31X'),
            -contains('AGE42X'),
            -contains('AGE53x'), # Remove some of the extra age variables
[…]

### 2022-12-22 scripts/manuscript/manuscript_draft.qmd
Transitioning to server

@@
 library(gt)
+
+`%!in%` <- Negate(`%in%`)
 
@@
 
-The data we used comes from the full-year consolidated file from MEPS for the 12 year time span. Our analysis is adjusted for the complex survey design
+The data we used comes from the full-year consolidated file from MEPS for the 12 year time span. Our analysis is adjusted for the complex survey design, including clustering and stratification.
 
@@
 tar_load(age_adjusted_preventive)
-age_adjusted_preventive %>% 
-  filter(label == 'Three preventive practices followed') %>% 
+preventive_practice_table <- age_adjusted_preventive %>% 
+  filter(label == 'At least three preventive practices followed') %>% 
   mutate(age_adjusted_prop = age_adjusted_prop * 100) %>% 
@@
   ) %>% 
-  group_by(stratifier, strata) %>%
-  select(stratifier, label, `2008`:`2020`) %>%
+  filter(strata %!in% c('Not available', 'Other Race/Not Hispanic')) %>% 
+  mutate(stratifier = factor(stratifier,
+                             c('overall', 'age', 'sex', 'race', 'edu', 'insurance', 'poverty')),
+         strata = case_when(strata == 'stat_0' ~ '-', 
+                            strata == 'Greater than HS' ~ 'Greater than high school',
+                            TRUE ~ strata)) %>% 
+  mutate(strata = as.factor(strata)) %>% 
+  mutate(stratifier = recode_factor(
+    stratifier,
+    overall = 'Overall',
+    age = 'Age',
+    sex = 'Sex',
+    race = 'Race/Ethnicity',
+    edu = 'Highest degree earned',
+    insurance = 'Insurance coverage',
+    poverty = 'Poverty level'
+  )) %>% 
+  group_by(stratifier) %>%
+  select(stratifier, strata, `2008`:`2020`) %>%
   gt() %>% 
-  fmt_number(columns = `2008`:`2020`, decimals = 1) %>% 
+  fmt_number(columns = `2008`:`2020`, decimals = 1)
+preventive_practice_table$`_data` <- preventive_practice_table$`_data`[c(1:18, 20, 19, 21), ]
+preventive_practice_table %>% 
+  gtsave('preventive_practices.docx')
+```
+
+```{r}
+
+preventive_practice_table <- age_adjusted_preventive %>% 
+  filter(label == 'At least three preventive practices followed') %>% 
+  mutate(age_adjusted_prop = age_adjusted_prop * 100) %>% 
+  pivot_wider(
+    id_cols = c(stratifier, variable, label, strata),
+    names_from = year,
+    values_from = age_adjusted_prop
+  ) %>% 
+  filter(strata %!in% c('Not available', 'Other Race/Not Hispanic')) %>% 
+  mutate(stratifier = factor(stratifier,
+                             c('overall', 'age', 'sex', 'race', 'edu', 'insurance', 'poverty')),
+         strata = case_when(strata == 'stat_0' ~ '-', 
+                            strata == 'Greater than HS' ~ 'Greater than high school',
+                            TRUE ~ strata)) %>% 
+  mutate(strata = as.factor(strata)) %>% 
+  mutate(stratifier = recode_factor(
+    stratifier,
+    overall = 'Overall',
+    age = 'Age',
+    sex = 'Sex',
+    race = 'Race/Ethnicity',
+    edu = 'Highest degree earned',
+    insurance = 'Insurance coverage',
+    poverty = 'Poverty level'
+  )) %>% 
+  group_by(stratifier) %>%
+  select(stratifier, strata, `2008`:`2020`) %>%
+  gt() %>% 
+  fmt_number(columns = `2008`:`2020`, decimals = 1)
+preventive_practice_table$`_data` <- preventive_practice_table$`_data`[c(1:18, 20, 19, 21), ]
+preventive_practice_table %>% 
   gtsave('preventive_practices.docx')

### 2022-12-22 scripts/functions.R

@@ -1009,34 +1009,34 @@ preventivePracticebyAge <- function(survey.object, by = NULL, data) {
         by = by,
         digits = list(everything() ~ 12),
         include = c(
-          #zero_practices,
-          #one_practices,
-          #two_practices,
+          zero_practices,
+          one_practices,
+          two_practices,
           three_practices,
-          #four_practices,
-          #five_practices,
-          #six_practices,
-          #atleast_one_practices,
-          #atleast_two_practices,
-          atleast_three_practices
-          #atleast_four_practices,
-          #atleast_five_practices,
-          #atleast_six_practices
+          four_practices,
+          five_practices,
+          six_practices,
+          atleast_one_practices,
+          atleast_two_practices,
+          atleast_three_practices,
+          atleast_four_practices,
+          atleast_five_practices,
+          atleast_six_practices
         ),
         label = list(
-          #zero_practices ~ "No preventive practices followed",
-          #one_practices ~ "One preventive practice followed",
-          #two_practices ~ "Two preventive practices followed",
+          zero_practices ~ "No preventive practices followed",
+          one_practices ~ "One preventive practice followed",
+          two_practices ~ "Two preventive practices followed",
           three_practices ~ "Three preventive practices followed",
-          #four_practices ~ "Four preventive practices followed",
-          #five_practices ~ "Five preventive practices followed",
-          #six_practices ~ "Six preventive practices followed",
-          #atleast_one_practices ~ "At least one preventive practice followed",
-          #atleast_two_practices ~ "At least two preventive practices followed",
-          atleast_three_practices ~ "At least three preventive practices followed"
-          #atleast_four_practices ~ "At least four preventive practices followed",
-          #atleast_five_practices ~ "At least five preventive practices followed",
-          #atleast_six_practices ~ "At least six preventive practices followed"
+          four_practices ~ "Four preventive practices followed",
+          five_practices ~ "Five preventive practices followed",
+          six_practices ~ "Six preventive practices followed",
+          atleast_one_practices ~ "At least one preventive practice followed",
+          atleast_two_practices ~ "At least two preventive practices followed",
+          atleast_three_practices ~ "At least three preventive practices followed",
+          atleast_four_practices ~ "At least four preventive practices followed",
+          atleast_five_practices ~ "At least five preventive practices followed",
[…]

### 2022-12-27 _targets.R
few ms changes

@@ -19,6 +19,10 @@ tar_option_set(
   format = "rds" # default storage format
   # Set other options as needed.
 )
+# tar_make_future_config:
+library(future)
+library(future.callr)
+plan(callr)
 
 # Run the R scripts in the R/ folder with your custom functions:
 tar_source('scripts/functions.R')

### 2022-12-27 _targets.R
SE for age adjusted rates

@@ -14,7 +14,8 @@ options(clustermq.scheduler = 'multiprocess')
 
 # Set target options:
 tar_option_set(
-  packages = c("tidyverse", "haven", 'sitrep', 'gtsummary', 'srvyr', 'dtplyr'),
+  packages = c("tidyverse", "haven", 'sitrep', 'gtsummary', 'srvyr', 'dtplyr',
+               'nih.joinpoint'),
   # packages that your targets need to run
   format = "rds" # default storage format
   # Set other options as needed.
@@ -767,6 +768,47 @@ list(
     ) %>%
       mutate(age_adjusted_prop = case_when(stratifier == 'age' ~ p / 100,
                                            TRUE ~ age_adjusted_prop))
+  ),
+
+# Joinpoint analysis ------------------------------------------------------
+
+  tar_target(
+    joinpoint_regressions_proportions,
+    age_adjusted_stats %>%
+      filter(strata != 'Total') %>%
+      filter(strata != 'Not available') %>%
+      filter(strata != 'Other Race/Not Hispanic') %>%
+      mutate(variable_text = case_when(variable == 'a1c' ~ '2 or more A1C tests',
+                                       variable == 'CHOL_all' ~ 'Cholesterol tested',
+                                       variable == 'DENT_all' ~ '1 or more dentist visits',
+                                       variable == 'eye-exam' ~ 'Eye exam with dilation',
+                                       variable == 'flu' ~ 'Received flu vaccine',
+                                       variable == 'foot' ~ 'Foot examination'),
+             strata = case_when(strata == 'stat_0' ~ 'Overall',
+                                TRUE ~ strata)) %>%
+      mutate(strata = as.factor(strata),
+             year_adj = year - 2007) %>%
+      split(., f = ~.$stratifier + .$variable) %>%
+      map(., ~joinPointRegression(.x))
+  ),
+  tar_target(
+    joinpoint_regressions_preventive,
+    age_adjusted_preventive %>%
+      filter(strata != 'Total') %>%
+      filter(strata != 'Not available') %>%
+      filter(strata != 'Other Race/Not Hispanic') %>%
+      mutate(variable_text = case_when(variable == 'a1c' ~ '2 or more A1C tests',
+                                       variable == 'CHOL_all' ~ 'Cholesterol tested',
+                                       variable == 'DENT_all' ~ '1 or more dentist visits',
+                                       variable == 'eye-exam' ~ 'Eye exam with dilation',
[…]

### 2022-12-27 joinpoint_test.R

@@ -1,0 +1,62 @@
+library(tidyverse)
+library(nih.joinpoint)
+library(targets)
+
+nih_sample_data %>% group_by(sex) %>% slice(1, 2, n()-1, n()) #first 2 and last 2 of each group
+
+
+ggplot(nih_sample_data, aes(x=year, y=rate, color=sex)) + geom_point() + geom_line()
+
+run_opt = run_options(model="ln", max_joinpoints=4, n_cores=3)
+export_opt = export_options()
+
+jp = joinpoint(nih_sample_data, x=year, y=rate, by=sex, se=se,
+               run_opts=run_opt, export_opts=export_opt, dir = 'temp')
+names(jp)
+
+tar_load(age_adjusted_stats)
+
+
+stats_table_plot_dat <- age_adjusted_stats %>%
+  filter(strata != 'Total') %>%
+  filter(strata != 'Not available') %>%
+  filter(strata != 'Other Race/Not Hispanic') %>%
+  mutate(variable_text = case_when(variable == 'a1c' ~ '2 or more A1C tests',
+                                   variable == 'CHOL_all' ~ 'Cholesterol tested',
+                                   variable == 'DENT_all' ~ '1 or more dentist visits',
+                                   variable == 'eye-exam' ~ 'Eye exam with dilation',
+                                   variable == 'flu' ~ 'Received flu vaccine',
+                                   variable == 'foot' ~ 'Foot examination'),
+         strata = case_when(strata == 'stat_0' ~ 'Overall',
+                            TRUE ~ strata)) %>%
+  mutate(strata = as.factor(strata),
+         p_100 = p / 100,
+         year_adj = year - 2007) %>%
+  split(., f = ~.$stratifier + .$variable)
+
+run_opt = run_options(
+  model = "ln",
+  min_joinpoints = 0,
+  max_joinpoints = 3,
+  n_cores = 3,
+  # min_obs_end = 1,
+  # min_obs_between = 1,
+  het_error = 'constant variance',
+  dependent_variable_type = 'proportion'
+)
+export_opt = export_options()
+jp2 = joinpoint(
+  stats_table_plot_dat$insurance.CHOL_all,
+  x = year,
+  y = p,
+  by = strata,
+  verbose = F,
+  run_opts = run_opt,
+  export_opts = export_opt,
+  se = NULL,
+  dir = 'temp'
+)
+jp2
+jp2$apc
+summary(jp2)
+jp_plot(jp2)

### 2022-12-27 scripts/functions.R

@@ -858,9 +858,20 @@ ageAdjustTables <- function(data) {
                            age_prop = c(0.530535, 0.299194, 0.088967, 0.081304))
   data %>%
     left_join(age_prop_table, by = 'age') %>%
-    mutate(age_adjusted_prop = (p / 100) * age_prop) %>%
+    mutate(age_adjusted_prop = (p / 100) * age_prop,
+           age_adjusted_perc = age_adjusted_prop * 100,
+           count_div_pop_sq = n / (N^2),
+           age_prop_sq = age_prop ^ 2,
+           age_perc_sq = (age_prop * 100) ^2
+           ) %>%
     group_by(variable, label, strata, year) %>%
-    summarise(age_adjusted_prop = sum(age_adjusted_prop, na.rm = TRUE))
+    mutate(sum_age_prop_sq = sum(age_prop_sq),
+           sum_age_perc_sq = sum(age_perc_sq)
+           ) %>%
+    summarise(age_adjusted_prop = sum(age_adjusted_prop, na.rm = TRUE),
+              age_adjusted_perc = sum(age_adjusted_perc, na.rm = TRUE),
+              age_adjusted_se = sum(age_prop_sq * count_div_pop_sq, na.rm = TRUE)^0.5,
+              age_adjusted_se_perc = sum(age_perc_sq * count_div_pop_sq, na.rm = TRUE) ^ 0.5)
 }
 
 # Need to join the estimates from tbl_svysummary to the rest of the
@@ -1126,4 +1137,28 @@ makePreventiveTablesLongerbyAge2 <- function(table) {
     separate(parameters, into = col_names, sep = "-") %>%
     mutate(across(n:p_unweighted, ~as.numeric(gsub(",", "", .x))))
 
+}
+
+joinPointRegression <- function(data) {
+
+  run_opt <- run_options(
+    model = "ln",
+    min_joinpoints = 0,
+    max_joinpoints = 3,
+    n_cores = 1,
+    het_error = 'constant variance',
+    dependent_variable_type = 'proportion'
+  )
+  export_opt <- export_options()
+  jp <- joinpoint(
+    data,
+    x = year,
+    y = age_adjusted_prop,
+    by = strata,
+    verbose = F,
+    run_opts = run_opt,
+    export_opts = export_opt,
+    se = NULL
+  )
+  return(jp)
 }

### 2022-12-27 scripts/manuscript/manuscript_draft.qmd
SE for age adjusted rates

@@
 ---
+
 ```{r}
@@
 
-Jacob T. Wittman, PhD
-Kai M. Bullard
-Stephen R. Benoit
+Jacob T. Wittman, PhD Kai M. Bullard Stephen R. Benoit
 
@@
 The MEP survey targets the civilian noninstitutionalized population in the US and provides national and regional estimates of health care use, expenditures, sources of payment and health insurance coverage.
-This survey also contains information on patient demographics, socioeconomics, and via the Diabetes Care Survey (DCS), information on diabetes preventive care practices.
+This survey also contains information on patient demographics, socioeconomics, and, via the Diabetes Care Survey (DCS), information on diabetes preventive care practices.
 The DCS is a self-administered paper-and-pencil questionnaire that is provided to MEPS respondents who indicate that they have been told by a doctor or health professional that they have diabetes.
 
-The data we used comes from the full-year consolidated file from MEPS for the 12 year time span. Our analysis is adjusted for the complex survey design, including clustering and stratification.
+The data we used comes from the full-year consolidated file from MEPS for the 12 year time span of our report.
+We used a weighted population of XXX in this analysis.
+Our analysis is adjusted for the complex survey design, including clustering and stratification.
+Reported values for the proportions of different groups receiving recommended preventive care practices are age-adjusted.
 
@@
 # Tables
+
 ```{r}

### 2022-12-28 scripts/manuscript/manuscript_draft.qmd
Updated preventive table with SE, apc, and aapc

@@
 `%!in%` <- Negate(`%in%`)
+sigfig <- function(number, digits) {
+
+   formatC(signif(number, digits = digits), digits = digits, format = "fg", flag = "#")
+
+}
 
@@
 ```{r}
+# Clean up the AAPC table and get it into format for printing to table
+cleaned_jp_aapc <- jp_prevention_aapc %>% 
+  select(-aapc_index) %>% 
+  mutate(across(starts_with('aapc'),
+                ~sigfig(.x, digits = 2)),
+         across(starts_with('aapc'),
+                ~case_when(.x == ' NA' ~ NA_character_,
+                           TRUE ~ .x)), 
+         AAPC = case_when(!is.na(aapc) ~ glue::glue('{aapc} ({aapc_c_i_low}, {aapc_c_i_high})'),
+                          TRUE ~ NA_character_)) %>%
+  select(stratifier, strata, AAPC)
 
-preventive_practice_table <- age_adjusted_preventive %>% 
+# Format APC table for future joining
+cleaned_jp_apc <- jp_prevention_apc %>% 
+  # No model has more than a single joinpoint, so make wider and then
+  # remove the excess columns to determine if there's no join point (segmend_end = 2020)
+  # or a joinpoint (segment_end != 2020)
+  pivot_wider(id_cols = c(stratifier, strata, model),
+              names_from = segment,
+              values_from = c(segment_start, segment_end, apc, p_value, apc_significant,
+                              apc_95_lcl, apc_95_ucl)
+  ) %>% 
+  select(-segment_start_0, -segment_start_1, -segment_end_1) %>% 
+  # Make segment empty if no joinpoint
+  mutate(segment = case_when(segment_end_0 == 2020 ~ NA_integer_,
+                             TRUE ~ segment_end_0)) %>% 
+  # MAke apc empty if not significant
+  mutate(across(c(apc_0, apc_95_lcl_0, apc_95_ucl_0),
+                ~ case_when(p_value_0 > 0.05 & p_value_1 > 0.05 ~ NA_real_,
+                            TRUE ~ .x)), 
+         across(c(apc_1, apc_95_lcl_1, apc_95_ucl_1),
+                ~ case_when(p_value_0 > 0.05 & p_value_1 > 0.05 ~ NA_real_,
+                            TRUE ~ .x)),
+         across(starts_with('apc') | starts_with('p_'),
+                ~sigfig(.x, digits = 2)),
+         across(starts_with('apc') | starts_with('p_'),
+                ~case_when(.x == ' NA' ~ NA_character_,
+                           TRUE ~ .x))) %>% 
+  # Concatenate apc column with CI columns
+  mutate(`APC Period 1` = case_when(
+       !is.na(apc_0) ~ glue::glue('{apc_0} ({apc_95_lcl_0}, {apc_95_ucl_0})'),
+       TRUE ~ NA_character_
+                                    ),
+    `APC Period 2` = case_when(
+       !is.na(apc_1) ~ glue::glue('{apc_1} ({apc_95_lcl_1}, {apc_95_ucl_1})'),
+       TRUE ~ NA_character_
+    )
+  ) %>%
+  select(stratifier, strata, segment, starts_with('APC '))
+
+# Clean up the age adjusted preventive practices and then join with the aapc table
+clean_age_adjusted <- age_adjusted_preventive %>% 
+  # Filter to just the >=3 practices
   filter(label == 'At least three preventive practices followed') %>% 
-  mutate(age_adjusted_prop = age_adjusted_prop * 100) %>% 
+  # Filter down to every other year
+  filter(year %in% seq(2000, 2020, by = 2)) %>% 
+  mutate(age_adjusted_prop = age_adjusted_prop * 100,
+         chr_age_adj_prop = sigfig(age_adjusted_prop, digits = 4),
+         age_adjusted_se_perc = sigfig(age_adjusted_se_perc, digits = 2),
+         percentage = glue::glue('{chr_age_adj_prop} ({age_adjusted_se_perc})')) %>% 
   pivot_wider(
@@
     names_from = year,
-    values_from = age_adjusted_prop
+    values_from = c(age_adjusted_prop, percentage),
   ) %>% 
+  # Remove excess strata
   filter(strata %!in% c('Not available', 'Other Race/Not Hispanic')) %>% 
+  # Relevel stratifier factor, clean up stratifier and strata names
   mutate(stratifier = factor(stratifier,
@@
                             strata == 'Greater than HS' ~ 'Greater than high school',
-                            TRUE ~ strata)) %>% 
+                            TRUE ~ strata),
+         `Percent Change` = sigfig(((age_adjusted_prop_2020 - age_adjusted_prop_2008) / age_adjusted_prop_2008) * 100, digits = 4)) %>% 
+  select(-starts_with('age_adjusted_prop')) %>% 
+  setNames(., str_replace(names(.), 'percentage_', "")) %>% 
   mutate(strata = as.factor(strata)) %>% 
@@
   )) %>% 
+  # Join with AAPC table
+  left_join(cleaned_jp_aapc, by = c('stratifier', 'strata'))
+
+cleaned_preventive_df <- left_join(clean_age_adjusted, cleaned_jp_apc, by = c('stratifier', 'strata')) %>% 
+  mutate(AAPC = case_when(is.na(AAPC) & is.na(`APC Period 2`) ~ `APC Period 1`,
+                          TRUE ~ AAPC),
+         `APC Period 1` = case_when(is.na(`APC Period 1`) & is.na(`APC Period 2`) ~ AAPC,
+                                    TRUE ~ `APC Period 1`)) %>%
+  # Rename poverty levels
+  mutate(strata = case_when(as.character(strata) == 'Poor/Negative' ~ 'Income < 100% of the poverty line',
+                            as.character(strata) == 'Low income' ~ 'Income 100% - 199% of the poverty line',
+                            as.character(strata) == 'Middle income' ~ 'Income 200% - 399% of the poverty line',
+                            as.character(strata) == 'High income' ~ 'Income > 400% of the poverty line',
+                            TRUE ~ as.character(strata)))
+
+preventive_practice_table <- cleaned_preventive_df %>% 
   group_by(stratifier) %>%
-  select(stratifier, strata, `2008`:`2020`) %>%
+  select(stratifier, strata, `2008`:`2020`, `Percent Change`, `Joinpoint Year` = segment,
+         `APC Period 1`, `APC Period 2`, `AAPC`) %>%
   gt() %>% 
-  fmt_number(columns = `2008`:`2020`, decimals = 1)
+  sub_missing(missing_text = ' ')
 preventive_practice_table$`_data` <- preventive_practice_table$`_data`[c(1:18, 20, 19, 21), ]

### 2022-12-28 _targets.R

@@ -722,7 +722,8 @@ list(
         nest = TRUE
       ) %>%
       preventivePracticebyAge(., by = 'AGE_all', diab_list) %>%
-      makePreventiveTablesLongerbyAge2(),
+      makePreventiveTablesLongerbyAge2() %>%
+      mutate(age_adjusted_se_perc = p.std.error),
     pattern = map(diab_list)
   ),
   tar_target(
@@ -777,7 +778,7 @@ list(
 # Joinpoint analysis ------------------------------------------------------
 
   tar_target(
-    joinpoint_regressions_proportions,
+    jp_regressions_proportions,
     age_adjusted_stats %>%
       filter(strata != 'Total') %>%
       filter(strata != 'Not available') %>%
@@ -796,7 +797,7 @@ list(
       map(., ~joinPointRegression(.x))
   ),
   tar_target(
-    joinpoint_regressions_preventive,
+    jp_regressions_preventive,
     age_adjusted_preventive %>%
       filter(strata != 'Total') %>%
       filter(strata != 'Not available') %>%
@@ -813,6 +814,88 @@ list(
              year_adj = year - 2007) %>%
       split(., f = ~.$stratifier + .$variable) %>%
       map(., ~joinPointRegression(.x))
+  ),
+  tar_target(
+    jp_proportion_lines,
+    map2(jp_regressions_proportions, names(jp_regressions_proportions), function(.x, .y) {
+      .x$report %>%
+        mutate(group.practice = .y)
+    }) %>%
+      bind_rows() %>%
+      separate(group.practice, c('stratifier', 'practice'), sep = '[.]') %>%
+      mutate(strata = case_when(stratifier == 'overall' ~ 'stat_0',
+                                TRUE ~ strata)) %>%
+      mutate(stratifier = factor(stratifier,
+                                 c('overall', 'age', 'sex', 'race', 'edu', 'insurance', 'poverty')),
+             strata = case_when(strata == 'stat_0' ~ '-',
+                                strata == 'Greater than HS' ~ 'Greater than high school',
+                                TRUE ~ strata)) %>%
+      mutate(strata = as.factor(strata)) %>%
+      mutate(stratifier = recode_factor(
+        stratifier,
+        overall = 'Overall',
+        age = 'Age',
+        sex = 'Sex',
+        race = 'Race/Ethnicity',
+        edu = 'Highest degree earned',
+        insurance = 'Insurance coverage',
+        poverty = 'Poverty level'
[…]

### 2022-12-28 scripts/functions.R

@@ -1149,7 +1149,9 @@ joinPointRegression <- function(data) {
     het_error = 'constant variance',
     dependent_variable_type = 'proportion'
   )
-  export_opt <- export_options()
+  export_opt <- export_options(
+    aapc_full_range = TRUE
+  )
   jp <- joinpoint(
     data,
     x = year,

### 2022-12-29 scripts/manuscript/manuscript_draft.qmd
For remote syncing

@@
   # Rename poverty levels
-  mutate(strata = case_when(as.character(strata) == 'Poor/Negative' ~ 'Income < 100% of the poverty line',
-                            as.character(strata) == 'Low income' ~ 'Income 100% - 199% of the poverty line',
-                            as.character(strata) == 'Middle income' ~ 'Income 200% - 399% of the poverty line',
-                            as.character(strata) == 'High income' ~ 'Income > 400% of the poverty line',
+  mutate(strata = case_when(as.character(strata) == 'Poor/Negative' ~ '< 100%',
+                            as.character(strata) == 'Low income' ~ '100% - 199%',
+                            as.character(strata) == 'Middle income' ~ '200% - 399%',
+                            as.character(strata) == 'High income' ~ '> 400%',
                             TRUE ~ as.character(strata)))
@@
          `APC Period 1`, `APC Period 2`, `AAPC`) %>%
+  mutate(stratifier = case_when(as.character(stratifier) == 'Poverty level' ~ 'Income as % of poverty line',
+                                TRUE ~ as.character(stratifier))) %>% 
   gt() %>% 
@@
 tar_load(age_adjusted_stats)
+tar_load(jp_proportion_plot_data)
 
-stats_table_plot_dat <- age_adjusted_stats %>% 
+stats_table_plot_dat <- jp_proportion_plot_data %>% 
   filter(strata != 'Total') %>%
@@
 # Relevel the poverty factors
-stats_table_plot_dat$poverty$strata <- factor(stats_table_plot_dat$poverty$strata, levels = c('High income', 'Middle income', 'Low income', 'Poor/Negative'))
+stats_table_plot_dat$poverty$strata <-
+  factor(
+    stats_table_plot_dat$poverty$strata,
+    levels = c('High income', 'Middle income', 'Low income', 'Poor/Negative'),
+    labels = c(
+      '> 400% ',
+      '200% - 399%',
+      '100% - 199%',
+      '< 100%'
+
+    )
+  )
 test_plots <- stats_table_plot_dat %>% 
@@
       #geom_point() +
-      geom_smooth( se = FALSE) +
-      geom_smooth(data = filter(overall_data, variable %in% c('a1c', 'CHOL_all', 'flu')),
-                  aes(x = year, y = age_adjusted_prop * 100),
+      geom_line(aes(x = year, y = model * 100, group = strata, color = strata)) +
+      geom_line(data = filter(overall_data, variable %in% c('a1c', 'CHOL_all', 'flu')),
+                  aes(x = year, y = model * 100),
                   color = 'black',
-                  se = FALSE,
                   linetype = 'dashed') +
@@
       theme(axis.text = element_text(color = 'black'),
-            axis.text.x = element_text(angle = 45, hjust = 0.9, vjust = 0.95)) +
+            axis.text.x = element_text(angle = 45, hjust = 0.9, vjust = 0.95),
+            legend.title = element_text(size = 8),
+            legend.text = element_text(size = 6)) +
       labs(x = 'Year', y = 'Percentage')
@@
 
-test_plots[[1]] <- test_plots[[1]] + labs(color = 'Age (grouped)') 
-test_plots[[2]] <- test_plots[[2]] + labs(color = 'Highest degree \nobtained') + theme(strip.background =  element_blank(),
-                                                                          strip.text = element_blank())
-test_plots[[3]] <- test_plots[[3]] + labs(color = "Insurance") + theme(strip.background =  element_blank(),
-                                                                            strip.text = element_blank())
-test_plots[[4]] <- test_plots[[4]] + labs(color = 'Poverty') + theme(strip.background =  element_blank(),
-                                                                            strip.text = element_blank())
-test_plots[[5]] <- test_plots[[5]] + labs(color = 'Race/Ethnicity') + theme(strip.background =  element_blank(),
-                                                                             strip.text = element_blank())
-test_plots[[6]] <- test_plots[[6]] + labs(color = 'Sex') + theme(strip.background =  element_blank(),
-                                                                          strip.text = element_blank())
+test_plots[[1]] <- test_plots[[1]] + labs(color = 'Age (grouped)') +
+  theme(axis.title.x = element_blank())
+test_plots[[2]] <-
+  test_plots[[2]] + labs(color = 'Highest degree \nobtained') + theme(
+    strip.background =  element_blank(),
+    strip.text = element_blank(),
+    axis.title.x = element_blank()
+  )
+test_plots[[3]] <-
+  test_plots[[3]] + labs(color = "Insurance") + theme(
+    strip.background =  element_blank(),
+    strip.text = element_blank(),
+    axis.title.x = element_blank()
+  )
+test_plots[[4]] <-
+  test_plots[[4]] + labs(color = 'Income as % of \npoverty line') + theme(
+    strip.background =  element_blank(),
+    strip.text = element_blank()
+  )
+test_plots[[5]] <-
+  test_plots[[5]] + labs(color = 'Race/Ethnicity') + theme(
+    strip.background =  element_blank(),
+    strip.text = element_blank(),
+    axis.title.x = element_blank()
+  )
+test_plots[[6]] <-
+  test_plots[[6]] + labs(color = 'Sex') + theme(strip.background =  element_blank(),
+                                                strip.text = element_blank(),
+    axis.title.x = element_blank())
 test_plots <- list(
@@
       #geom_point() +
-      geom_smooth(se = FALSE) +
-      geom_smooth(data = filter(overall_data, variable %!in% c('a1c', 'CHOL_all', 'flu')),
-                  aes(x = year, y = age_adjusted_prop * 100),
+      geom_line(aes(x = year, y = model * 100, group = strata, color = strata)) +
+      geom_line(data = filter(overall_data, variable %!in% c('a1c', 'CHOL_all', 'flu')),
+                  aes(x = year, y = model * 100),
                   color = 'black',
-                  se = FALSE,
                   linetype = 'dashed') +
@@
 
-exam_plots[[1]] <- exam_plots[[1]] + labs(color = 'Age (grouped)')
-exam_plots[[2]] <- exam_plots[[2]] + labs(color = 'Highest degree \nobtained') + theme(strip.background =  element_blank(),
-                                                                          strip.text = element_blank())
-exam_plots[[3]] <- exam_plots[[3]] + labs(color = "Insurance") + theme(strip.background =  element_blank(),
-                                                                            strip.text = element_blank())
-exam_plots[[4]] <- exam_plots[[4]] + labs(color = 'Poverty') + theme(strip.background =  element_blank(),
-                                                                            strip.text = element_blank())
-exam_plots[[5]] <- exam_plots[[5]] + labs(color = 'Race/Ethnicity') + theme(strip.background =  element_blank(),
-                                                                             strip.text = element_blank())
-exam_plots[[6]] <- exam_plots[[6]] + labs(color = 'Sex') + theme(strip.background =  element_blank(),
-                                                                          strip.text = element_blank())
+exam_plots[[1]] <- exam_plots[[1]] + labs(color = 'Age (grouped)') +
+  theme(axis.title.x = element_blank())
+exam_plots[[2]] <-
+  exam_plots[[2]] + labs(color = 'Highest degree \nobtained') + theme(
+    strip.background =  element_blank(),
+    strip.text = element_blank(),
+    axis.title.x = element_blank()
+  )
+exam_plots[[3]] <-
+  exam_plots[[3]] + labs(color = "Insurance") + theme(
+    strip.background =  element_blank(),
+    strip.text = element_blank(),
+    axis.title.x = element_blank()
+  )
+exam_plots[[4]] <-
+  exam_plots[[4]] + labs(color = 'Income as % of \npoverty line') + theme(
+    strip.background =  element_blank(),
+    strip.text = element_blank()
+  )
+exam_plots[[5]] <-
+  exam_plots[[5]] + labs(color = 'Race/Ethnicity') + theme(
+    strip.background =  element_blank(),
+    strip.text = element_blank()
+  )
+exam_plots[[6]] <-
+  exam_plots[[6]] + labs(color = 'Sex') + theme(strip.background =  element_blank(),
+                                                strip.text = element_blank(),
+    axis.title.x = element_blank())
 exam_plots <- list(
@@
        filename = 'figures/all_exam_plots.tiff',
-       dpi = 200)
+       dpi = 200,
+       width = 10,
+       height = 7)
 ggsave(plot = all_test_plots,
        filename = 'figures/all_test_plots.tiff',
-       dpi = 200)
+       dpi = 200,
+       width = 10,
+       height = 7)
+ggsave(plot = all_exam_plots,
+       filename = 'figures/all_exam_plots.svg',
+       dpi = 200,
+       width = 10,
+       height = 7)
+ggsave(plot = all_test_plots,
+       filename = 'figures/all_test_plots.svg',
+       dpi = 200,
+       width = 10,
+       height = 7)
 ```

### 2022-12-29 _targets.R

@@ -895,7 +895,17 @@ tar_target(
       insurance = 'Insurance coverage',
       poverty = 'Poverty level'
     ))
-  )
+  ),
+tar_target(
+  jp_proportion_plot_data,
+  map(jp_regressions_proportions, ~.x$data_export %>%
+        mutate(apc = as.character(apc))) %>%
+    map2(., names(.), ~.x %>%
+            mutate(stratifier.practice = .y)) %>%
+    bind_rows() %>%
+    separate(stratifier.practice, c('stratifier', 'variable'), sep = '[.]') %>%
+    ungroup()
+)
 )
 
 

### 2023-01-19 scripts/manuscript/manuscript_draft.qmd
Age standardized results and calculated correct SE

--- 2022-12-27 scripts/manuscript/manuscript_draft.qmd
@@
 ---
-title: "Trends in Preventive Care Practices among US Adults with Diabetes, 2008-2020 "
-format: docx
+title: ""
+format: 
+  docx:
+    page-width: 10
+    reference-doc: template.docx
 editor: visual
@@
 csl: ama.csl
+execute:
+  echo: false
+  warning: false
+project: 
+  execute-dir: project
+crossref: 
+  fig-title: Fig
+filters:
+  - docx-landscape.lua
 ---
@@
 library(gt)
+# https://www2.census.gov/programs-surveys/acs/tech_docs/accuracy/percchg.pdf
+# https://blog.analytics-toolkit.com/2018/confidence-intervals-p-values-percent-change-relative-difference/
+# For calculating significance of percent change
+# Use to get citations for packages
+library(grateful)
+# To just make a bibtex file
+# get_pkgs_info(pkgs = c('gtsummary', 'patchwork', 'gt', 'gtsummary'))
 
 `%!in%` <- Negate(`%in%`)
+sigfig <- function(number, digits) {
 
-```
+   formatC(signif(number, digits = digits), digits = digits, format = "fg", flag = "#")
 
-**Trends in Preventive Care Practices among US Adults with Diabetes, 2008-2020**
+}
 
-Jacob T. Wittman, PhD Kai M. Bullard Stephen R. Benoit
+specifyDecimal <- function(x, digits) trimws(format(round(x, digits), nsmall=digits))
 
-CDC Affiliation
-
-\pagebreak
-
-# Abstract
-
-\pagebreak
-
-# Introduction
-
--   Diabetes affects a lot of people
-    -   Kills people, makes them sick, reduces quality of life
-    -   Cost of management is high and increasing
--   Advances in diabetes management
-    -   Patients with diabetes must actually receive this care
--   Present trends in self-reported receipt of preventive care practices according to MEPS from 2008 - 2020.
-
-Diabetes is a chronic disease that affects XX people in the USA.
-
-# Methods
-
-## Data Source
-
-We used data from the Medical Expenditure Panel Survey (MEPS) from years 2008 - 2020.
-Participants in this survey are a subsample of households that participate in the National Health Interview Survey (NHIS).
-The MEP survey targets the civilian noninstitutionalized population in the US and provides national and regional estimates of health care use, expenditures, sources of payment and health insurance coverage.
-This survey also contains information on patient demographics, socioeconomics, and, via the Diabetes Care Survey (DCS), information on diabetes preventive care practices.
-The DCS is a self-administered paper-and-pencil questionnaire that is provided to MEPS respondents who indicate that they have been told by a doctor or health professional that they have diabetes.
-
-The data we used comes from the full-year consolidated file from MEPS for the 12 year time span of our report.
-We used a weighted population of XXX in this analysis.
-Our analysis is adjusted for the complex survey design, including clustering and stratification.
-Reported values for the proportions of different groups receiving recommended preventive care practices are age-adjusted.
-
-# Results
-
-# Discussion
-
-# References
-
-::: {#refs}
-:::
-
-# Tables
-
-```{r}
-# tar_load(age_adjusted_stats)
-# age_adjusted_stats %>% 
-#   #filter(stratifier != 'age') %>% 
-#   mutate(age_adjusted_prop = age_adjusted_prop * 100) %>% 
-#   pivot_wider(
-#     id_cols = c(stratifier, variable, var_label, strata),
-#     names_from = year,
-#     values_from = age_adjusted_prop
-#   ) %>% 
-#   group_by(stratifier, strata) %>%
-#   select(stratifier, var_label, `2008`:`2020`) %>%
-#   gt() %>% 
-#   fmt_number(columns = `2008`:`2020`, decimals = 1) %>% 
-#   gtsave('table_one.docx')
+# For pulling specifically from the preventive table since the column name I use is
+# weird and doesn't like being bang-bang-banged.
+pullNumber <- function(data, filter.by, column) {
+  data %>% 
+    filter(` ` == filter.by) %>% 
+    select(!!!column) %>% 
+    pull()
+}
+# For other tables that don't use such weird column names
+pullNumber2 <- function(data, filter.column, filter.by, select.column) {
+    data %>% 
+    filter(!!!filter.column == filter.by) %>% 
+    select(!!!column) %>% 
+    pull()
+}
 ```
@@
 ```{r}
-tar_load(age_adjusted_preventive)
-preventive_practice_table <- age_adjusted_preventive %>% 
+
+tar_load(c(jp_prevention_apc,
+           jp_prevention_aapc,
+           age_adjusted_preventive,
+           jp_proportion_plot_data,
+           age_adjusted_stats
+           ),
+         store = here::here('_targets/'))
+# Clean up the AAPC table and get it into format for printing to table
+cleaned_jp_aapc <- jp_prevention_aapc %>% 
+  select(-aapc_index) %>% 
+  mutate(aapc = specifyDecimal(aapc, digits = 1),
+        across(starts_with('aapc_'),
+                ~specifyDecimal(x = .x, digits = 2)),
+         across(starts_with('aapc'),
+                ~case_when(.x == ' NA' ~ NA_character_,
+                           TRUE ~ .x)),
+         AAPC = case_when(!is.na(aapc) ~ glue::glue('{aapc} ({aapc_c_i_low}, {aapc_c_i_high})'),
+                          TRUE ~ NA_character_)) %>%
+  select(stratifier, strata, AAPC)
+
+# Format APC table for future joining
+cleaned_jp_apc <- jp_prevention_apc %>% 
+  # No model has more than a single joinpoint, so make wider and then
+  # remove the excess columns to determine if there's no join point (segmend_end = 2020)
+  # or a joinpoint (segment_end != 2020)
+  pivot_wider(id_cols = c(stratifier, strata, model),
+              names_from = segment,
+              values_from = c(segment_start, segment_end, apc, p_value, apc_significant,
+                              apc_95_lcl, apc_95_ucl)
+  ) %>% 
+  select(-segment_start_0, -segment_start_1, -segment_end_1, -apc_significant_0, -apc_significant_1) %>% 
+  # Make segment empty if no joinpoint
+  mutate(segment = case_when(segment_end_0 == 2020 ~ NA_integer_,
+                             TRUE ~ segment_end_0)) %>% 
+  # MAke apc empty if not significant
+  mutate(across(c(apc_0, apc_95_lcl_0, apc_95_ucl_0),
+                ~ case_when(p_value_0 > 0.05 & p_value_1 > 0.05 ~ NA_real_,
+                            TRUE ~ .x)), 
+         across(c(apc_1, apc_95_lcl_1, apc_95_ucl_1),
+                ~ case_when(p_value_0 > 0.05 & p_value_1 > 0.05 ~ NA_real_,
+                            TRUE ~ .x)),
+         across(starts_with('apc_0') | starts_with('apc_1') | starts_with('p_'),
+                ~specifyDecimal(.x, digits = 1)),
+         across(contains('cl'),
+                ~specifyDecimal(.x, digits = 2)),
+         across(starts_with('apc') | starts_with('p_'),
+                ~case_when(.x == 'NA' ~ NA_character_,
+                           TRUE ~ .x))) %>% 
+  # Concatenate apc column with CI columns
+  mutate(`APC Period 1` = case_when(
+       !is.na(apc_0) ~ glue::glue('{apc_0} ({apc_95_lcl_0}, {apc_95_ucl_0})'),
+       TRUE ~ NA_character_
+                                    ),
+    `APC Period 2` = case_when(
+       !is.na(apc_1) ~ glue::glue('{apc_1} ({apc_95_lcl_1}, {apc_95_ucl_1})'),
+       TRUE ~ NA_character_
+    )
+  ) %>%
+  select(stratifier, strata, segment, starts_with('APC '))
+
+# Clean up the age adjusted preventive practices and then join with the aapc table
+clean_age_adjusted <- age_adjusted_preventive %>% 
+  # Filter to just the >=3 practices
   filter(label == 'At least three preventive practices followed') %>% 
-  mutate(age_adjusted_prop = age_adjusted_prop * 100) %>% 
+  # Filter down to every other year
+  filter(year %in% seq(2000, 2020, by = 2)) %>% 
+  mutate(chr_age_adj_prop = sigfig(p, digits = 3),
+         p.std.error = p.std.error * 100,
+         age_adjusted_se_perc = sigfig(p.std.error, digits = 3),
+         percentage = glue::glue('{chr_age_adj_prop} ({age_adjusted_se_perc})')) %>% 
   pivot_wider(
@@
     names_from = year,
-    values_from = age_adjusted_prop
+    values_from = c(p, percentage, p.std.error),
   ) %>% 
+  # Remove excess strata
   filter(strata %!in% c('Not available', 'Other Race/Not Hispanic')) %>% 
+  # Relevel stratifier factor, clean up stratifier and strata names
   mutate(stratifier = factor(stratifier,
@@
                             strata == 'Greater than HS' ~ 'Greater than high school',
-                            TRUE ~ strata)) %>% 
+                            TRUE ~ strata),
+         percent_change = ((p_2020 - p_2008) / p_2008) * 100,
+         percent_change_se = (abs(p_2020 / p_2008) * sqrt((p.std.error_2020^2 / p_2020^2) + (p.std.error_2008^2 / p_2008^2)) * 100),
+         perc_change_lcl = percent_change - 1.96 * percent_change_se,
+         perc_change_ucl = percent_change + 1.96 * percent_change_se,
+         perc_change_char = specifyDecimal(percent_change, digits = 1),
+         perc_change_lcl_char = specifyDecimal(perc_change_lcl, digits = 2),
+         perc_change_ucl_char = specifyDecimal(perc_change_ucl, digits = 2),
+         `Percent Change (95% CI)` = glue::glue('{perc_change_char} ({perc_change_lcl_char}, {perc_change_ucl_char})')) %>% 
+  select(-starts_with('age_adjusted_prop'), -starts_with('p.std.error'), -contains('_change_')) %>% 
+  setNames(., str_replace(names(.), 'percentage_', "")) %>% 
   mutate(strata = as.factor(strata)) %>% 
@@
   )) %>% 
+  # Join with AAPC table
+  left_join(cleaned_jp_aapc, by = c('stratifier', 'strata'))
+
+cleaned_preventive_df <- left_join(clean_age_adjusted, cleaned_jp_apc, by = c('stratifier', 'strata')) %>% 
+  mutate(AAPC = case_when(is.na(AAPC) & is.na(`APC Period 2`) ~ `APC Period 1`,
+                          TRUE ~ AAPC),
+         `APC Period 1` = case_when(is.na(`APC Period 1`) & is.na(`APC Period 2`) ~ AAPC,
+                                    TRUE ~ `APC Period 1`)) %>%
+  # Rename poverty levels
+  mutate(strata = case_when(as.character(strata) == 'Poor/Negative' ~ '< 100%',
+                            as.character(strata) == 'Low income' ~ '100% - 199%',
+                            as.character(strata) == 'Middle income' ~ '200% - 399%',
+                            as.character(strata) == 'High income' ~ '> 400%',
+                            TRUE ~ as.character(strata)))
+
+# Rename strata to a blank name to remove it from the final table
+preventive_practice_table <- cleaned_preventive_df %>% 
   group_by(stratifier) %>%
-  select(stratifier, strata, `2008`:`2020`) %>%
+  select(stratifier, ` ` = strata, `2008`:`2020`, `Percent Change (95% CI)`, `Joinpoint Year` = segment,
+         `APC Period 1`, `APC Period 2`, `AAPC`) %>%
+  mutate(stratifier = case_when(as.character(stratifier) == 'Poverty level' ~ 'Poverty income ratio',
+                                TRUE ~ as.character(stratifier))) %>% 
+  # Rename some columns to add () info
+  rename(`2008 (SE)` = `2008`,
+         `2010 (SE)` = `2010`,
+         `2012 (SE)` = `2012`,
+         `2014 (SE)` = `2014`,
+         `2016 (SE)` = `2016`,
+         `2018 (SE)` = `2018`,
+         `2020 (SE)` = `2020`,
+         `APC Period 1 (95% CI)` = `APC Period 1`,
+         `APC Period 2 (95% CI)` = `APC Period 2`,
+         `AAPC (95% CI)` = `AAPC`) %>% 
   gt() %>% 
-  fmt_number(columns = `2008`:`2020`, decimals = 1)
+  sub_missing(missing_text = ' ')
 preventive_practice_table$`_data` <- preventive_practice_table$`_data`[c(1:18, 20, 19, 21), ]
-preventive_practice_table %>% 
-  gtsave('preventive_practices.docx')
+
+tab1 <- preventive_practice_table$`_data`
 ```
@@
 
-preventive_practice_table <- age_adjusted_preventive %>% 
-  filter(label == 'At least three preventive practices followed') %>% 
-  mutate(age_adjusted_prop = age_adjusted_prop * 100) %>% 
-  pivot_wider(
-    id_cols = c(stratifier, variable, label, strata),
-    names_from = year,
-    values_from = age_adjusted_prop
-  ) %>% 
-  filter(strata %!in% c('Not available', 'Other Race/Not Hispanic')) %>% 
-  mutate(stratifier = factor(stratifier,
-                             c('overall', 'age', 'sex', 'race', 'edu', 'insurance', 'poverty')),
-         strata = case_when(strata == 'stat_0' ~ '-', 
-                            strata == 'Greater than HS' ~ 'Greater than high school',
-                            TRUE ~ strata)) %>% 
-  mutate(strata = as.factor(strata)) %>% 
-  mutate(stratifier = recode_factor(
-    stratifier,
-    overall = 'Overall',
-    age = 'Age',
-    sex = 'Sex',
-    race = 'Race/Ethnicity',
-    edu = 'Highest degree earned',
-    insurance = 'Insurance coverage',
-    poverty = 'Poverty level'
-  )) %>% 
-  group_by(stratifier) %>%
-  select(stratifier, strata, `2008`:`2020`) %>%
-  gt() %>% 
-  fmt_number(columns = `2008`:`2020`, decimals = 1)
-preventive_practice_table$`_data` <- preventive_practice_table$`_data`[c(1:18, 20, 19, 21), ]
-preventive_practice_table %>% 
-  gtsave('preventive_practices.docx')
-```
-
-# Figures
-
-```{r}
-tar_load(age_adjusted_stats)
-
-stats_table_plot_dat <- age_adjusted_stats %>% 
+stats_table_plot_dat <- jp_proportion_plot_data %>% 
   filter(strata != 'Total') %>%
@@
   filter(strata != 'Other Race/Not Hispanic') %>% 
-  mutate(variable_text = case_when(variable == 'a1c' ~ '2 or more A1C tests',
+  mutate(variable_text = case_when(variable == 'a1c' ~ 'Two or more A1C tests',
                                    variable == 'CHOL_all' ~ 'Cholesterol tested',
-                                   variable == 'DENT_all' ~ '1 or more dentist visits',
+                                   variable == 'DENT_all' ~ 'One or more dentist visits',
                                    variable == 'eye-exam' ~ 'Eye exam with dilation',
@@
       x = year,
-      y = age_adjusted_prop * 100,
+      y = p,
       group = strata,
@@
       #geom_point() +
-      geom_smooth( se = FALSE) +
-      geom_smooth(data = filter(overall_data, variable %in% c('a1c', 'CHOL_all', 'flu')),
-                  aes(x = year, y = age_adjusted_prop * 100),
+      geom_line(aes(x = year, y = model, group = strata, color = strata)) +
+      geom_line(data = filter(overall_data, variable %in% c('a1c', 'CHOL_all', 'flu')),
+                  aes(x = year, y = model),
                   color = 'black',
-                  se = FALSE,
                   linetype = 'dashed') +
@@
 
-test_plots[[1]] <- test_plots[[1]] + labs(color = 'Age (grouped)') 
-test_plots[[2]] <- test_plots[[2]] + labs(color = 'Highest degree \nobtained') + theme(strip.background =  element_blank(),
-                                                                          strip.text = element_blank())
-test_plots[[3]] <- test_plots[[3]] + labs(color = "Insurance") + theme(strip.background =  element_blank(),
-                                                                            strip.text = element_blank())
-test_plots[[4]] <- test_plots[[4]] + labs(color = 'Poverty') + theme(strip.background =  element_blank(),
-                                                                            strip.text = element_blank())
-test_plots[[5]] <- test_plots[[5]] + labs(color = 'Race/Ethnicity') + theme(strip.background =  element_blank(),
-                                                                             strip.text = element_blank())
-test_plots[[6]] <- test_plots[[6]] + labs(color = 'Sex') + theme(strip.background =  element_blank(),
-                                                                          strip.text = element_blank())
+test_plots[[1]] <- test_plots[[1]] + labs(color = 'Age (grouped)') +
+  theme(axis.title.x = element_blank())
+test_plots[[2]] <-
+  test_plots[[2]] + labs(color = 'Highest degree \nobtained') + theme(
+    strip.background =  element_blank(),
+    strip.text = element_blank(),
+    axis.title.x = element_blank()
+  )
+test_plots[[3]] <-
+  test_plots[[3]] + labs(color = "Insurance") + theme(
+    strip.background =  element_blank(),
+    strip.text = element_blank(),
+    axis.title.x = element_blank()
+  )
+test_plots[[4]] <-
+  test_plots[[4]] + labs(color = 'Poverty income ratio') + theme(
+    strip.background =  element_blank(),
+    strip.text = element_blank()
+  )
+test_plots[[5]] <-
+  test_plots[[5]] + labs(color = 'Race & Ethnicity') + theme(
+    strip.background =  element_blank(),
+    strip.text = element_blank(),
+    axis.title.x = element_blank()
+  )
+test_plots[[6]] <-
+  test_plots[[6]] + labs(color = 'Sex') + theme(strip.background =  element_blank(),
+                                                strip.text = element_blank(),
+    axis.title.x = element_blank())
 test_plots <- list(
@@
       #geom_point() +
-      geom_smooth(se = FALSE) +
-      geom_smooth(data = filter(overall_data, variable %!in% c('a1c', 'CHOL_all', 'flu')),
-                  aes(x = year, y = age_adjusted_prop * 100),
+      geom_line(aes(x = year, y = model, group = strata, color = strata)) +
+      geom_line(data = filter(overall_data, variable %!in% c('a1c', 'CHOL_all', 'flu')),
+                  aes(x = year, y = model),
                   color = 'black',
-                  se = FALSE,
                   linetype = 'dashed') +
@@
 
-exam_plots[[1]] <- exam_plots[[1]] + labs(color = 'Age (grouped)')
-exam_plots[[2]] <- exam_plots[[2]] + labs(color = 'Highest degree \nobtained') + theme(strip.background =  element_blank(),
-                                                                          strip.text = element_blank())
-exam_plots[[3]] <- exam_plots[[3]] + labs(color = "Insurance") + theme(strip.background =  element_blank(),
-                                                                            strip.text = element_blank())
-exam_plots[[4]] <- exam_plots[[4]] + labs(color = 'Poverty') + theme(strip.background =  element_blank(),
-                                                                            strip.text = element_blank())
-exam_plots[[5]] <- exam_plots[[5]] + labs(color = 'Race/Ethnicity') + theme(strip.background =  element_blank(),
-                                                                             strip.text = element_blank())
-exam_plots[[6]] <- exam_plots[[6]] + labs(color = 'Sex') + theme(strip.background =  element_blank(),
-                                                                          strip.text = element_blank())
+exam_plots[[1]] <- exam_plots[[1]] + labs(color = 'Age (grouped)') +
+  theme(axis.title.x = element_blank())
+exam_plots[[2]] <-
+  exam_plots[[2]] + labs(color = 'Highest degree \nobtained') + theme(
+    strip.background =  element_blank(),
+    strip.text = element_blank(),
+    axis.title.x = element_blank()
+  )
+exam_plots[[3]] <-
+  exam_plots[[3]] + labs(color = "Insurance") + theme(
+    strip.background =  element_blank(),
+    strip.text = element_blank(),
+    axis.title.x = element_blank()
+  )
+exam_plots[[4]] <-
+  exam_plots[[4]] + labs(color = 'Poverty income ratio') + theme(
+    strip.background =  element_blank(),
+    strip.text = element_blank()
+  )
+exam_plots[[5]] <-
+  exam_plots[[5]] + labs(color = 'Race & Ethnicity') + theme(
+    strip.background =  element_blank(),
+    strip.text = element_blank(),
+    axis.title.x = element_blank()
+  )
+exam_plots[[6]] <-
+  exam_plots[[6]] + labs(color = 'Sex') + theme(strip.background =  element_blank(),
+                                                strip.text = element_blank(),
+    axis.title.x = element_blank())
 exam_plots <- list(
@@
 )
-(all_exam_plots <- exam_plots %>% 
+
+all_exam_plots <- exam_plots %>% 
+  wrap_plots(nrow = 6) &
+  theme(plot.margin = margin(0.5, 0.5, 0.5, 0.5, 'pt'))
+all_test_plots <- test_plots %>% 
+  wrap_plots(nrow = 6) &
+  theme(plot.margin = margin(0.5, 0.5, 0.5, 0.5, 'pt'))
+```
+
+```{r}
+#| include: false
+# Save figure/table output
+preventive_practice_table %>%
+  gtsave('preventive_practices.docx')
+ggsave(plot = all_exam_plots,
+       filename = 'figures/all_exam_plots.tiff',
+       dpi = 200,
+       width = 10,
+       height = 6)
+ggsave(plot = all_test_plots,
+       filename = 'figures/all_test_plots.tiff',
+       dpi = 200,
+       width = 10,
+       height = 6)
+ggsave(plot = all_exam_plots,
+       filename = 'figures/all_exam_plots.svg',
+       dpi = 200,
+       width = 10,
+       height = 6)
+ggsave(plot = all_test_plots,
+       filename = 'figures/all_test_plots.svg',
+       dpi = 200,
+       width = 10,
+       height = 6)
+```
+**Trends in Preventive Care Practices among US Adults with Diabetes, 2008-2020**
+
+Jacob T. Wittman, PhD, Kai M. Bullard, MPH, PHD, PhD Stephen R. Benoit, MD, MPH
+
+CDC Affiliation
+
+\pagebreak
+
+# Abstract
+
+\pagebreak
+
+# Introduction
+
+Intro -- peak incidence in 2008/2009, increasing rates of some major complications + projections of diabetes numbers; previous reports of preventive care practices
+
+Diabetes is a chronic disease that affects XX people in the USA.
+
+# Methods
+
+## Data Source
+
+We used data from the Medical Expenditure Panel Survey (MEPS) from the years 2008 - 2020 to evaluate trends in preventive care practices in adults 18 years or older with diabetes in the USA.
+Participants in this survey are a subsample of households that participate in the National Health Interview Survey (NHIS).
+The MEP survey targets the civilian noninstitutionalized population in the US and provides national and regional estimates of health care use, expenditures, sources of payment and health insurance coverage.
+This survey also contains information on patient demographics, socioeconomic, and, via the Diabetes Care Survey (DCS), information on diabetes preventive care practices.
+The DCS is a self-administered paper-and-pencil questionnaire that is provided to MEPS respondents who indicate that they have been told by a doctor or health professional that they have diabetes.
+The data we used comes from the full-year consolidated file from MEPS for the 12 year time span of our report.
+
+## Outcomes
+
+We selected six outcome variables that were readily available in the data from 2008 - 2020 and that are based on American Diabetes Association annual care recommendations.
+These six recommendations include at least one dental examination, an eye examination that includes dilation, a foot examination, at least two A1C tests, a cholesterol test, and the receipt of a flu vaccine.
+The number of total dentist visits in a year is available in the MEPS data and was used to determine which adults had one or more dentist visits in a year.
+Respondents were also asked if they had an eye examination, a foot examination, a flu vaccine, or a cholesterol test in a given year of the survey.
+The number of A1C tests received by a respondent was recorded and we grouped respondents into those that had two or more A1C tests in a year and those that had less than two.
+Using the binary outcomes for each of these six measures, we further classified adults as having received at least three of those recommended care practices and those that received less than three of these practices.
+
+## Analysis
+
+Our analysis is adjusted for the complex survey design used, including clustering and stratification.
+Reported values for the percentages of the population receiving recommended preventive care practices are direct age-adjusted estimates.
+These estimates are presented for the overall population, as well as stratified by age, sex, race and ethnicity, highest degree of education obtained, type of insurance, and the ratio of income to poverty line.
+
+We used R Statistical Software (v4.2.1) @rcore2022 to perform all analyses.
+The package gtsummary was used to account for the complex survey design and age-adjust estimates @gtsummary.
+Trends in preventive care practices were analyzed using Joinpoint Command Line Software @joinpoint with R via the R package nih.joinpoint @nihjoinpoint.
+Joinpoint regression uses permutation tests to detect statistically significant changes at a pre-specified alpha of 0.05 in direction and/or magnitude of trends @kim2000permutation.
+The Joinpoint software also provided estimates of the annual percent change (APC) for each trend segment and the average annual percent change (AAPC) for the entire trend.
+
+# Results
+
+For the entire population of adults diagnosed with diabetes in the USA there was a significant decrease of `r pullNumber(tab1, '-', 'Percent Change (95% CI)')` in the percentage of people receiving at least three of the recommended practices from 2008 to 2020 (Table 1).
+(Table 1).
+The largest decreases in the percentage of adults receiving at least three preventive care practices were seen in those with no high school diploma (`r pullNumber(tab1, 'Less than high school', 'Percent Change (95% CI)')`%), Asian/Not Hispanic (`r pullNumber(tab1, 'Asian/Not Hispanic', 'Percent Change (95% CI)')`%), the uninsured (`r pullNumber(tab1, 'Uninsured', 'Percent Change (95% CI)')`%), and those with an income to poverty line ratio between 100% and 199% (`r pullNumber(tab1, '100% - 199%', 'Percent Change (95% CI)')`%) (Table 1).
+
+While the percent change and AAPC for nearly all groups were negative, some groups had APC values that were initially flat (i.e.
+the 95% CI overlapped 0) in the first period but became negative in the second period (Table 1).
+The year in which Joinpoint regression identified statistically significant changes in the slope of the trend ranged from 2010 - 2015 (Table 1).
+Only adults in the highest poverty to income ratio category (\>400%) had an initial APC that was positive at `r pullNumber(tab1, '> 400%', 'APC Period 1 (95% CI)')`% (Table 1).
+
+Overall trends in each of the individual preventive practices decreased from 2008 to 2020, with the exception of the percentage of people receiving two or more A1C tests in one year, which increased from `r sigfig(overall_data$age_adjusted_prop[1] * 100, digits = 3)`% to `r sigfig(overall_data$age_adjusted_prop[13] * 100, digits = 3)`% (@fig-exams & @fig-tests).
+Trends in the percentages of people getting an eye exam with dilation and one or more dentist visits tended to be close to flat or decreasing, with a few exceptions where percentages first increased until the mid 2010s and then began to decrease (e.g., see the eye exam graph for the poverty income ratio stratifier and dentist visits for race and ethnicity stratifier, @fig-exams).
+The overall trend for foot exams initially increased and then started to decrease in 2012, and many of the stratifier-specific groups follow a similar trend (@fig-exams).
+The trend overall and among our stratifying variables for cholesterol testing and receiving a flu vaccine also generally follow the trend of increasing until between 2013 - 2015, where they begin to decrease, although a few specific stratifying groups only decrease over the examined time period (@fig-tests).
+The percentage of the population receiving two or more A1C tests in a year only increased overall and for all groups (@fig-tests).
+
+# Discussion
+
+Discussion -- ACA and recovery from Great Recession as context for increasing trends after 2008 until 2016 (then what happened?); compare to BRFSS state estimates; impact of COVID on receipt of PCP; speculation about future burden of complications due to suboptimal preventive care
+
+BRFSS estimates
+- Median state eye exam is roughly flat - individual states bounce all over
+- Median foot exam is flat/maybe increasing? 
+- Median state A1c tests - also flattish/maybe increasing? hard to say
+- Median state flu vaccine - bounces around a bit more.
+Overall line would probably be flat though?
+Nationally though the estimate is pretty clearly increasing overall and for all available stratifiers
+- No cholesterol or dentist info from BRFSS? Not on dashboard anyway.
+
+Limitations -- cross-sectional, self-report only, declining response rate
+
+# References
+
+::: {#refs}
+:::
+
+\pagebreak
+
+# Tables
+
+```{r}
+#| label: tbl-prev
+#| tbl-cap: Age-adjusted trends in proportions of US adults with diabetes that report receiving at least three of six recommended care practices - at least one dental visit, one eye exam with dilation, one foot exam, two or more A1C tests, cholesterol level tested, and receiving a flu vaccine.
+
+preventive_practice_table
+```
+
+\pagebreak
+
+::: landscape
+# Figures
+
+```{r}
+#| label: fig-exams
+#| fig-cap: Age-adjusted trends in proportions of US adults with diabetes who reported receiving recommended medical examinations. The dashed black line is the overall trend.
+#| fig-width: 8
+
+all_exam_plots
+```
+
+\pagebreak
+
+```{r}
+#| label: fig-tests
+#| fig-cap: Age-adjusted trends in proportions of US adults with diabetes who reported receiving recommended lab tests and vaccinations. The dashed black line is the overall trend. 
+#| fig-width: 10
+
+all_test_plots
+```
+:::
+
+## Alternative figure options
+
+```{r}
+test_plots1 <- stats_table_plot_dat %>% 
+   map(
+    ~ ggplot(filter(.x, variable %in% c('a1c', 'CHOL_all')),
+             aes(
+      x = year,
+      y = p,
+      group = strata,
+      color = strata
+    )) +
+      #geom_point() +
+      geom_line(aes(x = year, y = model, group = strata, color = strata)) +
+      geom_line(data = filter(overall_data, variable %in% c('a1c', 'CHOL_all')),
+                  aes(x = year, y = model),
+                  color = 'black',
+                  linetype = 'dashed') +
+      facet_wrap( ~ variable_text, ncol = 3) +
+      theme_classic() +
+      scale_y_continuous(
+        limits = c(00, 100),
+        breaks = seq(0, 100, 25),
+        labels = seq(0, 100, 25)
+      ) +
+      scale_x_continuous(
+        limits = c(2008, 2020),
+        breaks = seq(2008, 2020, 2),
+        labels = seq(2008, 2020, 2)
+      ) +
+      scale_color_brewer(type = 'qual', palette = 'Set2') +
+      theme(axis.text = element_text(color = 'black'),
+            axis.text.x = element_text(angle = 45, hjust = 0.9, vjust = 0.95),
+            legend.title = element_text(size = 8),
+            legend.text = element_text(size = 6)) +
+      labs(x = 'Year', y = 'Percentage')
+  )
+
+test_plots1[[1]] <- test_plots1[[1]] + labs(color = 'Age (grouped)') +
+  theme(axis.title.x = element_blank())
+test_plots1[[2]] <-
+  test_plots1[[2]] + labs(color = 'Highest degree \nobtained') + theme(
+    strip.background =  element_blank(),
+    strip.text = element_blank(),
+    axis.title.x = element_blank()
+  )
+test_plots1[[3]] <-
+  test_plots1[[3]] + labs(color = "Insurance") + theme(
+    strip.background =  element_blank(),
+    strip.text = element_blank(),
+    axis.title.x = element_blank()
+  )
+test_plots1[[4]] <-
+  test_plots1[[4]] + labs(color = 'Poverty income ratio') + theme(
+    strip.background =  element_blank(),
+    strip.text = element_blank()
+  )
+test_plots1[[5]] <-
+  test_plots1[[5]] + labs(color = 'Race & Ethnicity') + theme(
+    strip.background =  element_blank(),
+    strip.text = element_blank(),
+    axis.title.x = element_blank()
+  )
+test_plots1[[6]] <-
+  test_plots1[[6]] + labs(color = 'Sex') + theme(strip.background =  element_blank(),
+                                                strip.text = element_blank(),
+    axis.title.x = element_blank())
+test_plots1 <- list(
+  test_plots1[[1]],
+  test_plots1[[6]],
+  test_plots1[[5]],
+  test_plots1[[2]],
+  test_plots1[[3]],
+  test_plots1[[4]]
+)
+
+test_plots2 <- stats_table_plot_dat %>% 
+   map(
+    ~ ggplot(filter(.x, variable %in% c('foot', 'flu')),
+             aes(
+      x = year,
+      y = p,
+      group = strata,
+      color = strata
+    )) +
+      #geom_point() +
+      geom_line(aes(x = year, y = model , group = strata, color = strata)) +
+      geom_line(data = filter(overall_data, variable %in% c('foot', 'flu')),
+                  aes(x = year, y = model ),
+                  color = 'black',
+                  linetype = 'dashed') +
+      facet_wrap( ~ variable_text, ncol = 3) +
+      theme_classic() +
+      scale_y_continuous(
+        limits = c(00, 100),
+        breaks = seq(0, 100, 25),
+        labels = seq(0, 100, 25)
+      ) +
+      scale_x_continuous(
+        limits = c(2008, 2020),
+        breaks = seq(2008, 2020, 2),
+        labels = seq(2008, 2020, 2)
+      ) +
+      scale_color_brewer(type = 'qual', palette = 'Set2') +
+      theme(axis.text = element_text(color = 'black'),
+            axis.text.x = element_text(angle = 45, hjust = 0.9, vjust = 0.95),
+            legend.title = element_text(size = 8),
+            legend.text = element_text(size = 6)) +
+      labs(x = 'Year', y = 'Percentage')
+  )
+
+test_plots2[[1]] <- test_plots2[[1]] + labs(color = 'Age (grouped)') +
+  theme(axis.title.x = element_blank())
+test_plots2[[2]] <-
+  test_plots2[[2]] + labs(color = 'Highest degree \nobtained') + theme(
+    strip.background =  element_blank(),
+    strip.text = element_blank(),
+    axis.title.x = element_blank()
+  )
+test_plots2[[3]] <-
+  test_plots2[[3]] + labs(color = "Insurance") + theme(
+    strip.background =  element_blank(),
+    strip.text = element_blank(),
+    axis.title.x = element_blank()
+  )
+test_plots2[[4]] <-
+  test_plots2[[4]] + labs(color = 'Poverty income ratio') + theme(
+    strip.background =  element_blank(),
+    strip.text = element_blank()
+  )
+test_plots2[[5]] <-
+  test_plots2[[5]] + labs(color = 'Race & Ethnicity') + theme(
+    strip.background =  element_blank(),
+    strip.text = element_blank(),
+    axis.title.x = element_blank()
+  )
+test_plots2[[6]] <-
+  test_plots2[[6]] + labs(color = 'Sex') + theme(strip.background =  element_blank(),
+                                                strip.text = element_blank(),
+    axis.title.x = element_blank())
+test_plots2 <- list(
+  test_plots2[[1]],
+  test_plots2[[6]],
+  test_plots2[[5]],
+  test_plots2[[2]],
+  test_plots2[[3]],
+  test_plots2[[4]]
+)
+
+exam_plots1 <- stats_table_plot_dat %>% 
+   map(
+    ~ ggplot(filter(.x, variable %!in% c('a1c', 'CHOL_all', 'flu', 'foot')),
+             aes(
+      x = year,
+      y = p,
+      group = strata,
+      color = strata
+    )) +
+      #geom_point() +
+      geom_line(aes(x = year, y = model, group = strata, color = strata)) +
+      geom_line(data = filter(overall_data, variable %!in% c('a1c', 'CHOL_all', 'flu', 'foot')),
+                  aes(x = year, y = model),
+                  color = 'black',
+                  linetype = 'dashed') +
+      facet_wrap( ~ variable_text, ncol = 3) +
+      theme_classic() +
+      scale_y_continuous(
+        limits = c(  0, 100),
+        breaks = seq(0, 100, 25),
+        labels = seq(0, 100, 25)
+      ) +
+      scale_x_continuous(
+        limits = c(2008, 2020),
+        breaks = seq(2008, 2020, 2),
+        labels = seq(2008, 2020, 2)
+      ) +
+      scale_color_brewer(type = 'qual', palette = 'Set2') +
+      theme(axis.text = element_text(color = 'black'),
+            axis.text.x = element_text(angle = 45, hjust = 0.9, vjust = 0.95),
+            legend.title = element_text(size = 8),
+            legend.text = element_text(size = 6)) +
+      labs(x = 'Year', y = 'Percentage')
+  )
+
+exam_plots1[[1]] <- exam_plots1[[1]] + labs(color = 'Age (grouped)') +
+  theme(axis.title.x = element_blank())
+exam_plots1[[2]] <-
+  exam_plots1[[2]] + labs(color = 'Highest degree \nobtained') + theme(
+    strip.background =  element_blank(),
+    strip.text = element_blank(),
+    axis.title.x = element_blank()
+  )
+exam_plots1[[3]] <-
+  exam_plots1[[3]] + labs(color = "Insurance") + theme(
+    strip.background =  element_blank(),
+    strip.text = element_blank(),
+    axis.title.x = element_blank()
+  )
+exam_plots1[[4]] <-
+  exam_plots1[[4]] + labs(color = 'Poverty income ratio') + theme(
+    strip.background =  element_blank(),
+    strip.text = element_blank()
+  )
+exam_plots1[[5]] <-
+  exam_plots1[[5]] + labs(color = 'Race & Ethnicity') + theme(
+    strip.background =  element_blank(),
+    strip.text = element_blank(),
+    axis.title.x = element_blank()
+  )
+exam_plots1[[6]] <-
+  exam_plots1[[6]] + labs(color = 'Sex') + theme(strip.background =  element_blank(),
+                                                strip.text = element_blank(),
+    axis.title.x = element_blank())
+exam_plots1 <- list(
+  exam_plots1[[1]],
+  exam_plots1[[6]],
+  exam_plots1[[5]],
+  exam_plots1[[2]],
+  exam_plots1[[3]],
+  exam_plots1[[4]]
+)
+```
+
+```{r}
+#| fig-height: 9
+#| fig-width: 6
+(all_exam_plots1 <- exam_plots1 %>% 
   wrap_plots(nrow = 6) &
   theme(plot.margin = margin(0.5, 0.5, 0.5, 0.5, 'pt')))
-(all_test_plots <- test_plots %>% 
+```
+
+```{r}
+#| fig-height: 9
+#| fig-width: 6
+
+(all_test_plots1 <- test_plots1 %>% 
   wrap_plots(nrow = 6) &
   theme(plot.margin = margin(0.5, 0.5, 0.5, 0.5, 'pt')))
-ggsave(plot = all_exam_plots,
-       filename = 'figures/all_exam_plots.tiff',
-       dpi = 200)
-ggsave(plot = all_test_plots,
-       filename = 'figures/all_test_plots.tiff',
-       dpi = 200)
 ```
+
+```{r}
+#| fig-height: 9
+#| fig-width: 6
+
+(all_test_plots2 <- test_plots2 %>% 
+  wrap_plots(nrow = 6) &
+  theme(plot.margin = margin(0.5, 0.5, 0.5, 0.5, 'pt')))
+```

### 2023-01-19 _targets.R

@@ -15,7 +15,8 @@ options(clustermq.scheduler = 'multiprocess')
 # Set target options:
 tar_option_set(
   packages = c("tidyverse", "haven", 'sitrep', 'gtsummary', 'srvyr', 'dtplyr',
-               'nih.joinpoint'),
+               'nih.joinpoint', 'survey'),
+  debug = 'jp_regressions_proportions',
   # packages that your targets need to run
   format = "rds" # default storage format
   # Set other options as needed.
@@ -324,6 +325,7 @@ list(
         strata = VARSTR_all,
         nest = TRUE
       ) %>%
+      svystandardize(., ~ AGE_all, ~1, population = c(0.530535, 0.299194, 0.088967, 0.081304)) %>%
       createTableAllStats(., by = NULL, diab_list) %>%
       makeTablesLonger(),
     pattern = map(diab_list)
@@ -337,9 +339,9 @@ list(
         strata = VARSTR_all,
         nest = TRUE
       ) %>%
-      createTableAllStatsbyAge(., by = NULL, diab_list) %>%
-      makeTablesLongerbyAge() %>%
-      ageAdjustTables(),
+      svystandardize(., ~ AGE_all, ~1, population = c(0.530535, 0.299194, 0.088967, 0.081304)) %>%
+      createTableAllStats(., by = NULL, diab_list) %>%
+      makeTablesLonger(),
     pattern = map(diab_list)
   ),
   tar_target(
@@ -369,9 +371,9 @@ list(
         strata = VARSTR_all,
         nest = TRUE
       ) %>%
-      createTableAllStatsbyAge(., by = "SEX", diab_list) %>%
-      makeTablesLongerbyAge() %>%
-      ageAdjustTables(),
+      svystandardize(., ~ AGE_all, ~1, population = c(0.530535, 0.299194, 0.088967, 0.081304)) %>%
+      createTableAllStats(., by = "SEX", diab_list) %>%
+      makeTablesLonger(),
     pattern = map(diab_list)
     ),
   tar_target(sex_stats_joined,
@@ -399,9 +401,9 @@ list(
         strata = VARSTR_all,
         nest = TRUE
       ) %>%
-      createTableAllStatsbyAge(., by = "RACE_all", diab_list) %>%
-      makeTablesLongerbyAge() %>%
-      ageAdjustTables(),
+      svystandardize(., ~ AGE_all, ~1, population = c(0.530535, 0.299194, 0.088967, 0.081304)) %>%
[…]

### 2023-01-19 scripts/functions.R

@@ -1009,66 +1009,7 @@ cumulativePractices <- function(data) {
     select(-ends_with('bin'))
 }
 
-preventivePracticebyAge <- function(survey.object, by = NULL, data) {
-  if (is.null(by) || by != 'AGE_all'){
-  out_table <- tbl_strata(
-    survey.object,
-    strata = AGE_all,
-    .tbl_fun =
-      ~.x %>%
-      tbl_svysummary(
-        by = by,
-        digits = list(everything() ~ 12),
-        include = c(
-          zero_practices,
-          one_practices,
-          two_practices,
-          three_practices,
-          four_practices,
-          five_practices,
-          six_practices,
-          atleast_one_practices,
-          atleast_two_practices,
-          atleast_three_practices,
-          atleast_four_practices,
-          atleast_five_practices,
-          atleast_six_practices
-        ),
-        label = list(
-          zero_practices ~ "No preventive practices followed",
-          one_practices ~ "One preventive practice followed",
-          two_practices ~ "Two preventive practices followed",
-          three_practices ~ "Three preventive practices followed",
-          four_practices ~ "Four preventive practices followed",
-          five_practices ~ "Five preventive practices followed",
-          six_practices ~ "Six preventive practices followed",
-          atleast_one_practices ~ "At least one preventive practice followed",
-          atleast_two_practices ~ "At least two preventive practices followed",
-          atleast_three_practices ~ "At least three preventive practices followed",
-          atleast_four_practices ~ "At least four preventive practices followed",
-          atleast_five_practices ~ "At least five preventive practices followed",
-          atleast_six_practices ~ "At least six preventive practices followed"
-        ),
-        statistic = list(
-          all_categorical() ~ "{n}-{N}-{p}-{p.std.error}-{n_unweighted}-{N_unweighted}-{p_unweighted}"
-        )
-      )
-  )
-
-  out_table$table_body <- out_table$table_body %>%
-    mutate(
-      year = data$year[1]
-    )
-  if (is.null(by) == FALSE) {
-    names(out_table$table_body)[str_detect(names(out_table$table_body), pattern = 'stat')] <-
[…]

### 2023-03-30 scripts/manuscript/graveyard.qmd
Should probably commit before doing more edits

---
title: "text graveyard"
format: html
---

For the entire population of adults diagnosed with diabetes in the US there was a significant percent decrease of `r pullNumber(tab1, '-', 'Percent Change (95% CI)')` of people receiving at least three of the recommended practices from 2008 to 2020 (Table 1). The percent change observed among subgroups were either decreasing or showed no change (the 95% confidence intervals for percent change overlap with zero) (Table 1). The largest negative percent change was in the income poverty ratio group between 100% and 199% at `r pullNumber(tab1, '100% - 199%', 'Percent Change (95% CI)')`. There was also a `r pullNumber(tab1, '200% - 399%', 'Percent Change (95% CI)')` percent change in the income poverty ratio group between 200% and 399% and a `r pullNumber(tab1, 'Less than high school', 'Percent Change (95% CI)')` percent change seen in those with no high school diploma (Table 1). Other groups that had significant percent decreases include a `r pullNumber(tab1, '45 to 64', 'Percent Change (95% CI)')` percent change in adults aged 45 to 64, a `r pullNumber(tab1, 'Female', 'Percent Change (95% CI)')` percent change for adult females, a `r pullNumber(tab1, 'Any private', 'Percent Change (95% CI)')` percent change for adults with any private insurance, and a `r pullNumber(tab1, 'Public only', 'Percent Change (95% CI)')` percent change for adults with only public insurance.

## Trends in ≥ 3 preventive care practices received

Overall, we observed no statistically significant percent change of adults receiving three or more recommended preventive care practices between 2008 and 2019 (`r pullNumber(tab_sans_2020, '-', 'Percent Change (95% CI)', brackets = TRUE)`) (Table 1). Few groups exhibited significant changes in this trend over the same time period (Table 1). For adults age 75 and older, the percentage receiving three or more of the recommended care practices was flat from 2008 to 2014 (APC `r pullNumber(tab_sans_2020, '75+', 'APC Period 1 (95% CI)', brackets = T)`), and after 2015 was decreasing (APC `r pullNumber(tab_sans_2020, '75+', 'APC Period 2 (95% CI)', brackets = T)`). Adults with less than a high school education had a flat trend until 2012, which was followed by an APC in the second period of `r pullNumber(tab_sans_2020, 'Less than high school', 'APC Period 2 (95% CI)', brackets = F)`.

Both males and females showed decreasing percentages of adults receiving three or more recommended preventive care practices. The AAPC for females was `r pullNumber(tab_sans_2020, 'Female', 'APC Period 1 (95% CI)', brackets = F)` over the entire period, whereas the trend for males was flat until 2015, at which point it began to decrease (APC `r pullNumber(tab_sans_2020, 'Male', 'APC Period 2 (95% CI)', brackets = T)`). Among the insurance groups, there were no significant change with the exception of Medicaid, which showed an overall decline in percentage of adults receiving three or more practices (AAPC `r pullNumber(tab_sans_2020, 'Medicaid', 'APC Period 1 (95% CI)', brackets = F)`). The percentage of adults in the highest earning group receiving three or more recommended care practices increased annually by `r pullNumber(tab_sans_2020, '> 400%', 'APC Period 1 (95% CI)', brackets = F)` and was flat after 2010 (`r pullNumber(tab_sans_2020, '> 400%', 'APC Period 2 (95% CI)', brackets = T)`). Adults earning just above the poverty line that received three or more of the recommended practices changed by `r pullNumber(tab_sans_2020, '100% - 199%', 'APC Period 1 (95% CI)', brackets = F)`. Estimated proportions tended to be lower in 2020 than in 2019 for most groups, except Black/Not Hispanic, males, and the uninsured.

## Trends for each preventive care practice

@fig-exams and @fig-tests show the trends for individual preventive care practices and indicate which trends were significantly increasing or decreasing, or had segments that were significantly increasing or decreasing. Estimates plotted in @fig-exams can be found in the table in Appendix 1. Trends for all adults with diabetes receiving a foot examination  decreased starting in 2011 (@fig-exams). The percent of adults getting a flu vaccine increased until 2013 then began to decrease (@fig-tests). The shape of the trends in subgroups tend to mirror the overall trend for each practice, although the year at which trend values change may differ among these subgroups. The trend in some subgroups for each preventive practice do not always follow the shape of the overall trend, however. For example, the overall trend in the percentage of adults with diabetes receiving an eye examination with dilation was flat over 2008 to 2019. Within the income poverty ratio subgroups, only those in the highest poverty income ratio group (\> 400%) deviate from this flat trend by first increasing, then decreasing starting in 2013 (@fig-exams). Different groups exhibit different amounts of variation among the categories in each group. For example, the trends for all six practices split by sex tend to be very similar, whereas the gaps between the different insurance group trends are larger.

### 2023-03-30 scripts/manuscript/manuscript_draft.qmd
Should probably commit before doing more edits

--- 2022-12-29 scripts/manuscript/manuscript_draft.qmd
@@
 ---
-title: "Trends in Preventive Care Practices among US Adults with Diabetes, 2008-2020 "
-format: docx
-editor: visual
+title: ""
+format: 
+  docx:
+    page-width: 10
+    reference-doc: template.docx
+editor: source
 bibliography: references.bib
 csl: ama.csl
+execute:
+  echo: false
+  warning: false
+project: 
+  execute-dir: project
+crossref: 
+  fig-title: Fig
+filters:
+  - docx-landscape.lua
 ---
@@
 library(gt)
+# https://www2.census.gov/programs-surveys/acs/tech_docs/accuracy/percchg.pdf
+# https://blog.analytics-toolkit.com/2018/confidence-intervals-p-values-percent-change-relative-difference/
+# For calculating significance of percent change
+# Use to get citations for packages
+library(grateful)
+# To just make a bibtex file
+# get_pkgs_info(pkgs = c('gtsummary', 'patchwork', 'gt', 'gtsummary'))
+ggplot2::theme_update(text = element_text(family = 'Arial')) # I think this sets default plot font to Arial. May also try
+# family = sans
 
@@
 
+specifyDecimal <- function(x, digits) trimws(format(round(x, digits), nsmall=digits))
+
+# For pulling specifically from the preventive table since the column name I use is
+# weird and doesn't like being bang-bang-banged.
+pullNumber <- function(data, filter.by, column, brackets = FALSE) {
+  out <- data %>% 
+    filter(` ` == filter.by) %>% 
+    select(!!!column) %>% 
+    pull() 
+  out <- gsub("\\(", "(95% CI: ", out)
+  if (brackets == TRUE) {
+    out <- out %>% 
+    str_replace("\\(", "\\[") %>% 
+    str_replace("\\)", "\\]")
+  }
+  out
+}
+# For other tables that don't use such weird column names
+pullNumber2 <- function(data, filter.column, filter.by, select.column) {
+    data %>% 
+    filter(!!!filter.column == filter.by) %>% 
+    select(!!!column) %>% 
+    pull()
+}
+
+# Some numbers pulled from MEPS page:
+sample_size_response_rate <- tibble(
+  year = 2020:2008,
+  n = c(26847, 27648, 29415, 30716, 33259, 33893, 33162, 35068, 37182, 33622, 31228, 34920, 31262),
+  full_year_response = c(27.6, 39.5, 42.7, 44.2, 46.0, 47.7, 48.5, 52.8, 56.3, 54.9, 53.5, 57.2, 59.3)
+)
+
 ```
 
-**Trends in Preventive Care Practices among US Adults with Diabetes, 2008-2020**
+```{r preventive-table}
 
-Jacob T. Wittman, PhD Kai M. Bullard Stephen R. Benoit
-
-CDC Affiliation
-
-\pagebreak
-
-# Abstract
-
-\pagebreak
-
-# Introduction
-
--   Diabetes affects a lot of people
-    -   Kills people, makes them sick, reduces quality of life
-    -   Cost of management is high and increasing
--   Advances in diabetes management
-    -   Patients with diabetes must actually receive this care
--   Present trends in self-reported receipt of preventive care practices according to MEPS from 2008 - 2020.
-
-Diabetes is a chronic disease that affects XX people in the USA.
-
-# Methods
-
-## Data Source
-
-We used data from the Medical Expenditure Panel Survey (MEPS) from years 2008 - 2020.
-Participants in this survey are a subsample of households that participate in the National Health Interview Survey (NHIS).
-The MEP survey targets the civilian noninstitutionalized population in the US and provides national and regional estimates of health care use, expenditures, sources of payment and health insurance coverage.
-This survey also contains information on patient demographics, socioeconomics, and, via the Diabetes Care Survey (DCS), information on diabetes preventive care practices.
-The DCS is a self-administered paper-and-pencil questionnaire that is provided to MEPS respondents who indicate that they have been told by a doctor or health professional that they have diabetes.
-
-The data we used comes from the full-year consolidated file from MEPS for the 12 year time span of our report.
-We used a weighted population of XXX in this analysis.
-Our analysis is adjusted for the complex survey design, including clustering and stratification.
-Reported values for the proportions of different groups receiving recommended preventive care practices are age-adjusted.
-
-# Results
-
-# Discussion
-
-# References
-
-::: {#refs}
-:::
-
-# Tables
-
-```{r}
-# tar_load(age_adjusted_stats)
-# age_adjusted_stats %>% 
-#   #filter(stratifier != 'age') %>% 
-#   mutate(age_adjusted_prop = age_adjusted_prop * 100) %>% 
-#   pivot_wider(
-#     id_cols = c(stratifier, variable, var_label, strata),
-#     names_from = year,
-#     values_from = age_adjusted_prop
-#   ) %>% 
-#   group_by(stratifier, strata) %>%
-#   select(stratifier, var_label, `2008`:`2020`) %>%
-#   gt() %>% 
-#   fmt_number(columns = `2008`:`2020`, decimals = 1) %>% 
-#   gtsave('table_one.docx')
-```
-
-```{r}
-tar_load(age_adjusted_preventive)
-preventive_practice_table <- age_adjusted_preventive %>% 
-  filter(label == 'At least three preventive practices followed') %>% 
-  mutate(age_adjusted_prop = age_adjusted_prop * 100) %>% 
-  pivot_wider(
-    id_cols = c(stratifier, variable, label, strata),
-    names_from = year,
-    values_from = age_adjusted_prop
-  ) %>% 
-  filter(strata %!in% c('Not available', 'Other Race/Not Hispanic')) %>% 
-  mutate(stratifier = factor(stratifier,
-                             c('overall', 'age', 'sex', 'race', 'edu', 'insurance', 'poverty')),
-         strata = case_when(strata == 'stat_0' ~ '-', 
-                            strata == 'Greater than HS' ~ 'Greater than high school',
-                            TRUE ~ strata)) %>% 
-  mutate(strata = as.factor(strata)) %>% 
-  mutate(stratifier = recode_factor(
-    stratifier,
-    overall = 'Overall',
-    age = 'Age',
-    sex = 'Sex',
-    race = 'Race/Ethnicity',
-    edu = 'Highest degree earned',
-    insurance = 'Insurance coverage',
-    poverty = 'Poverty level'
-  )) %>% 
-  group_by(stratifier) %>%
-  select(stratifier, strata, `2008`:`2020`) %>%
-  gt() %>% 
-  fmt_number(columns = `2008`:`2020`, decimals = 1)
-preventive_practice_table$`_data` <- preventive_practice_table$`_data`[c(1:18, 20, 19, 21), ]
-preventive_practice_table %>% 
-  gtsave('preventive_practices.docx')
-```
-
-```{r}
+tar_load(c(jp_prevention_apc,
+           jp_prevention_aapc,
+           age_adjusted_preventive,
+           jp_proportion_plot_data,
+           age_adjusted_stats
+           ),
+         store = here::here('_targets/'))
 # Clean up the AAPC table and get it into format for printing to table
@@
   select(-aapc_index) %>% 
-  mutate(across(starts_with('aapc'),
-                ~sigfig(.x, digits = 2)),
+  mutate(aapc = specifyDecimal(aapc, digits = 1),
+        across(starts_with('aapc_'),
+                ~specifyDecimal(x = .x, digits = 1)),
          across(starts_with('aapc'),
@@
   ) %>% 
-  select(-segment_start_0, -segment_start_1, -segment_end_1) %>% 
+  select(-segment_start_0, -segment_start_1, -segment_end_1, -apc_significant_0, -apc_significant_1) %>% 
   # Make segment empty if no joinpoint
@@
                             TRUE ~ .x)),
+         across(starts_with('apc_0') | starts_with('apc_1') | starts_with('p_'),
+                ~specifyDecimal(.x, digits = 1)),
+         across(contains('cl'),
+                ~specifyDecimal(.x, digits = 1)),
          across(starts_with('apc') | starts_with('p_'),
-                ~sigfig(.x, digits = 2)),
-         across(starts_with('apc') | starts_with('p_'),
-                ~case_when(.x == ' NA' ~ NA_character_,
+                ~case_when(.x == 'NA' ~ NA_character_,
                            TRUE ~ .x))) %>% 
@@
   # Filter to just the >=3 practices
-  filter(label == 'At least three preventive practices followed') %>% 
+  filter(variable == 'zero_practices') %>% 
   # Filter down to every other year
-  filter(year %in% seq(2000, 2020, by = 2)) %>% 
-  mutate(age_adjusted_prop = age_adjusted_prop * 100,
-         chr_age_adj_prop = sigfig(age_adjusted_prop, digits = 4),
-         age_adjusted_se_perc = sigfig(age_adjusted_se_perc, digits = 2),
+  filter(year %in% seq(2000, 2020, by = 1)) %>% 
+  mutate(chr_age_adj_prop = sigfig(p, digits = 3),
+         p.std.error = p.std.error * 100,
+         age_adjusted_se_perc = sigfig(p.std.error, digits = 2),
          percentage = glue::glue('{chr_age_adj_prop} ({age_adjusted_se_perc})')) %>% 
@@
     names_from = year,
-    values_from = c(age_adjusted_prop, percentage),
+    values_from = c(p, percentage, p.std.error),
   ) %>% 
@@
                             TRUE ~ strata),
-         `Percent Change` = sigfig(((age_adjusted_prop_2020 - age_adjusted_prop_2008) / age_adjusted_prop_2008) * 100, digits = 4)) %>% 
-  select(-starts_with('age_adjusted_prop')) %>% 
+         percent_change = ((p_2020 - p_2008) / p_2008) * 100,
+         percent_change_se = (abs(p_2020 / p_2008) * sqrt((p.std.error_2020^2 / p_2020^2) + (p.std.error_2008^2 / p_2008^2)) * 100),
+         perc_change_lcl = percent_change - 1.96 * percent_change_se,
+         perc_change_ucl = percent_change + 1.96 * percent_change_se,
+         perc_change_char = specifyDecimal(percent_change, digits = 1),
+         perc_change_lcl_char = specifyDecimal(perc_change_lcl, digits = 1),
+         perc_change_ucl_char = specifyDecimal(perc_change_ucl, digits = 1),
+         `Percent Change (95% CI)` = glue::glue('{perc_change_char} ({perc_change_lcl_char}, {perc_change_ucl_char})')) %>% 
+  select(-starts_with('age_adjusted_prop'), -starts_with('p.std.error'), -contains('_change_')) %>% 
   setNames(., str_replace(names(.), 'percentage_', "")) %>% 
@@
 
+# Rename strata to a blank name to remove it from the final table
 preventive_practice_table <- cleaned_preventive_df %>% 
+  filter(strata != 'Other') %>% 
   group_by(stratifier) %>%
-  select(stratifier, strata, `2008`:`2020`, `Percent Change`, `Joinpoint Year` = segment,
+  select(stratifier, ` ` = strata, `2008`:`2020`, `Percent Change (95% CI)`, `Joinpoint Year` = segment,
          `APC Period 1`, `APC Period 2`, `AAPC`) %>%
-  mutate(stratifier = case_when(as.character(stratifier) == 'Poverty level' ~ 'Income as % of poverty line',
+  mutate(stratifier = case_when(as.character(stratifier) == 'Poverty level' ~ 'Poverty income ratio',
                                 TRUE ~ as.character(stratifier))) %>% 
+  # Rename some columns to add () info
+  rename(`2008 (SE)` = `2008`,
+         `2009 (SE)` = `2009`,
+         `2010 (SE)` = `2010`,
+         `2011 (SE)` = `2011`,
+         `2012 (SE)` = `2012`,
+         `2013 (SE)` = `2013`,
+         `2014 (SE)` = `2014`,
+         `2015 (SE)` = `2015`,
+         `2016 (SE)` = `2016`,
+         `2017 (SE)` = `2017`,
+         `2018 (SE)` = `2018`,
+         `2019 (SE)` = `2019`,
+         `2020 (SE)` = `2020`,
+         `APC Period 1 (95% CI)` = `APC Period 1`,
+         `APC Period 2 (95% CI)` = `APC Period 2`,
+         `AAPC (95% CI)` = `AAPC`) %>% 
   gt() %>% 
   sub_missing(missing_text = ' ')
-preventive_practice_table$`_data` <- preventive_practice_table$`_data`[c(1:18, 20, 19, 21), ]
-preventive_practice_table %>% 
-  gtsave('preventive_practices.docx')
+
+# Reorganize insurance variables
+preventive_practice_table$`_data` <- preventive_practice_table$`_data`[c(1:14, 15, 18, 16, 17, 19:22), ]
+tab1 <- preventive_practice_table$`_data`
 ```
 
-# Figures
+```{r preventive-table-sans-2020}
+tar_load(ends_with('sans_2020'),
+         store = here::here('_targets/'))
+# Clean up the AAPC table and get it into format for printing to table
+cleaned_jp_aapc_sans_2020 <- jp_prevention_aapc_sans_2020 %>% 
+  select(-aapc_index) %>% 
+  mutate(aapc = specifyDecimal(aapc, digits = 1),
+        across(starts_with('aapc_'),
+                ~specifyDecimal(x = .x, digits = 1)),
+         across(starts_with('aapc'),
+                ~case_when(.x == ' NA' ~ NA_character_,
+                           TRUE ~ .x)),
+         AAPC = case_when(!is.na(aapc) ~ glue::glue('{aapc} ({aapc_c_i_low}, {aapc_c_i_high})'),
+                          TRUE ~ NA_character_)) %>%
+  select(stratifier, strata, AAPC)
 
-```{r}
-tar_load(age_adjusted_stats)
-tar_load(jp_proportion_plot_data)
+# Format APC table for future joining
+cleaned_jp_apc_sans_2020 <- jp_prevention_apc_sans_2020 %>% 
+  # No model has more than a single joinpoint, so make wider and then
+  # remove the excess columns to determine if there's no join point (segmend_end = 2020)
+  # or a joinpoint (segment_end != 2019)
+  pivot_wider(id_cols = c(stratifier, strata, model),
+              names_from = segment,
+              values_from = c(segment_start, segment_end, apc, p_value, apc_significant,
+                              apc_95_lcl, apc_95_ucl)
+  ) %>% 
+  select(-segment_start_0, -segment_start_1, -segment_end_1, -apc_significant_0, -apc_significant_1) %>% 
+  # Make segment empty if no joinpoint
+  mutate(segment = case_when(segment_end_0 == 2019 ~ NA_integer_,
+                             TRUE ~ segment_end_0)) %>% 
+  # MAke apc empty if not significant
+  mutate(across(c(apc_0, apc_95_lcl_0, apc_95_ucl_0),
+                ~ case_when(p_value_0 > 0.05 & p_value_1 > 0.05 ~ NA_real_,
+                            TRUE ~ .x)), 
+         across(c(apc_1, apc_95_lcl_1, apc_95_ucl_1),
+                ~ case_when(p_value_0 > 0.05 & p_value_1 > 0.05 ~ NA_real_,
+                            TRUE ~ .x)),
+         across(starts_with('apc_0') | starts_with('apc_1') | starts_with('p_'),
+                ~specifyDecimal(.x, digits = 1)),
+         across(contains('cl'),
+                ~specifyDecimal(.x, digits = 1)),
+         across(starts_with('apc') | starts_with('p_'),
+                ~case_when(.x == 'NA' ~ NA_character_,
+                           TRUE ~ .x))) %>% 
+  # Concatenate apc column with CI columns
+  mutate(`APC Period 1` = case_when(
+       !is.na(apc_0) ~ glue::glue('{apc_0} ({apc_95_lcl_0}, {apc_95_ucl_0})'),
+       TRUE ~ NA_character_
+                                    ),
+    `APC Period 2` = case_when(
+       !is.na(apc_1) ~ glue::glue('{apc_1} ({apc_95_lcl_1}, {apc_95_ucl_1})'),
+       TRUE ~ NA_character_
+    )
+  ) %>%
+  select(stratifier, strata, segment, starts_with('APC '))
+
+# Clean up the age adjusted preventive practices and then join with the aapc table
+clean_age_adjusted <- age_adjusted_preventive %>% 
+  # Filter to just the >=3 practices
+  filter(variable == 'zero_practices') %>% 
+  # Filter down to every other year
+  filter(year %in% seq(2000, 2020, by = 1)) %>% 
+  mutate(chr_age_adj_prop = specifyDecimal(p, digits = 1),
+         p.std.error = p.std.error * 100,
+         age_adjusted_se_perc = specifyDecimal(p.std.error, digits = 1),
+         percentage = glue::glue('{chr_age_adj_prop} ({age_adjusted_se_perc})')) %>% 
+  pivot_wider(
+    id_cols = c(stratifier, variable, label, strata),
+    names_from = year,
+    values_from = c(p, percentage, p.std.error),
+  ) %>% 
+  # Remove excess strata
+  filter(strata %!in% c('Not available', 'Other Race/Not Hispanic')) %>% 
+  # Relevel stratifier factor, clean up stratifier and strata names
+  mutate(stratifier = factor(stratifier,
+                             c('overall', 'age', 'sex', 'race', 'edu', 'insurance', 'poverty')),
+         strata = case_when(strata == 'stat_0' ~ '-', 
+                            strata == 'Greater than HS' ~ 'Greater than high school',
+                            TRUE ~ strata),
+         percent_change = ((p_2019 - p_2008) / p_2008) * 100,
+         percent_change_se = (abs(p_2019 / p_2008) * sqrt((p.std.error_2019^2 / p_2019^2) + (p.std.error_2008^2 / p_2008^2)) * 100),
+         perc_change_lcl = percent_change - 1.96 * percent_change_se,
+         perc_change_ucl = percent_change + 1.96 * percent_change_se,
+         perc_change_char = specifyDecimal(percent_change, digits = 1),
+         perc_change_lcl_char = specifyDecimal(perc_change_lcl, digits = 1),
+         perc_change_ucl_char = specifyDecimal(perc_change_ucl, digits = 1),
+         `Percent Change (95% CI)` = glue::glue('{perc_change_char} ({perc_change_lcl_char}, {perc_change_ucl_char})')) %>% 
+  select(-starts_with('age_adjusted_prop'), -starts_with('p.std.error'), -contains('_change_')) %>% 
+  setNames(., str_replace(names(.), 'percentage_', "")) %>% 
+  mutate(strata = as.factor(strata)) %>% 
+  mutate(stratifier = recode_factor(
+    stratifier,
+    overall = 'Overall',
+    age = 'Age',
+    sex = 'Sex',
+    race = 'Race/Ethnicity',
+    edu = 'Highest degree earned',
+    insurance = 'Insurance coverage',
+    poverty = 'Poverty level'
+  )) %>% 
+  # Join with AAPC table
+  left_join(cleaned_jp_aapc_sans_2020, by = c('stratifier', 'strata'))
+
+cleaned_preventive_df_sans_2020 <- left_join(clean_age_adjusted, cleaned_jp_apc_sans_2020, by = c('stratifier', 'strata')) %>% 
+  mutate(AAPC = case_when(is.na(AAPC) & is.na(`APC Period 2`) ~ `APC Period 1`,
+                          TRUE ~ AAPC),
+         `APC Period 1` = case_when(is.na(`APC Period 1`) & is.na(`APC Period 2`) ~ AAPC,
+                                    TRUE ~ `APC Period 1`)) %>%
+  # Rename poverty levels
+  mutate(strata = case_when(as.character(strata) == 'Poor/Negative' ~ '< 100%',
+                            as.character(strata) == 'Low income' ~ '100% - 199%',
+                            as.character(strata) == 'Middle income' ~ '200% - 399%',
+                            as.character(strata) == 'High income' ~ '> 400%',
+                            TRUE ~ as.character(strata)))
+
+# Rename strata to a blank name to remove it from the final table
+preventive_practice_table_sans_2020 <- cleaned_preventive_df_sans_2020 %>% 
+  filter(strata != 'Other') %>% 
+  group_by(stratifier) %>%
+  select(stratifier, ` ` = strata, `2008`:`2020`, `Percent Change (95% CI)`, `Joinpoint Year` = segment,
+         `APC Period 1`, `APC Period 2`, `AAPC`) %>%
+  mutate(stratifier = case_when(as.character(stratifier) == 'Poverty level' ~ 'Poverty income ratio',
+                                TRUE ~ as.character(stratifier))) %>% 
+  # Rename some columns to add () info
+  rename(`2008 (SE)` = `2008`,
+         `2009 (SE)` = `2009`,
+         `2010 (SE)` = `2010`,
+         `2011 (SE)` = `2011`,
+         `2012 (SE)` = `2012`,
+         `2013 (SE)` = `2013`,
+         `2014 (SE)` = `2014`,
+         `2015 (SE)` = `2015`,
+         `2016 (SE)` = `2016`,
+         `2017 (SE)` = `2017`,
+         `2018 (SE)` = `2018`,
+         `2019 (SE)` = `2019`,
+         `2020 (SE)` = `2020`,
+         `APC Period 1 (95% CI)` = `APC Period 1`,
+         `APC Period 2 (95% CI)` = `APC Period 2`,
+         `AAPC (95% CI)` = `AAPC`) %>% 
+  gt() %>% 
+  sub_missing(missing_text = ' ') %>% 
+  tab_footnote(
+    footnote = "Values in these columns were estimated excluding data from 2020.",
+    locations = cells_column_labels(
+      columns = c(`Percent Change (95% CI)`,
+      `APC Period 1 (95% CI)`,
+      `APC Period 2 (95% CI)`,
+      `AAPC (95% CI)`
+    ))
+  ) %>% 
+  tab_options(footnotes.marks = "a")
+# Reorganize insurance variables
+ preventive_practice_table_sans_2020$`_data` <- preventive_practice_table_sans_2020$`_data`[c(1:14, 15, 18, 16, 17, 19:22), ]
+
+tab_sans_2020 <- preventive_practice_table_sans_2020$`_data`
+
+```
+
+```{r proportion-table-sans-2020}
+# Clean up the AAPC table and get it into format for printing to table
+cleaned_prop_aapc_sans_2020 <- jp_proportion_aapc_sans_2020 %>% 
+  select(-aapc_index) %>% 
+  mutate(aapc = specifyDecimal(aapc, digits = 1),
+        across(starts_with('aapc_'),
+                ~specifyDecimal(x = .x, digits = 1)),
+         across(starts_with('aapc'),
+                ~case_when(.x == ' NA' ~ NA_character_,
+                           TRUE ~ .x)),
+         AAPC = case_when(!is.na(aapc) ~ glue::glue('{aapc} ({aapc_c_i_low}, {aapc_c_i_high})'),
+                          TRUE ~ NA_character_)) %>%
+  select(stratifier, strata, practice, AAPC)
+
+# Format APC table for future joining
+cleaned_prop_apc_sans_2020 <- jp_proportion_apc_sans_2020 %>% 
+  # No model has more than a single joinpoint, so make wider and then
+  # remove the excess columns to determine if there's no join point (segmend_end = 2020)
+  # or a joinpoint (segment_end != 2019)
+  pivot_wider(id_cols = c(stratifier, strata, practice, model),
+              names_from = segment,
+              values_from = c(segment_start, segment_end, apc, p_value, apc_significant,
+                              apc_95_lcl, apc_95_ucl)
+  ) %>% 
+  mutate(
+    across(
+      c(apc_0, apc_95_lcl_0, apc_95_ucl_0),
+      ~ case_when(p_value_0 > 0.05 &
+                    p_value_1 > 0.05 & p_value_2 > 0.05 & p_value_3 > 0.05 ~ NA_real_,
+                  TRUE ~ .x)
+    ),
+    across(
+      c(apc_1, apc_95_lcl_1, apc_95_ucl_1),
+      ~ case_when(p_value_0 > 0.05 &
+                    p_value_1 > 0.05 & p_value_2 > 0.05 & p_value_3 > 0.05 ~ NA_real_,
+                  TRUE ~ .x)
+    ),
+    across(
+      c(apc_2, apc_95_lcl_2, apc_95_ucl_2),
+      ~ case_when(p_value_0 > 0.05 &
+                    p_value_1 > 0.05 & p_value_2 > 0.05 & p_value_3 > 0.05 ~ NA_real_,
+                  TRUE ~ .x)
+    ),
+    across(
+      c(apc_3, apc_95_lcl_3, apc_95_ucl_3),
+      ~ case_when(p_value_0 > 0.05 &
+                    p_value_1 > 0.05 & p_value_2 > 0.05 & p_value_3 > 0.05 ~ NA_real_,
+                  TRUE ~ .x)
+    ),
+    across(
+      matches('apc_[0-9]{1}') | starts_with('p_'),
+      ~ specifyDecimal(.x, digits = 1)
+    )
+  ) %>% 
+    select(-contains('significant')) %>% 
+    mutate(across(starts_with('apc') | starts_with('p_'),
+                ~case_when(.x == 'NA' ~ NA_character_,
+                           TRUE ~ .x))) %>% 
+  # Concatenate apc column with CI columns
+  mutate(`APC Period 1` = case_when(
+       !is.na(apc_0) ~ glue::glue('{apc_0} ({apc_95_lcl_0}, {apc_95_ucl_0})'),
+       TRUE ~ NA_character_
+                                    ),
+    `APC Period 2` = case_when(
+       !is.na(apc_1) ~ glue::glue('{apc_1} ({apc_95_lcl_1}, {apc_95_ucl_1})'),
+       TRUE ~ NA_character_
+    ),
+    `APC Period 3` = case_when(
+       !is.na(apc_2) ~ glue::glue('{apc_2} ({apc_95_lcl_2}, {apc_95_ucl_2})'),
+       TRUE ~ NA_character_
+    )
+  ) %>%
+    # Make segment empty if no joinpoint
+  mutate(segment = ifelse(!is.na(segment_start_1) & !is.na(segment_start_2) & !is.na(segment_start_3), 
+                             paste(segment_start_1, segment_start_2, segment_start_3, sep = ", "),
+                             ifelse(!is.na(segment_start_1) & !is.na(segment_start_2) & is.na(segment_start_3),
+                                    paste(segment_start_1, segment_start_2, sep = ", "),
+                                    ifelse(!is.na(segment_start_1) & is.na(segment_start_2) & is.na(segment_start_3),
+                                           segment_start_1,
+                                           ifelse(segment_end_0 == 2019, NA_character_, 'Check me')
+                                           )
+                                    )
+                             )
+         ) %>% 
+  # MAke apc empty if not significant
+  select(stratifier, strata, practice, segment, starts_with('APC '), -segment_start_0, -segment_start_1, -segment_end_1)
+
+# Clean up the age adjusted preventive practices and then join with the aapc table
+clean_age_adjusted_prop <- age_adjusted_stats %>% 
+  # Filter to just the >=3 practices
+  #filter(label == 'At least three preventive practices followed') %>% 
+  # Filter down to every other year
+  filter(year %in% seq(2000, 2020, by = 1)) %>% 
+  mutate(chr_age_adj_prop = specifyDecimal(p, digits = 1),
+         p.std.error = p.std.error * 100,
+         age_adjusted_se_perc = specifyDecimal(p.std.error, digits = 1),
+         percentage = glue::glue('{chr_age_adj_prop} ({age_adjusted_se_perc})')) %>% 
+  pivot_wider(
+    id_cols = c(stratifier, variable, label, strata),
+    names_from = year,
+    values_from = c(p, percentage, p.std.error),
+  ) %>% 
+  # Remove excess strata
+  filter(strata %!in% c('Not available', 'Other Race/Not Hispanic')) %>% 
+  # Relevel stratifier factor, clean up stratifier and strata names
+  mutate(stratifier = factor(stratifier,
+                             c('overall', 'age', 'sex', 'race', 'edu', 'insurance', 'poverty')),
+         strata = case_when(strata == 'stat_0' ~ '-', 
+                            strata == 'Greater than HS' ~ 'Greater than high school',
+                            TRUE ~ strata),
+         percent_change = ((p_2019 - p_2008) / p_2008) * 100,
+         percent_change_se = (abs(p_2019 / p_2008) * sqrt((p.std.error_2019^2 / p_2019^2) + (p.std.error_2008^2 / p_2008^2)) * 100),
+         perc_change_lcl = percent_change - 1.96 * percent_change_se,
+         perc_change_ucl = percent_change + 1.96 * percent_change_se,
+         perc_change_char = specifyDecimal(percent_change, digits = 1),
+         perc_change_lcl_char = specifyDecimal(perc_change_lcl, digits = 1),
+         perc_change_ucl_char = specifyDecimal(perc_change_ucl, digits = 1),
+         `Percent Change (95% CI)` = glue::glue('{perc_change_char} ({perc_change_lcl_char}, {perc_change_ucl_char})')) %>% 
+  select(-starts_with('age_adjusted_prop'), -starts_with('p.std.error'), -contains('_change_')) %>% 
+  setNames(., str_replace(names(.), 'percentage_', "")) %>% 
+  mutate(strata = as.factor(strata)) %>% 
+  mutate(stratifier = recode_factor(
+    stratifier,
+    overall = 'Overall',
+    age = 'Age',
+    sex = 'Sex',
+    race = 'Race/Ethnicity',
+    edu = 'Highest degree earned',
+    insurance = 'Insurance coverage',
+    poverty = 'Poverty level'
+  )) %>% 
+  # Join with AAPC table
+  left_join(cleaned_prop_aapc_sans_2020, by = c('stratifier', 'strata', 'variable' = 'practice'))
+
+cleaned_proportion_df_sans_2020 <- left_join(clean_age_adjusted_prop, cleaned_prop_apc_sans_2020, by = c('stratifier', 'strata', 'variable' = 'practice')) %>% 
+  mutate(AAPC = case_when(is.na(AAPC) & is.na(`APC Period 2`) & is.na(`APC Period 3`) ~ `APC Period 1`,
+                          TRUE ~ AAPC),
+         `APC Period 1` = case_when(is.na(`APC Period 1`) & is.na(`APC Period 2`) ~ AAPC,
+                                    TRUE ~ `APC Period 1`)) %>%
+  # Rename poverty levels
+  mutate(strata = case_when(as.character(strata) == 'Poor/Negative' ~ '< 100%',
+                            as.character(strata) == 'Low income' ~ '100% - 199%',
+                            as.character(strata) == 'Middle income' ~ '200% - 399%',
+                            as.character(strata) == 'High income' ~ '> 400%',
+                            TRUE ~ as.character(strata)))
+
+# Rename strata to a blank name to remove it from the final table
+proportion_table_sans_2020 <- cleaned_proportion_df_sans_2020 %>% 
+  filter(strata != 'Other') %>% 
+  group_by(stratifier) %>%
+  mutate(variable = case_when(variable == 'a1c' ~ 'Two or more A1C tests',
+                                   variable == 'CHOL_all' ~ 'Cholesterol tested',
+                                   variable == 'DENT_all' ~ 'One or more dentist visits',
+                                   variable == 'eye-exam' ~ 'Eye exam with dilation',
+                                   variable == 'flu' ~ 'Received flu vaccine',
+                                   variable == 'foot' ~ 'Foot examination')) %>% 
+  select(stratifier,
+         ` ` = strata,
+         `Preventive Practice` = variable, `2008`:`2020`, `Percent Change (95% CI)`, `Joinpoint Year` = segment,
+         `APC Period 1`, `APC Period 2`, `APC Period 3`, `AAPC`) %>%
+  mutate(stratifier = case_when(as.character(stratifier) == 'Poverty level' ~ 'Poverty income ratio',
+                                TRUE ~ as.character(stratifier))) %>% 
+  mutate(`APC (95% CI)` = paste(`APC Period 1`, `APC Period 2`, `APC Period 3`, sep = ", ") %>%
+           str_replace(., ", NA", "") %>%
+           str_replace(., ", NA", "")) %>% 
+  # Rename some columns to add () info
+  rename(`2008 (SE)` = `2008`,
+         #`2009 (SE)` = `2009`,
+         #`2010 (SE)` = `2010`,
+         `2011 (SE)` = `2011`,
+         #`2012 (SE)` = `2012`,
+         #`2013 (SE)` = `2013`,
+         `2014 (SE)` = `2014`,
+         #`2015 (SE)` = `2015`,
+         #`2016 (SE)` = `2016`,
+         `2017 (SE)` = `2017`,
+         #`2018 (SE)` = `2018`,
+         `2019 (SE)` = `2019`,
+         `2020 (SE)` = `2020`,
+         `APC Period 1 (95% CI)` = `APC Period 1`,
+         `APC Period 2 (95% CI)` = `APC Period 2`,
+         `APC Period 3 (95% CI)` = `APC Period 3`,
+         `AAPC (95% CI)` = `AAPC`) %>% 
+  select(
+    ` `,
+    `Preventive Practice`,
+    `2008 (SE)`,
+    #`2009 (SE),
+    #`2010 (SE),
+    `2011 (SE)`,
+    #`2012 (SE),
+    #`2013 (SE),
+    `2014 (SE)`,
+    #`2015 (SE),
+    #`2016 (SE),
+    `2017 (SE)`,
+    #`2018 (SE),
+    `2019 (SE)`,
+    `2020 (SE)`,
+    `Percent Change (95% CI)`,
+    `Joinpoint Year`,
+    `APC (95% CI)`,
+    `AAPC (95% CI)`,
+    -starts_with('APC Period')
+  ) %>%
+  gt() %>% 
+  sub_missing(missing_text = ' ') %>% 
+  tab_footnote(
+    footnote = "Values in these columns were estimated excluding data from 2020.",
+    locations = cells_column_labels(
+      columns = c(`Percent Change (95% CI)`,
+      `APC (95% CI)`,
+      `AAPC (95% CI)`
+    ))
+  ) %>% 
+  tab_options(footnotes.marks = "a")
+# Reorganize insurance variables
+ proportion_table_sans_2020$`_data` <- proportion_table_sans_2020$`_data`[c(1:84,
+                                                                            85, 88, 86, 87,
+                                                                            89, 92, 90, 91,
+                                                                            93, 96, 94, 95,
+                                                                            97, 100, 98, 99,
+                                                                            101, 104, 102, 103,
+                                                                            105, 108, 106, 107, 
+                                                                            109:nrow(proportion_table_sans_2020$`_data`)), ]
+
+prop_tab_sans_2020 <- proportion_table_sans_2020$`_data`
+proportion_table_sans_2020 %>%
+  gtsave('proportion_2020.docx')
+```
+
+```{r all-plots}
 
 stats_table_plot_dat <- jp_proportion_plot_data %>%
+  mutate(model = as.numeric(model)) %>% 
   filter(strata != 'Total') %>%
@@
   filter(strata != 'Other Race/Not Hispanic') %>% 
-  mutate(variable_text = case_when(variable == 'a1c' ~ '2 or more A1C tests',
+  filter(strata != 'Other') %>% 
+  mutate(variable_text = case_when(variable == 'a1c' ~ 'Two or more A1C tests',
                                    variable == 'CHOL_all' ~ 'Cholesterol tested',
-                                   variable == 'DENT_all' ~ '1 or more dentist visits',
+                                   variable == 'DENT_all' ~ 'One or more dentist visits',
                                    variable == 'eye-exam' ~ 'Eye exam with dilation',
@@
 
-overall_data <- stats_table_plot_dat$overall
+overall_data <- stats_table_plot_dat$overall %>% 
+  mutate(strata = case_when(strata == 'Overall' ~ 'z'))
 # Remove the overall data from the list
@@
       #geom_point() +
-      geom_line(aes(x = year, y = model * 100, group = strata, color = strata)) +
+      geom_line(aes(x = year, y = model, group = strata, color = strata)) +
       geom_line(data = filter(overall_data, variable %in% c('a1c', 'CHOL_all', 'flu')),
-                  aes(x = year, y = model * 100),
+                  aes(x = year, y = model),
                   color = 'black',
@@
 test_plots[[4]] <-
-  test_plots[[4]] + labs(color = 'Income as % of \npoverty line') + theme(
+  test_plots[[4]] + labs(color = 'Poverty income ratio') + theme(
     strip.background =  element_blank(),
@@
 test_plots[[5]] <-
-  test_plots[[5]] + labs(color = 'Race/Ethnicity') + theme(
+  test_plots[[5]] + labs(color = 'Race & Ethnicity') + theme(
     strip.background =  element_blank(),
@@
       #geom_point() +
-      geom_line(aes(x = year, y = model * 100, group = strata, color = strata)) +
+      geom_line(aes(x = year, y = model, group = strata, color = strata)) +
       geom_line(data = filter(overall_data, variable %!in% c('a1c', 'CHOL_all', 'flu')),
-                  aes(x = year, y = model * 100),
+                  aes(x = year, y = model),
                   color = 'black',
@@
             legend.title = element_text(size = 8),
-            legend.text = element_text(size = 6)) +
+            legend.text = element_text(size = 7)) +
       labs(x = 'Year', y = 'Percentage')
@@
 exam_plots[[4]] <-
-  exam_plots[[4]] + labs(color = 'Income as % of \npoverty line') + theme(
+  exam_plots[[4]] + labs(color = 'Poverty income ratio') + theme(
     strip.background =  element_blank(),
@@
 exam_plots[[5]] <-
-  exam_plots[[5]] + labs(color = 'Race/Ethnicity') + theme(
+  exam_plots[[5]] + labs(color = 'Race & Ethnicity') + theme(
     strip.background =  element_blank(),
-    strip.text = element_blank()
+    strip.text = element_blank(),
+    axis.title.x = element_blank()
   )
@@
 )
-(all_exam_plots <- exam_plots %>% 
+
+# all_exam_plots <- exam_plots %>% 
+#   wrap_plots(nrow = 6) &
+#   theme(plot.margin = margin(0.5, 0.5, 0.5, 0.5, 'pt'))
+# all_test_plots <- test_plots %>% 
+#   wrap_plots(nrow = 6) &
+#   theme(plot.margin = margin(0.5, 0.5, 0.5, 0.5, 'pt'))
+```
+
+```{r plots-sans-2020}
+set.seed(963458237)
+stats_table_plot_dat_sans_2020 <- jp_proportion_plot_data_sans_2020 %>%
+  mutate(model = as.numeric(model)) %>% 
+  filter(strata != 'Total') %>%
+  filter(strata != 'Not available') %>% 
+  filter(strata != 'Other Race/Not Hispanic') %>% 
+  filter(strata != 'Other') %>% 
+  mutate(variable_text = case_when(variable == 'a1c' ~ 'Two or more A1C tests',
+                                   variable == 'CHOL_all' ~ 'Cholesterol tested',
+                                   variable == 'DENT_all' ~ 'One or more dentist visits',
+                                   variable == 'eye-exam' ~ 'Eye exam with dilation',
+                                   variable == 'flu' ~ 'Received flu vaccine',
+                                   variable == 'foot' ~ 'Foot examination'),
+         strata = case_when(strata == 'Overall' ~ 'z',
+                            TRUE ~ strata)) %>% 
+  group_by(strata, variable) %>% 
+  mutate(strata = as.factor(strata),
+         significant_indicator = any(str_detect(apc, "[*]"))) %>% 
+  ungroup() %>% 
+  split(., f = .$stratifier)
+
+stats_table_plot_dat_sans_2020 <- map(stats_table_plot_dat_sans_2020, function(.x) {
+  .x %>% 
+    mutate(strata = fct_drop(strata))
+})
+
+overall_data_sans_2020 <- stats_table_plot_dat_sans_2020$overall
+# Remove the overall data from the list
+stats_table_plot_dat_sans_2020 <- stats_table_plot_dat_sans_2020[-4]
+# Relevel the poverty factors
+stats_table_plot_dat_sans_2020$poverty$strata <-
+  factor(
+    stats_table_plot_dat_sans_2020$poverty$strata,
+    levels = c('High income', 'Middle income', 'Low income', 'Poor/Negative'),
+    labels = c(
+      '> 400% ',
+      '200% - 399%',
+      '100% - 199%',
+      '< 100%'
+
+    )
+  )
+# Set up color palette for up to 4 categories
+color_pal <- RColorBrewer::brewer.pal(n = 4, 'Set2')
+# Get the p for 2020 but remove the join point stuff so the line doesn't plot
+stats_table_2020_only <- stats_table_plot_dat %>% 
+  map(~filter(.x, year == 2020) %>% 
+        group_by(strata, variable) %>% 
+        mutate(model = NA,
+                significant_indicator = any(str_detect(apc, "[*]"))) %>% 
+        ungroup()
+  )
+
+legend_labels <- stats_table_plot_dat_sans_2020 %>% 
+  map(~.x %>% 
+        group_by(strata, variable) %>% 
+        summarise(sig_ind = mean(significant_indicator)) %>% 
+        ungroup()
+  )
+overall_legend <- overall_data_sans_2020 %>%
+  group_by(strata, variable) %>%
+  summarise(sig_ind = mean(significant_indicator)) %>%
+  ungroup()
+
+test_plots_sans_2020 <-
+  map2(
+    stats_table_plot_dat_sans_2020,
+    stats_table_2020_only,
+    ~ ggplot(
+      filter(.x, variable %in% c('a1c', 'CHOL_all', 'flu')),
+      aes(
+        x = year,
+        y = p,
+        group = strata,
+        color = strata
+      )
+    ) +
+      geom_line(aes(
+        x = year,
+        y = model,
+        group = strata,
+        color = strata,
+        linetype = strata
+      )) +
+      geom_line(
+        data = filter(
+          overall_data_sans_2020,
+          variable %in% c('a1c', 'CHOL_all', 'flu')
+        ),
+        aes(
+          x = year,
+          y = model,
+          color = strata,
+          linetype = strata
+        ),
+      ) +
+      geom_jitter(
+        data = filter(.y, variable %in% c('a1c', 'CHOL_all')) ,
+        aes(
+          x = year,
+          y = p,
+          group = strata,
+          color = strata
+        ),
+        inherit.aes = FALSE,
+        width = 0.22,
+        height = 0.005
+      ) +
+      geom_point(
+        data = filter(
+          overall_data,
+          variable %in% c('a1c', 'CHOL_all'),
+          year == 2020
+        ),
+        aes(x = year, y = p, color = strata),
+        inherit.aes = FALSE
+      ) +
+      facet_wrap(~ variable_text, ncol = 3) +
+      theme_classic() +
+      scale_y_continuous(
+        limits = c(0, 100),
+        breaks = seq(0, 100, 25),
+        labels = seq(0, 100, 25)
+      ) +
+      scale_x_continuous(
+        limits = c(2008, 2020.3),
+        breaks = seq(2008, 2020, 2),
+        labels = seq(2008, 2020, 2)
+      ) +
+      theme(
+        axis.text = element_text(color = 'black'),
+        #axis.text.x = element_text(angle = 45, hjust = 0.9, vjust = 0.95),
+        legend.title = element_text(size = 11),
+        legend.text = element_text(size = 9)
+      ) +
+      labs(x = 'Year', y = 'Percentage')
+
+  )
+
+test_plots_sans_2020[[1]] <-
+  test_plots_sans_2020[[1]] +
+  theme(axis.title.x = element_blank()) +
+  scale_color_manual(
+    name = 'Age (grouped)',
+    values = c(
+     '18 to 44' = color_pal[1],
+     '45 to 64'  = color_pal[2],
+     '65 to 74' = color_pal[3],
+     '75+' = color_pal[4],
+     'z' = '#000000'
+    ),
+    labels = c('18 to 44ᵇ',
+               '45 to 64ᵃᵇᶜ',
+               '65 to 74ᵇᶜ',
+               '75+ᵇᶜ',
+               'Overallᵇ')
+  ) +
+  scale_linetype_manual(
+    name = 'Age (grouped)',
+    values = c(
+     '18 to 44' = 'solid',
+     '45 to 64'  = 'solid',
+     '65 to 74' = 'solid',
+     '75+' = 'solid',
+     'z' = 'dashed'
+    ),
+    labels = c('18 to 44ᵇ',
+               '45 to 64ᵃᵇᶜ',
+               '65 to 74ᵇᶜ',
+               '75+ᵇᶜ',
+               'Overallᵇ')
+  )
+
+test_plots_sans_2020[[2]] <-
+  test_plots_sans_2020[[2]] +
+  theme(
+    strip.background =  element_blank(),
+    strip.text = element_blank(),
+    axis.title.x = element_blank()
+  ) +
+  scale_color_manual(
+    name = 'Highest degree obtained',
+    labels = c('Greater than HSᵇ',
+               'High school',
+               'Less than HSᵃᵇ',
+               'Overallᵇ'),
+    values = c(
+     'Greater than HS' = color_pal[1],
+     'High school' = color_pal[2],
+     'Less than high school'  = color_pal[3],
+     'z' = '#000000'
+    )
+  ) +
+  scale_linetype_manual(
+    name = 'Highest degree obtained',
+    labels = c('Greater than HSᵇ',
+               'High school',
+               'Less than HSᵃᵇ',
+               'Overallᵇ'),
+    values = c(
+     'Greater than HS' = 'solid',
+     'High school' = 'solid',
+     'Less than high school'  = 'solid',
+     'z' = 'dashed'
+    )
+  )
+
+test_plots_sans_2020[[3]] <-
+  test_plots_sans_2020[[3]] +
+  theme(
+    strip.background =  element_blank(),
+    strip.text = element_blank(),
+    axis.title.x = element_blank()
+  ) +
+  scale_color_manual(
+    name = 'Insurance',
+    values = c(
+      'Medicaid' = color_pal[1],
+      'Medicare only' = color_pal[2],
+      'Private only' = color_pal[3],
+      'Uninsured' = color_pal[4],
+      'z' = '#000000'
+    ),   labels = c(
+      'Medicaidᶜ',
+      'Medicare onlyᵃ',
+      'Private onlyᵃᶜ',
+      'Uninsuredᵃᶜ',
+      'Overallᵇ'
+    )
+  ) +
+  scale_linetype_manual(
+    name = 'Insurance',
+    values = c(
+      'Medicaid' = 'solid',
+      'Medicare only' = 'solid',
+      'Private only' = 'solid',
+      'Uninsured' = 'solid',
+      'z' = 'dashed'
+    ),
+        labels = c(
+      'Medicaidᶜ',
+      'Medicare onlyᵃ',
+      'Private onlyᵃᶜ',
+      'Uninsuredᵃᶜ',
+      'Overallᵇ'
+    )
+  )
+
+test_plots_sans_2020[[4]] <-
+  test_plots_sans_2020[[4]] +
+  theme(strip.background =  element_blank(),
+        strip.text = element_blank()) +
+  scale_color_manual(
+    name = 'Poverty income ratio',
+    labels = c('> 400%ᶜ',
+               '200% - 399%',
+               '100% - 199%ᵃ',
+               '< 100%ᵇ',
+               'Overallᵇ'),
+
+    values = c(
+      '> 400% ' = color_pal[1],
+      '200% - 399%' = color_pal[2],
+      '100% - 199%' = color_pal[3],
+      '< 100%' = color_pal[4],
+      'z' = '#000000'
+    )
+  ) +
+  scale_linetype_manual(
+    name = 'Poverty income ratio',
+    labels = c('> 400%ᶜ',
+               '200% - 399%',
+               '100% - 199%ᵃ',
+               '< 100%ᵇ',
+               'Overallᵇ'),
+    values = c(
+      '> 400% ' = 'solid',
+      '200% - 399%' = 'solid',
+      '100% - 199%' = 'solid',
+      '< 100%' = 'solid',
+      'z' = 'dashed'
+    )
+  ) + 
+ labs(caption = "ᵃ p < 0.05 for cholesterol tested \nᵇ p < 0.05 for received flu vaccine \nᶜ p < 0.05 for A1C tests")
+
+test_plots_sans_2020[[5]] <-
+  test_plots_sans_2020[[5]] + theme(
+    strip.background =  element_blank(),
+    strip.text = element_blank(),
+    axis.title.x = element_blank()
+  ) +
+  scale_color_manual(
+    name = 'Race & Ethnicity',
+    labels = c(
+      'Asian/Not Hispanic',
+      'Black/Not Hispanic',
+      'Hispanicᶜ',
+      'White/Not Hispanicᵃᵇᶜ',
+      'Overallᵇ'
+    ),
+    values = c(
+     'Asian/Not Hispanic' = color_pal[1],
+     'Black/Not Hispanic'  = color_pal[2],
+     'Hispanic' = color_pal[3],
+     'White/Not Hispanic' = color_pal[4],
+     'z' = '#000000'
+    )
+  ) +
+  scale_linetype_manual(
+    name = 'Race & Ethnicity',
+    labels = c(
+      'Asian/Not Hispanic',
+      'Black/Not Hispanic',
+      'Hispanicᶜ',
+      'White/Not Hispanicᵃᵇᶜ',
+      'Overallᵇ'
+    ),
+    values = c(
+     'Asian/Not Hispanic' = 'solid',
+     'Black/Not Hispanic'  = 'solid',
+     'Hispanic' = 'solid',
+     'White/Not Hispanic' = 'solid',
+     'z' = 'dashed'
+    )
+  )
+test_plots_sans_2020[[6]] <-
+  test_plots_sans_2020[[6]] +
+  theme(
+    strip.background =  element_blank(),
+    strip.text = element_blank(),
+    axis.title.x = element_blank()
+  ) +
+  scale_color_manual(
+    name = 'Sex',
+    labels = c('Femaleᵇ',
+               'Maleᵃᵇ',
+               'Overallᵇ'),
+    values = c(
+     'Female' = color_pal[1],
+     'Male'  = color_pal[2],
+     'z' = '#000000'
+    )
+  ) +
+  scale_linetype_manual(
+    name = 'Sex',
+    labels = c('Femaleᵇ',
+               'Maleᵃᵇ',
+               'Overallᵇ'),
+        values = c(
+     'Female' = 'solid',
+     'Male'  = 'solid',
+     'z' = 'dashed'
+    )
+  )
+test_plots_sans_2020 <- list(
+  test_plots_sans_2020[[1]],
+  test_plots_sans_2020[[6]],
+  test_plots_sans_2020[[5]],
+  test_plots_sans_2020[[2]],
+  test_plots_sans_2020[[3]],
+  test_plots_sans_2020[[4]]
+)
+
+exam_plots_sans_2020 <-
+  map2(
+    stats_table_plot_dat_sans_2020,
+    stats_table_2020_only,
+    ~ ggplot(
+      filter(.x, variable %!in% c('a1c', 'CHOL_all', 'flu')),
+      aes(
+        x = year,
+        y = p,
+        group = strata,
+        color = strata
+      )
+    ) +
+      geom_line(aes(
+        x = year,
+        y = model,
+        group = strata,
+        color = strata,
+        linetype = strata
+      )) +
+      geom_line(
+        data = filter(
+          overall_data_sans_2020,
+          variable %!in% c('a1c', 'CHOL_all', 'flu')
+        ),
+        aes(x = year, y = model, color = strata, linetype = strata),
+      ) +
+      geom_jitter(
+        data = filter(.y, variable %!in% c('a1c', 'CHOL_all', 'flu')) ,
+        aes(
+          x = year,
+          y = p,
+          group = strata,
+          color = strata
+        ),
+        inherit.aes = FALSE,
+        width = 0.22,
+        height = 0.005
+      ) +
+      geom_point(
+        data = filter(
+          overall_data,
+          variable %!in% c('a1c', 'CHOL_all', 'flu'),
+          year == 2020
+        ),
+        aes(x = year, y = p, color = strata),
+        #color = 'black',
+        inherit.aes = FALSE
+      ) +
+      facet_wrap(~ variable_text, ncol = 3) +
+      theme_classic() +
+      scale_y_continuous(
+        limits = c(0, 100),
+        breaks = seq(0, 100, 25),
+        labels = seq(0, 100, 25)
+      ) +
+      scale_x_continuous(
+        limits = c(2008, 2020.3),
+        breaks = seq(2008, 2020, 2),
+        labels = seq(2008, 2020, 2)
+      ) +
+      theme(
+        axis.text = element_text(color = 'black'),
+        #axis.text.x = element_text(angle = 45, hjust = 0.9, vjust = 0.95),
+        legend.title = element_text(size = 11),
+        legend.text = element_text(size = 9)
+      ) +
+      labs(x = 'Year', y = 'Percentage')
+  )
+
+# Set up legends on all plots
+exam_plots_sans_2020[[1]] <- exam_plots_sans_2020[[1]] +
+  theme(axis.title.x = element_blank()) +
+  scale_color_manual(
+    name = 'Age (grouped)',
+    labels = c('18 to 44',
+               '45 to 64',
+               '65 to 74ᵇᶜ',
+               '75+ᵃᵇ',
+               'Overallᵇ'),
+    values =   c(
+      '18 to 44' = color_pal[1],
+      '45 to 64'  = color_pal[2],
+      '65 to 74' = color_pal[3],
+      '75+' = color_pal[4],
+      'z' = '#000000'
+    )
+  ) +
+  scale_linetype_manual(
+    name = 'Age (grouped)',
+    labels = c('18 to 44',
+               '45 to 64',
+               '65 to 74ᵇᶜ',
+               '75+ᵃᵇ',
+               'Overallᵇ'),
+    values = c(
+      '18 to 44' = 'solid',
+      '45 to 64'  = 'solid',
+      '65 to 74' = 'solid',
+      '75+' = 'solid',
+      'z' = 'dashed'
+    )
+  )
+
+exam_plots_sans_2020[[2]] <-
+  exam_plots_sans_2020[[2]] +
+  theme(
+    strip.background =  element_blank(),
+    strip.text = element_blank(),
+    axis.title.x = element_blank()
+  ) +
+  scale_color_manual(
+    name = 'Highest degree obtained',
+    labels = c('Greater than HS',
+               'High schoolᶜ',
+               'Less than HS',
+               'Overallᵇ'),
+        values = c(
+      'Greater than HS' = color_pal[1],
+      'High school' = color_pal[2],
+      'Less than high school'  = color_pal[3],
+      'z' = '#000000'
+    )
+  ) +
+    scale_linetype_manual(
+      name = 'Highest degree obtained',
+    labels = c('Greater than HS',
+               'High schoolᶜ',
+               'Less than HS',
+               'Overallᵇ'),
+    values = c(
+      'Greater than HS' = 'solid',
+      'High school' = 'solid',
+      'Less than high school'  = 'solid',
+      'z' = 'dashed'
+    )
+  )
+
+exam_plots_sans_2020[[3]] <-
+  exam_plots_sans_2020[[3]] +
+  theme(
+    strip.background =  element_blank(),
+    strip.text = element_blank(),
+    axis.title.x = element_blank()
+  ) +
+  scale_color_manual(
+    name = 'Insurance',
+    labels = c(
+      'Medicaid',
+      'Medicare only',
+      'Private onlyᵃᵇ',
+      'Uninsuredᵃ',
+      'Overallᵇ'
+    ),
+        values = c(
+      'Medicaid' = color_pal[1],
+      'Medicare only' = color_pal[2],
+      'Private only' = color_pal[3],
+      'Uninsured' = color_pal[4],
+      'z' = '#000000'
+    )
+  ) +
+  scale_linetype_manual(
+    name = 'Insurance',
+    labels =  c(
+      'Medicaid',
+      'Medicare only',
+      'Private onlyᵃᵇ',
+      'Uninsuredᵃ',
+      'Overallᵇ'
+    ),
+    values = c(
+      'Medicaid' = 'solid',
+      'Medicare only' = 'solid',
+      'Private only' = 'solid',
+      'Uninsured' = 'solid',
+      'z' = 'dashed'
+    )
+  )
+
+exam_plots_sans_2020[[4]] <-
+  exam_plots_sans_2020[[4]] +
+  theme(strip.background =  element_blank(),
+        strip.text = element_blank()) +
+  scale_color_manual(
+    name = 'Poverty income ratio',
+    labels = c('> 400%ᵃ',
+               '200% - 399%',
+               '100% - 199%',
+               '< 100%ᶜ',
+               'Overallᵇ'),
+    values = c(
+      '> 400% ' = color_pal[1],
+      '200% - 399%' = color_pal[2],
+      '100% - 199%' = color_pal[3],
+      '< 100%' = color_pal[4],
+      'z' = '#000000'
+    )
+  ) +
+  scale_linetype_manual(
+    name = 'Poverty income ratio',
+    labels = c('> 400%ᵃ',
+               '200% - 399%',
+               '100% - 199%',
+               '< 100%ᶜ',
+               'Overallᵇ'),
+    values = c(
+      '> 400% ' = 'solid',
+      '200% - 399%' = 'solid',
+      '100% - 199%' = 'solid',
+      '< 100%' = 'solid',
+      'z' = 'dashed'
+    )
+  ) +
+  labs(caption = "ᵃ p < 0.05 for eye-exam \nᵇ p < 0.05 for foot exam \nᶜ p < 0.05 for dentist visit")
+
+exam_plots_sans_2020[[5]] <-
+  exam_plots_sans_2020[[5]] +
+  theme(
+    strip.background =  element_blank(),
+    strip.text = element_blank(),
+    axis.title.x = element_blank()
+  ) +
+  scale_color_manual(
+    name = 'Race & Ethnicity',
+    labels = c(
+      'Asian/Not Hispanic',
+      'Black/Not Hispanic',
+      'Hispanic',
+      'White/Not Hispanicᶜ',
+      'Overallᵇ'
+    ),
+    values = c(
+      'Asian/Not Hispanic' = color_pal[1],
+      'Black/Not Hispanic'  = color_pal[2],
+      'Hispanic' = color_pal[3],
+      'White/Not Hispanic' = color_pal[4],
+      'z' = '#000000'
+    )
+  ) +
+  scale_linetype_manual(
+    name = 'Race & Ethnicity',
+        labels = c(
+      'Asian/Not Hispanic',
+      'Black/Not Hispanic',
+      'Hispanic',
+      'White/Not Hispanicᶜ',
+      'Overallᵇ'
+    ),
+    values = c(
+      'Asian/Not Hispanic' = 'solid',
+      'Black/Not Hispanic'  = 'solid',
+      'Hispanic' = 'solid',
+      'White/Not Hispanic' = 'solid',
+      'z' = 'dashed'
+    )
+  )
+
+exam_plots_sans_2020[[6]] <-
+  exam_plots_sans_2020[[6]] +
+  theme(
+    strip.background =  element_blank(),
+    strip.text = element_blank(),
+    axis.title.x = element_blank()
+  ) +
+  scale_color_manual(
+    name = 'Sex',
+    labels = c('Female',
+               'Maleᵃ',
+               'Overallᵇ'),
+    values = c(
+      'Female' = color_pal[1],
+      'Male'  = color_pal[2],
+      'z' = '#000000'
+    )
+  ) +
+  scale_linetype_manual(
+    name = 'Sex',
+    labels = c('Female',
+               'Maleᵃ',
+               'Overallᵇ'),
+    values = c(
+      'Female' = 'solid',
+      'Male'  = 'solid',
+      'z' = 'dashed'
+    )
+  )
+
+exam_plots_sans_2020 <- list(
+  exam_plots_sans_2020[[1]],
+  exam_plots_sans_2020[[6]],
+  exam_plots_sans_2020[[5]],
+  exam_plots_sans_2020[[2]],
+  exam_plots_sans_2020[[3]],
+  exam_plots_sans_2020[[4]]
+)
+
+all_exam_plots_sans_2020 <- exam_plots_sans_2020 %>% 
   wrap_plots(nrow = 6) &
-  theme(plot.margin = margin(0.5, 0.5, 0.5, 0.5, 'pt')))
-(all_test_plots <- test_plots %>% 
+  theme(plot.margin = margin(0.5, 0.5, 0.5, 0.5, 'pt'),
+        legend.justification = 'left',
+        plot.caption = element_text(hjust = 0)) &
+  guides(color = guide_legend(ncol = 2)) 
+all_test_plots_sans_2020 <- test_plots_sans_2020 %>% 
   wrap_plots(nrow = 6) &
-  theme(plot.margin = margin(0.5, 0.5, 0.5, 0.5, 'pt')))
-ggsave(plot = all_exam_plots,
+  theme(plot.margin = margin(0.5, 0.5, 0.5, 0.5, 'pt'),
+        legend.justification = 'left',
+         plot.caption = element_text(hjust = 0)) &
+  guides(color = guide_legend(ncol = 2))
+```
+
+```{r}
+#| include: false
+# Save figure/table output
+preventive_practice_table %>%
+  gtsave('preventive_practices.docx')
+preventive_practice_table_sans_2020 %>%
+  gtsave('preventive_practices_2020.docx')
+ggsave(plot = all_exam_plots_sans_2020,
        filename = 'figures/all_exam_plots.tiff',
-       dpi = 200,
+       dpi = 1200,
        width = 10,
-       height = 7)
-ggsave(plot = all_test_plots,
+       height = 6)
+ggsave(plot = all_test_plots_sans_2020,
        filename = 'figures/all_test_plots.tiff',
-       dpi = 200,
+       dpi = 1200,
        width = 10,
-       height = 7)
-ggsave(plot = all_exam_plots,
-       filename = 'figures/all_exam_plots.svg',
-       dpi = 200,
-       width = 10,
-       height = 7)
-ggsave(plot = all_test_plots,
-       filename = 'figures/all_test_plots.svg',
-       dpi = 200,
-       width = 10,
-       height = 7)
+       height = 6)
+# ggsave(plot = all_exam_plots,
+#        filename = 'figures/all_exam_plots.svg',
+#        dpi = 200,
+#        width = 10,
+#        height = 6)
+# ggsave(plot = all_test_plots,
+#        filename = 'figures/all_test_plots.svg',
+#        dpi = 200,
+#        width = 10,
+#        height = 6)
 ```
+
+*Target Journal: American Journal of Preventive Medicine*
+
+**Trends in Preventive Care Practices among US Adults with Diabetes, 2008-2020**
+
+Jacob T. Wittman, PhD, Kai McKeever Bullard, MPH, PhD, Stephen R. Benoit, MD, MPH
+
+CDC Affiliation
+
+Corresponding Author:
+
+Word Count:
+
+Conflict of Interest Statement:
+
+Financial Disclosure:
+
+\pagebreak
+
+# Abstract
+
+**Introduction:** Preventive care practices are important for managing complications associated with diabetes.
+We report on trends in receipt of six American Diabetes Associated recommended preventive care practices during 2008 - 2020.
+
+**Methods:** We used 2008 - 2020 data from the Medical Expenditures Panel Survey to calculate the proportion of adults diagnosed with diabetes 18 years of age and older that reported receiving preventive care practices overall and for subpopulations.
+We used Joinpoint regression to identify trends in the data from 2008 - 2019.
+The six practices we have data for were at least one dental examination, an eye examination that includes dilation, a foot examination, at least two A1C tests, a cholesterol test, and the receipt of a flu vaccine.
+
+**Results:** From 2008 to 2019, the proportion of adults reporting having received at least three of six recommended practices decreased from 71.0% in 2008 to 67.3%, although this trend was not significant.
+No significant changes were seen for most subgroups.
+Most individual practices examined also were flat or decreased over the study period, except for the receipt of 2 or more A1C tests in year, which increased.
+
+**Conclusions:** Receipt of preventive care for diabetes was flat from 2008 to 2019 overall and for most subgroups.
+Declining trends were observed in few subgroups and may lead to increasing diabetes burden among these subgroups.
+
+\pagebreak
+
+# Introduction
+
+Diabetes is a chronic disease that affects 11.3% of the adult population, or 37.1 million adults, in the United States @nationalreport.
+Diabetes is also costly: total direct and indirect costs associated with diabetes are estimated at \$327 billion @economic2018.
+Incidence of diabetes peaked in the US at 8.5 cases per 1,000 in 2008 and 2009 and has fallen since to 5.1 cases per 1,000 [@dashboard; @magliano2019].
+Despite this decrease in the incidence of diabetes, rates of hospitalization with diabetes as the primary diagnosis have been increasing since the year 2000 by about 2.5% per year @zhang2022.
+The prevalence of diabetes in the US is expected to increase to 60.6 million adults by the year 2060 @lin2018.
+Access to preventive services health care is important to minimize complications due to diabetes and reduce rates of hospitalization.
+
+In this study, we report the proportion of and trends in the receipt of six preventive care practices recommended by the ADA overall and among subgroups.
+These data are valuable for identifying groups that may be underutilizing health care services, examining any effects the COVID-19 pandemic may have had on the receipt of these practices, and providing benchmarks for future studies.
+
+# Methods
+
+## Data Source
+
+We used data from the Medical Expenditure Panel Survey (MEPS) from the years 2008 - 2020.
+We chose 2008 to 2020 due to method changes in MEPS and the consistency of particular questions related to preventive care practices during that time period.
+Respondents were randomly chosen from a subsample of households that participated in the National Health Interview Survey (NHIS).
+Data used from MEPS were collected through a combination of computer assisted personal interviewing and pencil-and-paper surveys.
+The average number annual of individual respondents over this 13 year period was 32,170.
+MEPS targets the civilian noninstitutionalized population in the US and provides national and regional estimates of health care use, expenditures, sources of payment and health insurance coverage.
+This survey also contains information on patient demographics, socioeconomic, and, via the Diabetes Care Survey (DCS), information on diabetes preventive care practices.
+The DCS is a self-administered paper-and-pencil questionnaire that is provided to MEPS respondents who indicate that they have been told by a doctor or health professional that they have diabetes.
+The data we used comes from the full-year consolidated file from MEPS for the 13 year time span of our report.
+
+## Outcomes
+
+Among those respondents with self-reported diagnosed diabetes, we selected six preventive care variables that were available in the data from 2008 -- 2020, based on self-reported receipt in the past year @ada2021: ≥1 dental examination, a dilated eye examination, a foot examination, ≥2 A1C tests, a cholesterol test, and an influenza vaccine.
+We also created a binary variable classifying adults as having received at least three of those recommended preventive care practices.
+
+## Analysis
+
+Our analysis accounts for the complex survey design used, including clustering and stratification.
+Reported values throughout were age-adjusted using the direct method, standardized to the 2000 US population grouped by ages 18 - 44, 45 - 64, 65 - 74, and older than 75.
+We presented these estimates for the overall population, as well as stratified by age, sex, race and ethnicity, highest degree of education obtained, type of insurance, and the ratio of family income to the poverty line (income poverty ratio).
+We used the package gtsummary in R Statistical Software (v4.2.1) to calculate estimates [@gtsummary; @rcore2022].
+
+Medical care utilization decreased as a result of the COVID-19 pandemic starting in early 2020 @cantor2022.
+We reported the estimated proportions for 2020 in Table 1 and as points in @fig-exams and @fig-tests, but 2020 was excluded from trend analysis.
+Trends were analyzed using Joinpoint Command Line Software @joinpoint with R via the R package nih.joinpoint @nihjoinpoint.
+Joinpoint regression uses permutation tests to detect statistically significant changes at a pre-specified alpha of 0.05 in direction or magnitude of trends @kim2000permutation.
+The Joinpoint software also provided estimates of the annual percent change (APC) for each trend segment and the average annual percent change (AAPC) for the entire trend.
+
+# Results
+
+## Trends in ≥ 3 preventive care practices received
+
+Overall, we observed no statistically significant percent change of adults receiving three or more recommended preventive care practices between 2008 and 2019 (`r pullNumber(tab_sans_2020, '-', 'Percent Change (95% CI)', brackets = TRUE)`) (Table 1).
+Few groups exhibited significant changes in this trend over the same time period (Table 1).
+For adults age 75 and older, the percentage receiving three or more of the recommended care practices was flat from 2008 to 2014 (APC `r pullNumber(tab_sans_2020, '75+', 'APC Period 1 (95% CI)', brackets = T)`), and after 2015 was decreasing (APC `r pullNumber(tab_sans_2020, '75+', 'APC Period 2 (95% CI)', brackets = T)`).
+Adults with less than a high school education had a flat trend until 2012, which was followed by an APC in the second period of `r pullNumber(tab_sans_2020, 'Less than high school', 'APC Period 2 (95% CI)', brackets = F)`.
+
+Both males and females showed decreasing percentages of adults receiving three or more recommended preventive care practices.
+The AAPC for females was `r pullNumber(tab_sans_2020, 'Female', 'APC Period 1 (95% CI)', brackets = F)` over the entire period, whereas the trend for males was flat until 2015, at which point it began to decrease (APC `r pullNumber(tab_sans_2020, 'Male', 'APC Period 2 (95% CI)', brackets = T)`).
+Among the insurance groups, there were no significant change with the exception of Medicaid, which showed an overall decline in percentage of adults receiving three or more practices (AAPC `r pullNumber(tab_sans_2020, 'Medicaid', 'APC Period 1 (95% CI)', brackets = F)`).
+The percentage of adults in the highest earning group receiving three or more recommended care practices increased annually by `r pullNumber(tab_sans_2020, '> 400%', 'APC Period 1 (95% CI)', brackets = F)` and was flat after 2010 (`r pullNumber(tab_sans_2020, '> 400%', 'APC Period 2 (95% CI)', brackets = T)`).
+Adults earning just above the poverty line that received three or more of the recommended practices changed by `r pullNumber(tab_sans_2020, '100% - 199%', 'APC Period 1 (95% CI)', brackets = F)`.
+Estimated proportions tended to be lower in 2020 than in 2019 for most groups, except Black/Not Hispanic, males, and the uninsured.
+
+## Trends for each preventive care practice
+
+@fig-exams and @fig-tests show the trends for individual preventive care practices and indicate which trends were significantly increasing or decreasing, or had segments that were significantly increasing or decreasing.
+Estimates plotted in @fig-exams can be found in the table in Appendix 1.
+Trends for all adults with diabetes receiving a foot examination  decreased starting in 2011 (@fig-exams).
+The percent of adults getting a flu vaccine increased until 2013 then began to decrease (@fig-tests).
+The shape of the trends in subgroups tend to mirror the overall trend for each practice, although the year at which trend values change may differ among these subgroups.
+The trend in some subgroups for each preventive practice do not always follow the shape of the overall trend, however.
+For example, the overall trend in the percentage of adults with diabetes receiving an eye examination with dilation was flat over 2008 to 2019.
+Within the income poverty ratio subgroups, only those in the highest poverty income ratio group (\> 400%) deviate from this flat trend by first increasing, then decreasing starting in 2013 (@fig-exams).
+Different groups exhibit different amounts of variation among the categories in each group.
+For example, the trends for all six practices split by sex tend to be very similar, whereas the gaps between the different insurance group trends are larger.
+
+# Discussion
+
+Despite the recovery from the Great Recession in 2008 and the passing of the Affordable Care Act (ACA) in 2010, there was no change overall and for many subgroups in the percentage of people receiving at least three recommended preventive care services, while a few subgroups showed decreasing percentages.
+While the passing of the ACA led to an increase in the number of adults with diagnosed and undiagnosed diabetes that have health insurance and an increase in their use of health care services [@myerson2019; @simon2017], detecting changes in the receipt of preventive care has proved more elusive.
+Two studies that used data from the Behavioral Risk Factor Surveillance System (BRFSS) found no changes overall in the receipt of preventive care for adults with diabetes as a result of the Medicaid expansion [@monnette2020; @luo2019].
+It may be difficult to detect changes in any single preventive care practice or aggregate count of preventive care, especially if other factors are presenting stronger barriers to care.
+For example, depression may reduce adherence to or seeking of patient-initiated activities such as diet and exercise recommendations among adults with diabetes [@gonzalez2007].
+Even with higher rates of medical service use among adults with both depression and diabetes, rates of physician-initiated services were no different between adults with and without depression [@lin2004].
+
+Other studies on the trends in preventive care using different data sources report different findings.
+A study using data from the National Health and Nutrition Examination Survey (NHANES) found increases in the proportion of adults with diabetes that reported having a primary care doctor, received an annual check-up with a physician, had at least two A1C tests in a year, had their cholesterol levels tested, and had an annual foot exam by a doctor @shin2021.
+Another study that reported on data from NHANES, the National Health Interview Survey, and (BRFSS) found that foot exams, flu vaccinations, and A1C testing increased from 1999 - 2016, although eye exams stayed roughly constant @fang2020.
+
+## Limitations
+
+This report is not without limitations.
+The data from MEPS are self-report only, which may introduce bias, and the study group is cross-sectional.
+Additionally, there has been a steadily declining response rate for this survey from a peak during the studied time period of 59.3% in 2008 to 39.5% in 2019 and 27.6% in 2020, although weights for these data are adjusted for non-response.
+Furthermore, we were unable to distinguish between type 1 and type 2 diabetes in these data.
+Because of the greater prevalence of type 2 diabetes the trends we report likely are more reflective of type 2 diabetes than type 1.
+
+# Conclusions
+
+In summary, receipt of preventive care for diabetes was flat from 2008 to 2019 overall and for most subgroups.
+Decreasing trends in preventive care percentages were seen in adults with diabetes over the age of 74, adults with less than a high school education, males and females, and adults with private insurance only or Medicaid.
+Declining trends in preventive care may lead to increasing complications due to diabetes in these subgroups, increasing the burden of diabetes.
+
+# Acknowledgements
+
+# References
+
+::: {#refs}
+:::
+
+\pagebreak
+
+::: landscape
+# Tables
+
+```{r}
+#| label: tbl-prev
+#| tbl-cap: Age-adjusted trends in proportions of US adults with diabetes that report receiving at least three of six recommended care practices - at least one dental visit, one eye exam with dilation, one foot exam, two or more A1C tests, cholesterol level tested, and receiving a flu vaccine.
+
+preventive_practice_table_sans_2020
+```
+
+\pagebreak
+
+# Figures
+
+```{r}
+#| label: fig-exams
+#| fig-cap: Age-adjusted trends in proportions of US adults with diabetes who reported receiving recommended medical examinations from 2008 - 2019.
+The dashed black line is the overall trend, while dots represent percentages for 2020.
+Data from 2020 was not included in the trend analysis.
+#| fig-width: 8
+
+all_exam_plots_sans_2020
+```
+
+\pagebreak
+
+```{r}
+#| label: fig-tests
+#| fig-cap: Age-adjusted trends in proportions of US adults with diabetes who reported receiving recommended lab tests and vaccinations.
+The dashed black line is the overall trend, while dots represent percentages for 2020.
+Data from 2020 was not included in the trend analysis.
+#| fig-width: 10
+
+all_test_plots_sans_2020
+```
+
+\pagebreak
+
+# Supplemental Table
+
+```{r}
+#| label: tbl-prop
+#| tbl-cap: Age-adjusted trends in proportions of US adults with diabetes that report receiving six recommended care practices - at least one dental visit, one eye exam with dilation, one foot exam, two or more A1C tests, cholesterol level tested, and receiving a flu vaccine.
+
+proportion_table_sans_2020
+```
+
+:::

### 2023-03-30 _targets.R

@@ -83,6 +83,8 @@ list(
       DSA1C53,
       DSCKFT53,
       PERWT,
+      MEDICAID,
+      MEDICARE
     ) %>%
       mutate(year = as.numeric(str_extract(year, '[0-9]{4}'))) %>%
       filter(year >= 2008),
@@ -100,101 +102,101 @@ list(
 # Calculate proportions ---------------------------------------------------
 
 
-  tar_target(
-    overall,
-    calcProp(diab_list, years, NULL),
-    pattern = map(diab_list, years)
-  ),
-  tar_target(
-    sex,
-    calcProp(diab_list, years, 'SEX'),
-    pattern = map(diab_list, years)
-  ),
-  tar_target(
-    race,
-    calcProp(diab_list, years, 'RACE_all'),
-    pattern = map(diab_list, years)
-  ),
-  tar_target(
-    edu,
-    calcProp(diab_list, years, 'HIDEG_all'),
-    pattern = map(diab_list, years)
-  ),
-  tar_target(
-    ages,
-    calcProp(diab_list, years, "AGE_all"),
-    pattern = map(diab_list, years)
-  ),
-  tar_target(
-    pov,
-    calcProp(diab_list, years, 'POVCAT_all'),
-    pattern = map(diab_list, years)
-  ),
-  tar_target(
-    region,
-    calcProp(diab_list, years, 'REGION_all'),
-    pattern = map(diab_list, years)
-  ),
-  tar_target(
-    insurance,
-    calcProp(diab_list, years, 'INSCOV_all'),
-    pattern = map(diab_list, years)
-    ),
-  tar_target(dash_files,
-             list.files(
-               here::here('data', 'dashboard'), full.names = TRUE
-             )),
+  # tar_target(
+  #   overall,
+  #   calcProp(diab_list, years, NULL),
+  #   pattern = map(diab_list, years)
+  # ),
+  # tar_target(
+  #   sex,
+  #   calcProp(diab_list, years, 'SEX'),
+  #   pattern = map(diab_list, years)
+  # ),
+  # tar_target(
+  #   race,
+  #   calcProp(diab_list, years, 'RACE_all'),
+  #   pattern = map(diab_list, years)
+  # ),
+  # tar_target(
+  #   edu,
+  #   calcProp(diab_list, years, 'HIDEG_all'),
+  #   pattern = map(diab_list, years)
+  # ),
+  # tar_target(
+  #   ages,
+  #   calcProp(diab_list, years, "AGE_all"),
[…]

### 2023-03-30 scripts/functions.R

@@ -6,10 +6,21 @@ library(haven)
 # Read in data
 readAndSelect <- function(data_path, data_year) {
   yr <- substr(data_year, 7, 8)
+  prv_yr <- str_pad(as.numeric(yr) - 1, width = 2, side = 'left', pad = '0')
   eye_var <- paste0('DSEY', yr, '53')
   chol_var <- paste0('DSCH', yr, '53')
   feet_var <- paste0('DSFT', yr, '53')
   flu_var <- paste0('DSFL', yr, '53')
+  flu_var_prv <- paste0('DSFL', prv_yr, '53') # Checking the previous year flu shot variable
+  medicaid <- paste0('MCDEV', yr)
+  medicare <- paste0('MCREV', yr)
+  private <- paste0('PRVEV', yr)
+  tricare <- paste0('TRIEV', yr)
+  other_pub <- paste0('GVAEV', yr) # Other public
+  other_pub2 <- paste0('GVBEV', yr) # Other public that is HMO
+  other_pub3 <- paste0('GVCEV', yr) # Other public where premium paid
+  other_pubA <- paste0('OPAEV', yr) # Other pub pre 2018
+  other_pubB <- paste0('OPBEV', yr) # Other pub pre 2018
   if (str_ends(data_path, '[sSpP]{3}') == TRUE) {
     temp <- read_xpt(data_path)
 
@@ -46,15 +57,16 @@ readAndSelect <- function(data_path, data_year) {
            starts_with('POVCAT'), # Categorical poverty status
            #starts_with('POVLEV'), # Continuous poverty status
            starts_with('REGION'),
-           starts_with('DENTCK53'), # Dental checkup, only 2000 - 2016,
+           #starts_with('DENTCK53'), # Dental checkup, only 2000 - 2016,
            matches('DVTOT[0-9]{2}'), # # of dental care visits in YYYY
            starts_with('CHOLCK'), # Cholesterol check, only 2000 - 2016,
            starts_with('CHECK53'), # Routine check up, only 2000 - 2016,
            starts_with('FLUSHT'), # Flu shot. only 2000 - 2016
-           starts_with('DSFL'),
+           #starts_with('DSFL'),
            starts_with('DIAB'), # 3 different variable names for diabetes, all start with DIABDX. this should also grab the DAIBW weight variables
            starts_with(!!eye_var), # Get only the eye variable for each year
-           starts_with(!!flu_var),
+           #starts_with(!!flu_var),
[…]

### 2023-03-30 scripts/temp_code.R

@@ -1,0 +1,161 @@
+library(gtsummary)
+library(tidyverse)
+library(srvyr)
+library(gt)
+library(survey)
+library(targets)
+tar_load(diab_list)
+`%!in%` <- Negate(`%in%`)
+
+ageStandardSurvey <- function(data) {
+  data %>%
+    as_survey_design(
+      ids = VARPSU_all,
+      weights = DIABW,
+      strata = VARSTR_all,
+      nest = TRUE
+    ) %>%
+    svystandardize(.,
+                   ~ AGE_all,
+                   ~ 1,
+                   population = c(0.530535, 0.299194, 0.088967, 0.081304))
+}
+
+countsAndProps <- function(data, variable, year) {
+  variable_sym <- as.symbol(variable)
+  counts <- data %>%
+    group_by( {{variable_sym}} ) %>%
+    survey_count()
+
+  props <- data %>%
+    group_by( {{variable_sym}}) %>%
+    summarise(survey_prop()) %>%
+    rename(prop = coef)
+
+  out <- left_join(counts, props) %>%
+    ungroup() %>%
+    mutate(Insurance_Type = case_when({{variable_sym}} == 'YES' ~ paste0(variable, '_YES'),
+                                        {{variable_sym}} == 'NO' ~ paste0(variable, '_NO')))
+  out <- out[, c('Insurance_Type', 'prop', 'n')]
+  names(out)[c(2, 3)] <- paste(names(out)[c(2, 3)], year, sep = "_")
+  out
+
+}
+
+unweightedCounts <- function(data) {
+  data %>%
+    tbl_svysummary(include = 'MEDICARE',
+                  statistic = list(all_categorical() ~ "{n_unweighted}"))
+}
+
+diab_age_srvy <- map(diab_list, ~ageStandardSurvey(.x))
+dat_grid <- expand_grid(
+  year = 2008:2020,
+  variable = c(
+    'MEDICARE',
+    'MEDICAID',
+    'OPAEV_all',
+    'OPBEV_all',
+    'PRVEV_all',
+    'TRIEV_all',
+    'GVAEV_all',
+    'GVBEV_all',
+    'GVCEV_all'
+  )
+) %>%
+  arrange(variable, year) %>%
+  mutate(data = rep(diab_age_srvy, 9)) %>%
+  filter(
+    variable %in% c(
+      'MEDICARE',
+      'MEDICAID',
+      'OPAEV_all',
[…]

### 2023-05-19 scripts/manuscript/graveyard.qmd
Committing before making a big change to code

@@
 For example, the trends for all six practices split by sex tend to be very similar, whereas the gaps between the different insurance group trends are larger.
+
+         ` ` = as.factor(` `) %>% fct_relevel('Overall',
+                           'Age: 18 to 44',
+                           'Age: 45 to 64',
+                           'Age: 65 to 74',
+                           'Age: 75+',
+                           'Sex: Female',
+                           'Sex: Male',
+                           'Race/Ethnicity: Asian/Not Hispanic',
+                           'Race/Ethnicity: Black/Not Hispanic',
+                           'Race/Ethnicity: Hispanic',
+                           'Race/Ethnicity: White/Not Hispanic',
+                           'Highest degree earned: Greater than high school',
+                           'Highest degree earned: High school',
+                           'Highest degree earned: Less than high school',
+                           'Insurance coverage: Medicaid',
+                           'Insurance coverage: Medicare only',
+                           'Insurance coverage: Private only',
+                           'Insurance coverage: Uninsured',
+                           'Poverty income ratio: > 400%',
+                           'Poverty income ratio: 200% - 399%',
+                           'Poverty income ratio: 100% - 199%',
+                           'Poverty income ratio: < 100%')) %>%
+
+# This code here changes the apc values to NA if they aren't significant, but I think
+    # what I need to do is change the APC values if there are no identified joinpoints
+    # across(
+    #   c(apc_0, apc_95_lcl_0, apc_95_ucl_0),
+    #   ~ case_when(p_value_0 > 0.05 &
+    #                 p_value_1 > 0.05 & p_value_2 > 0.05 & p_value_3 > 0.05 ~ NA_real_,
+    #               TRUE ~ .x)
+    # ),
+    # across(
+    #   c(apc_1, apc_95_lcl_1, apc_95_ucl_1),
+    #   ~ case_when(p_value_0 > 0.05 &
+    #                 p_value_1 > 0.05 & p_value_2 > 0.05 & p_value_3 > 0.05 ~ NA_real_,
+    #               TRUE ~ .x)
+    # ),
+    # across(
+    #   c(apc_2, apc_95_lcl_2, apc_95_ucl_2),
+    #   ~ case_when(p_value_0 > 0.05 &
+    #                 p_value_1 > 0.05 & p_value_2 > 0.05 & p_value_3 > 0.05 ~ NA_real_,
+    #               TRUE ~ .x)
+    # ),
+    # across(
+    #   c(apc_3, apc_95_lcl_3, apc_95_ucl_3),
+    #   ~ case_when(p_value_0 > 0.05 &
+    #                 p_value_1 > 0.05 & p_value_2 > 0.05 & p_value_3 > 0.05 ~ NA_real_,
+    #               TRUE ~ .x)
+    # ),
+
+```{r all-plots}
+
+stats_table_plot_dat <- jp_proportion_plot_data %>%
+  mutate(model = as.numeric(model)) %>% 
+  filter(strata != 'Total') %>%
+  filter(strata != 'Not available') %>% 
+  filter(strata != 'Other Race/Not Hispanic') %>% 
+  filter(strata != 'Other') %>% 
+  mutate(variable_text = case_when(variable == 'a1c' ~ 'Two or more A1C tests',
+                                   variable == 'CHOL_all' ~ 'Cholesterol tested',
+                                   variable == 'DENT_all' ~ 'One or more dentist visits',
+                                   variable == 'eye-exam' ~ 'Eye exam with dilation',
+                                   variable == 'flu' ~ 'Received flu vaccine',
+                                   variable == 'foot' ~ 'Foot examination'),
+         strata = case_when(strata == 'stat_0' ~ 'Overall',
+                            TRUE ~ strata)) %>% 
+  mutate(strata = as.factor(strata)) %>% 
+  split(., f = .$stratifier)
+
+stats_table_plot_dat <- map(stats_table_plot_dat, function(.x) {
+  .x %>% 
+    mutate(strata = fct_drop(strata))
+})
+
+overall_data <- stats_table_plot_dat$overall %>% 
+  mutate(strata = case_when(strata == 'Overall' ~ 'z'))
+# Remove the overall data from the list
+stats_table_plot_dat <- stats_table_plot_dat[-4]
+# Relevel the poverty factors
+stats_table_plot_dat$poverty$strata <-
+  factor(
+    stats_table_plot_dat$poverty$strata,
+    levels = c('High income', 'Middle income', 'Low income', 'Poor/Negative'),
+    labels = c(
+      '> 400% ',
+      '200% - 399%',
+      '100% - 199%',
+      '< 100%'
+
+    )
+  )
+test_plots <- stats_table_plot_dat %>% 
+   map(
+    ~ ggplot(filter(.x, variable %in% c('a1c', 'CHOL_all', 'flu')),
+             aes(
+      x = year,
+      y = p,
+      group = strata,
+      color = strata
+    )) +
+      #geom_point() +
+      geom_line(aes(x = year, y = model, group = strata, color = strata)) +
+      geom_line(data = filter(overall_data, variable %in% c('a1c', 'CHOL_all', 'flu')),
+                  aes(x = year, y = model),
+                  color = 'black',
+                  linetype = 'dashed') +
+      facet_wrap( ~ variable_text, ncol = 3) +
+      theme_classic() +
+      scale_y_continuous(
+        limits = c(00, 100),
+        breaks = seq(0, 100, 25),
+        labels = seq(0, 100, 25)
+      ) +
+      scale_x_continuous(
+        limits = c(2008, 2020),
+        breaks = seq(2008, 2020, 2),
+        labels = seq(2008, 2020, 2)
+      ) +
+      scale_color_brewer(type = 'qual', palette = 'Set2') +
+      theme(axis.text = element_text(color = 'black'),
+            axis.text.x = element_text(angle = 45, hjust = 0.9, vjust = 0.95),
+            legend.title = element_text(size = 8),
+            legend.text = element_text(size = 6)) +
+      labs(x = 'Year', y = 'Percentage')
+  )
+
+test_plots[[1]] <- test_plots[[1]] + labs(color = 'Age (grouped)') +
+  theme(axis.title.x = element_blank())
+test_plots[[2]] <-
+  test_plots[[2]] + labs(color = 'Highest degree \nobtained') + theme(
+    strip.background =  element_blank(),
+    strip.text = element_blank(),
+    axis.title.x = element_blank()
+  )
+test_plots[[3]] <-
+  test_plots[[3]] + labs(color = "Insurance") + theme(
+    strip.background =  element_blank(),
+    strip.text = element_blank(),
+    axis.title.x = element_blank()
+  )
+test_plots[[4]] <-
+  test_plots[[4]] + labs(color = 'Poverty income ratio') + theme(
+    strip.background =  element_blank(),
+    strip.text = element_blank()
+  )
+test_plots[[5]] <-
+  test_plots[[5]] + labs(color = 'Race & Ethnicity') + theme(
+    strip.background =  element_blank(),
+    strip.text = element_blank(),
+    axis.title.x = element_blank()
+  )
+test_plots[[6]] <-
+  test_plots[[6]] + labs(color = 'Sex') + theme(strip.background =  element_blank(),
+                                                strip.text = element_blank(),
+    axis.title.x = element_blank())
+test_plots <- list(
+  test_plots[[1]],
+  test_plots[[6]],
+  test_plots[[5]],
+  test_plots[[2]],
+  test_plots[[3]],
+  test_plots[[4]]
+)
+
+exam_plots <- stats_table_plot_dat %>% 
+   map(
+    ~ ggplot(filter(.x, variable %!in% c('a1c', 'CHOL_all', 'flu')),
+             aes(
+      x = year,
+      y = p,
+      group = strata,
+      color = strata
+    )) +
+      #geom_point() +
+      geom_line(aes(x = year, y = model, group = strata, color = strata)) +
+      geom_line(data = filter(overall_data, variable %!in% c('a1c', 'CHOL_all', 'flu')),
+                  aes(x = year, y = model),
+                  color = 'black',
+                  linetype = 'dashed') +
+      facet_wrap( ~ variable_text, ncol = 3) +
+      theme_classic() +
+      scale_y_continuous(
+        limits = c(  0, 100),
+        breaks = seq(0, 100, 25),
+        labels = seq(0, 100, 25)
+      ) +
+      scale_x_continuous(
+        limits = c(2008, 2020),
+        breaks = seq(2008, 2020, 2),
+        labels = seq(2008, 2020, 2)
+      ) +
+      scale_color_brewer(type = 'qual', palette = 'Set2') +
+      theme(axis.text = element_text(color = 'black'),
+            axis.text.x = element_text(angle = 45, hjust = 0.9, vjust = 0.95),
+            legend.title = element_text(size = 8),
+            legend.text = element_text(size = 7)) +
+      labs(x = 'Year', y = 'Percentage')
+  )
+
+exam_plots[[1]] <- exam_plots[[1]] + labs(color = 'Age (grouped)') +
+  theme(axis.title.x = element_blank())
+exam_plots[[2]] <-
+  exam_plots[[2]] + labs(color = 'Highest degree \nobtained') + theme(
+    strip.background =  element_blank(),
+    strip.text = element_blank(),
+    axis.title.x = element_blank()
+  )
+exam_plots[[3]] <-
+  exam_plots[[3]] + labs(color = "Insurance") + theme(
+    strip.background =  element_blank(),
+    strip.text = element_blank(),
+    axis.title.x = element_blank()
+  )
+exam_plots[[4]] <-
+  exam_plots[[4]] + labs(color = 'Poverty income ratio') + theme(
+    strip.background =  element_blank(),
+    strip.text = element_blank()
+  )
+exam_plots[[5]] <-
+  exam_plots[[5]] + labs(color = 'Race & Ethnicity') + theme(
+    strip.background =  element_blank(),
+    strip.text = element_blank(),
+    axis.title.x = element_blank()
+  )
+exam_plots[[6]] <-
+  exam_plots[[6]] + labs(color = 'Sex') + theme(strip.background =  element_blank(),
+                                                strip.text = element_blank(),
+    axis.title.x = element_blank())
+exam_plots <- list(
+  exam_plots[[1]],
+  exam_plots[[6]],
+  exam_plots[[5]],
+  exam_plots[[2]],
+  exam_plots[[3]],
+  exam_plots[[4]]
+)
+
+# all_exam_plots <- exam_plots %>% 
+#   wrap_plots(nrow = 6) &
+#   theme(plot.margin = margin(0.5, 0.5, 0.5, 0.5, 'pt'))
+# all_test_plots <- test_plots %>% 
+#   wrap_plots(nrow = 6) &
+#   theme(plot.margin = margin(0.5, 0.5, 0.5, 0.5, 'pt'))
+```
+
+Youngest age group was consistently lower than all others for cholesterol testing and receiving flu vaccine, and eye exam and foot exam
+
+Hispanic - lowest, although close for cholesterol and A1C (A1C until \~ 2018). And eye exam, but again real close
+
+\< HS consistently lower on all exams and A1c tests Uninsured lower on everything
+
+Flu - lots of increases. Hung et al found no change over 2007 - 2018 using NHIS data
+
+Cholesterol - a few decreases
+
+A1C - a few increases
+
+Dentists - kind of all over the place; Aldosari 2022 found no difference in utilization between people with diabetes and without (so not a trend analysis).
+Luo et al 2018 found declines for people with diabetes from 2004 - 2014
+
+Foot exams - mostly all flat, except older. PEraj 2019 found that Hispanic americans and asian-americans were significantly less likely to have a foot exam
+
+Eye exams - mostly flat or decreasing, except uninsured.
+Chen 2020 found there were increases after Medicaid expansion but only for the first two years.
+Eppley 2019 found no change in adherance from 2005 to 2016 using NHANES
+
+Mostly flat, some decreases.

### 2023-05-19 scripts/manuscript/manuscript_draft.qmd
Committing before making a big change to code

--- 2022-12-29 scripts/manuscript/manuscript_draft.qmd
@@
 
+specifyDecimal <- function(x, digits) trimws(format(round(x, digits), nsmall=digits))
+
+# For pulling specifically from the preventive table since the column name I use is
+# weird and doesn't like being bang-bang-banged.
+pullNumber <- function(data, filter.by, column, brackets = FALSE) {
+  out <- data %>% 
+    filter(` ` == filter.by) %>% 
+    select(!!!column) %>% 
+    pull() 
+  out <- gsub("\\(", "(95% CI: ", out)
+  if (brackets == TRUE) {
+    out <- out %>% 
+    str_replace("\\(", "\\[") %>% 
+    str_replace("\\)", "\\]")
+  }
+  out
+}
+# For other tables that don't use such weird column names
+pullNumber2 <- function(data, select.column, brackets = FALSE, ...) {
+  browser()
+   out <- data %>% 
+    ungroup() %>% 
+    filter(...) %>% 
+    pull( {{select.column}} )
+    out <- gsub("\\(", "(95% CI: ", out)
+    out <- gsub("(-?\\d+\\.\\d+)", "\\1%", out)
+  if (brackets == TRUE) {
+    out <- out %>% 
+    str_replace("\\(", "\\[") %>% 
+    str_replace("\\)", "\\]")
+  }
+  out
+}
+
+# Some numbers pulled from MEPS page:
+sample_size_response_rate <- tibble(
+  year = 2020:2008,
+  n = c(26847, 27648, 29415, 30716, 33259, 33893, 33162, 35068, 37182, 33622, 31228, 34920, 31262),
+  full_year_response = c(27.6, 39.5, 42.7, 44.2, 46.0, 47.7, 48.5, 52.8, 56.3, 54.9, 53.5, 57.2, 59.3)
+)
+
 ```
 
-**Trends in Preventive Care Practices among US Adults with Diabetes, 2008-2020**
+```{r preventive-table}
 
-Jacob T. Wittman, PhD Kai M. Bullard Stephen R. Benoit
-
-CDC Affiliation
-
-\pagebreak
-
-# Abstract
-
-\pagebreak
-
-# Introduction
-
--   Diabetes affects a lot of people
-    -   Kills people, makes them sick, reduces quality of life
-    -   Cost of management is high and increasing
--   Advances in diabetes management
-    -   Patients with diabetes must actually receive this care
--   Present trends in self-reported receipt of preventive care practices according to MEPS from 2008 - 2020.
-
-Diabetes is a chronic disease that affects XX people in the USA.
-
-# Methods
-
-## Data Source
-
-We used data from the Medical Expenditure Panel Survey (MEPS) from years 2008 - 2020.
-Participants in this survey are a subsample of households that participate in the National Health Interview Survey (NHIS).
-The MEP survey targets the civilian noninstitutionalized population in the US and provides national and regional estimates of health care use, expenditures, sources of payment and health insurance coverage.
-This survey also contains information on patient demographics, socioeconomics, and, via the Diabetes Care Survey (DCS), information on diabetes preventive care practices.
-The DCS is a self-administered paper-and-pencil questionnaire that is provided to MEPS respondents who indicate that they have been told by a doctor or health professional that they have diabetes.
-
-The data we used comes from the full-year consolidated file from MEPS for the 12 year time span of our report.
-We used a weighted population of XXX in this analysis.
-Our analysis is adjusted for the complex survey design, including clustering and stratification.
-Reported values for the proportions of different groups receiving recommended preventive care practices are age-adjusted.
-
-# Results
-
-# Discussion
-
-# References
-
-::: {#refs}
-:::
-
-# Tables
-
-```{r}
-# tar_load(age_adjusted_stats)
-# age_adjusted_stats %>% 
-#   #filter(stratifier != 'age') %>% 
-#   mutate(age_adjusted_prop = age_adjusted_prop * 100) %>% 
-#   pivot_wider(
-#     id_cols = c(stratifier, variable, var_label, strata),
-#     names_from = year,
-#     values_from = age_adjusted_prop
-#   ) %>% 
-#   group_by(stratifier, strata) %>%
-#   select(stratifier, var_label, `2008`:`2020`) %>%
-#   gt() %>% 
-#   fmt_number(columns = `2008`:`2020`, decimals = 1) %>% 
-#   gtsave('table_one.docx')
-```
-
-```{r}
-tar_load(age_adjusted_preventive)
-preventive_practice_table <- age_adjusted_preventive %>% 
-  filter(label == 'At least three preventive practices followed') %>% 
-  mutate(age_adjusted_prop = age_adjusted_prop * 100) %>% 
-  pivot_wider(
-    id_cols = c(stratifier, variable, label, strata),
-    names_from = year,
-    values_from = age_adjusted_prop
-  ) %>% 
-  filter(strata %!in% c('Not available', 'Other Race/Not Hispanic')) %>% 
-  mutate(stratifier = factor(stratifier,
-                             c('overall', 'age', 'sex', 'race', 'edu', 'insurance', 'poverty')),
-         strata = case_when(strata == 'stat_0' ~ '-', 
-                            strata == 'Greater than HS' ~ 'Greater than high school',
-                            TRUE ~ strata)) %>% 
-  mutate(strata = as.factor(strata)) %>% 
-  mutate(stratifier = recode_factor(
-    stratifier,
-    overall = 'Overall',
-    age = 'Age',
-    sex = 'Sex',
-    race = 'Race/Ethnicity',
-    edu = 'Highest degree earned',
-    insurance = 'Insurance coverage',
-    poverty = 'Poverty level'
-  )) %>% 
-  group_by(stratifier) %>%
-  select(stratifier, strata, `2008`:`2020`) %>%
-  gt() %>% 
-  fmt_number(columns = `2008`:`2020`, decimals = 1)
-preventive_practice_table$`_data` <- preventive_practice_table$`_data`[c(1:18, 20, 19, 21), ]
-preventive_practice_table %>% 
-  gtsave('preventive_practices.docx')
-```
-
-```{r}
+tar_load(c(jp_prevention_apc,
+           jp_prevention_aapc,
+           age_adjusted_preventive,
+           jp_proportion_plot_data,
+           age_adjusted_stats
+           ),
+         store = here::here('_targets/'))
 # Clean up the AAPC table and get it into format for printing to table
@@
 
-# Clean up the age adjusted preventive practices and then join with the aapc table
+# Clean up the age adjusted preventive services and then join with the aapc table
 clean_age_adjusted <- age_adjusted_preventive %>% 
   # Filter to just the >=3 practices
-  filter(label == 'At least three preventive practices followed') %>% 
+  filter(variable == 'zero_practices') %>% 
   # Filter down to every other year
-  filter(year %in% seq(2000, 2020, by = 2)) %>% 
-  mutate(age_adjusted_prop = age_adjusted_prop * 100,
-         chr_age_adj_prop = sigfig(age_adjusted_prop, digits = 4),
-         age_adjusted_se_perc = sigfig(age_adjusted_se_perc, digits = 2),
+  filter(year %in% seq(2000, 2020, by = 1)) %>% 
+  mutate(chr_age_adj_prop = sigfig(p, digits = 3),
+         p.std.error = p.std.error * 100,
+         age_adjusted_se_perc = sigfig(p.std.error, digits = 2),
          percentage = glue::glue('{chr_age_adj_prop} ({age_adjusted_se_perc})')) %>% 
@@
 
+# Rename strata to a blank name to remove it from the final table
 preventive_practice_table <- cleaned_preventive_df %>% 
+  filter(strata != 'Other') %>% 
   group_by(stratifier) %>%
-  select(stratifier, strata, `2008`:`2020`, `Percent Change`, `Joinpoint Year` = segment,
+  select(stratifier, ` ` = strata, `2008`:`2020`, `Percent Change (95% CI)`, `Joinpoint Year` = segment,
          `APC Period 1`, `APC Period 2`, `AAPC`) %>%
-  mutate(stratifier = case_when(as.character(stratifier) == 'Poverty level' ~ 'Income as % of poverty line',
+  mutate(stratifier = case_when(as.character(stratifier) == 'Poverty level' ~ 'Poverty income ratio',
                                 TRUE ~ as.character(stratifier))) %>% 
+  # Rename some columns to add () info
+  rename(`2008 (SE)` = `2008`,
+         `2009 (SE)` = `2009`,
+         `2010 (SE)` = `2010`,
+         `2011 (SE)` = `2011`,
+         `2012 (SE)` = `2012`,
+         `2013 (SE)` = `2013`,
+         `2014 (SE)` = `2014`,
+         `2015 (SE)` = `2015`,
+         `2016 (SE)` = `2016`,
+         `2017 (SE)` = `2017`,
+         `2018 (SE)` = `2018`,
+         `2019 (SE)` = `2019`,
+         `2020 (SE)` = `2020`,
+         `APC Period 1 (95% CI)` = `APC Period 1`,
+         `APC Period 2 (95% CI)` = `APC Period 2`,
+         `AAPC (95% CI)` = `AAPC`) %>% 
   gt() %>% 
   sub_missing(missing_text = ' ')
-preventive_practice_table$`_data` <- preventive_practice_table$`_data`[c(1:18, 20, 19, 21), ]
-preventive_practice_table %>% 
-  gtsave('preventive_practices.docx')
+
+# Reorganize insurance variables
+preventive_practice_table$`_data` <- preventive_practice_table$`_data`[c(1:14, 15, 18, 16, 17, 19:22), ]
+tab1 <- preventive_practice_table$`_data`
 ```
 
-# Figures
+```{r preventive-table-sans-2020}
+tar_load(ends_with('sans_2020'),
+         store = here::here('_targets/'))
+# Clean up the AAPC table and get it into format for printing to table
+cleaned_jp_aapc_sans_2020 <- jp_prevention_aapc_sans_2020 %>% 
+  select(-aapc_index) %>% 
+  mutate(aapc = specifyDecimal(aapc, digits = 1),
+        across(starts_with('aapc_'),
+                ~specifyDecimal(x = .x, digits = 1)),
+         across(starts_with('aapc'),
+                ~case_when(.x == ' NA' ~ NA_character_,
+                           TRUE ~ .x)),
+         AAPC = case_when(!is.na(aapc) ~ glue::glue('{aapc} ({aapc_c_i_low}, {aapc_c_i_high})'),
+                          TRUE ~ NA_character_)) %>%
+  select(stratifier, strata, AAPC)
 
-```{r}
-tar_load(age_adjusted_stats)
-tar_load(jp_proportion_plot_data)
+# Format APC table for future joining
+cleaned_jp_apc_sans_2020 <- jp_prevention_apc_sans_2020 %>% 
+  # No model has more than a single joinpoint, so make wider and then
+  # remove the excess columns to determine if there's no join point (segmend_end = 2020)
+  # or a joinpoint (segment_end != 2019)
+  pivot_wider(id_cols = c(stratifier, strata, model),
+              names_from = segment,
+              values_from = c(segment_start, segment_end, apc, p_value, apc_significant,
+                              apc_95_lcl, apc_95_ucl)
+  ) %>% 
+  select(-segment_start_0, -segment_start_1, -segment_end_1, -apc_significant_0, -apc_significant_1) %>% 
+  # Make segment empty if no joinpoint
+  mutate(segment = case_when(segment_end_0 == 2019 ~ NA_integer_,
+                             TRUE ~ segment_end_0)) %>% 
+  # MAke apc empty if not significant
+  mutate(across(c(apc_0, apc_95_lcl_0, apc_95_ucl_0),
+                ~ case_when(p_value_0 > 0.05 & p_value_1 > 0.05 ~ NA_real_,
+                            TRUE ~ .x)), 
+         across(c(apc_1, apc_95_lcl_1, apc_95_ucl_1),
+                ~ case_when(p_value_0 > 0.05 & p_value_1 > 0.05 ~ NA_real_,
+                            TRUE ~ .x)),
+         across(starts_with('apc_0') | starts_with('apc_1') | starts_with('p_'),
+                ~specifyDecimal(.x, digits = 1)),
+         across(contains('cl'),
+                ~specifyDecimal(.x, digits = 1)),
+         across(starts_with('apc') | starts_with('p_'),
+                ~case_when(.x == 'NA' ~ NA_character_,
+                           TRUE ~ .x))) %>% 
+  # Concatenate apc column with CI columns
+  mutate(`APC Period 1` = case_when(
+       !is.na(apc_0) ~ glue::glue('{apc_0} ({apc_95_lcl_0}, {apc_95_ucl_0})'),
+       TRUE ~ NA_character_
+                                    ),
+    `APC Period 2` = case_when(
+       !is.na(apc_1) ~ glue::glue('{apc_1} ({apc_95_lcl_1}, {apc_95_ucl_1})'),
+       TRUE ~ NA_character_
+    )
+  ) %>%
+  select(stratifier, strata, segment, starts_with('APC '))
 
+# Clean up the age adjusted preventive practices and then join with the aapc table
+clean_age_adjusted <- age_adjusted_preventive %>% 
+  # Filter to just the >=3 practices
+  filter(variable == 'zero_practices') %>% 
+  # Filter down to every other year
+  filter(year %in% seq(2000, 2020, by = 1)) %>% 
+  mutate(chr_age_adj_prop = specifyDecimal(p, digits = 1),
+         p.std.error = p.std.error * 100,
+         age_adjusted_se_perc = specifyDecimal(p.std.error, digits = 1),
+         percentage = glue::glue('{chr_age_adj_prop} ({age_adjusted_se_perc})')) %>% 
+  pivot_wider(
+    id_cols = c(stratifier, variable, label, strata),
+    names_from = year,
+    values_from = c(p, percentage, p.std.error),
+  ) %>% 
+  # Remove excess strata
+  filter(strata %!in% c('Not available', 'Other Race/Not Hispanic')) %>% 
+  # Relevel stratifier factor, clean up stratifier and strata names
+  mutate(stratifier = factor(stratifier,
+                             c('overall', 'age', 'sex', 'race', 'edu', 'insurance', 'poverty')),
+         strata = case_when(strata == 'stat_0' ~ '-', 
+                            strata == 'Greater than HS' ~ 'Greater than high school',
+                            TRUE ~ strata),
+         percent_change = ((p_2019 - p_2008) / p_2008) * 100,
+         percent_change_se = (abs(p_2019 / p_2008) * sqrt((p.std.error_2019^2 / p_2019^2) + (p.std.error_2008^2 / p_2008^2)) * 100),
+         perc_change_lcl = percent_change - 1.96 * percent_change_se,
+         perc_change_ucl = percent_change + 1.96 * percent_change_se,
+         perc_change_char = specifyDecimal(percent_change, digits = 1),
+         perc_change_lcl_char = specifyDecimal(perc_change_lcl, digits = 1),
+         perc_change_ucl_char = specifyDecimal(perc_change_ucl, digits = 1),
+         `Percent Change (95% CI)` = glue::glue('{perc_change_char} ({perc_change_lcl_char}, {perc_change_ucl_char})')) %>% 
+  select(-starts_with('age_adjusted_prop'), -starts_with('p.std.error'), -contains('_change_')) %>% 
+  setNames(., str_replace(names(.), 'percentage_', "")) %>% 
+  mutate(strata = as.factor(strata)) %>% 
+  mutate(stratifier = recode_factor(
+    stratifier,
+    overall = 'Overall',
+    age = 'Age',
+    sex = 'Sex',
+    race = 'Race/Ethnicity',
+    edu = 'Highest degree earned',
+    insurance = 'Insurance coverage',
+    poverty = 'Poverty level'
+  )) %>% 
+  # Join with AAPC table
+  left_join(cleaned_jp_aapc_sans_2020, by = c('stratifier', 'strata'))
+
+cleaned_preventive_df_sans_2020 <- left_join(clean_age_adjusted, cleaned_jp_apc_sans_2020, by = c('stratifier', 'strata')) %>% 
+  mutate(AAPC = case_when(is.na(AAPC) & is.na(`APC Period 2`) ~ `APC Period 1`,
+                          TRUE ~ AAPC),
+         `APC Period 1` = case_when(is.na(`APC Period 1`) & is.na(`APC Period 2`) ~ AAPC,
+                                    TRUE ~ `APC Period 1`)) %>%
+  # Rename poverty levels
+  mutate(strata = case_when(as.character(strata) == 'Poor/Negative' ~ '< 100%',
+                            as.character(strata) == 'Low income' ~ '100% - 199%',
+                            as.character(strata) == 'Middle income' ~ '200% - 399%',
+                            as.character(strata) == 'High income' ~ '> 400%',
+                            TRUE ~ as.character(strata)))
+
+# Rename strata to a blank name to remove it from the final table
+preventive_practice_table_sans_2020 <- cleaned_preventive_df_sans_2020 %>% 
+  filter(strata != 'Other') %>% 
+  group_by(stratifier) %>%
+  select(stratifier, ` ` = strata, `2008`:`2020`, `Percent Change (95% CI)`, `Joinpoint Year` = segment,
+         `APC Period 1`, `APC Period 2`, `AAPC`) %>%
+  mutate(stratifier = case_when(as.character(stratifier) == 'Poverty level' ~ 'Poverty income ratio',
+                                TRUE ~ as.character(stratifier))) %>% 
+  # Rename some columns to add () info
+  rename(`2008 (SE)` = `2008`,
+         `2009 (SE)` = `2009`,
+         `2010 (SE)` = `2010`,
+         `2011 (SE)` = `2011`,
+         `2012 (SE)` = `2012`,
+         `2013 (SE)` = `2013`,
+         `2014 (SE)` = `2014`,
+         `2015 (SE)` = `2015`,
+         `2016 (SE)` = `2016`,
+         `2017 (SE)` = `2017`,
+         `2018 (SE)` = `2018`,
+         `2019 (SE)` = `2019`,
+         `2020 (SE)` = `2020`,
+         `APC Period 1 (95% CI)` = `APC Period 1`,
+         `APC Period 2 (95% CI)` = `APC Period 2`,
+         `AAPC (95% CI)` = `AAPC`) %>% 
+  gt() %>% 
+  sub_missing(missing_text = ' ') %>% 
+  tab_footnote(
+    footnote = "Values in these columns were estimated excluding data from 2020.",
+    locations = cells_column_labels(
+      columns = c(`Percent Change (95% CI)`,
+      `APC Period 1 (95% CI)`,
+      `APC Period 2 (95% CI)`,
+      `AAPC (95% CI)`
+    ))
+  ) %>% 
+  tab_options(footnotes.marks = "a")
+# Reorganize insurance variables
+ preventive_practice_table_sans_2020$`_data` <- preventive_practice_table_sans_2020$`_data`[c(1:14, 15, 18, 16, 17, 19:22), ]
+
+tab_sans_2020 <- preventive_practice_table_sans_2020$`_data`
+
+```
+
+```{r proportion-table-sans-2020}
+# Clean up the AAPC table and get it into format for printing to table
+cleaned_prop_aapc_sans_2020 <- jp_proportion_aapc_sans_2020 %>% 
+  select(-aapc_index) %>% 
+  mutate(aapc = specifyDecimal(aapc, digits = 1),
+        across(starts_with('aapc_'),
+                ~specifyDecimal(x = .x, digits = 1)),
+         across(starts_with('aapc'),
+                ~case_when(.x == ' NA' ~ NA_character_,
+                           TRUE ~ .x)),
+         AAPC = case_when(!is.na(aapc) ~ glue::glue('{aapc} ({aapc_c_i_low}, {aapc_c_i_high})'),
+                          TRUE ~ NA_character_)) %>%
+  select(stratifier, strata, practice, AAPC)
+
+# Format APC table for future joining
+cleaned_prop_apc_sans_2020 <- jp_proportion_apc_sans_2020 %>% 
+  # No model has more than a single joinpoint, so make wider and then
+  # remove the excess columns to determine if there's no join point (segmend_end = 2020)
+  # or a joinpoint (segment_end != 2019)
+  pivot_wider(id_cols = c(stratifier, strata, practice, model),
+              names_from = segment,
+              values_from = c(segment_start, segment_end, apc, p_value, apc_significant,
+                              apc_95_lcl, apc_95_ucl)
+  ) %>% 
+  mutate(
+    # This code here changes the apc values to NA if they aren't significant, but I think
+    # what I need to do is change the APC values if there are no identified joinpoints
+    # across(
+    #   c(apc_0, apc_95_lcl_0, apc_95_ucl_0),
+    #   ~ case_when(!is.na(segment_start_1) 0.05 &
+    #                 p_value_1 > 0.05 & p_value_2 > 0.05 & p_value_3 > 0.05 ~ NA_real_,
+    #               TRUE ~ .x)
+    # ),
+    # across(
+    #   c(apc_1, apc_95_lcl_1, apc_95_ucl_1),
+    #   ~ case_when(p_value_0 > 0.05 &
+    #                 p_value_1 > 0.05 & p_value_2 > 0.05 & p_value_3 > 0.05 ~ NA_real_,
+    #               TRUE ~ .x)
+    # ),
+    # across(
+    #   c(apc_2, apc_95_lcl_2, apc_95_ucl_2),
+    #   ~ case_when(p_value_0 > 0.05 &
+    #                 p_value_1 > 0.05 & p_value_2 > 0.05 & p_value_3 > 0.05 ~ NA_real_,
+    #               TRUE ~ .x)
+    # ),
+    # across(
+    #   c(apc_3, apc_95_lcl_3, apc_95_ucl_3),
+    #   ~ case_when(p_value_0 > 0.05 &
+    #                 p_value_1 > 0.05 & p_value_2 > 0.05 & p_value_3 > 0.05 ~ NA_real_,
+    #               TRUE ~ .x)
+    # ),
+    across(
+      matches('apc_[0-9]{1}') | starts_with('p_'),
+      ~ specifyDecimal(.x, digits = 1)
+    )
+  ) %>% 
+    select(-contains('significant')) %>% 
+    mutate(across(starts_with('apc') | starts_with('p_'),
+                ~case_when(.x == 'NA' ~ NA_character_,
+                           TRUE ~ .x))) %>% 
+  # Concatenate apc column with CI columns
+  mutate(`APC Period 1` = case_when(
+       !is.na(apc_0) ~ glue::glue('{apc_0} ({apc_95_lcl_0}, {apc_95_ucl_0})'),
+       TRUE ~ NA_character_
+                                    ),
+    `APC Period 2` = case_when(
+       !is.na(apc_1) ~ glue::glue('{apc_1} ({apc_95_lcl_1}, {apc_95_ucl_1})'),
+       TRUE ~ NA_character_
+    ),
+    `APC Period 3` = case_when(
+       !is.na(apc_2) ~ glue::glue('{apc_2} ({apc_95_lcl_2}, {apc_95_ucl_2})'),
+       TRUE ~ NA_character_
+    ),
+    `APC Period 4` = case_when(
+       !is.na(apc_3) ~ glue::glue('{apc_3} ({apc_95_lcl_3}, {apc_95_ucl_3})'),
+       TRUE ~ NA_character_
+    )
+  ) %>%
+    # Make segment empty if no joinpoint
+  mutate(segment = ifelse(!is.na(segment_start_1) & !is.na(segment_start_2) & !is.na(segment_start_3), 
+                             paste(segment_start_1, segment_start_2, segment_start_3, sep = ", "),
+                             ifelse(!is.na(segment_start_1) & !is.na(segment_start_2) & is.na(segment_start_3),
+                                    paste(segment_start_1, segment_start_2, sep = ", "),
+                                    ifelse(!is.na(segment_start_1) & is.na(segment_start_2) & is.na(segment_start_3),
+                                           segment_start_1,
+                                           ifelse(segment_end_0 == 2019, NA_character_, 'Check me')
+                                           )
+                                    )
+                             )
+         ) %>% 
+  # MAke apc empty if not significant
+  select(stratifier, strata, practice, segment, starts_with('APC '), -segment_start_0, -segment_start_1, -segment_end_1)
+
+# Clean up the age adjusted preventive practices and then join with the aapc table
+clean_age_adjusted_prop <- age_adjusted_stats %>% 
+  # Filter to just the >=3 practices
+  #filter(label == 'At least three preventive practices followed') %>% 
+  # Filter down to every other year
+  filter(year %in% seq(2000, 2020, by = 1)) %>% 
+  mutate(chr_age_adj_prop = specifyDecimal(p, digits = 1),
+         p.std.error = p.std.error * 100,
+         age_adjusted_se_perc = specifyDecimal(p.std.error, digits = 1),
+         percentage = glue::glue('{chr_age_adj_prop} ({age_adjusted_se_perc})')) %>% 
+  pivot_wider(
+    id_cols = c(stratifier, variable, label, strata),
+    names_from = year,
+    values_from = c(p, percentage, p.std.error),
+  ) %>% 
+  # Remove excess strata
+  filter(strata %!in% c('Not available', 'Other Race/Not Hispanic')) %>% 
+  # Relevel stratifier factor, clean up stratifier and strata names
+  mutate(stratifier = factor(stratifier,
+                             c('overall', 'age', 'sex', 'race', 'edu', 'insurance', 'poverty')),
+         strata = case_when(strata == 'stat_0' ~ '-', 
+                            strata == 'Greater than HS' ~ 'Greater than high school',
+                            TRUE ~ strata),
+         percent_change = ((p_2019 - p_2008) / p_2008) * 100,
+         percent_change_se = (abs(p_2019 / p_2008) * sqrt((p.std.error_2019^2 / p_2019^2) + (p.std.error_2008^2 / p_2008^2)) * 100),
+         perc_change_lcl = percent_change - 1.96 * percent_change_se,
+         perc_change_ucl = percent_change + 1.96 * percent_change_se,
+         perc_change_char = specifyDecimal(percent_change, digits = 1),
+         perc_change_lcl_char = specifyDecimal(perc_change_lcl, digits = 1),
+         perc_change_ucl_char = specifyDecimal(perc_change_ucl, digits = 1),
+         `Percent Change (95% CI)` = glue::glue('{perc_change_char} ({perc_change_lcl_char}, {perc_change_ucl_char})')) %>% 
+  select(-starts_with('age_adjusted_prop'), -starts_with('p.std.error'), -contains('_change_')) %>% 
+  setNames(., str_replace(names(.), 'percentage_', "")) %>% 
+  mutate(strata = as.factor(strata)) %>% 
+  mutate(stratifier = recode_factor(
+    stratifier,
+    overall = 'Overall',
+    age = 'Age',
+    sex = 'Sex',
+    race = 'Race/Ethnicity',
+    edu = 'Highest degree earned',
+    insurance = 'Insurance coverage',
+    poverty = 'Poverty level'
+  )) %>% 
+  # Join with AAPC table
+  left_join(cleaned_prop_aapc_sans_2020, by = c('stratifier', 'strata', 'variable' = 'practice'))
+
+cleaned_proportion_df_sans_2020 <- left_join(clean_age_adjusted_prop, cleaned_prop_apc_sans_2020, by = c('stratifier', 'strata', 'variable' = 'practice')) %>% 
+  mutate(AAPC = case_when(is.na(AAPC) & is.na(`APC Period 2`) & is.na(`APC Period 3`) ~ `APC Period 1`,
+                          TRUE ~ AAPC),
+         `APC Period 1` = case_when(is.na(`APC Period 1`) & is.na(`APC Period 2`) ~ AAPC,
+                                    TRUE ~ `APC Period 1`)) %>%
+  # Rename poverty levels
+  mutate(strata = case_when(as.character(strata) == 'Poor/Negative' ~ '< 100%',
+                            as.character(strata) == 'Low income' ~ '100% - 199%',
+                            as.character(strata) == 'Middle income' ~ '200% - 399%',
+                            as.character(strata) == 'High income' ~ '> 400%',
+                            TRUE ~ as.character(strata)))
+
+# Rename strata to a blank name to remove it from the final table
+prop_tab_sans_2020 <- cleaned_proportion_df_sans_2020 %>% 
+  filter(strata != 'Other') %>% 
+  group_by(variable) %>%
+  mutate(strata = case_when(strata == '-' ~ 'Overall', TRUE ~ strata)) %>% 
+  mutate(variable = case_when(variable == 'a1c' ~ 'Two or more A1C tests',
+                                   variable == 'CHOL_all' ~ 'Cholesterol tested',
+                                   variable == 'DENT_all' ~ 'One or more dentist visits',
+                                   variable == 'eye-exam' ~ 'Dilated eye exam',
+                                   variable == 'flu' ~ 'Received influenza vaccine',
+                                   variable == 'foot' ~ 'Foot examination')) %>% 
+  # Select table variables
+  select(
+    stratifier,
+    ` ` = strata,
+    `Preventive Practice` = variable,
+    `2008`:`2020`,
+    `Percent Change (95% CI)`,
+    `Joinpoint Year` = segment,
+    `APC Period 1`,
+    `APC Period 2`,
+    `APC Period 3`,
+    `APC Period 4`,
+    `AAPC`
+  ) %>% 
+  # Clean up name
+  mutate(stratifier = case_when(as.character(stratifier) == 'Poverty level' ~ 'Poverty income ratio',
+                                TRUE ~ as.character(stratifier))) %>% 
+  # Combine stratifier and strata names for table, then relevel factor for
+  # appropriate table order
+  mutate(` ` = case_when(stratifier == 'Overall' ~ 'Overall',
+                         TRUE ~ paste(stratifier, ` `, sep = ": ")),
+         ` ` = as.factor(` `) %>% fct_relevel('Overall',
+                           'Age: 18 to 44',
+                           'Age: 45 to 64',
+                           'Age: 65 to 74',
+                           'Age: 75+',
+                           'Sex: Female',
+                           'Sex: Male',
+                           'Race/Ethnicity: Asian/Not Hispanic',
+                           'Race/Ethnicity: Black/Not Hispanic',
+                           'Race/Ethnicity: Hispanic',
+                           'Race/Ethnicity: White/Not Hispanic',
+                           'Highest degree earned: Greater than high school',
+                           'Highest degree earned: High school',
+                           'Highest degree earned: Less than high school',
+                           'Insurance coverage: Medicaid',
+                           'Insurance coverage: Medicare only',
+                           'Insurance coverage: Private only',
+                           'Insurance coverage: Uninsured',
+                           'Poverty income ratio: > 400%',
+                           'Poverty income ratio: 200% - 399%',
+                           'Poverty income ratio: 100% - 199%',
+                           'Poverty income ratio: < 100%')) %>% 
+  # Clean up APC values
+  mutate(`APC (95% CI)` = paste(`APC Period 1`, `APC Period 2`, `APC Period 3`, `APC Period 4`, sep = ", ") %>%
+           str_replace(., ", NA", "") %>%
+           str_replace(., ", NA", "") %>%
+           str_replace(., ", NA", "")) %>% 
+  # Rename some columns to add () info
+  rename(`2008 (SE)` = `2008`,
+         `2009 (SE)` = `2009`,
+         `2010 (SE)` = `2010`,
+         `2011 (SE)` = `2011`,
+         `2012 (SE)` = `2012`,
+         `2013 (SE)` = `2013`,
+         `2014 (SE)` = `2014`,
+         `2015 (SE)` = `2015`,
+         `2016 (SE)` = `2016`,
+         `2017 (SE)` = `2017`,
+         `2018 (SE)` = `2018`,
+         `2019 (SE)` = `2019`,
+         `2020 (SE)` = `2020`,
+         `APC Period 1 (95% CI)` = `APC Period 1`,
+         `APC Period 2 (95% CI)` = `APC Period 2`,
+         `APC Period 3 (95% CI)` = `APC Period 3`,
+         `APC Period 4 (95% CI)` = `APC Period 4`,
+         `AAPC (95% CI)` = `AAPC`)
+
+proportion_table_sans_2020 <- prop_tab_sans_2020 %>% 
+  ungroup() %>% 
+  filter(stratifier == 'Overall') %>% 
+  select(
+    `Preventive Practice`,
+    `2008 (SE)`,
+    `2009 (SE)`,
+    `2010 (SE)`,
+    `2011 (SE)`,
+    `2012 (SE)`,
+    `2013 (SE)`,
+    `2014 (SE)`,
+    `2015 (SE)`,
+    `2016 (SE)`,
+    `2017 (SE)`,
+    `2018 (SE)`,
+    `2019 (SE)`,
+    `2020 (SE)`,
+    `Percent Change (95% CI)`,
+    `Joinpoint Year`,
+    `APC (95% CI)`,
+    `AAPC (95% CI)`,
+    -starts_with('APC Period')
+  ) %>% 
+  gt() %>% 
+  sub_missing(missing_text = ' ') %>% 
+  tab_footnote(
+    footnote = "Values in these columns were estimated excluding data from 2020.",
+    locations = cells_column_labels(
+      columns = c(`Percent Change (95% CI)`,
+      `APC (95% CI)`,
+      `AAPC (95% CI)`
+    ))
+  ) %>% 
+  tab_options(footnotes.marks = "a",
+              table.font.names = 'Times New Roman',
+              table.font.size = 12)
+# Reorganize insurance variables
+ # proportion_table_sans_2020$`_data` <- proportion_table_sans_2020$`_data`[c(1:84,
+ #                                                                            85, 88, 86, 87,
+ #                                                                            89, 92, 90, 91,
+ #                                                                            93, 96, 94, 95,
+ #                                                                            97, 100, 98, 99,
+ #                                                                            101, 104, 102, 103,
+ #                                                                            105, 108, 106, 107,
+ #                                                                            109:nrow(proportion_table_sans_2020$`_data`)), ]
+
+# prop_tab_sans_2020 <- proportion_table_sans_2020$`_data`
+proportion_table_sans_2020 %>%
+  gtsave('proportion_2020.docx')
+
+supplement_prop_tab <- prop_tab_sans_2020 %>% 
+  select(
+    ` `,
+    `Preventive Practice`,
+    `2008 (SE)`,
+    `2009 (SE)`,
+    `2010 (SE)`,
+    `2011 (SE)`,
+    `2012 (SE)`,
+    `2013 (SE)`,
+    `2014 (SE)`,
+    `2015 (SE)`,
+    `2016 (SE)`,
+    `2017 (SE)`,
+    `2018 (SE)`,
+    `2019 (SE)`,
+    `2020 (SE)`,
+    `Percent Change (95% CI)`,
+    `Joinpoint Year`,
+    `APC (95% CI)`,
+    `AAPC (95% CI)`,
+    -starts_with('APC Period')
+  ) %>% 
+  gt() %>% 
+  sub_missing(missing_text = ' ') %>% 
+  tab_footnote(
+    footnote = "Values in these columns were estimated excluding data from 2020.",
+    locations = cells_column_labels(
+      columns = c(`Percent Change (95% CI)`,
+      `APC (95% CI)`,
+      `AAPC (95% CI)`
+    ))
+  ) %>% 
+  tab_options(footnotes.marks = "a",
+              table.font.names = 'Times New Roman',
+              table.font.size = 12)
+
+prop_tab_sans_2020 <- rename(prop_tab_sans_2020, stratifier_column = ` `) %>% 
+  janitor::clean_names()
+```
+
+```{r plots-sans-2020}
+set.seed(963458237)
+# Need this to grab 2020 data, I think
 stats_table_plot_dat <- jp_proportion_plot_data %>%
+  mutate(model = as.numeric(model)) %>% 
   filter(strata != 'Total') %>%
@@
   filter(strata != 'Other Race/Not Hispanic') %>% 
-  mutate(variable_text = case_when(variable == 'a1c' ~ '2 or more A1C tests',
+  filter(strata != 'Other') %>% 
+  mutate(variable_text = case_when(variable == 'a1c' ~ 'Two or more A1C tests',
                                    variable == 'CHOL_all' ~ 'Cholesterol tested',
-                                   variable == 'DENT_all' ~ '1 or more dentist visits',
-                                   variable == 'eye-exam' ~ 'Eye exam with dilation',
-                                   variable == 'flu' ~ 'Received flu vaccine',
+                                   variable == 'DENT_all' ~ 'One or more dentist visits',
+                                   variable == 'eye-exam' ~ 'Dilated eye exam',
+                                   variable == 'flu' ~ 'Received influenza vaccine',
                                    variable == 'foot' ~ 'Foot examination'),
@@
   )
-test_plots <- stats_table_plot_dat %>% 
-   map(
-    ~ ggplot(filter(.x, variable %in% c('a1c', 'CHOL_all', 'flu')),
+# rest of the stuff
+stats_table_plot_dat_sans_2020 <- jp_proportion_plot_data_sans_2020 %>%
+  mutate(model = as.numeric(model)) %>% 
+  filter(strata != 'Total') %>%
+  filter(strata != 'Not available') %>% 
+  filter(strata != 'Other Race/Not Hispanic') %>% 
+  filter(strata != 'Other') %>% 
+  mutate(variable_text = case_when(variable == 'a1c' ~ 'Two or more A1C tests',
+                                   variable == 'CHOL_all' ~ 'Cholesterol tested',
+                                   variable == 'DENT_all' ~ 'One or more dentist visits',
+                                   variable == 'eye-exam' ~ 'Dilated eye exam',
+                                   variable == 'flu' ~ 'Received influenza vaccine',
+                                   variable == 'foot' ~ 'Foot examination'),
+         strata = case_when(strata == 'Overall' ~ 'z',
+                            TRUE ~ strata)) %>% 
+  group_by(strata, variable) %>% 
+  mutate(strata = as.factor(strata),
+         significant_indicator = case_when(joinpoints == '0' & any(str_detect(apc, "[*]")) ~ TRUE,
+                                           joinpoints != '0' ~ TRUE,
+                                           TRUE ~ FALSE)) %>% 
+  ungroup() %>% 
+  split(., f = .$stratifier)
+
+stats_table_plot_dat_sans_2020 <- map(stats_table_plot_dat_sans_2020, function(.x) {
+  .x %>% 
+    mutate(strata = fct_drop(strata))
+})
+
+overall_data_sans_2020 <- stats_table_plot_dat_sans_2020$overall
+# Remove the overall data from the list
+stats_table_plot_dat_sans_2020 <- stats_table_plot_dat_sans_2020[-4]
+# Relevel the poverty factors
+stats_table_plot_dat_sans_2020$poverty$strata <-
+  factor(
+    stats_table_plot_dat_sans_2020$poverty$strata,
+    levels = c('Poor/Negative', 'Low income', 'Middle income', 'High income'), 
+    labels = c(
+      'd< 100%',
+      'c100% - 199%',
+      'b200% - 399%',
+      'a> 400% '
+    ),
+    ordered = TRUE
+  )
+# Set up color palette for up to 4 categories
+color_pal <- RColorBrewer::brewer.pal(n = 4, 'Set2')
+# Get the p for 2020 but remove the join point stuff so the line doesn't plot
+stats_table_2020_only <- stats_table_plot_dat %>% 
+  map(~filter(.x, year == 2020) %>% 
+        group_by(strata, variable) %>% 
+        mutate(model = NA,
+                significant_indicator = any(str_detect(apc, "[*]"))) %>% 
+        ungroup()
+  )
+stats_table_2020_only$poverty$strata <-
+  factor(
+    stats_table_2020_only$poverty$strata,
+    levels = c('< 100%',
+               '100% - 199%',
+               '200% - 399%',
+               '> 400% '), 
+    labels = c(
+      'd< 100%',
+      'c100% - 199%',
+      'b200% - 399%',
+      'a> 400% '
+    ),
+    ordered = TRUE
+  )
+legend_labels <- stats_table_plot_dat_sans_2020 %>% 
+  map(~.x %>% 
+        group_by(strata, variable) %>% 
+        summarise(sig_ind = mean(significant_indicator)) %>% 
+        ungroup()
+  )
+overall_legend <- overall_data_sans_2020 %>%
+  group_by(strata, variable) %>%
+  summarise(sig_ind = mean(significant_indicator)) %>%
+  ungroup()
+
+test_plots_sans_2020 <-
+  map2(
+    stats_table_plot_dat_sans_2020,
+    stats_table_2020_only,
+    ~ ggplot(
+      filter(.x, variable %in% c('a1c', 'CHOL_all', 'flu')),
       aes(
         x = year,
-      y = age_adjusted_prop * 100,
+        y = p,
         group = strata,
         color = strata
+      )
+    ) +
+      geom_line(aes(
+        x = year,
+        y = model,
+        group = strata,
+        color = strata,
+        linetype = strata
       )) +
-      #geom_point() +
-      geom_line(aes(x = year, y = model * 100, group = strata, color = strata)) +
-      geom_line(data = filter(overall_data, variable %in% c('a1c', 'CHOL_all', 'flu')),
-                  aes(x = year, y = model * 100),
-                  color = 'black',
-                  linetype = 'dashed') +
-      facet_wrap( ~ variable_text, ncol = 3) +
+      geom_line(
+        data = filter(
+          overall_data_sans_2020,
+          variable %in% c('a1c', 'CHOL_all', 'flu')
+        ),
+        aes(
+          x = year,
+          y = model,
+          color = strata,
+          linetype = strata
+        ),
+      ) +
+      geom_jitter(
+        data = filter(.y, variable %in% c('a1c', 'CHOL_all', 'flu')) ,
+        aes(
+          x = year,
+          y = p,
+          group = strata,
+          color = strata
+        ),
+        inherit.aes = FALSE,
+        width = 0.22,
+        height = 0.005
+      ) +
+      geom_point(
+        data = filter(
+          overall_data,
+          variable %in% c('a1c', 'CHOL_all', 'flu'),
+          year == 2020
+        ),
+        aes(x = year, y = p, color = strata),
+        inherit.aes = FALSE
+      ) +
+      facet_wrap(~ variable_text, ncol = 3) +
       theme_classic() +
       scale_y_continuous(
-        limits = c(00, 100),
+        limits = c(0, 100),
         breaks = seq(0, 100, 25),
@@
       scale_x_continuous(
-        limits = c(2008, 2020),
+        limits = c(2008, 2020.3),
         breaks = seq(2008, 2020, 2),
-        labels = seq(2008, 2020, 2)
+        labels = c(2008, "", 2012, "", 2016, "", 2020)
       ) +
-      scale_color_brewer(type = 'qual', palette = 'Set2') +
-      theme(axis.text = element_text(color = 'black'),
-            axis.text.x = element_text(angle = 45, hjust = 0.9, vjust = 0.95),
-            legend.title = element_text(size = 8),
-            legend.text = element_text(size = 6)) +
+      theme(
+        axis.text = element_text(color = 'black'),
+        #axis.text.x = element_text(angle = 45, hjust = 0.9, vjust = 0.95),
+        legend.title = element_text(size = 11),
+        legend.text = element_text(size = 9)
+      ) +
       labs(x = 'Year', y = 'Percentage')
+
   )
 
-test_plots[[1]] <- test_plots[[1]] + labs(color = 'Age (grouped)') +
-  theme(axis.title.x = element_blank())
-test_plots[[2]] <-
-  test_plots[[2]] + labs(color = 'Highest degree \nobtained') + theme(
+test_plots_sans_2020[[1]] <-
+  test_plots_sans_2020[[1]] +
+  theme(axis.title.x = element_blank()) +
+  scale_color_manual(
+    name = 'Age (grouped)',
+    values = c(
+     '18 to 44' = color_pal[1],
+     '45 to 64'  = color_pal[2],
+     '65 to 74' = color_pal[3],
+     '75+' = color_pal[4],
+     'z' = '#000000'
+    ),
+    labels = c('18 to 44' = '18 to 44ᵇ',
+               '45 to 64' = '45 to 64ᵃᵇᶜ',
+               '65 to 74' = '65 to 74ᶜ',
+               '75+'      = '75+ᶜ',
+               'z'        = 'Overallᵇ')
+  ) +
+  scale_linetype_manual(
+    name = 'Age (grouped)',
+    values = c(
+     '18 to 44' = 'solid',
+     '45 to 64'  = 'solid',
+     '65 to 74' = 'solid',
+     '75+' = 'solid',
+     'z' = 'dashed'
+    ),
+    labels = c('18 to 44' = '18 to 44ᵇ',
+               '45 to 64' = '45 to 64ᵃᵇᶜ',
+               '65 to 74' = '65 to 74ᶜ',
+               '75+'      = '75+ᶜ',
+               'z'        = 'Overallᵇ')
+  )
+
+test_plots_sans_2020[[2]] <-
+  test_plots_sans_2020[[2]] +
+  theme(
     strip.background =  element_blank(),
@@
     axis.title.x = element_blank()
+  ) +
+  scale_color_manual(
+    name = 'Highest degree obtained',
+    labels = c('Greater than HS'       = 'Greater than HS',
+               'High school'           = 'High school',
+               'Less than high school' = 'Less than HSᵃ',
+               'z'                     = 'Overallᵇ'),
+    values = c(
+     'Greater than HS' = color_pal[1],
+     'High school' = color_pal[2],
+     'Less than high school'  = color_pal[3],
+     'z' = '#000000'
     )
-test_plots[[3]] <-
-  test_plots[[3]] + labs(color = "Insurance") + theme(
+  ) +
+  scale_linetype_manual(
+    name = 'Highest degree obtained',
+    labels = c('Greater than HS'       = 'Greater than HS',
+               'High school'           = 'High school',
+               'Less than high school' = 'Less than HSᵃ',
+               'z'                     = 'Overallᵇ'),
+    values = c(
+     'Greater than HS' = 'solid',
+     'High school' = 'solid',
+     'Less than high school'  = 'solid',
+     'z' = 'dashed'
+    )
+  )
+
+test_plots_sans_2020[[3]] <-
+  test_plots_sans_2020[[3]] +
+  theme(
     strip.background =  element_blank(),
@@
     axis.title.x = element_blank()
+  ) +
+  scale_color_manual(
+    name = 'Insurance',
+    values = c(
+      'Medicaid' = color_pal[1],
+      'Medicare only' = color_pal[2],
+      'Private only' = color_pal[3],
+      'Uninsured' = color_pal[4],
+      'z' = '#000000'
+    ),   labels = c(
+      'Medicaid'      = 'Medicaidᵃ',
+      'Medicare only' = 'Medicare onlyᵇᶜ',
+      'Private only'  = 'Private onlyᵇ',
+      'Uninsured'     = 'Uninsured',
+      'z'             = 'Overallᵇ'
     )
-test_plots[[4]] <-
-  test_plots[[4]] + labs(color = 'Income as % of \npoverty line') + theme(
-    strip.background =  element_blank(),
-    strip.text = element_blank()
+  ) +
+  scale_linetype_manual(
+    name = 'Insurance',
+    values = c(
+      'Medicaid' = 'solid',
+      'Medicare only' = 'solid',
+      'Private only' = 'solid',
+      'Uninsured' = 'solid',
+      'z' = 'dashed'
+    ),
+        labels = c(
+      'Medicaid'      = 'Medicaidᵃ',
+      'Medicare only' = 'Medicare onlyᵇᶜ',
+      'Private only'  = 'Private onlyᵇ',
+      'Uninsured'     = 'Uninsured',
+      'z'             = 'Overallᵇ'
     )
-test_plots[[5]] <-
-  test_plots[[5]] + labs(color = 'Race/Ethnicity') + theme(
+  )
+
+test_plots_sans_2020[[4]] <-
+  test_plots_sans_2020[[4]] +
+  theme(strip.background =  element_blank(),
+        strip.text = element_blank()) +
+  scale_color_manual(
+    name = 'Poverty income ratio',
+    labels = c('a> 400% '     = '> 400%ᵇᶜ',
+               'b200% - 399%' = '200% - 399%ᵇ',
+               'c100% - 199%' = '100% - 199%ᵃ',
+               'd< 100%'      = '< 100%',
+               'z'           = 'Overallᵇ'),
+
+    values = c(
+      'a> 400% ' = color_pal[1],
+      'b200% - 399%' = color_pal[2],
+      'c100% - 199%' = color_pal[3],
+      'd< 100%' = color_pal[4],
+      'z' = '#000000'
+    )
+  ) +
+  scale_linetype_manual(
+    name = 'Poverty income ratio',
+    labels = c('a> 400% '     = '> 400%ᵇᶜ',
+               'b200% - 399%' = '200% - 399%ᵇ',
+               'c100% - 199%' = '100% - 199%ᵃ',
+               'd< 100%'      = '< 100%',
+               'z'           = 'Overallᵇ'),
+    values = c(
+      'a> 400% ' = 'solid',
+      'b200% - 399%' = 'solid',
+      'c100% - 199%' = 'solid',
+      'd< 100%' = 'solid',
+      'z' = 'dashed'
+    )
+  ) + 
+ labs(caption = "ᵃ p < 0.05 for cholesterol tested \nᵇ p < 0.05 for received influenza vaccine \nᶜ p < 0.05 for A1C tests")
+
+test_plots_sans_2020[[5]] <-
+  test_plots_sans_2020[[5]] + theme(
     strip.background =  element_blank(),
@@
     axis.title.x = element_blank()
+  ) +
+  scale_color_manual(
+    name = 'Race & Ethnicity',
+    labels = c(
+     'Asian/Not Hispanic' = 'Asian/Not Hispanicᵇ',
+     'Black/Not Hispanic' = 'Black/Not Hispanic',
+     'Hispanic'           = 'Hispanicᶜ',
+     'White/Not Hispanic' = 'White/Not Hispanicᵇᶜ',
+     'z'                  = 'Overallᵇ'
+    ),
+    values = c(
+     'Asian/Not Hispanic' = color_pal[1],
+     'Black/Not Hispanic'  = color_pal[2],
+     'Hispanic' = color_pal[3],
+     'White/Not Hispanic' = color_pal[4],
+     'z' = '#000000'
     )
-test_plots[[6]] <-
-  test_plots[[6]] + labs(color = 'Sex') + theme(strip.background =  element_blank(),
+  ) +
+  scale_linetype_manual(
+    name = 'Race & Ethnicity',
+    labels = c(
+     'Asian/Not Hispanic' = 'Asian/Not Hispanicᵇ',
+     'Black/Not Hispanic' = 'Black/Not Hispanic',
+     'Hispanic'           = 'Hispanicᶜ',
+     'White/Not Hispanic' = 'White/Not Hispanicᵇᶜ',
+     'z'                  = 'Overallᵇ'
+    ),
+    values = c(
+     'Asian/Not Hispanic' = 'solid',
+     'Black/Not Hispanic'  = 'solid',
+     'Hispanic' = 'solid',
+     'White/Not Hispanic' = 'solid',
+     'z' = 'dashed'
+    )
+  )
+test_plots_sans_2020[[6]] <-
+  test_plots_sans_2020[[6]] +
+  theme(
+    strip.background =  element_blank(),
     strip.text = element_blank(),
-    axis.title.x = element_blank())
-test_plots <- list(
-  test_plots[[1]],
-  test_plots[[6]],
-  test_plots[[5]],
-  test_plots[[2]],
-  test_plots[[3]],
-  test_plots[[4]]
+    axis.title.x = element_blank()
+  ) +
+  scale_color_manual(
+    name = 'Sex',
+    labels = c('Female'  = 'Femaleᵇ',
+               'Male'    = 'Maleᵃᵇ',
+               'z' = 'Overallᵇ'),
+    values = c(
+     'Female' = color_pal[1],
+     'Male'  = color_pal[2],
+     'z' = '#000000'
+    )
+  ) +
+  scale_linetype_manual(
+    name = 'Sex',
+    labels = c('Female'  = 'Femaleᵇ',
+               'Male'    = 'Maleᵃᵇ',
+               'z' = 'Overallᵇ'),
+        values = c(
+     'Female' = 'solid',
+     'Male'  = 'solid',
+     'z' = 'dashed'
+    )
+  )
+test_plots_sans_2020 <- list(
+  test_plots_sans_2020[[1]],
+  test_plots_sans_2020[[6]],
+  test_plots_sans_2020[[5]],
+  test_plots_sans_2020[[2]],
+  test_plots_sans_2020[[3]],
+  test_plots_sans_2020[[4]]
 )
 
-exam_plots <- stats_table_plot_dat %>% 
-   map(
-    ~ ggplot(filter(.x, variable %!in% c('a1c', 'CHOL_all', 'flu')),
+exam_plots_sans_2020 <-
+  map2(
+    stats_table_plot_dat_sans_2020,
+    stats_table_2020_only,
+    ~ ggplot(
+      filter(.x, variable %!in% c('a1c', 'CHOL_all', 'flu')),
       aes(
         x = year,
-      y = age_adjusted_prop * 100,
+        y = p,
         group = strata,
         color = strata
+      )
+    ) +
+      geom_line(aes(
+        x = year,
+        y = model,
+        group = strata,
+        color = strata,
+        linetype = strata
       )) +
-      #geom_point() +
-      geom_line(aes(x = year, y = model * 100, group = strata, color = strata)) +
-      geom_line(data = filter(overall_data, variable %!in% c('a1c', 'CHOL_all', 'flu')),
-                  aes(x = year, y = model * 100),
-                  color = 'black',
-                  linetype = 'dashed') +
-      facet_wrap( ~ variable_text, ncol = 3) +
+      geom_line(
+        data = filter(
+          overall_data_sans_2020,
+          variable %!in% c('a1c', 'CHOL_all', 'flu')
+        ),
+        aes(x = year, y = model, color = strata, linetype = strata),
+      ) +
+      geom_jitter(
+        data = filter(.y, variable %!in% c('a1c', 'CHOL_all', 'flu')) ,
+        aes(
+          x = year,
+          y = p,
+          group = strata,
+          color = strata
+        ),
+        inherit.aes = FALSE,
+        width = 0.22,
+        height = 0.005
+      ) +
+      geom_point(
+        data = filter(
+          overall_data,
+          variable %!in% c('a1c', 'CHOL_all', 'flu'),
+          year == 2020
+        ),
+        aes(x = year, y = p, color = strata),
+        #color = 'black',
+        inherit.aes = FALSE
+      ) +
+      facet_wrap(~ variable_text, ncol = 3) +
       theme_classic() +
       scale_y_continuous(
-        limits = c(  0, 100),
+        limits = c(0, 100),
         breaks = seq(0, 100, 25),
@@
       scale_x_continuous(
-        limits = c(2008, 2020),
+        limits = c(2008, 2020.3),
         breaks = seq(2008, 2020, 2),
-        labels = seq(2008, 2020, 2)
+        labels = c(2008, "", 2012, "", 2016, "", 2020)
       ) +
-      scale_color_brewer(type = 'qual', palette = 'Set2') +
-      theme(axis.text = element_text(color = 'black'),
-            axis.text.x = element_text(angle = 45, hjust = 0.9, vjust = 0.95),
-            legend.title = element_text(size = 8),
-            legend.text = element_text(size = 6)) +
+      theme(
+        axis.text = element_text(color = 'black'),
+        #axis.text.x = element_text(angle = 45, hjust = 0.9, vjust = 0.95),
+        legend.title = element_text(size = 11),
+        legend.text = element_text(size = 9)
+      ) +
       labs(x = 'Year', y = 'Percentage')
@@
 
-exam_plots[[1]] <- exam_plots[[1]] + labs(color = 'Age (grouped)') +
-  theme(axis.title.x = element_blank())
-exam_plots[[2]] <-
-  exam_plots[[2]] + labs(color = 'Highest degree \nobtained') + theme(
+# Set up legends on all plots
+exam_plots_sans_2020[[1]] <- exam_plots_sans_2020[[1]] +
+  theme(axis.title.x = element_blank()) +
+  scale_color_manual(
+    name = 'Age (grouped)',
+    labels = c('18 to 44' = '18 to 44',
+               '45 to 64' = '45 to 64',
+               '65 to 74' = '65 to 74ᵇᶜ',
+               '75+'      = '75+ᶜ',
+               'z'        = 'Overallᵇ'),
+    values =   c(
+      '18 to 44' = color_pal[1],
+      '45 to 64' = color_pal[2],
+      '65 to 74' = color_pal[3],
+      '75+'      = color_pal[4],
+      'z'        = '#000000'
+    )
+  ) +
+  scale_linetype_manual(
+    name = 'Age (grouped)',
+    labels = c('18 to 44' = '18 to 44',
+               '45 to 64' = '45 to 64',
+               '65 to 74' = '65 to 74ᵇᶜ',
+               '75+'      = '75+ᶜ',
+               'z'        = 'Overallᵇ'),
+    values = c(
+      '18 to 44' = 'solid',
+      '45 to 64'  = 'solid',
+      '65 to 74' = 'solid',
+      '75+' = 'solid',
+      'z' = 'dashed'
+    )
+  )
+
+exam_plots_sans_2020[[2]] <-
+  exam_plots_sans_2020[[2]] +
+  theme(
     strip.background =  element_blank(),
@@
     axis.title.x = element_blank()
+  ) +
+  scale_color_manual(
+    name = 'Highest degree obtained',
+    labels = c('Greater than HS'       = 'Greater than HS',
+               'High school'           = 'High schoolᶜ',
+               'Less than high school' = 'Less than HS',
+               'z'                     = 'Overallᵇ'),
+        values = c(
+      'Greater than HS'       = color_pal[1],
+      'High school'           = color_pal[2],
+      'Less than high school' = color_pal[3],
+      'z'                     = '#000000'
     )
-exam_plots[[3]] <-
-  exam_plots[[3]] + labs(color = "Insurance") + theme(
+  ) +
+    scale_linetype_manual(
+      name = 'Highest degree obtained',
+    labels = c('Greater than HS'       = 'Greater than HS',
+               'High school'           = 'High schoolᶜ',
+               'Less than high school' = 'Less than HS',
+               'z'                     = 'Overallᵇ'),
+    values = c(
+      'Greater than HS' = 'solid',
+      'High school' = 'solid',
+      'Less than high school'  = 'solid',
+      'z' = 'dashed'
+    )
+  )
+
+exam_plots_sans_2020[[3]] <-
+  exam_plots_sans_2020[[3]] +
+  theme(
     strip.background =  element_blank(),
@@
     axis.title.x = element_blank()
+  ) +
+  scale_color_manual(
+    name = 'Insurance',
+    labels = c(
+     'Medicaid'      =  'Medicaid',
+     'Medicare only' =  'Medicare only',
+     'Private only'  =  'Private onlyᶜ',
+     'Uninsured'     =  'Uninsuredᵃᶜ',
+     'z'             =  'Overallᵇ'
+    ),
+    values = c(
+      'Medicaid'      = color_pal[1],
+      'Medicare only' = color_pal[2],
+      'Private only'  = color_pal[3],
+      'Uninsured'     = color_pal[4],
+      'z'             = '#000000'
     )
-exam_plots[[4]] <-
-  exam_plots[[4]] + labs(color = 'Income as % of \npoverty line') + theme(
+  ) +
+  scale_linetype_manual(
+    name = 'Insurance',
+    labels =  c(
+     'Medicaid'      =  'Medicaid',
+     'Medicare only' =  'Medicare only',
+     'Private only'  =  'Private onlyᶜ',
+     'Uninsured'     =  'Uninsuredᵃᶜ',
+     'z'             =  'Overallᵇ'
+    ),
+    values = c(
+      'Medicaid' = 'solid',
+      'Medicare only' = 'solid',
+      'Private only' = 'solid',
+      'Uninsured' = 'solid',
+      'z' = 'dashed'
+    )
+  )
+
+exam_plots_sans_2020[[4]] <-
+  exam_plots_sans_2020[[4]] +
+  theme(strip.background =  element_blank(),
+        strip.text = element_blank()) +
+  scale_color_manual(
+    name = 'Poverty income ratio',
+    labels = c('a> 400% '     = '> 400%ᵃ',
+               'b200% - 399%' = '200% - 399%',
+               'c100% - 199%' = '100% - 199%',
+               'd< 100%'      = '< 100%ᶜ',
+               'z'           = 'Overallᵇ'),
+    values = c(
+      'a> 400% '     = color_pal[1],
+      'b200% - 399%' = color_pal[2],
+      'c100% - 199%' = color_pal[3],
+      'd< 100%'      = color_pal[4],
+      'z'           = '#000000'
+    )
+  ) +
+  scale_linetype_manual(
+    name = 'Poverty income ratio',
+    labels = c('a> 400% '     = '> 400%ᵃ',
+               'b200% - 399%' = '200% - 399%',
+               'c100% - 199%' = '100% - 199%',
+               'd< 100%'      = '< 100%ᶜ',
+               'z'           = 'Overallᵇ'),
+    values = c(
+      'a> 400% ' = 'solid',
+      'b200% - 399%' = 'solid',
+      'c100% - 199%' = 'solid',
+      'd< 100%' = 'solid',
+      'z' = 'dashed'
+    )
+  ) +
+  labs(caption = "ᵃ p < 0.05 for eye-exam \nᵇ p < 0.05 for foot exam \nᶜ p < 0.05 for dentist visit")
+
+exam_plots_sans_2020[[5]] <-
+  exam_plots_sans_2020[[5]] +
+  theme(
     strip.background =  element_blank(),
-    strip.text = element_blank()
+    strip.text = element_blank(),
+    axis.title.x = element_blank()
+  ) +
+  scale_color_manual(
+    name = 'Race & Ethnicity',
+    labels = c(
+      'Asian/Not Hispanic' = 'Asian/Not Hispanic',
+      'Black/Not Hispanic' = 'Black/Not Hispanic',
+      'Hispanic'           = 'Hispanic',
+      'White/Not Hispanic' = 'White/Not Hispanicᶜ',
+      'z'                  = 'Overallᵇ'
+    ),
+    values = c(
+      'Asian/Not Hispanic' = color_pal[1],
+      'Black/Not Hispanic' = color_pal[2],
+      'Hispanic'           = color_pal[3],
+      'White/Not Hispanic' = color_pal[4],
+      'z'                  = '#000000'
     )
-exam_plots[[5]] <-
-  exam_plots[[5]] + labs(color = 'Race/Ethnicity') + theme(
+  ) +
+  scale_linetype_manual(
+    name = 'Race & Ethnicity',
+        labels = c(
+       'Asian/Not Hispanic' = 'Asian/Not Hispanic',
+       'Black/Not Hispanic' = 'Black/Not Hispanic',
+       'Hispanic'           = 'Hispanic',
+       'White/Not Hispanic' = 'White/Not Hispanicᶜ',
+       'z'                  = 'Overallᵇ'
+    ),
+    values = c(
+      'Asian/Not Hispanic' = 'solid',
+      'Black/Not Hispanic'  = 'solid',
+      'Hispanic' = 'solid',
+      'White/Not Hispanic' = 'solid',
+      'z' = 'dashed'
+    )
+  )
+
+exam_plots_sans_2020[[6]] <-
+  exam_plots_sans_2020[[6]] +
+  theme(
     strip.background =  element_blank(),
-    strip.text = element_blank()
+    strip.text = element_blank(),
+    axis.title.x = element_blank()
+  ) +
+  scale_color_manual(
+    name = 'Sex',
+    labels = c('Female'  = 'Female',
+               'Male'    = 'Maleᵃ',
+               'z' = 'Overallᵇ'),
+    values = c(
+      'Female' = color_pal[1],
+      'Male'  = color_pal[2],
+      'z' = '#000000'
     )
-exam_plots[[6]] <-
-  exam_plots[[6]] + labs(color = 'Sex') + theme(strip.background =  element_blank(),
+  ) +
+  scale_linetype_manual(
+    name = 'Sex',
+    labels = c('Female' = 'Female',
+               'Male' = 'Maleᵃ',
+               'z' = 'Overallᵇ'),
+    values = c(
+      'Female' = 'solid',
+      'Male'  = 'solid',
+      'z' = 'dashed'
+    )
+  )
+
+exam_plots_sans_2020 <- list(
+  exam_plots_sans_2020[[1]],
+  exam_plots_sans_2020[[6]],
+  exam_plots_sans_2020[[5]],
+  exam_plots_sans_2020[[2]],
+  exam_plots_sans_2020[[3]],
+  exam_plots_sans_2020[[4]]
+)
+
+all_exam_plots_sans_2020 <- exam_plots_sans_2020 %>% 
+  wrap_plots(nrow = 6) &
+  theme(plot.margin = margin(0.5, 0.5, 0.5, 0.5, 'pt'),
+        legend.justification = 'left',
+        plot.caption = element_text(hjust = 0)) &
+  guides(color = guide_legend(ncol = 2)) 
+all_test_plots_sans_2020 <- test_plots_sans_2020 %>% 
+  wrap_plots(nrow = 6) &
+  theme(plot.margin = margin(0.5, 0.5, 0.5, 0.5, 'pt'),
+        legend.justification = 'left',
+         plot.caption = element_text(hjust = 0)) &
+  guides(color = guide_legend(ncol = 2))
+```
+
+```{r}
+#| include: false
+# Save figure/table output
+preventive_practice_table %>%
+  gtsave('preventive_practices.docx')
+preventive_practice_table_sans_2020 %>%
+  gtsave('preventive_practices_2020.docx')
+ggsave(plot = all_exam_plots_sans_2020,
+       filename = 'figures/all_exam_plots.tiff',
+       dpi = 1200,
+       width = 10,
+       height = 6)
+ggsave(plot = all_test_plots_sans_2020,
+       filename = 'figures/all_test_plots.tiff',
+       dpi = 1200,
+       width = 10,
+       height = 6)
+# ggsave(plot = all_exam_plots,
+#        filename = 'figures/all_exam_plots.svg',
+#        dpi = 200,
+#        width = 10,
+#        height = 6)
+# ggsave(plot = all_test_plots,
+#        filename = 'figures/all_test_plots.svg',
+#        dpi = 200,
+#        width = 10,
+#        height = 6)
+```
+
+*Target Journal: American Journal of Preventive Medicine*
+
+**Trends in Preventive Care Services among US Adults with Diagnosed Diabetes, 2008-2020**
+
+Jacob T. Wittman, PhD, Kai McKeever Bullard, MPH, PhD, Stephen R. Benoit, MD, MPH
+
+CDC Affiliation
+
+Corresponding Author:
+
+Word Count:
+
+Conflict of Interest Statement:
+
+Financial Disclosure:
+
+\pagebreak
+
+# Abstract
+
+**Introduction:** Preventive care services are important for managing complications associated with diabetes.
+We reported trends in receipt of six American Diabetes Association recommended preventive care services during 2008 -- 2020.
+
+**Methods:** We used 2008 -- 2020 data from the Medical Expenditures Panel Survey to calculate the proportion of US adults ≥ 18 years of age with diagnosed diabetes that reported receiving preventive care services, overall and for subpopulations.
+We used Joinpoint regression to identify trends during 2008 -- 2019.
+The six services in the past year included at least one dental examination, a dilated eye examination, foot examination, ≥ 2 A1C tests, a cholesterol test, and the receipt of an influenza vaccine.
+
+**Results:** From 2008 to 2019, overall trends in preventive services among US adults with diabetes were stable with the exception of an increase in the receipt of influenza vaccines (average annual percent change: `r pullNumber2(prop_tab_sans_2020, 'aapc_95_percent_ci', brackets = TRUE, stratifier_column == 'Overall', preventive_practice == 'Received influenza vaccine')`).
+Trend analysis at the subgroup level was heterogenous but influenza vaccination, A1C testing, and dental visits tended to improve while foot exams, cholesterol testing, and dental visits among the uninsured tended to decline.
+In 2020, 8.2% (95% CI: 4.5%, 11.9%) received none of the six recommended preventive care services.
+
+**Conclusions:** Other than influenza vaccination, we observed no improvement in receipt of preventive care services among US adults with diabetes.
+These data highlight services and specific subgroups that could be targeted to improve preventive care among adults with diabetes.
+
+\pagebreak
+
+# Introduction
+
+Diabetes is a chronic disease that affects 11.3% of the adult population, or 37.1 million adults, in the United States @nationalreport.
+Diabetes is also costly: total direct and indirect costs are estimated at \$327 billion @economic2018.
+The prevalence of diabetes in the US is expected to increase to 60.6 million adults by the year 2060 @lin2018.
+Incidence of diabetes peaked in the US at 8.5 cases per 1,000 in 2008 and 2009 and has fallen since to 5.1 cases per 1,000 in 2021 [@dashboard; @magliano2019].
+Despite this decrease in the number of newly diagnosed cases of diabetes, rates of hospitalization with diabetes as the primary diagnosis have been increasing since the year 2000 by about 2.5% per year @zhang2022.
+
+Access to preventive services is important to minimize complications due to diabetes and reduce rates of hospitalization.
+Other studies have reported on trends in receipt of some preventive services in the 2000s using data from various surveys, such as the Behavioral Risk Factor Surveillance System (BRFSS) and the National Health and Nutrition Examination Survey (NHANES) [@monnette2020; @luo2019; @shin2021; @fang2020; @eppley2019].
+To our knowledge, the proportion and trend of receipt of preventive services from the Medical Expenditure Panel Survey (MEPS) has not been reported.
+We reported the proportion of and trends in the receipt of six preventive care services recommended by the ADA overall and among subgroups.
+These data are valuable for identifying groups that may be underutilizing health care services, examining any effects the COVID-19 pandemic may have had on the receipt of these services, and providing benchmarks for future studies.
+
+# Methods
+
+## Data Source
+
+We used data from MEPS from the years 2008 -- 2020 MEPS, a household survey of U.S.
+noninstitutionalized populations administered and maintained by the Agency for Healthcare Research and Quality since 1996.
+We chose 2008 to 2020 due to method changes in MEPS and the consistency of questions related to preventive care services during that time period.
+Data used from MEPS were collected through a combination of computer assisted personal interviewing and pencil-and-paper surveys.
+MEPS provides national and regional estimates of health care use, expenditures, sources of payment and health insurance coverage.
+This survey also contains information on patient demographics, socioeconomic, and, via the Diabetes Care Survey (DCS), information on diabetes preventive care services.
+The DCS is a self-administered paper-and-pencil questionnaire that is provided to MEPS respondents who indicate that they have been told by a doctor or health professional that they have diabetes.
+In this analysis, we used data from the full-year consolidated MEPS file with an average annual number of 32,170 individual respondents over the 13-year period and response rates ranging from 59.3% in 2008 to 27.6% in 2020.
+
+## Outcome measures
+
+Among those respondents with self-reported diagnosed diabetes, we selected six preventive care variables that were available in the data from 2008--2020.
+These variables are based on self-reported receipt in a given year @ada2021: ≥1 dental examination (derived from total number of reported dental care visits), a dilated eye examination, a foot examination by a healthcare provider, ≥2 A1C tests, a blood cholesterol test, and an influenza vaccine.
+Respondents were asked about receiving each of these services in a given year (e.g.
+"Did you receive an influenza vaccine in 2013?").
+We also created a binary variable classifying adults with diabetes having received none of the recommended preventive care services, although these results are only presented for the overall population due to small sample sizes in many of the examined subgroups.
+
+## Analysis
+
+Our analysis accounts for the complex survey design used, including clustering and stratification.
+Reported values were age-adjusted using the direct method, standardized to the 2000 US population grouped by ages 18 -- 44, 45 -- 64, 65 -- 74, and ≥75.
+We presented these estimates for the overall population, as well as stratified by age, sex, race and ethnicity, highest degree of education obtained, type of insurance, and the ratio of family income to the poverty line (poverty income ratio).
+We used the package gtsummary in R Statistical Software (v4.2.1) to calculate estimates [@gtsummary; @rcore2022].
+
+Medical care utilization decreased as a result of the COVID-19 pandemic starting in early 2020 @cantor2022.
+We reported the estimated proportions for 2020 in Table 1 and as points in @fig-exams and @fig-tests, but 2020 was excluded from trend analysis.
+Trends were analyzed using Joinpoint Command Line Software @joinpoint with R via the R package nih.joinpoint @nihjoinpoint.
+Joinpoint regression uses permutation tests to detect statistically significant changes at a pre-specified alpha of 0.05 in direction or magnitude of trends @kim2000permutation.
+The Joinpoint software also provided estimates of the annual percent change (APC) for each trend segment and the average annual percent change (AAPC) for the entire trend.
+
+# Results
+
+All values presented below, as well as those that are not described, can be found in Supplemental Table 1.
+
+## Cholesterol testing
+
+During 2008--2019, we found no significant change in the percentage of adults with diabetes who received cholesterol tests (Table 1).
+For adults age 45--64 years, cholesterol testing was flat from 2008 to 2015 and showed a significant decrease starting in 2016 (APC: `r pullNumber2(prop_tab_sans_2020, 'apc_period_2_95_percent_ci', brackets = TRUE, stratifier_column == 'Age: 45 to 64', preventive_practice == 'Cholesterol tested')`, AAPC: `r pullNumber2(prop_tab_sans_2020, 'aapc_95_percent_ci', brackets = TRUE, stratifier_column == 'Age: 45 to 64', preventive_practice == 'Cholesterol tested')`).
+We found significant decreases starting in 2016 in the percentage of males receiving cholesterol testing (APC: `r pullNumber2(prop_tab_sans_2020, 'apc_period_2_95_percent_ci', brackets = TRUE, stratifier_column == 'Sex: Male', preventive_practice == 'Cholesterol tested')`) and adults with less than a high school education (APC: `r pullNumber2(prop_tab_sans_2020, 'apc_period_2_95_percent_ci', brackets = TRUE, stratifier_column == 'Highest degree earned: Less than high school', preventive_practice == 'Cholesterol tested')`, AAPC: `r pullNumber2(prop_tab_sans_2020, 'aapc_95_percent_ci', brackets = TRUE, stratifier_column == 'Highest degree earned: Less than high school', preventive_practice == 'Cholesterol tested')`).
+Adults with Medicaid had an AAPC: of `r pullNumber2(prop_tab_sans_2020, 'aapc_95_percent_ci', brackets = TRUE, stratifier_column == 'Insurance coverage: Medicaid', preventive_practice == 'Cholesterol tested')`.
+
+## Influenza vaccine
+
+From 2008 to 2019, receipt of influenza vaccines increased at an AAPC of `r pullNumber2(prop_tab_sans_2020, 'aapc_95_percent_ci', brackets = FALSE, stratifier_column == 'Overall', preventive_practice == 'Received influenza vaccine')`.
+Specifically, we noted significant increases during 2008 -- 2012 (APC: `r pullNumber2(prop_tab_sans_2020, 'apc_period_1_95_percent_ci', brackets = TRUE, stratifier_column == 'Overall', preventive_practice == 'Received influenza vaccine')`, AAPC: ), and after 2015 (APC: `r pullNumber2(prop_tab_sans_2020, 'apc_period_3_95_percent_ci', brackets = TRUE, stratifier_column == 'Overall', preventive_practice == 'Received influenza vaccine')`) (Table 1).
+The influenza vaccine trend for non-Hispanic White adults followed a similar pattern (`r pullNumber2(prop_tab_sans_2020, 'aapc_95_percent_ci', brackets = F, stratifier_column == 'Race/Ethnicity: White/Not Hispanic', preventive_practice == 'Received influenza vaccine')`), although only the period from 2008 to 2012 had a significant increase (APC: `r pullNumber2(prop_tab_sans_2020, 'apc_period_1_95_percent_ci', brackets = TRUE, stratifier_column == 'Race/Ethnicity: White/Not Hispanic', preventive_practice == 'Received influenza vaccine')`).
+Receipt of influenza vaccines increased among females over the entire study period (AAPC: `r pullNumber2(prop_tab_sans_2020, 'aapc_95_percent_ci', brackets = TRUE, stratifier_column == 'Sex: Female', preventive_practice == 'Received influenza vaccine')`).
+Adult males, adults in the poverty income ratio group 200%--399% and \>400%, and adults on private insurance show increase in the receipt of influenza vaccines in the early part of the study period, but flat thereafter.
+Receipt of influenza vaccines increased slightly for adults on Medicare (AAPC: `r pullNumber2(prop_tab_sans_2020, 'aapc_95_percent_ci', brackets = TRUE, stratifier_column == 'Insurance coverage: Medicare only', preventive_practice == 'Received influenza vaccine')`).
+
+## A1C tests
+
+We observed no significant changes in the overall trend in the proportion of adults receiving two or more A1C tests in a year (Table 1).
+Proportions increased annually by `r pullNumber2(prop_tab_sans_2020, 'aapc_95_percent_ci', brackets = FALSE, stratifier_column == 'Age: 45 to 64', preventive_practice == 'Two or more A1C tests')`, `r pullNumber2(prop_tab_sans_2020, 'aapc_95_percent_ci', brackets = FALSE, stratifier_column == 'Age: 65 to 74', preventive_practice == 'Two or more A1C tests')`, and `r pullNumber2(prop_tab_sans_2020, 'aapc_95_percent_ci', brackets = FALSE, stratifier_column == 'Age: 75+', preventive_practice == 'Two or more A1C tests')` for those age 45--64, 65--74, and ≥75 years, respectively.
+We also found increases in A1C testing for Hispanic adults (AAPC: `r pullNumber2(prop_tab_sans_2020, 'aapc_95_percent_ci', brackets = TRUE, stratifier_column == 'Race/Ethnicity: Hispanic', preventive_practice == 'Two or more A1C tests')` ) and for non-Hispanic White adults (AAPC: `r pullNumber2(prop_tab_sans_2020, 'aapc_95_percent_ci', brackets = TRUE, stratifier_column == 'Race/Ethnicity: White/Not Hispanic', preventive_practice == 'Two or more A1C tests')`), those with Medicare only (AAPC: `r pullNumber2(prop_tab_sans_2020, 'aapc_95_percent_ci', brackets = TRUE, stratifier_column == 'Insurance coverage: Medicare only', preventive_practice == 'Two or more A1C tests')`), and those in the highest poverty income ratio group (\> 400%) (AAPC: `r pullNumber2(prop_tab_sans_2020, 'aapc_95_percent_ci', brackets = TRUE, stratifier_column == 'Poverty income ratio: > 400%', preventive_practice == 'Two or more A1C tests')`).
+
+## Dilated eye exam
+
+The overall proportion receiving dilated eye exams was stable during 2008--2019 (Table 1).
+Similarly for males, we observed stable trends from 2008 to 2011 but a significant decrease after 2011 (APC: `r pullNumber2(prop_tab_sans_2020, 'apc_period_2_95_percent_ci', brackets = TRUE, stratifier_column == 'Sex: Male', preventive_practice == 'Dilated eye exam')`).
+Uninsured adults with diabetes had average annual increases in the receipt of dilated eye exams of `r pullNumber2(prop_tab_sans_2020, 'aapc_95_percent_ci', brackets = TRUE, stratifier_column == 'Insurance coverage: Uninsured', preventive_practice == 'Dilated eye exam')`.
+Adults with diabetes in the highest income to poverty income ratio group (\> 400%) had a flat trend in dilated eye examinations until 2013, after which the proportion significantly decreased (APC: `r pullNumber2(prop_tab_sans_2020, 'apc_period_2_95_percent_ci', brackets = TRUE, stratifier_column == 'Poverty income ratio: > 400%', preventive_practice == 'Dilated eye exam')`).
+
+## Foot exam
+
+The trend for foot exams for the overall adult population with diabetes was flat until 2011, after which it decreased (APC: `r pullNumber2(prop_tab_sans_2020, 'apc_period_2_95_percent_ci', brackets = TRUE, stratifier_column == 'Overall', preventive_practice == 'Foot examination')`, Table 1).
+We found an increase in foot exams among adults with diabetes age 65--74 until 2014 (APC: `r pullNumber2(prop_tab_sans_2020, 'apc_period_1_95_percent_ci', brackets = TRUE, stratifier_column == 'Age: 65 to 74', preventive_practice == 'Foot examination')`), and the trend was flat thereafter.
+
+## One or more dentist visits
+
+Adults age 65--74 and ≥75 years had average annual percent increases of `r pullNumber2(prop_tab_sans_2020, 'aapc_95_percent_ci', brackets = FALSE, stratifier_column == 'Age: 65 to 74', preventive_practice == 'One or more dentist visits')` and `r pullNumber2(prop_tab_sans_2020, 'apc_period_1_95_percent_ci', brackets = FALSE, stratifier_column == 'Age: 75+', preventive_practice == 'One or more dentist visits')`, respectively.
+Non-Hispanic White adults with diabetes had an average annual percent increase of `r pullNumber2(prop_tab_sans_2020, 'aapc_95_percent_ci', brackets = FALSE, stratifier_column == 'Race/Ethnicity: White/Not Hispanic', preventive_practice == 'One or more dentist visits')`.
+Among those with private insurance, we found decreasing proportions visiting the dentist during 2008--2015 (APC `r pullNumber2(prop_tab_sans_2020, 'apc_period_1_95_percent_ci', brackets = TRUE, stratifier_column == 'Insurance coverage: Private only', preventive_practice == 'One or more dentist visits')`), followed by an increase after 2015 (APC: `r pullNumber2(prop_tab_sans_2020, 'apc_period_2_95_percent_ci', brackets = TRUE, stratifier_column == 'Insurance coverage: Private only', preventive_practice == 'One or more dentist visits')`.
+The trends for adults with diabetes in the poverty income ratio group \< 100% and those with a high school education had multiple changes in direction during the study period.
+
+## Absence of preventive care services
+
+In 2008, 5.1% (95% CI: 2.7%, 7.5%) adults with diabetes reported receiving none of the six recommended care services.
+In 2019, this estimate was 6.1% (95% CI: 3.7%, 8.5%) and in 2020 it was 8.2% (95% CI: 4.5%, 11.9%).
+
+## Comparisons among subgroups
+
+The youngest adults (18--44 years) often reported lower rates of dilated eye exams, foot exams, cholesterol testing, and influenza vaccination (Supplemental Figure 1 & 2).
+Uninsured adults also often reported the lowest rates of preventive care for dilated eye exams, foot exams, cholesterol testing, and A1C testing.
+Adults with less than a high school education were less likely to visit the dentist in most years, although they were only significantly less likely to visit the dentist from 2008--2010, 2013--2014, and in 2020.
+
+# Discussion
+
+Despite the recovery from the Great Recession in 2008 and the passing of the Affordable Care Act (ACA) in 2010, we found no significant change over time in five out of the six preventive care services for the overall US adult population with diabetes.
+Influenza vaccination was the only preventive service that increased during 2008--2019.
+Among subgroups, influenza vaccine uptake, A1c testing, and dental visits tended to improve.
+However, foot exams, cholesterol testing, and dental visits among the uninsured tended to decline.
+While the passing of the ACA led to an increase in the number of adults with diagnosed and undiagnosed diabetes that have health insurance and an increase in their use of health care services [@myerson2019; @simon2017], detecting corresponding increases in the receipt of preventive care has proved more elusive.
+As of 2020, 8.2% of adults with diabetes had received none of the six preventive services.
+
+Two studies that used data from BRFSS found no changes overall in the receipt of preventive care for adults with diabetes as a result of the Medicaid expansion between 2014 and 2019 [@monnette2020; @luo2019].
+Similarly the majority of subgroups exhibited no change or decreased in receipt of these six preventive services.
+The subgroup trends we observed suggest disparities in diabetes care that have been shown in other research.
+Consistent with our findings, studies using data from NHANES for 2005--2018 as well as BRFSS from 2004--2014 both found that younger adults with diabetes were less likely to report receiving various recommended preventive care services [@shin2021; @luo2018].
+Additionally, insurance was a barrier to preventive care, as uninsured adults also reported lower rates of preventive care in these studies [@shin2021; @luo2018].
+In our study, dental visits decreased over the study period but dilated eye exams increased.
+Education has also been linked to meeting recommendations for preventive care, with adults with lower education consistently reporting lower rates of prevention [@eppley2019; @shin2021].
+We found that adults with less than a high school education had decreasing trends in cholesterol testing and frequently were less likely to report visiting the dentist at least once than adults with higher educational attainment, although this difference was not always statistically significant.
+Future research may wish to examine the percentage of adults with diabetes reporting receiving none of the six preventive care services.
+While the confidence intervals for the estimates from 2008 and 2019/2020 overlap, the increase highlights there is sustained inadequate preventive care for a subset of adults with diabetes.
+
+A1C testing and influenza vaccinations were the only two preventive services that showed increases either among the overall population or various subgroups, which may be linked with the increase in health care service usage [@myerson2019].
+These services can be administered at the point-of-care during regular physician visits, whereas a dilated eye exam or dental visit require separate appointments.
+Lack of access to specialists, limited provider acceptance of public insurance options like Medicare, and inadequate care coordination may further complicate access to dilated eye exams or dentist visits and may explain why, for most groups, we observed no change or a decrease in the receipt of these services [@chen2020; @eppley2019; @fathy2016].
+
+Other studies on trends in preventive care using different data sources report some conflicting findings.
+A study using data from NHANES found increases in the proportion of adults with diabetes that reported having a primary care doctor, received an annual check-up with a physician, had at least two A1C tests in a year, had their cholesterol levels tested, and had an annual foot exam by a doctor @shin2021.
+Another study that reported on data from NHANES, the National Health Interview Survey (NHIS), and BRFSS found that foot exams, influenza vaccinations, and A1C testing increased from 1999 - 2016, although dilated eye exams stayed roughly constant @fang2020.
+Data from BRFSS showed that adults with diabetes had reported decreasing dentist visits from 2004 to 2014 [@luo2018], while reported dilated eye examinations increased briefly following expansion of Medicaid in 2014 and then decreased [@chen2020].
+In contrast, a study using data from NHANES found that dilated eye exams for adults with diabetes did not increase from 2005 to 2016 [@eppley2019].
+No change was found for rates of influenza vaccination from 2007 to 2018 for the overall population of adults with diabetes when evaluated using data from NHIS [@hung2020].
+Differences in the results of these surveys may be due to differences in how questions are phrased and differences in the population being asked questions.
+Additionally, it is difficult to compare trends for overlapping time periods of different lengths so caution should be used when interpreting these differences; when possible, trends should be compared over similar, longer time periods [@cusser2021; @bahlai2021].
+
+## Limitations
+
+The responses from MEPS were self-reported which may introduce bias.
+The study group was also cross-sectional and does not provide insight into how past receipt of preventive services may affect future receipt.
+In 2013, MEPS implemented efforts to improve collection of complete information by field interviewers with the goal of improving underreporting.
+This effort may have improved data quality after 2014 and could have impacted our trend analyses.
+Furthermore, changes to the NHIS sample design in 2016 were made to better cover the target population and reduce bias.
+
+We are also unable to identify factors that are causally linked to the changes in trends.
+Additionally, there has been a steadily declining response rate for both MEPS and DCS from a peak during the studied time period of 59.3% and 92.4%, respectively in 2008 to 39.5% and 65.8%, respectively, in 2019 and 27.6% and 59.3%, respectively in 2020.
+Although weights for these data were adjusted for non-response, the direction of bias due to non-response cannot be known.
+Furthermore, we were unable to distinguish between type 1 and type 2 diabetes in these data.
+Because of the greater prevalence of type 2 diabetes the trends we report likely are more reflective of type 2 diabetes than type 1.
+
+# Conclusions
+
+In summary, with the exception of influenza vaccination, overall, the receipt of preventive care for diabetes from 2008 to 2019 was flat.
+The trend pattern in subgroups was heterogeneous.
+This work highlights services and specific subgroups that could be targeted to improve preventive care, especially groups that reported declines in receipt of preventive care.
+Declining trends in preventive care may lead to increasing diabetes complications, increasing the morbidity of diabetes.
+
+# Acknowledgements
+
+# References
+
+::: {#refs}
+:::
+
+\pagebreak
+
+::: landscape
+# Tables
+
+```{r}
+#| label: tbl-prev
+#| tbl-cap: Age-adjusted trends in proportions of US adults with diabetes that report receiving at least three of six recommended care practices - at least one dental visit, one dilated eye exam, one foot exam, two or more A1C tests, cholesterol level tested, and receiving an influenza vaccine.
+
+proportion_table_sans_2020 %>% 
+  tab_header("Age-adjusted trends in proportions of US adults with diabetes that report receiving recommended care services - at least one dental visit, one dilated eye exam, one foot exam, two or more A1C tests, cholesterol level tested, and receiving an influenza vaccine.")
+```
+
+\pagebreak
+
+# Figures
+
+```{r}
+#| label: fig-exams
+#| fig-cap: Age-adjusted trends in proportions of US adults with diabetes who reported receiving recommended medical examinations from 2008 - 2019.
+The dashed black line is the overall trend, while dots represent percentages for 2020.
+Data from 2020 was not included in the trend analysis.
+#| fig-width: 8
+
+all_exam_plots_sans_2020
+```
+
+\pagebreak
+
+```{r}
+#| label: fig-tests
+#| fig-cap: Age-adjusted trends in proportions of US adults with diabetes who reported receiving recommended lab tests and vaccinations.
+The dashed black line is the overall trend, while dots represent percentages for 2020.
+Data from 2020 was not included in the trend analysis.
+#| fig-width: 10
+
+all_test_plots_sans_2020
+```
+
+\pagebreak
+
+# Supplement
+
+```{r}
+#| label: tbl-prop
+#| tbl-cap: Age-adjusted trends in proportions of US adults with diabetes that report receiving six recommended care services - at least one dental visit, one dilated eye exam, one foot exam, two or more A1C tests, cholesterol level tested, and receiving an influenza vaccine.
+
+supplement_prop_tab %>% 
+  tab_header('Age-adjusted trends in proportions of US adults overall and by subgroup with diabetes that report receiving six recommended care services - at least one dental visit, one dilated eye exam, one foot exam, two or more A1C tests, cholesterol level tested, and receiving an influenza vaccine.')
+```
+
+```{r}
+#| include: false
+#| echo: false
+# Create plots with actual proportions and standard errors
+supp_dat <- age_adjusted_stats %>%
+      filter(strata != 'Total') %>%
+      filter(stratifier != 'overall') %>% 
+      filter(strata != 'Not available') %>%
+      filter(strata != 'Other Race/Not Hispanic') %>%
+      filter(strata != 'Other') %>% 
+      mutate(variable_text = case_when(variable == 'a1c' ~ '2 or more A1C tests',
+                                       variable == 'CHOL_all' ~ 'Cholesterol tested',
+                                       variable == 'DENT_all' ~ '1 or more dentist visits',
+                                       variable == 'eye-exam' ~ 'Dilated eye exam',
+                                       variable == 'flu' ~ 'Received influenza vaccine',
+                                       variable == 'foot' ~ 'Foot examination'),
+             strata = case_when(strata == 'stat_0' ~ 'Overall',
+                                TRUE ~ strata)) %>%
+      mutate(strata = as.factor(strata),
+             year_adj = year - 2007) %>%  
+  mutate(strata = as.factor(strata)) %>% 
+  split(., f = .$stratifier)
+
+supp_dat <- map(supp_dat, function(.x) {
+  .x %>% 
+    mutate(strata = fct_drop(strata))
+})
+
+supp_dat$poverty$strata <-
+  factor(
+    supp_dat$poverty$strata,
+    levels = c('Poor/Negative', 'Low income', 'Middle income', 'High income'), 
+    labels = c(
+      'd< 100%',
+      'c100% - 199%',
+      'b200% - 399%',
+      'a> 400% '
+    ),
+    ordered = TRUE
+  )
+
+supplemental_test_plots <-
+  map(
+    supp_dat,
+    ~ ggplot(
+      filter(.x, variable %in% c('a1c', 'CHOL_all', 'flu')),
+      aes(
+        x = year,
+        y = p,
+        group = strata,
+        color = strata
+      )
+    ) +
+      geom_point() +
+      geom_errorbar(
+        aes(ymin = p - 1.96 * (p.std.error * 100),
+            ymax = p + 1.96 * (p.std.error * 100))
+      ) +
+      facet_wrap(~ variable_text, ncol = 3, scales = 'free_y') +
+      theme_classic() +
+      scale_x_continuous(
+        limits = c(2007.5, 2020.5),
+        breaks = seq(2008, 2020, 2),
+        labels = c(2008, "", 2012, "", 2016, "", 2020)
+      ) +
+      theme(
+        axis.text = element_text(color = 'black'),
+        #axis.text.x = element_text(angle = 45, hjust = 0.9, vjust = 0.95),
+        legend.title = element_text(size = 11),
+        legend.text = element_text(size = 9)
+      ) +
+      labs(x = 'Year', y = 'Percentage')
+
+  )
+
+supplemental_exam_plots <-
+  map(
+    supp_dat,
+    ~ ggplot(
+      filter(.x, variable %!in% c('a1c', 'CHOL_all', 'flu')),
+      aes(
+        x = year,
+        y = p,
+        group = strata,
+        color = strata
+      )
+    ) +
+      geom_point() +
+      geom_errorbar(
+        aes(ymin = p - 1.96 * (p.std.error * 100),
+            ymax = p + 1.96 * (p.std.error * 100))
+      ) +
+      facet_wrap(~ variable_text, ncol = 3, scales = 'free_y') +
+      theme_classic() +
+      scale_x_continuous(
+        limits = c(2007.5, 2020.5),
+        breaks = seq(2008, 2020, 2),
+        labels = c(2008, "", 2012, "", 2016, "", 2020)
+      ) +
+      theme(
+        axis.text = element_text(color = 'black'),
+        #axis.text.x = element_text(angle = 45, hjust = 0.9, vjust = 0.95),
+        legend.title = element_text(size = 11),
+        legend.text = element_text(size = 9)
+      ) +
+      labs(x = 'Year', y = 'Percentage')
+
+  )
+
+supplemental_test_plots[[1]] <-
+  supplemental_test_plots[[1]] +
+  theme(axis.title.x = element_blank()) +
+  scale_color_manual(
+    name = 'Age (grouped)',
+    values = c(
+     '18 to 44' = color_pal[1],
+     '45 to 64'  = color_pal[2],
+     '65 to 74' = color_pal[3],
+     '75+' = color_pal[4]
+    ),
+    labels = c('18 to 44' = '18 to 44',
+               '45 to 64' = '45 to 64',
+               '65 to 74' = '65 to 74',
+               '75+'      = '75+')
+  )
+
+supplemental_test_plots[[2]] <-
+  supplemental_test_plots[[2]] +
+  theme(
+    strip.background =  element_blank(),
     strip.text = element_blank(),
-    axis.title.x = element_blank())
-exam_plots <- list(
-  exam_plots[[1]],
-  exam_plots[[6]],
-  exam_plots[[5]],
-  exam_plots[[2]],
-  exam_plots[[3]],
-  exam_plots[[4]]
+    axis.title.x = element_blank()
+  ) +
+  scale_color_manual(
+    name = 'Highest degree obtained',
+    labels = c('Greater than HS'       = 'Greater than HS',
+               'High school'           = 'High school',
+               'Less than high school' = 'Less than HS'),
+    values = c(
+     'Greater than HS' = color_pal[1],
+     'High school' = color_pal[2],
+     'Less than high school'  = color_pal[3]
     )
-(all_exam_plots <- exam_plots %>% 
+  )
+
+supplemental_test_plots[[3]] <-
+  supplemental_test_plots[[3]] +
+  theme(
+    strip.background =  element_blank(),
+    strip.text = element_blank(),
+    axis.title.x = element_blank()
+  ) +
+  scale_color_manual(
+    name = 'Insurance',
+    values = c(
+      'Medicaid' = color_pal[1],
+      'Medicare only' = color_pal[2],
+      'Private only' = color_pal[3],
+      'Uninsured' = color_pal[4]
+    ),   labels = c(
+      'Medicaid'      = 'Medicaid',
+      'Medicare only' = 'Medicare only',
+      'Private only'  = 'Private only',
+      'Uninsured'     = 'Uninsured'
+    )
+  )
+
+supplemental_test_plots[[4]] <-
+  supplemental_test_plots[[4]] +
+  theme(strip.background =  element_blank(),
+        strip.text = element_blank()) +
+  scale_color_manual(
+    name = 'Poverty income ratio',
+    labels = c('a> 400% '     = '> 400%',
+               'b200% - 399%' = '200% - 399%',
+               'c100% - 199%' = '100% - 199%',
+               'd< 100%'      = '< 100%'),
+
+    values = c(
+      'a> 400% ' = color_pal[1],
+      'b200% - 399%' = color_pal[2],
+      'c100% - 199%' = color_pal[3],
+      'd< 100%' = color_pal[4]
+    )
+  )
+
+supplemental_test_plots[[5]] <-
+  supplemental_test_plots[[5]] + theme(
+    strip.background =  element_blank(),
+    strip.text = element_blank(),
+    axis.title.x = element_blank()
+  ) +
+  scale_color_manual(
+    name = 'Race & Ethnicity',
+    labels = c(
+     'Asian/Not Hispanic' = 'Asian/Not Hispanic',
+     'Black/Not Hispanic' = 'Black/Not Hispanic',
+     'Hispanic'           = 'Hispanic',
+     'White/Not Hispanic' = 'White/Not Hispanic'
+    ),
+    values = c(
+     'Asian/Not Hispanic' = color_pal[1],
+     'Black/Not Hispanic'  = color_pal[2],
+     'Hispanic' = color_pal[3],
+     'White/Not Hispanic' = color_pal[4]
+    )
+  )
+supplemental_test_plots[[6]] <-
+  supplemental_test_plots[[6]] +
+  theme(
+    strip.background =  element_blank(),
+    strip.text = element_blank(),
+    axis.title.x = element_blank()
+  ) +
+  scale_color_manual(
+    name = 'Sex',
+    labels = c('Female'  = 'Female',
+               'Male'    = 'Male'),
+    values = c(
+     'Female' = color_pal[1],
+     'Male'  = color_pal[2]
+    )
+  ) 
+supplemental_test_plots <- list(
+  supplemental_test_plots[[1]],
+  supplemental_test_plots[[6]],
+  supplemental_test_plots[[5]],
+  supplemental_test_plots[[2]],
+  supplemental_test_plots[[3]],
+  supplemental_test_plots[[4]]
+)
+
+# Set up legends on all plots
+supplemental_exam_plots[[1]] <- supplemental_exam_plots[[1]] +
+  theme(axis.title.x = element_blank()) +
+  scale_color_manual(
+    name = 'Age (grouped)',
+    labels = c('18 to 44' = '18 to 44',
+               '45 to 64' = '45 to 64',
+               '65 to 74' = '65 to 74',
+               '75+'      = '75+'),
+    values =   c(
+      '18 to 44' = color_pal[1],
+      '45 to 64' = color_pal[2],
+      '65 to 74' = color_pal[3],
+      '75+'      = color_pal[4]
+    )
+  )
+
+supplemental_exam_plots[[2]] <-
+  supplemental_exam_plots[[2]] +
+  theme(
+    strip.background =  element_blank(),
+    strip.text = element_blank(),
+    axis.title.x = element_blank()
+  ) +
+  scale_color_manual(
+    name = 'Highest degree obtained',
+    labels = c('Greater than HS'       = 'Greater than HS',
+               'High school'           = 'High school',
+               'Less than high school' = 'Less than HS'),
+        values = c(
+      'Greater than HS'       = color_pal[1],
+      'High school'           = color_pal[2],
+      'Less than high school' = color_pal[3]
+    )
+  )
+
+supplemental_exam_plots[[3]] <-
+  supplemental_exam_plots[[3]] +
+  theme(
+    strip.background =  element_blank(),
+    strip.text = element_blank(),
+    axis.title.x = element_blank()
+  ) +
+  scale_color_manual(
+    name = 'Insurance',
+    labels = c(
+     'Medicaid'      =  'Medicaid',
+     'Medicare only' =  'Medicare only',
+     'Private only'  =  'Private only',
+     'Uninsured'     =  'Uninsured'
+    ),
+    values = c(
+      'Medicaid'      = color_pal[1],
+      'Medicare only' = color_pal[2],
+      'Private only'  = color_pal[3],
+      'Uninsured'     = color_pal[4]
+    )
+  )
+
+supplemental_exam_plots[[4]] <-
+  supplemental_exam_plots[[4]] +
+  theme(strip.background =  element_blank(),
+        strip.text = element_blank()) +
+  scale_color_manual(
+    name = 'Poverty income ratio',
+    labels = c('a> 400% '     = '> 400%',
+               'b200% - 399%' = '200% - 399%',
+               'c100% - 199%' = '100% - 199%',
+               'd< 100%'      = '< 100%'),
+    values = c(
+      'a> 400% '     = color_pal[1],
+      'b200% - 399%' = color_pal[2],
+      'c100% - 199%' = color_pal[3],
+      'd< 100%'      = color_pal[4]
+    )
+  )
+
+supplemental_exam_plots[[5]] <-
+  supplemental_exam_plots[[5]] +
+  theme(
+    strip.background =  element_blank(),
+    strip.text = element_blank(),
+    axis.title.x = element_blank()
+  ) +
+  scale_color_manual(
+    name = 'Race & Ethnicity',
+    labels = c(
+      'Asian/Not Hispanic' = 'Asian/Not Hispanic',
+      'Black/Not Hispanic' = 'Black/Not Hispanic',
+      'Hispanic'           = 'Hispanic',
+      'White/Not Hispanic' = 'White/Not Hispanic'
+    ),
+    values = c(
+      'Asian/Not Hispanic' = color_pal[1],
+      'Black/Not Hispanic' = color_pal[2],
+      'Hispanic'           = color_pal[3],
+      'White/Not Hispanic' = color_pal[4]
+    )
+  )
+
+supplemental_exam_plots[[6]] <-
+  supplemental_exam_plots[[6]] +
+  theme(
+    strip.background =  element_blank(),
+    strip.text = element_blank(),
+    axis.title.x = element_blank()
+  ) +
+  scale_color_manual(
+    name = 'Sex',
+    labels = c('Female'  = 'Female',
+               'Male'    = 'Male'),
+    values = c(
+      'Female' = color_pal[1],
+      'Male'  = color_pal[2]
+    )
+  )
+
+supplemental_exam_plots <- list(
+  supplemental_exam_plots[[1]],
+  supplemental_exam_plots[[6]],
+  supplemental_exam_plots[[5]],
+  supplemental_exam_plots[[2]],
+  supplemental_exam_plots[[3]],
+  supplemental_exam_plots[[4]]
+)
+
+supplemental_all_exam <- supplemental_exam_plots %>% 
   wrap_plots(nrow = 6) &
-  theme(plot.margin = margin(0.5, 0.5, 0.5, 0.5, 'pt')))
-(all_test_plots <- test_plots %>% 
+  theme(plot.margin = margin(0.5, 0.5, 0.5, 0.5, 'pt'),
+        legend.justification = 'left',
+        plot.caption = element_text(hjust = 0)) &
+  guides(color = guide_legend(ncol = 2)) 
+supplemental_all_test <- supplemental_test_plots %>% 
   wrap_plots(nrow = 6) &
-  theme(plot.margin = margin(0.5, 0.5, 0.5, 0.5, 'pt')))
-ggsave(plot = all_exam_plots,
-       filename = 'figures/all_exam_plots.tiff',
-       dpi = 200,
+  theme(plot.margin = margin(0.5, 0.5, 0.5, 0.5, 'pt'),
+        legend.justification = 'left',
+         plot.caption = element_text(hjust = 0)) &
+  guides(color = guide_legend(ncol = 2))
+
+ggsave(plot = supplemental_all_exam,
+       filename = 'figures/supp_exam_plots.tiff',
+       dpi = 1200,
        width = 10,
-       height = 7)
-ggsave(plot = all_test_plots,
-       filename = 'figures/all_test_plots.tiff',
-       dpi = 200,
+       height = 6)
+ggsave(plot = supplemental_all_test,
+       filename = 'figures/supp_test_plots.tiff',
+       dpi = 1200,
        width = 10,
-       height = 7)
-ggsave(plot = all_exam_plots,
-       filename = 'figures/all_exam_plots.svg',
-       dpi = 200,
-       width = 10,
-       height = 7)
-ggsave(plot = all_test_plots,
-       filename = 'figures/all_test_plots.svg',
-       dpi = 200,
-       width = 10,
-       height = 7)
+       height = 6)
 ```
+
+```{r}
+#| include: FALSE
+#| fig-cap: Age-adjusted proportions with 95% confidence intervals of US adults with diabetes who reported receiving recommended medical examinations from 2008 - 2020. 
+supplemental_all_exam
+```
+
+```{r}
+#| include: FALSE
+#| fig-cap: Age-adjusted proportions with 95% confidence intervals of US adults with diabetes who reported receiving recommended lab tests and vaccinations from 2008 - 2020.
+supplemental_all_test
+```
+:::

### 2023-06-14 scripts/manuscript/manuscript_draft.qmd
Tweaking references to fit style

--- 2023-01-19 scripts/manuscript/manuscript_draft.qmd
@@
     reference-doc: template.docx
-editor: visual
+editor: source
 bibliography: references.bib
-csl: ama.csl
+csl: diabetes-care2.csl
 execute:
@@
 # get_pkgs_info(pkgs = c('gtsummary', 'patchwork', 'gt', 'gtsummary'))
+ggplot2::theme_update(text = element_text(family = 'Arial')) # I think this sets default plot font to Arial. May also try
+# family = sans
 
@@
 # weird and doesn't like being bang-bang-banged.
-pullNumber <- function(data, filter.by, column) {
-  data %>% 
+pullNumber <- function(data, filter.by, column, brackets = FALSE) {
+  out <- data %>% 
     filter(` ` == filter.by) %>% 
@@
     pull() 
+  out <- gsub("\\(", "(95% CI: ", out)
+  if (brackets == TRUE) {
+    out <- out %>% 
+    str_replace("\\(", "\\[") %>% 
+    str_replace("\\)", "\\]")
+  }
+  out
 }
 # For other tables that don't use such weird column names
-pullNumber2 <- function(data, filter.column, filter.by, select.column) {
-    data %>% 
-    filter(!!!filter.column == filter.by) %>% 
-    select(!!!column) %>% 
-    pull()
+pullNumber2 <-
+  function(data, select.column, brackets = FALSE, CI = FALSE, ...) {
+
+    out <- data %>%
+      ungroup() %>%
+      filter(...) %>%
+      pull({
+        {
+          select.column
         }
+      })
+    out <- gsub("-", "—", out)
+    out <- gsub("–", "—", out)
+    if (CI == TRUE) {
+      out <- gsub("\\(", "(95% CI: ", out)
+      out <- gsub("(-?\\d+\\.\\d+)", "\\1%", out)
+    } else {
+      out <- gsub("(-?\\d+\\.\\d+)", "\\1%", out)
+    }
+    if (brackets == TRUE) {
+      out <- out %>%
+        str_replace("\\(", "\\[") %>%
+        str_replace("\\)", "\\]")
+    }
+    out
+  }
+
+# Some numbers pulled from MEPS page:
+sample_size_response_rate <- tibble(
+  year = 2020:2008,
+  n = c(26847, 27648, 29415, 30716, 33259, 33893, 33162, 35068, 37182, 33622, 31228, 34920, 31262),
+  full_year_response = c(27.6, 39.5, 42.7, 44.2, 46.0, 47.7, 48.5, 52.8, 56.3, 54.9, 53.5, 57.2, 59.3)
+)
+
 ```
 
-```{r}
+```{r preventive-table}
 
@@
         across(starts_with('aapc_'),
-                ~specifyDecimal(x = .x, digits = 2)),
+                ~specifyDecimal(x = .x, digits = 1)),
          across(starts_with('aapc'),
@@
          across(contains('cl'),
-                ~specifyDecimal(.x, digits = 2)),
+                ~specifyDecimal(.x, digits = 1)),
          across(starts_with('apc') | starts_with('p_'),
@@
 
-# Clean up the age adjusted preventive practices and then join with the aapc table
+# Clean up the age adjusted preventive services and then join with the aapc table
 clean_age_adjusted <- age_adjusted_preventive %>% 
-  # Filter to just the >=3 practices
-  filter(label == 'At least three preventive practices followed') %>% 
+  # Filter to just the >=3 services
+  filter(variable == 'zero_services') %>% 
   # Filter down to every other year
-  filter(year %in% seq(2000, 2020, by = 2)) %>% 
+  filter(year %in% seq(2000, 2020, by = 1)) %>% 
   mutate(chr_age_adj_prop = sigfig(p, digits = 3),
          p.std.error = p.std.error * 100,
-         age_adjusted_se_perc = sigfig(p.std.error, digits = 3),
+         age_adjusted_se_perc = sigfig(p.std.error, digits = 2),
          percentage = glue::glue('{chr_age_adj_prop} ({age_adjusted_se_perc})')) %>% 
@@
   # Remove excess strata
-  filter(strata %!in% c('Not available', 'Other Race/Not Hispanic')) %>% 
+  filter(strata %!in% c('Not available', 'Other Race/not Hispanic')) %>% 
   # Relevel stratifier factor, clean up stratifier and strata names
@@
          perc_change_char = specifyDecimal(percent_change, digits = 1),
-         perc_change_lcl_char = specifyDecimal(perc_change_lcl, digits = 2),
-         perc_change_ucl_char = specifyDecimal(perc_change_ucl, digits = 2),
+         perc_change_lcl_char = specifyDecimal(perc_change_lcl, digits = 1),
+         perc_change_ucl_char = specifyDecimal(perc_change_ucl, digits = 1),
          `Percent Change (95% CI)` = glue::glue('{perc_change_char} ({perc_change_lcl_char}, {perc_change_ucl_char})')) %>% 
@@
   mutate(strata = case_when(as.character(strata) == 'Poor/Negative' ~ '< 100%',
-                            as.character(strata) == 'Low income' ~ '100% - 199%',
-                            as.character(strata) == 'Middle income' ~ '200% - 399%',
+                            as.character(strata) == 'Low income' ~ '100%—199%',
+                            as.character(strata) == 'Middle income' ~ '200%—399%',
                             as.character(strata) == 'High income' ~ '> 400%',
@@
 # Rename strata to a blank name to remove it from the final table
-preventive_practice_table <- cleaned_preventive_df %>% 
+preventive_service_table <- cleaned_preventive_df %>% 
+  filter(strata != 'Other') %>% 
   group_by(stratifier) %>%
@@
   rename(`2008 (SE)` = `2008`,
+         `2009 (SE)` = `2009`,
          `2010 (SE)` = `2010`,
+         `2011 (SE)` = `2011`,
          `2012 (SE)` = `2012`,
+         `2013 (SE)` = `2013`,
          `2014 (SE)` = `2014`,
+         `2015 (SE)` = `2015`,
          `2016 (SE)` = `2016`,
+         `2017 (SE)` = `2017`,
          `2018 (SE)` = `2018`,
+         `2019 (SE)` = `2019`,
          `2020 (SE)` = `2020`,
@@
   sub_missing(missing_text = ' ')
-preventive_practice_table$`_data` <- preventive_practice_table$`_data`[c(1:18, 20, 19, 21), ]
-
-tab1 <- preventive_practice_table$`_data`
+
+# Reorganize insurance variables
+preventive_service_table$`_data` <- preventive_service_table$`_data`[c(1:14, 15, 18, 16, 17, 19:22), ]
+tab1 <- preventive_service_table$`_data`
 ```
 
-```{r}
-
+```{r preventive-table-sans-2020}
+tar_load(ends_with('sans_2020'),
+         store = here::here('_targets/'))
+# Clean up the AAPC table and get it into format for printing to table
+cleaned_jp_aapc_sans_2020 <- jp_prevention_aapc_sans_2020 %>% 
+  select(-aapc_index) %>% 
+  mutate(aapc = specifyDecimal(aapc, digits = 1),
+        across(starts_with('aapc_'),
+                ~specifyDecimal(x = .x, digits = 1)),
+         across(starts_with('aapc'),
+                ~case_when(.x == ' NA' ~ NA_character_,
+                           TRUE ~ .x)),
+         AAPC = case_when(!is.na(aapc) ~ glue::glue('{aapc} ({aapc_c_i_low}, {aapc_c_i_high})'),
+                          TRUE ~ NA_character_)) %>%
+  select(stratifier, strata, AAPC)
+
+# Format APC table for future joining
+cleaned_jp_apc_sans_2020 <- jp_prevention_apc_sans_2020 %>% 
+  # No model has more than a single joinpoint, so make wider and then
+  # remove the excess columns to determine if there's no join point (segmend_end = 2020)
+  # or a joinpoint (segment_end != 2019)
+  pivot_wider(id_cols = c(stratifier, strata, model),
+              names_from = segment,
+              values_from = c(segment_start, segment_end, apc, p_value, apc_significant,
+                              apc_95_lcl, apc_95_ucl)
+  ) %>% 
+  select(-segment_start_0, -segment_start_1, -segment_end_1, -apc_significant_0, -apc_significant_1) %>% 
+  # Make segment empty if no joinpoint
+  mutate(segment = case_when(segment_end_0 == 2019 ~ NA_integer_,
+                             TRUE ~ segment_end_0)) %>% 
+  # MAke apc empty if not significant
+  mutate(across(c(apc_0, apc_95_lcl_0, apc_95_ucl_0),
+                ~ case_when(p_value_0 > 0.05 & p_value_1 > 0.05 ~ NA_real_,
+                            TRUE ~ .x)), 
+         across(c(apc_1, apc_95_lcl_1, apc_95_ucl_1),
+                ~ case_when(p_value_0 > 0.05 & p_value_1 > 0.05 ~ NA_real_,
+                            TRUE ~ .x)),
+         across(starts_with('apc_0') | starts_with('apc_1') | starts_with('p_'),
+                ~specifyDecimal(.x, digits = 1)),
+         across(contains('cl'),
+                ~specifyDecimal(.x, digits = 1)),
+         across(starts_with('apc') | starts_with('p_'),
+                ~case_when(.x == 'NA' ~ NA_character_,
+                           TRUE ~ .x))) %>% 
+  # Concatenate apc column with CI columns
+  mutate(`APC Period 1` = case_when(
+       !is.na(apc_0) ~ glue::glue('{apc_0} ({apc_95_lcl_0}, {apc_95_ucl_0})'),
+       TRUE ~ NA_character_
+                                    ),
+    `APC Period 2` = case_when(
+       !is.na(apc_1) ~ glue::glue('{apc_1} ({apc_95_lcl_1}, {apc_95_ucl_1})'),
+       TRUE ~ NA_character_
+    )
+  ) %>%
+  select(stratifier, strata, segment, starts_with('APC '))
+
+# Clean up the age adjusted preventive services and then join with the aapc table
+clean_age_adjusted <- age_adjusted_preventive %>% 
+  # Filter to just the >=3 services
+  filter(variable == 'zero_services') %>% 
+  # Filter down to every other year
+  filter(year %in% seq(2000, 2020, by = 1)) %>% 
+  mutate(chr_age_adj_prop = specifyDecimal(p, digits = 1),
+         p.std.error = p.std.error * 100,
+         age_adjusted_se_perc = specifyDecimal(p.std.error, digits = 1),
+         percentage = glue::glue('{chr_age_adj_prop} ({age_adjusted_se_perc})')) %>% 
+  pivot_wider(
+    id_cols = c(stratifier, variable, label, strata),
+    names_from = year,
+    values_from = c(p, percentage, p.std.error),
+  ) %>% 
+  # Remove excess strata
+  filter(strata %!in% c('Not available', 'Other Race/not Hispanic')) %>% 
+  # Relevel stratifier factor, clean up stratifier and strata names
+  mutate(stratifier = factor(stratifier,
+                             c('overall', 'age', 'sex', 'race', 'edu', 'insurance', 'poverty')),
+         strata = case_when(strata == 'stat_0' ~ '-', 
+                            strata == 'Greater than HS' ~ 'Greater than high school',
+                            TRUE ~ strata),
+         percent_change = ((p_2019 - p_2008) / p_2008) * 100,
+         percent_change_se = (abs(p_2019 / p_2008) * sqrt((p.std.error_2019^2 / p_2019^2) + (p.std.error_2008^2 / p_2008^2)) * 100),
+         perc_change_lcl = percent_change - 1.96 * percent_change_se,
+         perc_change_ucl = percent_change + 1.96 * percent_change_se,
+         perc_change_char = specifyDecimal(percent_change, digits = 1),
+         perc_change_lcl_char = specifyDecimal(perc_change_lcl, digits = 1),
+         perc_change_ucl_char = specifyDecimal(perc_change_ucl, digits = 1),
+         `Percent Change (95% CI)` = glue::glue('{perc_change_char} ({perc_change_lcl_char}, {perc_change_ucl_char})')) %>% 
+  select(-starts_with('age_adjusted_prop'), -starts_with('p.std.error'), -contains('_change_')) %>% 
+  setNames(., str_replace(names(.), 'percentage_', "")) %>% 
+  mutate(strata = as.factor(strata)) %>% 
+  mutate(stratifier = recode_factor(
+    stratifier,
+    overall = 'Overall',
+    age = 'Age',
+    sex = 'Sex',
+    race = 'Race/Ethnicity',
+    edu = 'Highest degree earned',
+    insurance = 'Insurance coverage',
+    poverty = 'Poverty level'
+  )) %>% 
+  # Join with AAPC table
+  left_join(cleaned_jp_aapc_sans_2020, by = c('stratifier', 'strata'))
+
+cleaned_preventive_df_sans_2020 <- left_join(clean_age_adjusted, cleaned_jp_apc_sans_2020, by = c('stratifier', 'strata')) %>% 
+  mutate(AAPC = case_when(is.na(AAPC) & is.na(`APC Period 2`) ~ `APC Period 1`,
+                          TRUE ~ AAPC),
+         `APC Period 1` = case_when(is.na(`APC Period 1`) & is.na(`APC Period 2`) ~ AAPC,
+                                    TRUE ~ `APC Period 1`)) %>%
+  # Rename poverty levels
+  mutate(strata = case_when(as.character(strata) == 'Poor/Negative' ~ '< 100%',
+                            as.character(strata) == 'Low income' ~ '100%—199%',
+                            as.character(strata) == 'Middle income' ~ '200%—399%',
+                            as.character(strata) == 'High income' ~ '> 400%',
+                            TRUE ~ as.character(strata)))
+
+# Rename strata to a blank name to remove it from the final table
+preventive_service_table_sans_2020 <- cleaned_preventive_df_sans_2020 %>% 
+  filter(strata != 'Other') %>% 
+  group_by(stratifier) %>%
+  select(stratifier, ` ` = strata, `2008`:`2020`, `Percent Change (95% CI)`, `Joinpoint Year` = segment,
+         `APC Period 1`, `APC Period 2`, `AAPC`) %>%
+  mutate(stratifier = case_when(as.character(stratifier) == 'Poverty level' ~ 'Poverty income ratio',
+                                TRUE ~ as.character(stratifier))) %>% 
+  # Rename some columns to add () info
+  rename(`2008 (SE)` = `2008`,
+         `2009 (SE)` = `2009`,
+         `2010 (SE)` = `2010`,
+         `2011 (SE)` = `2011`,
+         `2012 (SE)` = `2012`,
+         `2013 (SE)` = `2013`,
+         `2014 (SE)` = `2014`,
+         `2015 (SE)` = `2015`,
+         `2016 (SE)` = `2016`,
+         `2017 (SE)` = `2017`,
+         `2018 (SE)` = `2018`,
+         `2019 (SE)` = `2019`,
+         `2020 (SE)` = `2020`,
+         `APC Period 1 (95% CI)` = `APC Period 1`,
+         `APC Period 2 (95% CI)` = `APC Period 2`,
+         `AAPC (95% CI)` = `AAPC`) %>% 
+  gt() %>% 
+  sub_missing(missing_text = ' ') %>% 
+  tab_footnote(
+    footnote = "Values in these columns were estimated excluding data from 2020.",
+    locations = cells_column_labels(
+      columns = c(`Percent Change (95% CI)`,
+      `APC Period 1 (95% CI)`,
+      `APC Period 2 (95% CI)`,
+      `AAPC (95% CI)`
+    ))
+  ) %>% 
+  tab_options(footnotes.marks = "a")
+# Reorganize insurance variables
+ preventive_service_table_sans_2020$`_data` <- preventive_service_table_sans_2020$`_data`[c(1:14, 15, 18, 16, 17, 19:22), ]
+
+tab_sans_2020 <- preventive_service_table_sans_2020$`_data`
+
+```
+
+```{r proportion-table-sans-2020}
+# Clean up the AAPC table and get it into format for printing to table
+cleaned_prop_aapc_sans_2020 <- jp_proportion_aapc_sans_2020 %>% 
+  select(-aapc_index) %>% 
+  mutate(aapc = specifyDecimal(aapc, digits = 1),
+        across(starts_with('aapc_'),
+                ~specifyDecimal(x = .x, digits = 1)),
+         across(starts_with('aapc'),
+                ~case_when(.x == ' NA' ~ NA_character_,
+                           TRUE ~ .x)),
+         AAPC = case_when(!is.na(aapc) ~ glue::glue('{aapc} ({aapc_c_i_low}, {aapc_c_i_high})'),
+                          TRUE ~ NA_character_)) %>%
+  select(stratifier, strata, service, AAPC)
+
+# Format APC table for future joining
+cleaned_prop_apc_sans_2020 <- jp_proportion_apc_sans_2020 %>% 
+  # No model has more than a single joinpoint, so make wider and then
+  # remove the excess columns to determine if there's no join point (segmend_end = 2020)
+  # or a joinpoint (segment_end != 2019)
+  pivot_wider(id_cols = c(stratifier, strata, service, model),
+              names_from = segment,
+              values_from = c(segment_start, segment_end, apc, p_value, apc_significant,
+                              apc_95_lcl, apc_95_ucl)
+  ) %>% 
+  mutate(
+    # This code here changes the apc values to NA if they aren't significant, but I think
+    # what I need to do is change the APC values if there are no identified joinpoints
+    # across(
+    #   c(apc_0, apc_95_lcl_0, apc_95_ucl_0),
+    #   ~ case_when(!is.na(segment_start_1) 0.05 &
+    #                 p_value_1 > 0.05 & p_value_2 > 0.05 & p_value_3 > 0.05 ~ NA_real_,
+    #               TRUE ~ .x)
+    # ),
+    # across(
+    #   c(apc_1, apc_95_lcl_1, apc_95_ucl_1),
+    #   ~ case_when(p_value_0 > 0.05 &
+    #                 p_value_1 > 0.05 & p_value_2 > 0.05 & p_value_3 > 0.05 ~ NA_real_,
+    #               TRUE ~ .x)
+    # ),
+    # across(
+    #   c(apc_2, apc_95_lcl_2, apc_95_ucl_2),
+    #   ~ case_when(p_value_0 > 0.05 &
+    #                 p_value_1 > 0.05 & p_value_2 > 0.05 & p_value_3 > 0.05 ~ NA_real_,
+    #               TRUE ~ .x)
+    # ),
+    # across(
+    #   c(apc_3, apc_95_lcl_3, apc_95_ucl_3),
+    #   ~ case_when(p_value_0 > 0.05 &
+    #                 p_value_1 > 0.05 & p_value_2 > 0.05 & p_value_3 > 0.05 ~ NA_real_,
+    #               TRUE ~ .x)
+    # ),
+    across(
+      matches('apc_[0-9]{1}') | starts_with('p_'),
+      ~ specifyDecimal(.x, digits = 1)
+    )
+  ) %>% 
+    select(-contains('significant')) %>% 
+    mutate(across(starts_with('apc') | starts_with('p_'),
+                ~case_when(.x == 'NA' ~ NA_character_,
+                           TRUE ~ .x))) %>% 
+  # Concatenate apc column with CI columns
+  mutate(`APC Period 1` = case_when(
+       !is.na(apc_0) ~ glue::glue('{apc_0} ({apc_95_lcl_0}, {apc_95_ucl_0})'),
+       TRUE ~ NA_character_
+                                    ),
+    `APC Period 2` = case_when(
+       !is.na(apc_1) ~ glue::glue('{apc_1} ({apc_95_lcl_1}, {apc_95_ucl_1})'),
+       TRUE ~ NA_character_
+    ),
+    `APC Period 3` = case_when(
+       !is.na(apc_2) ~ glue::glue('{apc_2} ({apc_95_lcl_2}, {apc_95_ucl_2})'),
+       TRUE ~ NA_character_
+    ),
+    `APC Period 4` = case_when(
+       !is.na(apc_3) ~ glue::glue('{apc_3} ({apc_95_lcl_3}, {apc_95_ucl_3})'),
+       TRUE ~ NA_character_
+    )
+  ) %>%
+    # Make segment empty if no joinpoint
+  mutate(segment = ifelse(!is.na(segment_start_1) & !is.na(segment_start_2) & !is.na(segment_start_3), 
+                             paste(segment_start_1, segment_start_2, segment_start_3, sep = ", "),
+                             ifelse(!is.na(segment_start_1) & !is.na(segment_start_2) & is.na(segment_start_3),
+                                    paste(segment_start_1, segment_start_2, sep = ", "),
+                                    ifelse(!is.na(segment_start_1) & is.na(segment_start_2) & is.na(segment_start_3),
+                                           segment_start_1,
+                                           ifelse(segment_end_0 == 2019, NA_character_, 'Check me')
+                                           )
+                                    )
+                             )
+         ) %>% 
+  # MAke apc empty if not significant
+  select(stratifier, strata, service, segment, starts_with('APC '), -segment_start_0, -segment_start_1, -segment_end_1)
+
+# Clean up the age adjusted preventive services and then join with the aapc table
+clean_age_adjusted_prop <- age_adjusted_stats %>% 
+  # Filter to just the >=3 services
+  #filter(label == 'At least three preventive services followed') %>% 
+  # Filter down to every other year
+  filter(year %in% seq(2000, 2020, by = 1)) %>% 
+  mutate(chr_age_adj_prop = specifyDecimal(p, digits = 1),
+         p.std.error = p.std.error * 100,
+         age_adjusted_se_perc = specifyDecimal(p.std.error, digits = 1),
+         percentage = glue::glue('{chr_age_adj_prop} ({age_adjusted_se_perc})')) %>% 
+  pivot_wider(
+    id_cols = c(stratifier, variable, label, strata),
+    names_from = year,
+    values_from = c(p, percentage, p.std.error),
+  ) %>% 
+  # Calculate average proportion for all years and SE
+  rowwise() %>% 
+  mutate(p_average = mean(c_across(p_2008:p_2019)),
+         p_se = sd(c_across(p_2008:p_2019)) / sqrt(13),
+         p_lci = p_average - 1.96 * p_se,
+         p_uci = p_average + 1.96 * p_se) %>% 
+  ungroup() %>% 
+  # Now combine
+  mutate(p_average_chr = specifyDecimal(p_average, digits = 1),
+         p_se_chr = specifyDecimal(p_se, digits = 1),
+         `Average` = glue::glue('{p_average_chr} ({p_se_chr})')) %>% 
+  # Remove excess strata
+  filter(strata %!in% c('Not available', 'Other Race/not Hispanic')) %>% 
+  # Relevel stratifier factor, clean up stratifier and strata names
+  mutate(stratifier = factor(stratifier,
+                             c('overall', 'age', 'sex', 'race', 'edu', 'insurance', 'poverty')),
+         strata = case_when(strata == 'stat_0' ~ '-', 
+                            strata == 'Greater than HS' ~ 'Greater than high school',
+                            TRUE ~ strata),
+         percent_change = ((p_2019 - p_2008) / p_2008) * 100,
+         percent_change_se = (abs(p_2019 / p_2008) * sqrt((p.std.error_2019^2 / p_2019^2) + (p.std.error_2008^2 / p_2008^2)) * 100),
+         perc_change_lcl = percent_change - 1.96 * percent_change_se,
+         perc_change_ucl = percent_change + 1.96 * percent_change_se,
+         perc_change_char = specifyDecimal(percent_change, digits = 1),
+         perc_change_lcl_char = specifyDecimal(perc_change_lcl, digits = 1),
+         perc_change_ucl_char = specifyDecimal(perc_change_ucl, digits = 1),
+         `Percent Change (95% CI)` = glue::glue('{perc_change_char} ({perc_change_lcl_char}, {perc_change_ucl_char})')) %>% 
+  select(-starts_with('age_adjusted_prop'), -starts_with('p.std.error'), -contains('_change_')) %>% 
+  setNames(., str_replace(names(.), 'percentage_', "")) %>% 
+  mutate(strata = as.factor(strata)) %>% 
+  mutate(stratifier = recode_factor(
+    stratifier,
+    overall = 'Overall',
+    age = 'Age',
+    sex = 'Sex',
+    race = 'Race/Ethnicity',
+    edu = 'Highest degree earned',
+    insurance = 'Insurance coverage',
+    poverty = 'Poverty level'
+  )) %>% 
+  # Join with AAPC table
+  left_join(cleaned_prop_aapc_sans_2020, by = c('stratifier', 'strata', 'variable' = 'service'))
+
+cleaned_proportion_df_sans_2020 <- left_join(clean_age_adjusted_prop, cleaned_prop_apc_sans_2020, by = c('stratifier', 'strata', 'variable' = 'service')) %>% 
+  mutate(AAPC = case_when(is.na(AAPC) & is.na(`APC Period 2`) & is.na(`APC Period 3`) ~ `APC Period 1`,
+                          TRUE ~ AAPC),
+         `APC Period 1` = case_when(is.na(`APC Period 1`) & is.na(`APC Period 2`) ~ AAPC,
+                                    TRUE ~ `APC Period 1`)) %>%
+  # Rename poverty levels
+  mutate(strata = case_when(as.character(strata) == 'Poor/Negative' ~ '< 100%',
+                            as.character(strata) == 'Low income' ~ '100%—199%',
+                            as.character(strata) == 'Middle income' ~ '200%—399%',
+                            as.character(strata) == 'High income' ~ '> 400%',
+                            TRUE ~ as.character(strata)))
+
+# Rename strata to a blank name to remove it from the final table
+prop_tab_sans_2020 <- cleaned_proportion_df_sans_2020 %>% 
+  filter(strata != 'Other') %>% 
+  group_by(variable) %>%
+  mutate(strata = case_when(strata == '-' ~ 'Overall', TRUE ~ strata)) %>% 
+  mutate(variable = case_when(variable == 'a1c' ~ 'Two or more A1C tests',
+                                   variable == 'CHOL_all' ~ 'Cholesterol tested',
+                                   variable == 'DENT_all' ~ 'One or more dentist visits',
+                                   variable == 'eye-exam' ~ 'Dilated eye exam',
+                                   variable == 'flu' ~ 'Received influenza vaccine',
+                                   variable == 'foot' ~ 'Foot examination')) %>% 
+  # Select table variables
+  select(
+    stratifier,
+    ` ` = strata,
+    `Preventive service` = variable,
+    `Average (SE)` = Average,
+    `2008`:`2020`,
+    `Percent Change (95% CI)`,
+    `Joinpoint Year` = segment,
+    `APC Period 1`,
+    `APC Period 2`,
+    `APC Period 3`,
+    `APC Period 4`,
+    `AAPC`
+  ) %>% 
+  # Clean up name
+  mutate(stratifier = case_when(as.character(stratifier) == 'Poverty level' ~ 'Poverty income ratio',
+                                TRUE ~ as.character(stratifier))) %>% 
+  # Combine stratifier and strata names for table, then relevel factor for
+  # appropriate table order
+  mutate(` ` = case_when(stratifier == 'Overall' ~ 'Overall',
+                         TRUE ~ paste(stratifier, ` `, sep = ": ")),
+         ` ` = as.factor(` `) %>% fct_relevel('Overall',
+                           'Age: 18 to 44',
+                           'Age: 45 to 64',
+                           'Age: 65 to 74',
+                           'Age: 75+',
+                           'Sex: Female',
+                           'Sex: Male',
+                           'Race/Ethnicity: Asian/not Hispanic',
+                           'Race/Ethnicity: Black/not Hispanic',
+                           'Race/Ethnicity: Hispanic',
+                           'Race/Ethnicity: White/not Hispanic',
+                           'Highest degree earned: Greater than high school',
+                           'Highest degree earned: High school',
+                           'Highest degree earned: Less than high school',
+                           'Insurance coverage: Medicaid',
+                           'Insurance coverage: Medicare only',
+                           'Insurance coverage: Private only',
+                           'Insurance coverage: Uninsured',
+                           'Poverty income ratio: > 400%',
+                           'Poverty income ratio: 200%—399%',
+                           'Poverty income ratio: 100%—199%',
+                           'Poverty income ratio: < 100%')) %>% 
+  # Clean up APC values
+  mutate(`APC (95% CI)` = paste(`APC Period 1`, `APC Period 2`, `APC Period 3`, `APC Period 4`, sep = ", ") %>%
+           str_replace(., ", NA", "") %>%
+           str_replace(., ", NA", "") %>%
+           str_replace(., ", NA", "")) %>% 
+  # Rename some columns to add () info
+  rename(`2008 (SE)` = `2008`,
+         `2009 (SE)` = `2009`,
+         `2010 (SE)` = `2010`,
+         `2011 (SE)` = `2011`,
+         `2012 (SE)` = `2012`,
+         `2013 (SE)` = `2013`,
+         `2014 (SE)` = `2014`,
+         `2015 (SE)` = `2015`,
+         `2016 (SE)` = `2016`,
+         `2017 (SE)` = `2017`,
+         `2018 (SE)` = `2018`,
+         `2019 (SE)` = `2019`,
+         `2020 (SE)` = `2020`,
+         `APC Period 1 (95% CI)` = `APC Period 1`,
+         `APC Period 2 (95% CI)` = `APC Period 2`,
+         `APC Period 3 (95% CI)` = `APC Period 3`,
+         `APC Period 4 (95% CI)` = `APC Period 4`,
+         `AAPC (95% CI)` = `AAPC`)
+
+proportion_table_sans_2020 <- prop_tab_sans_2020 %>% 
+  ungroup() %>% 
+  filter(stratifier == 'Overall') %>% 
+  select(
+    `Preventive service`,
+    `Average (SE)`,
+    `2008 (SE)`,
+    `2009 (SE)`,
+    `2010 (SE)`,
+    `2011 (SE)`,
+    `2012 (SE)`,
+    `2013 (SE)`,
+    `2014 (SE)`,
+    `2015 (SE)`,
+    `2016 (SE)`,
+    `2017 (SE)`,
+    `2018 (SE)`,
+    `2019 (SE)`,
+    `2020 (SE)`,
+    `Percent Change (95% CI)`,
+    `Joinpoint Year`,
+    `APC (95% CI)`,
+    `AAPC (95% CI)`,
+    -starts_with('APC Period')
+  ) %>% 
+  gt() %>% 
+  sub_missing(missing_text = ' ') %>% 
+  tab_footnote(
+    footnote = "Values in these columns were estimated excluding data from 2020.",
+    locations = cells_column_labels(
+      columns = c(
+      `Average (SE)`,
+      `Percent Change (95% CI)`,
+      `APC (95% CI)`,
+      `AAPC (95% CI)`
+    ))
+  ) %>% 
+  tab_options(footnotes.marks = "*",
+              table.font.names = 'Times New Roman',
+              table.font.size = 12)
+# Reorganize insurance variables
+ # proportion_table_sans_2020$`_data` <- proportion_table_sans_2020$`_data`[c(1:84,
+ #                                                                            85, 88, 86, 87,
+ #                                                                            89, 92, 90, 91,
+ #                                                                            93, 96, 94, 95,
+ #                                                                            97, 100, 98, 99,
+ #                                                                            101, 104, 102, 103,
+ #                                                                            105, 108, 106, 107,
+ #                                                                            109:nrow(proportion_table_sans_2020$`_data`)), ]
+
+# prop_tab_sans_2020 <- proportion_table_sans_2020$`_data`
+proportion_table_sans_2020 %>%
+  gtsave('table1.docx')
+
+supplement_prop_tab <- prop_tab_sans_2020 %>% 
+  select(
+    ` `,
+    `Preventive service`,
+    `Average (SE)`,
+    `2008 (SE)`,
+    `2009 (SE)`,
+    `2010 (SE)`,
+    `2011 (SE)`,
+    `2012 (SE)`,
+    `2013 (SE)`,
+    `2014 (SE)`,
+    `2015 (SE)`,
+    `2016 (SE)`,
+    `2017 (SE)`,
+    `2018 (SE)`,
+    `2019 (SE)`,
+    `2020 (SE)`,
+    `Percent Change (95% CI)`,
+    `Joinpoint Year`,
+    `APC (95% CI)`,
+    `AAPC (95% CI)`,
+    -starts_with('APC Period')
+  ) %>% 
+  gt() %>% 
+  sub_missing(missing_text = ' ') %>% 
+  tab_footnote(
+    footnote = "Values in these columns were estimated excluding data from 2020.",
+    locations = cells_column_labels(
+      columns = c(
+      `Average (SE)`,
+      `Percent Change (95% CI)`,
+      `APC (95% CI)`,
+      `AAPC (95% CI)`
+    ))
+  ) %>% 
+  tab_options(footnotes.marks = "*",
+              table.font.names = 'Times New Roman',
+              table.font.size = 12)
+# 
+# prop_tab_sans_2020 <- rename(prop_tab_sans_2020, stratifier_column = ` `) %>% 
+#   janitor::clean_names()
+
+in_text_prop_tab_sans_2020 <- rename(prop_tab_sans_2020,
+                                     preventive_service = `Preventive service`,
+                                     stratifier_column = ` `,
+                                     apc_period_1_95_percent_ci = `APC Period 1 (95% CI)`,
+                                     apc_period_2_95_percent_ci = `APC Period 2 (95% CI)`,
+                                     apc_period_3_95_percent_ci = `APC Period 3 (95% CI)`,
+                                     apc_period_4_95_percent_ci = `APC Period 4 (95% CI)`,
+                                     aapc_95_percent_ci = `AAPC (95% CI)`)
+```
+
+```{r plots-sans-2020}
+set.seed(963458237)
+# Need this to grab 2020 data, I think
 stats_table_plot_dat <- jp_proportion_plot_data %>%
+  mutate(model = as.numeric(model)) %>% 
   filter(strata != 'Total') %>%
   filter(strata != 'Not available') %>% 
-  filter(strata != 'Other Race/Not Hispanic') %>% 
+  filter(strata != 'Other Race/not Hispanic') %>% 
+  filter(strata != 'Other') %>% 
   mutate(variable_text = case_when(variable == 'a1c' ~ 'Two or more A1C tests',
@@
                                    variable == 'DENT_all' ~ 'One or more dentist visits',
-                                   variable == 'eye-exam' ~ 'Eye exam with dilation',
-                                   variable == 'flu' ~ 'Received flu vaccine',
+                                   variable == 'eye-exam' ~ 'Dilated eye exam',
+                                   variable == 'flu' ~ 'Received influenza vaccine',
                                    variable == 'foot' ~ 'Foot examination'),
@@
       '> 400% ',
-      '200% - 399%',
-      '100% - 199%',
+      '200%—399%',
+      '100%—199%',
       '< 100%'
@@
   )
-test_plots <- stats_table_plot_dat %>% 
-   map(
-    ~ ggplot(filter(.x, variable %in% c('a1c', 'CHOL_all', 'flu')),
+# rest of the stuff
+stats_table_plot_dat_sans_2020 <- jp_proportion_plot_data_sans_2020 %>%
+  mutate(model = as.numeric(model)) %>% 
+  filter(strata != 'Total') %>%
+  filter(strata != 'Not available') %>% 
+  filter(strata != 'Other Race/not Hispanic') %>% 
+  filter(strata != 'Other') %>% 
+  mutate(variable_text = case_when(variable == 'a1c' ~ 'Two or more A1C tests',
+                                   variable == 'CHOL_all' ~ 'Cholesterol tested',
+                                   variable == 'DENT_all' ~ 'One or more dentist visits',
+                                   variable == 'eye-exam' ~ 'Dilated eye exam',
+                                   variable == 'flu' ~ 'Received influenza vaccine',
+                                   variable == 'foot' ~ 'Foot examination'),
+         strata = case_when(strata == 'Overall' ~ 'z',
+                            TRUE ~ strata)) %>% 
+  group_by(strata, variable) %>% 
+  mutate(strata = as.factor(strata),
+         significant_indicator = case_when(joinpoints == '0' & any(str_detect(apc, "[*]")) ~ TRUE,
+                                           joinpoints != '0' ~ TRUE,
+                                           TRUE ~ FALSE)) %>% 
+  ungroup() %>% 
+  split(., f = .$stratifier)
+
+stats_table_plot_dat_sans_2020 <- map(stats_table_plot_dat_sans_2020, function(.x) {
+  .x %>% 
+    mutate(strata = fct_drop(strata))
+})
+
+overall_data_sans_2020 <- stats_table_plot_dat_sans_2020$overall
+# Remove the overall data from the list
+stats_table_plot_dat_sans_2020 <- stats_table_plot_dat_sans_2020[-4]
+# Relevel the poverty factors
+stats_table_plot_dat_sans_2020$poverty$strata <-
+  factor(
+    stats_table_plot_dat_sans_2020$poverty$strata,
+    levels = c('Poor/Negative', 'Low income', 'Middle income', 'High income'), 
+    labels = c(
+      'd< 100%',
+      'c100%—199%',
+      'b200%—399%',
+      'a> 400% '
+    ),
+    ordered = TRUE
+  )
+# Set up color palette for up to 4 categories
+color_pal <- RColorBrewer::brewer.pal(n = 4, 'Set2')
+# Get the p for 2020 but remove the join point stuff so the line doesn't plot
+stats_table_2020_only <- stats_table_plot_dat %>% 
+  map(~filter(.x, year == 2020) %>% 
+        group_by(strata, variable) %>% 
+        mutate(model = NA,
+                significant_indicator = any(str_detect(apc, "[*]"))) %>% 
+        ungroup()
+  )
+stats_table_2020_only$poverty$strata <-
+  factor(
+    stats_table_2020_only$poverty$strata,
+    levels = c('< 100%',
+               '100%—199%',
+               '200%—399%',
+               '> 400% '), 
+    labels = c(
+      'd< 100%',
+      'c100%—199%',
+      'b200%—399%',
+      'a> 400% '
+    ),
+    ordered = TRUE
+  )
+legend_labels <- stats_table_plot_dat_sans_2020 %>% 
+  map(~.x %>% 
+        group_by(strata, variable) %>% 
+        summarise(sig_ind = mean(significant_indicator)) %>% 
+        ungroup()
+  )
+overall_legend <- overall_data_sans_2020 %>%
+  group_by(strata, variable) %>%
+  summarise(sig_ind = mean(significant_indicator)) %>%
+  ungroup()
+
+test_plots_sans_2020 <-
+  map2(
+    stats_table_plot_dat_sans_2020,
+    stats_table_2020_only,
+    ~ ggplot(
+      filter(.x, variable %in% c('a1c', 'CHOL_all', 'flu')),
       aes(
@@
         color = strata
+      )
+    ) +
+      geom_line(aes(
+        x = year,
+        y = model,
+        group = strata,
+        color = strata,
+        linetype = strata
       )) +
-      #geom_point() +
-      geom_line(aes(x = year, y = model, group = strata, color = strata)) +
-      geom_line(data = filter(overall_data, variable %in% c('a1c', 'CHOL_all', 'flu')),
-                  aes(x = year, y = model),
-                  color = 'black',
-                  linetype = 'dashed') +
-      facet_wrap( ~ variable_text, ncol = 3) +
-      theme_classic() +
-      scale_y_continuous(
-        limits = c(00, 100),
-        breaks = seq(0, 100, 25),
-        labels = seq(0, 100, 25)
-      ) +
-      scale_x_continuous(
-        limits = c(2008, 2020),
-        breaks = seq(2008, 2020, 2),
-        labels = seq(2008, 2020, 2)
-      ) +
-      scale_color_brewer(type = 'qual', palette = 'Set2') +
-      theme(axis.text = element_text(color = 'black'),
-            axis.text.x = element_text(angle = 45, hjust = 0.9, vjust = 0.95),
-            legend.title = element_text(size = 8),
-            legend.text = element_text(size = 6)) +
-      labs(x = 'Year', y = 'Percentage')
-  )
-
-test_plots[[1]] <- test_plots[[1]] + labs(color = 'Age (grouped)') +
-  theme(axis.title.x = element_blank())
-test_plots[[2]] <-
-  test_plots[[2]] + labs(color = 'Highest degree \nobtained') + theme(
-    strip.background =  element_blank(),
-    strip.text = element_blank(),
-    axis.title.x = element_blank()
-  )
-test_plots[[3]] <-
-  test_plots[[3]] + labs(color = "Insurance") + theme(
-    strip.background =  element_blank(),
-    strip.text = element_blank(),
-    axis.title.x = element_blank()
-  )
-test_plots[[4]] <-
-  test_plots[[4]] + labs(color = 'Poverty income ratio') + theme(
-    strip.background =  element_blank(),
-    strip.text = element_blank()
-  )
-test_plots[[5]] <-
-  test_plots[[5]] + labs(color = 'Race & Ethnicity') + theme(
-    strip.background =  element_blank(),
-    strip.text = element_blank(),
-    axis.title.x = element_blank()
-  )
-test_plots[[6]] <-
-  test_plots[[6]] + labs(color = 'Sex') + theme(strip.background =  element_blank(),
-                                                strip.text = element_blank(),
-    axis.title.x = element_blank())
-test_plots <- list(
-  test_plots[[1]],
-  test_plots[[6]],
-  test_plots[[5]],
-  test_plots[[2]],
-  test_plots[[3]],
-  test_plots[[4]]
-)
-
-exam_plots <- stats_table_plot_dat %>% 
-   map(
-    ~ ggplot(filter(.x, variable %!in% c('a1c', 'CHOL_all', 'flu')),
+      geom_line(
+        data = filter(
+          overall_data_sans_2020,
+          variable %in% c('a1c', 'CHOL_all', 'flu')
+        ),
+        aes(
+          x = year,
+          y = model,
+          color = strata,
+          linetype = strata
+        ),
+      ) +
+      geom_jitter(
+        data = filter(.y, variable %in% c('a1c', 'CHOL_all', 'flu')) ,
         aes(
@@
           color = strata
-    )) +
-      #geom_point() +
-      geom_line(aes(x = year, y = model, group = strata, color = strata)) +
-      geom_line(data = filter(overall_data, variable %!in% c('a1c', 'CHOL_all', 'flu')),
-                  aes(x = year, y = model),
-                  color = 'black',
-                  linetype = 'dashed') +
-      facet_wrap( ~ variable_text, ncol = 3) +
+        ),
+        inherit.aes = FALSE,
+        width = 0.22,
+        height = 0.005
+      ) +
+      geom_point(
+        data = filter(
+          overall_data,
+          variable %in% c('a1c', 'CHOL_all', 'flu'),
+          year == 2020
+        ),
+        aes(x = year, y = p, color = strata),
+        inherit.aes = FALSE
+      ) +
+      facet_wrap(~ variable_text, ncol = 3) +
       theme_classic() +
       scale_y_continuous(
-        limits = c(  0, 100),
+        limits = c(0, 100),
         breaks = seq(0, 100, 25),
@@
       scale_x_continuous(
-        limits = c(2008, 2020),
+        limits = c(2008, 2020.3),
         breaks = seq(2008, 2020, 2),
-        labels = seq(2008, 2020, 2)
-      ) +
-      scale_color_brewer(type = 'qual', palette = 'Set2') +
-      theme(axis.text = element_text(color = 'black'),
-            axis.text.x = element_text(angle = 45, hjust = 0.9, vjust = 0.95),
-            legend.title = element_text(size = 8),
-            legend.text = element_text(size = 6)) +
+        labels = c(2008, "", 2012, "", 2016, "", 2020)
+      ) +
+      theme(
+        axis.text = element_text(color = 'black'),
+        #axis.text.x = element_text(angle = 45, hjust = 0.9, vjust = 0.95),
+        legend.title = element_text(size = 11),
+        legend.text = element_text(size = 9)
+      ) +
       labs(x = 'Year', y = 'Percentage')
-  )
-
-exam_plots[[1]] <- exam_plots[[1]] + labs(color = 'Age (grouped)') +
-  theme(axis.title.x = element_blank())
-exam_plots[[2]] <-
-  exam_plots[[2]] + labs(color = 'Highest degree \nobtained') + theme(
+
+  )
+
+test_plots_sans_2020[[1]] <-
+  test_plots_sans_2020[[1]] +
+  theme(axis.title.x = element_blank()) +
+  scale_color_manual(
+    name = 'Age (grouped)',
+    values = c(
+     '18 to 44' = color_pal[1],
+     '45 to 64'  = color_pal[2],
+     '65 to 74' = color_pal[3],
+     '75+' = color_pal[4],
+     'z' = '#000000'
+    ),
+    labels = c('18 to 44' = '18 to 44ᵇ',
+               '45 to 64' = '45 to 64ᵃᵇᶜ',
+               '65 to 74' = '65 to 74ᶜ',
+               '75+'      = '75+ᶜ',
+               'z'        = 'Overallᵇ')
+  ) +
+  scale_linetype_manual(
+    name = 'Age (grouped)',
+    values = c(
+     '18 to 44' = 'solid',
+     '45 to 64'  = 'solid',
+     '65 to 74' = 'solid',
+     '75+' = 'solid',
+     'z' = 'dashed'
+    ),
+    labels = c('18 to 44' = '18 to 44ᵇ',
+               '45 to 64' = '45 to 64ᵃᵇᶜ',
+               '65 to 74' = '65 to 74ᶜ',
+               '75+'      = '75+ᶜ',
+               'z'        = 'Overallᵇ')
+  )
+
+test_plots_sans_2020[[2]] <-
+  test_plots_sans_2020[[2]] +
+  theme(
     strip.background =  element_blank(),
@@
     axis.title.x = element_blank()
-  )
-exam_plots[[3]] <-
-  exam_plots[[3]] + labs(color = "Insurance") + theme(
+  ) +
+  scale_color_manual(
+    name = 'Highest degree obtained',
+    labels = c('Greater than HS'       = 'Greater than HS',
+               'High school'           = 'High school',
+               'Less than high school' = 'Less than HSᵃ',
+               'z'                     = 'Overallᵇ'),
+    values = c(
+     'Greater than HS' = color_pal[1],
+     'High school' = color_pal[2],
+     'Less than high school'  = color_pal[3],
+     'z' = '#000000'
+    )
+  ) +
+  scale_linetype_manual(
+    name = 'Highest degree obtained',
+    labels = c('Greater than HS'       = 'Greater than HS',
+               'High school'           = 'High school',
+               'Less than high school' = 'Less than HSᵃ',
+               'z'                     = 'Overallᵇ'),
+    values = c(
+     'Greater than HS' = 'solid',
+     'High school' = 'solid',
+     'Less than high school'  = 'solid',
+     'z' = 'dashed'
+    )
+  )
+
+test_plots_sans_2020[[3]] <-
+  test_plots_sans_2020[[3]] +
+  theme(
     strip.background =  element_blank(),
@@
     axis.title.x = element_blank()
-  )
-exam_plots[[4]] <-
-  exam_plots[[4]] + labs(color = 'Poverty income ratio') + theme(
-    strip.background =  element_blank(),
-    strip.text = element_blank()
-  )
-exam_plots[[5]] <-
-  exam_plots[[5]] + labs(color = 'Race & Ethnicity') + theme(
+  ) +
+  scale_color_manual(
+    name = 'Insurance',
+    values = c(
+      'Medicaid' = color_pal[1],
+      'Medicare only' = color_pal[2],
+      'Private only' = color_pal[3],
+      'Uninsured' = color_pal[4],
+      'z' = '#000000'
+    ),   labels = c(
+      'Medicaid'      = 'Medicaidᵃ',
+      'Medicare only' = 'Medicare onlyᵇᶜ',
+      'Private only'  = 'Private onlyᵇ',
+      'Uninsured'     = 'Uninsured',
+      'z'             = 'Overallᵇ'
+    )
+  ) +
+  scale_linetype_manual(
+    name = 'Insurance',
+    values = c(
+      'Medicaid' = 'solid',
+      'Medicare only' = 'solid',
+      'Private only' = 'solid',
+      'Uninsured' = 'solid',
+      'z' = 'dashed'
+    ),
+        labels = c(
+      'Medicaid'      = 'Medicaidᵃ',
+      'Medicare only' = 'Medicare onlyᵇᶜ',
+      'Private only'  = 'Private onlyᵇ',
+      'Uninsured'     = 'Uninsured',
+      'z'             = 'Overallᵇ'
+    )
+  )
+
+test_plots_sans_2020[[4]] <-
+  test_plots_sans_2020[[4]] +
+  theme(strip.background =  element_blank(),
+        strip.text = element_blank()) +
+  scale_color_manual(
+    name = 'Poverty income ratio',
+    labels = c('a> 400% '     = '> 400%ᵇᶜ',
+               'b200%—399%' = '200%—399%ᵇ',
+               'c100%—199%' = '100%—199%ᵃ',
+               'd< 100%'      = '< 100%',
+               'z'           = 'Overallᵇ'),
+
+    values = c(
+      'a> 400% ' = color_pal[1],
+      'b200%—399%' = color_pal[2],
+      'c100%—199%' = color_pal[3],
+      'd< 100%' = color_pal[4],
+      'z' = '#000000'
+    )
+  ) +
+  scale_linetype_manual(
+    name = 'Poverty income ratio',
+    labels = c('a> 400% '     = '> 400%ᵇᶜ',
+               'b200%—399%' = '200%—399%ᵇ',
+               'c100%—199%' = '100%—199%ᵃ',
+               'd< 100%'      = '< 100%',
+               'z'           = 'Overallᵇ'),
+    values = c(
+      'a> 400% ' = 'solid',
+      'b200%—399%' = 'solid',
+      'c100%—199%' = 'solid',
+      'd< 100%' = 'solid',
+      'z' = 'dashed'
+    )
+  ) + 
+ labs(caption = "ᵃ p < 0.05 for cholesterol tested \nᵇ p < 0.05 for received influenza vaccine \nᶜ p < 0.05 for A1C tests")
+
+test_plots_sans_2020[[5]] <-
+  test_plots_sans_2020[[5]] + theme(
     strip.background =  element_blank(),
@@
     axis.title.x = element_blank()
-  )
-exam_plots[[6]] <-
-  exam_plots[[6]] + labs(color = 'Sex') + theme(strip.background =  element_blank(),
+  ) +
+  scale_color_manual(
+    name = 'Race & Ethnicity',
+    labels = c(
+     'Asian/not Hispanic' = 'Asian/not Hispanicᵇ',
+     'Black/not Hispanic' = 'Black/not Hispanic',
+     'Hispanic'           = 'Hispanicᶜ',
+     'White/not Hispanic' = 'White/not Hispanicᵇᶜ',
+     'z'                  = 'Overallᵇ'
+    ),
+    values = c(
+     'Asian/not Hispanic' = color_pal[1],
+     'Black/not Hispanic'  = color_pal[2],
+     'Hispanic' = color_pal[3],
+     'White/not Hispanic' = color_pal[4],
+     'z' = '#000000'
+    )
+  ) +
+  scale_linetype_manual(
+    name = 'Race & Ethnicity',
+    labels = c(
+     'Asian/not Hispanic' = 'Asian/not Hispanicᵇ',
+     'Black/not Hispanic' = 'Black/not Hispanic',
+     'Hispanic'           = 'Hispanicᶜ',
+     'White/not Hispanic' = 'White/not Hispanicᵇᶜ',
+     'z'                  = 'Overallᵇ'
+    ),
+    values = c(
+     'Asian/not Hispanic' = 'solid',
+     'Black/not Hispanic'  = 'solid',
+     'Hispanic' = 'solid',
+     'White/not Hispanic' = 'solid',
+     'z' = 'dashed'
+    )
+  )
+test_plots_sans_2020[[6]] <-
+  test_plots_sans_2020[[6]] +
+  theme(
+    strip.background =  element_blank(),
     strip.text = element_blank(),
-    axis.title.x = element_blank())
-exam_plots <- list(
-  exam_plots[[1]],
-  exam_plots[[6]],
-  exam_plots[[5]],
-  exam_plots[[2]],
-  exam_plots[[3]],
-  exam_plots[[4]]
-)
-
-all_exam_plots <- exam_plots %>% 
-  wrap_plots(nrow = 6) &
-  theme(plot.margin = margin(0.5, 0.5, 0.5, 0.5, 'pt'))
-all_test_plots <- test_plots %>% 
-  wrap_plots(nrow = 6) &
-  theme(plot.margin = margin(0.5, 0.5, 0.5, 0.5, 'pt'))
-```
-
-```{r}
-#| include: false
-# Save figure/table output
-preventive_practice_table %>%
-  gtsave('preventive_practices.docx')
-ggsave(plot = all_exam_plots,
-       filename = 'figures/all_exam_plots.tiff',
-       dpi = 200,
-       width = 10,
-       height = 6)
-ggsave(plot = all_test_plots,
-       filename = 'figures/all_test_plots.tiff',
-       dpi = 200,
-       width = 10,
-       height = 6)
-ggsave(plot = all_exam_plots,
-       filename = 'figures/all_exam_plots.svg',
-       dpi = 200,
-       width = 10,
-       height = 6)
-ggsave(plot = all_test_plots,
-       filename = 'figures/all_test_plots.svg',
-       dpi = 200,
-       width = 10,
-       height = 6)
-```
-**Trends in Preventive Care Practices among US Adults with Diabetes, 2008-2020**
-
-Jacob T. Wittman, PhD, Kai M. Bullard, MPH, PHD, PhD Stephen R. Benoit, MD, MPH
-
-CDC Affiliation
-
-\pagebreak
-
-# Abstract
-
-\pagebreak
-
-# Introduction
-
-Intro -- peak incidence in 2008/2009, increasing rates of some major complications + projections of diabetes numbers; previous reports of preventive care practices
-
-Diabetes is a chronic disease that affects XX people in the USA.
-
-# Methods
-
-## Data Source
-
-We used data from the Medical Expenditure Panel Survey (MEPS) from the years 2008 - 2020 to evaluate trends in preventive care practices in adults 18 years or older with diabetes in the USA.
-Participants in this survey are a subsample of households that participate in the National Health Interview Survey (NHIS).
-The MEP survey targets the civilian noninstitutionalized population in the US and provides national and regional estimates of health care use, expenditures, sources of payment and health insurance coverage.
-This survey also contains information on patient demographics, socioeconomic, and, via the Diabetes Care Survey (DCS), information on diabetes preventive care practices.
-The DCS is a self-administered paper-and-pencil questionnaire that is provided to MEPS respondents who indicate that they have been told by a doctor or health professional that they have diabetes.
-The data we used comes from the full-year consolidated file from MEPS for the 12 year time span of our report.
-
-## Outcomes
-
-We selected six outcome variables that were readily available in the data from 2008 - 2020 and that are based on American Diabetes Association annual care recommendations.
-These six recommendations include at least one dental examination, an eye examination that includes dilation, a foot examination, at least two A1C tests, a cholesterol test, and the receipt of a flu vaccine.
-The number of total dentist visits in a year is available in the MEPS data and was used to determine which adults had one or more dentist visits in a year.
-Respondents were also asked if they had an eye examination, a foot examination, a flu vaccine, or a cholesterol test in a given year of the survey.
-The number of A1C tests received by a respondent was recorded and we grouped respondents into those that had two or more A1C tests in a year and those that had less than two.
-Using the binary outcomes for each of these six measures, we further classified adults as having received at least three of those recommended care practices and those that received less than three of these practices.
-
-## Analysis
-
-Our analysis is adjusted for the complex survey design used, including clustering and stratification.
-Reported values for the percentages of the population receiving recommended preventive care practices are direct age-adjusted estimates.
-These estimates are presented for the overall population, as well as stratified by age, sex, race and ethnicity, highest degree of education obtained, type of insurance, and the ratio of income to poverty line.
-
-We used R Statistical Software (v4.2.1) @rcore2022 to perform all analyses.
-The package gtsummary was used to account for the complex survey design and age-adjust estimates @gtsummary.
-Trends in preventive care practices were analyzed using Joinpoint Command Line Software @joinpoint with R via the R package nih.joinpoint @nihjoinpoint.
-Joinpoint regression uses permutation tests to detect statistically significant changes at a pre-specified alpha of 0.05 in direction and/or magnitude of trends @kim2000permutation.
-The Joinpoint software also provided estimates of the annual percent change (APC) for each trend segment and the average annual percent change (AAPC) for the entire trend.
-
-# Results
-
-For the entire population of adults diagnosed with diabetes in the USA there was a significant decrease of `r pullNumber(tab1, '-', 'Percent Change (95% CI)')` in the percentage of people receiving at least three of the recommended practices from 2008 to 2020 (Table 1).
-(Table 1).
-The largest decreases in the percentage of adults receiving at least three preventive care practices were seen in those with no high school diploma (`r pullNumber(tab1, 'Less than high school', 'Percent Change (95% CI)')`%), Asian/Not Hispanic (`r pullNumber(tab1, 'Asian/Not Hispanic', 'Percent Change (95% CI)')`%), the uninsured (`r pullNumber(tab1, 'Uninsured', 'Percent Change (95% CI)')`%), and those with an income to poverty line ratio between 100% and 199% (`r pullNumber(tab1, '100% - 199%', 'Percent Change (95% CI)')`%) (Table 1).
-
-While the percent change and AAPC for nearly all groups were negative, some groups had APC values that were initially flat (i.e.
-the 95% CI overlapped 0) in the first period but became negative in the second period (Table 1).
-The year in which Joinpoint regression identified statistically significant changes in the slope of the trend ranged from 2010 - 2015 (Table 1).
-Only adults in the highest poverty to income ratio category (\>400%) had an initial APC that was positive at `r pullNumber(tab1, '> 400%', 'APC Period 1 (95% CI)')`% (Table 1).
-
-Overall trends in each of the individual preventive practices decreased from 2008 to 2020, with the exception of the percentage of people receiving two or more A1C tests in one year, which increased from `r sigfig(overall_data$age_adjusted_prop[1] * 100, digits = 3)`% to `r sigfig(overall_data$age_adjusted_prop[13] * 100, digits = 3)`% (@fig-exams & @fig-tests).
-Trends in the percentages of people getting an eye exam with dilation and one or more dentist visits tended to be close to flat or decreasing, with a few exceptions where percentages first increased until the mid 2010s and then began to decrease (e.g., see the eye exam graph for the poverty income ratio stratifier and dentist visits for race and ethnicity stratifier, @fig-exams).
-The overall trend for foot exams initially increased and then started to decrease in 2012, and many of the stratifier-specific groups follow a similar trend (@fig-exams).
-The trend overall and among our stratifying variables for cholesterol testing and receiving a flu vaccine also generally follow the trend of increasing until between 2013 - 2015, where they begin to decrease, although a few specific stratifying groups only decrease over the examined time period (@fig-tests).
-The percentage of the population receiving two or more A1C tests in a year only increased overall and for all groups (@fig-tests).
-
-# Discussion
-
-Discussion -- ACA and recovery from Great Recession as context for increasing trends after 2008 until 2016 (then what happened?); compare to BRFSS state estimates; impact of COVID on receipt of PCP; speculation about future burden of complications due to suboptimal preventive care
-
-BRFSS estimates
-- Median state eye exam is roughly flat - individual states bounce all over
-- Median foot exam is flat/maybe increasing? 
-- Median state A1c tests - also flattish/maybe increasing? hard to say
-- Median state flu vaccine - bounces around a bit more.
-Overall line would probably be flat though?
-Nationally though the estimate is pretty clearly increasing overall and for all available stratifiers
-- No cholesterol or dentist info from BRFSS? Not on dashboard anyway.
-
-Limitations -- cross-sectional, self-report only, declining response rate
-
-# References
-
-::: {#refs}
-:::
-
-\pagebreak
-
-# Tables
-
-```{r}
-#| label: tbl-prev
-#| tbl-cap: Age-adjusted trends in proportions of US adults with diabetes that report receiving at least three of six recommended care practices - at least one dental visit, one eye exam with dilation, one foot exam, two or more A1C tests, cholesterol level tested, and receiving a flu vaccine.
-
-preventive_practice_table
-```
-
-\pagebreak
-
-::: landscape
-# Figures
-
-```{r}
-#| label: fig-exams
-#| fig-cap: Age-adjusted trends in proportions of US adults with diabetes who reported receiving recommended medical examinations. The dashed black line is the overall trend.
-#| fig-width: 8
-
-all_exam_plots
-```
-
-\pagebreak
-
-```{r}
-#| label: fig-tests
-#| fig-cap: Age-adjusted trends in proportions of US adults with diabetes who reported receiving recommended lab tests and vaccinations. The dashed black line is the overall trend. 
-#| fig-width: 10
-
-all_test_plots
-```
-:::
-
-## Alternative figure options
-
-```{r}
-test_plots1 <- stats_table_plot_dat %>% 
-   map(
-    ~ ggplot(filter(.x, variable %in% c('a1c', 'CHOL_all')),
+    axis.title.x = element_blank()
+  ) +
+  scale_color_manual(
+    name = 'Sex',
+    labels = c('Female'  = 'Femaleᵇ',
+               'Male'    = 'Maleᵃᵇ',
+               'z' = 'Overallᵇ'),
+    values = c(
+     'Female' = color_pal[1],
+     'Male'  = color_pal[2],
+     'z' = '#000000'
+    )
+  ) +
+  scale_linetype_manual(
+    name = 'Sex',
+    labels = c('Female'  = 'Femaleᵇ',
+               'Male'    = 'Maleᵃᵇ',
+               'z' = 'Overallᵇ'),
+        values = c(
+     'Female' = 'solid',
+     'Male'  = 'solid',
+     'z' = 'dashed'
+    )
+  )
+test_plots_sans_2020 <- list(
+  test_plots_sans_2020[[1]],
+  test_plots_sans_2020[[6]],
+  test_plots_sans_2020[[5]],
+  test_plots_sans_2020[[2]],
+  test_plots_sans_2020[[3]],
+  test_plots_sans_2020[[4]]
+)
+
+exam_plots_sans_2020 <-
+  map2(
+    stats_table_plot_dat_sans_2020,
+    stats_table_2020_only,
+    ~ ggplot(
+      filter(.x, variable %!in% c('a1c', 'CHOL_all', 'flu')),
       aes(
@@
         color = strata
+      )
+    ) +
+      geom_line(aes(
+        x = year,
+        y = model,
+        group = strata,
+        color = strata,
+        linetype = strata
       )) +
-      #geom_point() +
-      geom_line(aes(x = year, y = model, group = strata, color = strata)) +
-      geom_line(data = filter(overall_data, variable %in% c('a1c', 'CHOL_all')),
-                  aes(x = year, y = model),
-                  color = 'black',
-                  linetype = 'dashed') +
-      facet_wrap( ~ variable_text, ncol = 3) +
-      theme_classic() +
-      scale_y_continuous(
-        limits = c(00, 100),
-        breaks = seq(0, 100, 25),
-        labels = seq(0, 100, 25)
-      ) +
-      scale_x_continuous(
-        limits = c(2008, 2020),
-        breaks = seq(2008, 2020, 2),
-        labels = seq(2008, 2020, 2)
-      ) +
-      scale_color_brewer(type = 'qual', palette = 'Set2') +
-      theme(axis.text = element_text(color = 'black'),
-            axis.text.x = element_text(angle = 45, hjust = 0.9, vjust = 0.95),
-            legend.title = element_text(size = 8),
-            legend.text = element_text(size = 6)) +
-      labs(x = 'Year', y = 'Percentage')
-  )
-
-test_plots1[[1]] <- test_plots1[[1]] + labs(color = 'Age (grouped)') +
-  theme(axis.title.x = element_blank())
-test_plots1[[2]] <-
-  test_plots1[[2]] + labs(color = 'Highest degree \nobtained') + theme(
-    strip.background =  element_blank(),
-    strip.text = element_blank(),
-    axis.title.x = element_blank()
-  )
-test_plots1[[3]] <-
-  test_plots1[[3]] + labs(color = "Insurance") + theme(
-    strip.background =  element_blank(),
-    strip.text = element_blank(),
-    axis.title.x = element_blank()
-  )
-test_plots1[[4]] <-
-  test_plots1[[4]] + labs(color = 'Poverty income ratio') + theme(
-    strip.background =  element_blank(),
-    strip.text = element_blank()
-  )
-test_plots1[[5]] <-
-  test_plots1[[5]] + labs(color = 'Race & Ethnicity') + theme(
-    strip.background =  element_blank(),
-    strip.text = element_blank(),
-    axis.title.x = element_blank()
-  )
-test_plots1[[6]] <-
-  test_plots1[[6]] + labs(color = 'Sex') + theme(strip.background =  element_blank(),
-                                                strip.text = element_blank(),
-    axis.title.x = element_blank())
-test_plots1 <- list(
-  test_plots1[[1]],
-  test_plots1[[6]],
-  test_plots1[[5]],
-  test_plots1[[2]],
-  test_plots1[[3]],
-  test_plots1[[4]]
-)
-
-test_plots2 <- stats_table_plot_dat %>% 
-   map(
-    ~ ggplot(filter(.x, variable %in% c('foot', 'flu')),
+      geom_line(
+        data = filter(
+          overall_data_sans_2020,
+          variable %!in% c('a1c', 'CHOL_all', 'flu')
+        ),
+        aes(x = year, y = model, color = strata, linetype = strata),
+      ) +
+      geom_jitter(
+        data = filter(.y, variable %!in% c('a1c', 'CHOL_all', 'flu')) ,
         aes(
@@
           color = strata
-    )) +
-      #geom_point() +
-      geom_line(aes(x = year, y = model , group = strata, color = strata)) +
-      geom_line(data = filter(overall_data, variable %in% c('foot', 'flu')),
-                  aes(x = year, y = model ),
-                  color = 'black',
-                  linetype = 'dashed') +
-      facet_wrap( ~ variable_text, ncol = 3) +
+        ),
+        inherit.aes = FALSE,
+        width = 0.22,
+        height = 0.005
+      ) +
+      geom_point(
+        data = filter(
+          overall_data,
+          variable %!in% c('a1c', 'CHOL_all', 'flu'),
+          year == 2020
+        ),
+        aes(x = year, y = p, color = strata),
+        #color = 'black',
+        inherit.aes = FALSE
+      ) +
+      facet_wrap(~ variable_text, ncol = 3) +
       theme_classic() +
       scale_y_continuous(
-        limits = c(00, 100),
+        limits = c(0, 100),
         breaks = seq(0, 100, 25),
@@
       scale_x_continuous(
-        limits = c(2008, 2020),
+        limits = c(2008, 2020.3),
         breaks = seq(2008, 2020, 2),
-        labels = seq(2008, 2020, 2)
-      ) +
-      scale_color_brewer(type = 'qual', palette = 'Set2') +
-      theme(axis.text = element_text(color = 'black'),
-            axis.text.x = element_text(angle = 45, hjust = 0.9, vjust = 0.95),
-            legend.title = element_text(size = 8),
-            legend.text = element_text(size = 6)) +
+        labels = c(2008, "", 2012, "", 2016, "", 2020)
+      ) +
+      theme(
+        axis.text = element_text(color = 'black'),
+        #axis.text.x = element_text(angle = 45, hjust = 0.9, vjust = 0.95),
+        legend.title = element_text(size = 11),
+        legend.text = element_text(size = 9)
+      ) +
       labs(x = 'Year', y = 'Percentage')
@@
 
-test_plots2[[1]] <- test_plots2[[1]] + labs(color = 'Age (grouped)') +
-  theme(axis.title.x = element_blank())
-test_plots2[[2]] <-
-  test_plots2[[2]] + labs(color = 'Highest degree \nobtained') + theme(
+# Set up legends on all plots
+exam_plots_sans_2020[[1]] <- exam_plots_sans_2020[[1]] +
+  theme(axis.title.x = element_blank()) +
+  scale_color_manual(
+    name = 'Age (grouped)',
+    labels = c('18 to 44' = '18 to 44',
+               '45 to 64' = '45 to 64',
+               '65 to 74' = '65 to 74ᵇᶜ',
+               '75+'      = '75+ᶜ',
+               'z'        = 'Overallᵇ'),
+    values =   c(
+      '18 to 44' = color_pal[1],
+      '45 to 64' = color_pal[2],
+      '65 to 74' = color_pal[3],
+      '75+'      = color_pal[4],
+      'z'        = '#000000'
+    )
+  ) +
+  scale_linetype_manual(
+    name = 'Age (grouped)',
+    labels = c('18 to 44' = '18 to 44',
+               '45 to 64' = '45 to 64',
+               '65 to 74' = '65 to 74ᵇᶜ',
+               '75+'      = '75+ᶜ',
+               'z'        = 'Overallᵇ'),
+    values = c(
+      '18 to 44' = 'solid',
+      '45 to 64'  = 'solid',
+      '65 to 74' = 'solid',
+      '75+' = 'solid',
+      'z' = 'dashed'
+    )
+  )
+
+exam_plots_sans_2020[[2]] <-
+  exam_plots_sans_2020[[2]] +
+  theme(
     strip.background =  element_blank(),
@@
     axis.title.x = element_blank()
-  )
-test_plots2[[3]] <-
-  test_plots2[[3]] + labs(color = "Insurance") + theme(
+  ) +
+  scale_color_manual(
+    name = 'Highest degree obtained',
+    labels = c('Greater than HS'       = 'Greater than HS',
+               'High school'           = 'High schoolᶜ',
+               'Less than high school' = 'Less than HS',
+               'z'                     = 'Overallᵇ'),
+        values = c(
+      'Greater than HS'       = color_pal[1],
+      'High school'           = color_pal[2],
+      'Less than high school' = color_pal[3],
+      'z'                     = '#000000'
+    )
+  ) +
+    scale_linetype_manual(
+      name = 'Highest degree obtained',
+    labels = c('Greater than HS'       = 'Greater than HS',
+               'High school'           = 'High schoolᶜ',
+               'Less than high school' = 'Less than HS',
+               'z'                     = 'Overallᵇ'),
+    values = c(
+      'Greater than HS' = 'solid',
+      'High school' = 'solid',
+      'Less than high school'  = 'solid',
+      'z' = 'dashed'
+    )
+  )
+
+exam_plots_sans_2020[[3]] <-
+  exam_plots_sans_2020[[3]] +
+  theme(
     strip.background =  element_blank(),
@@
     axis.title.x = element_blank()
-  )
-test_plots2[[4]] <-
-  test_plots2[[4]] + labs(color = 'Poverty income ratio') + theme(
-    strip.background =  element_blank(),
-    strip.text = element_blank()
-  )
-test_plots2[[5]] <-
-  test_plots2[[5]] + labs(color = 'Race & Ethnicity') + theme(
+  ) +
+  scale_color_manual(
+    name = 'Insurance',
+    labels = c(
+     'Medicaid'      =  'Medicaid',
+     'Medicare only' =  'Medicare only',
+     'Private only'  =  'Private onlyᶜ',
+     'Uninsured'     =  'Uninsuredᵃᶜ',
+     'z'             =  'Overallᵇ'
+    ),
+    values = c(
+      'Medicaid'      = color_pal[1],
+      'Medicare only' = color_pal[2],
+      'Private only'  = color_pal[3],
+      'Uninsured'     = color_pal[4],
+      'z'             = '#000000'
+    )
+  ) +
+  scale_linetype_manual(
+    name = 'Insurance',
+    labels =  c(
+     'Medicaid'      =  'Medicaid',
+     'Medicare only' =  'Medicare only',
+     'Private only'  =  'Private onlyᶜ',
+     'Uninsured'     =  'Uninsuredᵃᶜ',
+     'z'             =  'Overallᵇ'
+    ),
+    values = c(
+      'Medicaid' = 'solid',
+      'Medicare only' = 'solid',
+      'Private only' = 'solid',
+      'Uninsured' = 'solid',
+      'z' = 'dashed'
+    )
+  )
+
+exam_plots_sans_2020[[4]] <-
+  exam_plots_sans_2020[[4]] +
+  theme(strip.background =  element_blank(),
+        strip.text = element_blank()) +
+  scale_color_manual(
+    name = 'Poverty income ratio',
+    labels = c('a> 400% '     = '> 400%ᵃ',
+               'b200%—399%' = '200%—399%',
+               'c100%—199%' = '100%—199%',
+               'd< 100%'      = '< 100%ᶜ',
+               'z'           = 'Overallᵇ'),
+    values = c(
+      'a> 400% '     = color_pal[1],
+      'b200%—399%' = color_pal[2],
+      'c100%—199%' = color_pal[3],
+      'd< 100%'      = color_pal[4],
+      'z'           = '#000000'
+    )
+  ) +
+  scale_linetype_manual(
+    name = 'Poverty income ratio',
+    labels = c('a> 400% '     = '> 400%ᵃ',
+               'b200%—399%' = '200%—399%',
+               'c100%—199%' = '100%—199%',
+               'd< 100%'      = '< 100%ᶜ',
+               'z'           = 'Overallᵇ'),
+    values = c(
+      'a> 400% ' = 'solid',
+      'b200%—399%' = 'solid',
+      'c100%—199%' = 'solid',
+      'd< 100%' = 'solid',
+      'z' = 'dashed'
+    )
+  ) +
+  labs(caption = "ᵃ p < 0.05 for eye-exam \nᵇ p < 0.05 for foot exam \nᶜ p < 0.05 for dentist visit")
+
+exam_plots_sans_2020[[5]] <-
+  exam_plots_sans_2020[[5]] +
+  theme(
     strip.background =  element_blank(),
@@
     axis.title.x = element_blank()
-  )
-test_plots2[[6]] <-
-  test_plots2[[6]] + labs(color = 'Sex') + theme(strip.background =  element_blank(),
+  ) +
+  scale_color_manual(
+    name = 'Race & Ethnicity',
+    labels = c(
+      'Asian/not Hispanic' = 'Asian/not Hispanic',
+      'Black/not Hispanic' = 'Black/not Hispanic',
+      'Hispanic'           = 'Hispanic',
+      'White/not Hispanic' = 'White/not Hispanicᶜ',
+      'z'                  = 'Overallᵇ'
+    ),
+    values = c(
+      'Asian/not Hispanic' = color_pal[1],
+      'Black/not Hispanic' = color_pal[2],
+      'Hispanic'           = color_pal[3],
+      'White/not Hispanic' = color_pal[4],
+      'z'                  = '#000000'
+    )
+  ) +
+  scale_linetype_manual(
+    name = 'Race & Ethnicity',
+        labels = c(
+       'Asian/not Hispanic' = 'Asian/not Hispanic',
+       'Black/not Hispanic' = 'Black/not Hispanic',
+       'Hispanic'           = 'Hispanic',
+       'White/not Hispanic' = 'White/not Hispanicᶜ',
+       'z'                  = 'Overallᵇ'
+    ),
+    values = c(
+      'Asian/not Hispanic' = 'solid',
+      'Black/not Hispanic'  = 'solid',
+      'Hispanic' = 'solid',
+      'White/not Hispanic' = 'solid',
+      'z' = 'dashed'
+    )
+  )
+
+exam_plots_sans_2020[[6]] <-
+  exam_plots_sans_2020[[6]] +
+  theme(
+    strip.background =  element_blank(),
     strip.text = element_blank(),
-    axis.title.x = element_blank())
-test_plots2 <- list(
-  test_plots2[[1]],
-  test_plots2[[6]],
-  test_plots2[[5]],
-  test_plots2[[2]],
-  test_plots2[[3]],
-  test_plots2[[4]]
-)
-
-exam_plots1 <- stats_table_plot_dat %>% 
+    axis.title.x = element_blank()
+  ) +
+  scale_color_manual(
+    name = 'Sex',
+    labels = c('Female'  = 'Female',
+               'Male'    = 'Maleᵃ',
+               'z' = 'Overallᵇ'),
+    values = c(
+      'Female' = color_pal[1],
+      'Male'  = color_pal[2],
+      'z' = '#000000'
+    )
+  ) +
+  scale_linetype_manual(
+    name = 'Sex',
+    labels = c('Female' = 'Female',
+               'Male' = 'Maleᵃ',
+               'z' = 'Overallᵇ'),
+    values = c(
+      'Female' = 'solid',
+      'Male'  = 'solid',
+      'z' = 'dashed'
+    )
+  )
+
+exam_plots_sans_2020 <- list(
+  exam_plots_sans_2020[[1]],
+  exam_plots_sans_2020[[6]],
+  exam_plots_sans_2020[[5]],
+  exam_plots_sans_2020[[2]],
+  exam_plots_sans_2020[[3]],
+  exam_plots_sans_2020[[4]]
+)
+
+all_exam_plots_sans_2020 <- exam_plots_sans_2020 %>% 
+  wrap_plots(nrow = 6) &
+  theme(plot.margin = margin(0.5, 0.5, 0.5, 0.5, 'pt'),
+        legend.justification = 'left',
+        plot.caption = element_text(hjust = 0)) &
+  guides(color = guide_legend(ncol = 2)) 
+all_test_plots_sans_2020 <- test_plots_sans_2020 %>% 
+  wrap_plots(nrow = 6) &
+  theme(plot.margin = margin(0.5, 0.5, 0.5, 0.5, 'pt'),
+        legend.justification = 'left',
+         plot.caption = element_text(hjust = 0)) &
+  guides(color = guide_legend(ncol = 2))
+```
+
+```{r}
+#| include: false
+# Save figure/table output
+supplement_prop_tab %>% 
+  tab_header('Age-adjusted trends in proportions of U.S.
+adults overall and by subgroup with diabetes that report receiving six recommended care services - at least one dental visit, one dilated eye exam, one foot exam, two or more A1C tests, cholesterol level tested, and receiving an influenza vaccine.') %>%
+  gtsave('supplemental_table1.docx')
+preventive_service_table %>%
+  gtsave('preventive_services.docx')
+preventive_service_table_sans_2020 %>%
+  gtsave('preventive_services_2020.docx')
+ggsave(plot = all_exam_plots_sans_2020,
+       filename = 'figures/figure1.tiff',
+       dpi = 1200,
+       width = 10,
+       height = 6)
+ggsave(plot = all_test_plots_sans_2020,
+       filename = 'figures/figure2.tiff',
+       dpi = 1200,
+       width = 10,
+       height = 6)
+# ggsave(plot = all_exam_plots,
+#        filename = 'figures/all_exam_plots.svg',
+#        dpi = 200,
+#        width = 10,
+#        height = 6)
+# ggsave(plot = all_test_plots,
+#        filename = 'figures/all_test_plots.svg',
+#        dpi = 200,
+#        width = 10,
+#        height = 6)
+```
+
+*Target Journal: Diabetes Care*
+
+**Trends in Preventive Care Services among U.S. Adults with Diagnosed Diabetes, 2008--2020**
+
+Running Title: Trends in preventive care services for diabetes
+
+Jacob T. Wittman, PhD, Kai McKeever Bullard, PhD, Stephen R. Benoit, MD
+
+Division of Diabetes Translation, Centers for Disease Control and Prevention, Atlanta, GA, United States
+
+Corresponding Author: Jacob T. Wittman, ugv4\@cdc.gov
+
+Disclaimer: The findings and conclusions in this report are those of the authors and do not necessarily represent the official position of the Centers for Disease Control and Prevention.
+
+Twitter Summary: We report trends of six ADA recommended preventive care services 2008 –- 2020.
+Other than flu vaccination, we saw no improvement in receipt of preventive care services for US adults with diabetes.
+
+Word Count:
+
+Number of tables and figures: 3
+
+\pagebreak
+
+# Abstract (250 words, current 250)
+
+**Objective:** Preventive care services are important to prevent or delay complications associated with diabetes.
+We reported trends in receipt of six American Diabetes Association recommended preventive care services during 2008 -- 2020.
+
+**Research Design and Methods:** We used 2008--2020 data from the cross-sectional Medical Expenditures Panel Survey to calculate the proportion of U.S.
+adults ≥ 18 years of age with diagnosed diabetes that reported receiving preventive care services, overall and for subpopulations.
+We used Joinpoint regression to identify trends during 2008 -- 2019.
+The six services in the past year included at least one dental examination, a dilated eye examination, foot examination, ≥ 2 A1C tests, a cholesterol test, and receipt of an influenza vaccine.
+
+**Results:** From 2008--2020, proportions of U.S.
+adults with diabetes receiving any individual preventive care service ranged from 32.6% to 89.9%.
+From 2008--2019, overall trends in preventive services among these adults were stable except for an increase in receipt of influenza vaccines (average annual percent change: `r pullNumber2(in_text_prop_tab_sans_2020, 'aapc_95_percent_ci', brackets = TRUE, CI = FALSE, stratifier_column == 'Overall', preventive_service == 'Received influenza vaccine')`).
+Trend analysis at the subgroup level was heterogeneous: influenza vaccination, A1C testing, and dental visits tended to improve while, among the uninsured, foot exams, cholesterol testing, and dental visits tended to decline.
+In 2020, 8.2% (4.5%, 11.9%) received none of the six recommended preventive care services.
+
+**Conclusions:** Other than influenza vaccination, we observed no improvement in receipt of preventive care services among U.S.
+adults with diabetes.
+These data highlight services and specific subgroups that could be targeted to improve preventive care among adults with diabetes.
+
+# Article Highlights (75 - 100 words, current: 99)
+
+-  We reported trends in receipt of six American Diabetes Association recommended preventive care services during 2008--2020.
+- The preventive services we evaluated were dental examinations, a dilated eye examination, a foot examination by a healthcare provider, ≥2 A1C tests, a blood cholesterol test, and an influenza vaccine.
+- From 2008 to 2019, overall trends in preventive services among U.S. adults with diabetes were stable except for an increase in the receipt of influenza vaccines.
+- These data highlight services and specific subgroups that could be targeted to improve preventive care among adults with diabetes.
+
+\pagebreak
+
+# Introduction
+
+Diabetes is a chronic disease that affects 11.3% of the adult population, or 37.1 million adults, in the United States @nationalreport.
+Diabetes is also costly: total direct and indirect costs are estimated at \$327 billion @economic2018.
+The prevalence of diabetes in the U.S.
+is expected to increase to 60.6 million adults by the year 2060 @lin2018.
+Incidence of diabetes peaked in the U.S.
+at 8.5 cases per 1,000 in 2008 and 2009 and has fallen since to 5.1 cases per 1,000 in 2021 [@dashboard; @magliano2019].
+While rates of newly diagnosed cases of diabetes have decreased, rates of hospitalization with diabetes as the primary diagnosis have been increasing since the year 2000 by about 2.5% per year @zhang2022.
+
+Access to preventive services is important to minimize diabetes-related complications and reduce rates of hospitalization.
+Other studies have reported on trends in receipt of some preventive services in the 2000s using data from various surveys, such as the Behavioral Risk Factor Surveillance System (BRFSS) and the National Health and Nutrition Examination Survey (NHANES) [@monnette2020; @luo2019; @shin2021; @fang2020; @eppley2019].
+To our knowledge, the proportion and trend of receipt of preventive services addressed in the Medical Expenditure Panel Survey (MEPS) has not been reported.
+We reported the proportion of and trends in the receipt of six preventive care services recommended by the American Diabetes Association (ADA) overall and among subgroups.
+These data are valuable for identifying groups that may be under-utilizing health care services, examining any effects the COVID-19 pandemic may have had on receipt of these services, and providing benchmarks for future studies.
+
+# Research Design and Methods
+
+## Data Source
+
+We used data from the 2008 -- 2020 MEPS, a household survey of U.S.
+noninstitutionalized populations administered and maintained by the Agency for Healthcare Research and Quality since 1996.
+The set of households surveyed for MEPS is a subsample of those surveyed in the National Health Interview Survey (NHIS).
+We chose the years 2008 to 2020 due to method changes in MEPS starting in 2008, and the consistency of questions related to preventive care during that time period.
+Data from MEPS were collected through a combination of computer-assisted personal interviewing and pencil-and-paper surveys.
+MEPS provides national and regional estimates of health care use, expenditures, sources of payment and health insurance coverage.
+This survey also contains information on patient demographics, socioeconomic characteristics, and, via the Diabetes Care Survey (DCS), information on diabetes preventive care services.
+The DCS is a self-administered paper-and-pencil questionnaire that is provided to MEPS respondents who indicate that they have been told by a doctor or health care professional that they have diabetes.
+In this analysis, we used data from the full-year consolidated MEPS files with an average annual number of 32,170 individual respondents over the 13-year period and response rates from 59.3% in 2008 to 27.6% in 2020.
+
+## Outcome Measures
+
+Among respondents with self-reported diagnosed diabetes, we selected six preventive care variables that were available in the data from 2008 to 2020.
+These variables are based on self-reported receipt in a given year @ada2021: ≥1 dental examination (derived from total number of reported dental care visits), a dilated eye examination, a foot examination by a healthcare provider, ≥2 A1C tests, a blood cholesterol test, and an influenza vaccine.
+Respondents were asked about receiving each of these services in a given year (e.g., "Did you receive an influenza vaccine in 2013?").
+We also created a binary variable classifying adults with diabetes who received none of the recommended preventive care services, although these results are presented only for the overall population due to small sample sizes in many of the examined subgroups.
+
+## Analysis
+
+Our analysis accounts for the complex survey design used, including clustering and stratification.
+Reported values were age-adjusted using the direct method, standardized to the 2000 U.S.
+population grouped by ages 18 -- 44, 45 -- 64, 65 -- 74, and ≥75 years.
+We presented these estimates for the overall population, as well as stratified by self-reported characteristics of age, sex, race and ethnicity, highest degree of education, type of health insurance, and the ratio of family income to the poverty line (poverty income ratio).
+We used the package gtsummary in R Statistical Software (v4.2.1) to calculate estimates [@gtsummary; @rcore2022].
+
+Medical care utilization decreased as a result of the COVID-19 pandemic starting in early 2020 @cantor2022.
+We reported the estimated proportions for 2020 in Table 1 and as points in @fig-exams and @fig-tests, but 2020 was excluded from trend analysis because of the decreased medical care utilization associated with the COVID-19 pandemic.
+Trends were analyzed using Joinpoint Command Line Software @joinpoint with R via the R package nih.joinpoint @nihjoinpoint.
+The Joinpoint software was used to fit a weighted least-squares regression model to the estimated proportions on the linear scale.
+A maximum of three joinpoints were searched for using the Grid search algorithm.
+As few as two observed time points were allowed between line segment.
+Joinpoint regression uses permutation tests to detect statistically significant changes at a pre-specified alpha of 0.05 in direction or magnitude of trends @kim2000permutation.
+The Joinpoint software also provided estimates of the annual percent change (APC) for each trend segment and the average annual percent change (AAPC) for the entire trend.
+
+## Data and Resource Availability
+
+The datasets generated during and/or analyzed in the current study are available from the corresponding author upon reasonable request.
+
+# Results
+
+All values pertaining to individual preventive practices presented here, as well as those that are not described, can be found in Supplemental Table 1.
+
+## Cholesterol Testing
+
+During 2008--2019, we found no significant change in the percentage of adults with diabetes who received cholesterol tests, which averaged 84.4% (95% CI: 81.8%, 87.0%) during this period (Table 1).
+For adults age 45--64 years, cholesterol testing was flat from 2008 to 2015 and showed a significant decrease starting in 2016 (APC `r pullNumber2(in_text_prop_tab_sans_2020, 'apc_period_2_95_percent_ci', brackets = TRUE, CI = FALSE, stratifier_column == 'Age: 45 to 64', preventive_service == 'Cholesterol tested')`, AAPC `r pullNumber2(in_text_prop_tab_sans_2020, 'aapc_95_percent_ci', brackets = TRUE, CI = FALSE, stratifier_column == 'Age: 45 to 64', preventive_service == 'Cholesterol tested')`).
+We found significant decreases starting in 2016 in the percentage of males (APC `r pullNumber2(in_text_prop_tab_sans_2020, 'apc_period_2_95_percent_ci', brackets = TRUE, CI = FALSE, stratifier_column == 'Sex: Male', preventive_service == 'Cholesterol tested')`) and adults with less than a high school education (APC `r pullNumber2(in_text_prop_tab_sans_2020, 'apc_period_2_95_percent_ci', brackets = TRUE, CI = FALSE, stratifier_column == 'Highest degree earned: Less than high school', preventive_service == 'Cholesterol tested')`, AAPC `r pullNumber2(in_text_prop_tab_sans_2020, 'aapc_95_percent_ci', brackets = TRUE, CI = FALSE, stratifier_column == 'Highest degree earned: Less than high school', preventive_service == 'Cholesterol tested')`) who received cholesterol testing.
+Adults with Medicaid had an AAPC of `r pullNumber2(in_text_prop_tab_sans_2020, 'aapc_95_percent_ci', brackets = FALSE, CI = FALSE, stratifier_column == 'Insurance coverage: Medicaid', preventive_service == 'Cholesterol tested')`.
+
+## Influenza Vaccine
+
+From 2008 to 2019, receipt of influenza vaccines increased at an AAPC of `r pullNumber2(in_text_prop_tab_sans_2020, 'aapc_95_percent_ci', brackets = FALSE, CI = FALSE, stratifier_column == 'Overall', preventive_service == 'Received influenza vaccine')`.
+The average proportion of adults with diabetes receiving an influenza vaccine over the study period was 41.8% (39.6%, 44.0%).
+Specifically, we noted significant increases during 2008 -- 2012 (APC `r pullNumber2(in_text_prop_tab_sans_2020, 'apc_period_1_95_percent_ci', brackets = TRUE, CI = FALSE, stratifier_column == 'Overall', preventive_service == 'Received influenza vaccine')`, AAPC `r pullNumber2(in_text_prop_tab_sans_2020, 'aapc_95_percent_ci', brackets = TRUE, CI = FALSE, stratifier_column == 'Overall', preventive_service == 'Received influenza vaccine')`), and after 2015 (APC `r pullNumber2(in_text_prop_tab_sans_2020, 'apc_period_3_95_percent_ci', brackets = TRUE, CI = FALSE, stratifier_column == 'Overall', preventive_service == 'Received influenza vaccine')`) (Table 1).
+The influenza vaccine trend for non-Hispanic White adults followed a similar pattern (AAPC `r pullNumber2(in_text_prop_tab_sans_2020, 'aapc_95_percent_ci', brackets = TRUE, CI = FALSE, stratifier_column == 'Race/Ethnicity: White/not Hispanic', preventive_service == 'Received influenza vaccine')`), although only the period from 2008 to 2012 had a significant increase (APC `r pullNumber2(in_text_prop_tab_sans_2020, 'apc_period_1_95_percent_ci', brackets = TRUE, CI = FALSE, stratifier_column == 'Race/Ethnicity: White/not Hispanic', preventive_service == 'Received influenza vaccine')`).
+Receipt of influenza vaccines increased among females over the entire study period (AAPC `r pullNumber2(in_text_prop_tab_sans_2020, 'aapc_95_percent_ci', brackets = TRUE, CI = FALSE, stratifier_column == 'Sex: Female', preventive_service == 'Received influenza vaccine')`).
+Adult males, adults in the poverty income ratio group 200%--399% and \>400%, and adults with private insurance showed an increase in the receipt of influenza vaccines in the early part of the study period, but flat thereafter.
+Receipt of influenza vaccines increased slightly for adults on Medicare (AAPC `r pullNumber2(in_text_prop_tab_sans_2020, 'aapc_95_percent_ci', brackets = TRUE, CI = FALSE, stratifier_column == 'Insurance coverage: Medicare only', preventive_service == 'Received influenza vaccine')`).
+
+## One or More Dentist Visits
+
+The trend for dentist visits for the overall adult population with diabetes was stable over the study period, averaging 35.7% (34.2%, 37.2%) (Table 1).
+Adults age 65--74 and ≥75 years had average annual percent increases of `r pullNumber2(in_text_prop_tab_sans_2020, 'aapc_95_percent_ci', brackets = FALSE, CI = FALSE, stratifier_column == 'Age: 65 to 74', preventive_service == 'One or more dentist visits')` and `r pullNumber2(in_text_prop_tab_sans_2020, 'apc_period_1_95_percent_ci', brackets = FALSE, CI = FALSE, stratifier_column == 'Age: 75+', preventive_service == 'One or more dentist visits')`, respectively.
+Non-Hispanic White adults with diabetes had an average annual percent increase of `r pullNumber2(in_text_prop_tab_sans_2020, 'aapc_95_percent_ci', brackets = FALSE, CI = FALSE, stratifier_column == 'Race/Ethnicity: White/not Hispanic', preventive_service == 'One or more dentist visits')`.
+Among those with private insurance, we found decreasing proportions visiting the dentist during 2008--2015 (APC `r pullNumber2(in_text_prop_tab_sans_2020, 'apc_period_1_95_percent_ci', brackets = TRUE, CI = FALSE, stratifier_column == 'Insurance coverage: Private only', preventive_service == 'One or more dentist visits')`), followed by an increase after 2015 (APC `r pullNumber2(in_text_prop_tab_sans_2020, 'apc_period_2_95_percent_ci', brackets = TRUE, CI = FALSE, stratifier_column == 'Insurance coverage: Private only', preventive_service == 'One or more dentist visits')`.
+The trends for adults with diabetes in the poverty income ratio group \< 100% and those with a high school education had multiple changes upward and downward during the study period.
+
+## A1C Tests
+
+We observed no significant changes in the overall trend in the proportion of adults receiving two or more A1C tests in a year, which averaged 53.0% (95% CI: 51.4%, 54.5%) over the study period (Table 1).
+Proportions increased annually by `r pullNumber2(in_text_prop_tab_sans_2020, 'aapc_95_percent_ci', brackets = FALSE, CI = FALSE, stratifier_column == 'Age: 45 to 64', preventive_service == 'Two or more A1C tests')`, `r pullNumber2(in_text_prop_tab_sans_2020, 'aapc_95_percent_ci', brackets = FALSE, CI = FALSE, stratifier_column == 'Age: 65 to 74', preventive_service == 'Two or more A1C tests')`, and `r pullNumber2(in_text_prop_tab_sans_2020, 'aapc_95_percent_ci', brackets = FALSE, CI = FALSE, stratifier_column == 'Age: 75+', preventive_service == 'Two or more A1C tests')` for those age 45--64, 65--74, and ≥75 years, respectively.
+We also found increases in A1C testing for Hispanic adults (AAPC `r pullNumber2(in_text_prop_tab_sans_2020, 'aapc_95_percent_ci', brackets = TRUE, CI = FALSE, stratifier_column == 'Race/Ethnicity: Hispanic', preventive_service == 'Two or more A1C tests')` ), non-Hispanic White adults (AAPC `r pullNumber2(in_text_prop_tab_sans_2020, 'aapc_95_percent_ci', brackets = TRUE, CI = FALSE, stratifier_column == 'Race/Ethnicity: White/not Hispanic', preventive_service == 'Two or more A1C tests')`), those with Medicare only (AAPC `r pullNumber2(in_text_prop_tab_sans_2020, 'aapc_95_percent_ci', brackets = TRUE, CI = FALSE, stratifier_column == 'Insurance coverage: Medicare only', preventive_service == 'Two or more A1C tests')`), and those in the highest poverty income ratio group (\> 400%) (AAPC `r pullNumber2(in_text_prop_tab_sans_2020, 'aapc_95_percent_ci', brackets = TRUE, CI = FALSE, stratifier_column == 'Poverty income ratio: > 400%', preventive_service == 'Two or more A1C tests')`).
+
+## Dilated Eye Exam
+
+The overall proportion receiving dilated eye exams was stable during 2008--2019 (Table 1).
+This proportion averaged 55.5% (95% CI: 54.0%, 57.0%) over this period.
+Similarly, for males, we observed stable trends from 2008 to 2011 but a significant decrease after 2011 (APC `r pullNumber2(in_text_prop_tab_sans_2020, 'apc_period_2_95_percent_ci', brackets = FALSE, CI = FALSE, stratifier_column == 'Sex: Male', preventive_service == 'Dilated eye exam')`).
+Uninsured adults with diabetes had average annual increase from 2008 to 2019 in the receipt of dilated eye exams of `r pullNumber2(in_text_prop_tab_sans_2020, 'aapc_95_percent_ci', brackets = FALSE, CI = FALSE, stratifier_column == 'Insurance coverage: Uninsured', preventive_service == 'Dilated eye exam')`.
+Adults with diabetes in the highest income group (poverty income ratio \> 400%) had a flat trend in dilated eye examinations until 2013, after which the proportion significantly decreased (APC `r pullNumber2(in_text_prop_tab_sans_2020, 'apc_period_2_95_percent_ci', brackets = TRUE, CI = FALSE, stratifier_column == 'Poverty income ratio: > 400%', preventive_service == 'Dilated eye exam')`).
+
+## Foot Exam
+
+The average proportion of U.S.
+adults with diabetes receiving a foot exam over the study period was 61.4% (95% CI: 60.0%, 62.8%).
+The trend for foot exams for the overall adult population with diabetes was flat until 2011, after which it decreased (APC `r pullNumber2(in_text_prop_tab_sans_2020, 'apc_period_2_95_percent_ci', brackets = TRUE, CI = FALSE, stratifier_column == 'Overall', preventive_service == 'Foot examination')`, Table 1).
+We found an increase in foot exams among adults with diabetes age 65--74 years until 2014 (APC `r pullNumber2(in_text_prop_tab_sans_2020, 'apc_period_1_95_percent_ci', brackets = TRUE, CI = FALSE, stratifier_column == 'Age: 65 to 74', preventive_service == 'Foot examination')`), and the trend was flat thereafter.
+
+## Absence of Preventive Care Services
+
+In 2008, 5.1% (95% CI: 2.7%, 7.5%) of adults with diabetes reported receiving none of the six recommended care services.
+In 2019, this estimate was 6.1% (3.7%, 8.5%) and in 2020 it was 8.2% (4.5%, 11.9%).
+
+## Comparisons Among Subgroups
+
+The youngest adults (18--44 years) often reported lower rates of dilated eye exams, foot exams, cholesterol testing, and influenza vaccination.
+Uninsured adults often reported the lowest rates of preventive care for dilated eye exams, foot exams, cholesterol testing, and A1C testing.
+Adults with less than a high school education were less likely to visit the dentist in most years, although they were only statistically significantly less likely to visit the dentist in 2008--2010, 2013--2014, and 2020.
+
+# Discussion
+
+The passing of the Affordable Care Act (ACA) in 2010 and subsequent Medicaid expansion has been seen as a mechanism to increase the receipt of preventive services [@luo2019]; however, we found no significant change over time in five out of the six preventive care services for the overall U.S.
+adult population with diagnosed diabetes from 2008 to 2019.
+Influenza vaccination was the only preventive service that increased significantly during 2008--2019 overall.
+Among subgroups, influenza vaccine uptake, A1C testing, and dental visits tended to improve.
+However, foot exams, cholesterol testing, and dental visits among the uninsured tended to decline.
+While the passing of the ACA led to an increase in the number of adults with diagnosed and undiagnosed diabetes who have health insurance, and an increase in their use of health care services [@myerson2019; @simon2017], detecting corresponding increases in the receipt of preventive care has proved more elusive.
+As of 2019, 6.1% of adults with diabetes had not received any of the six preventive services, and this percentage grew to 8.2% in 2020 during the onset of the COVID-19 pandemic.
+
+Two studies that used data from BRFSS found no changes overall in the receipt of preventive care for adults with diabetes resulting from Medicaid expansion between 2014 and 2019 [@monnette2020; @luo2019].
+Similarly, the majority of subgroups in these studies exhibited no change in or decreased receipt of these six preventive services.
+The subgroup trends we observed suggest disparities in diabetes care that have been shown in other research.
+Consistent with our findings, studies using NHANES data for 2005--2018 as well as BRFSS for 2004--2014 both found that younger adults with diabetes were less likely to report receiving various recommended preventive care services [@shin2021; @luo2018].
+Additionally, lack of insurance was a barrier to preventive care, as uninsured adults also reported lower rates of preventive care in these studies [@shin2021; @luo2018].
+In our study, dental visits decreased over the study period but dilated eye exams increased among the uninsured.
+Education has also been linked to meeting recommendations for preventive care; adults with lower education consistently report lower rates of prevention [@eppley2019; @shin2021].
+We found that adults with less than a high school education had decreasing trends in cholesterol testing and frequently were less likely to report visiting the dentist at least once than adults with more education, although this difference was not always statistically significant.
+Future research may wish to examine those adults with diabetes who reported receiving none of the six preventive care services, and factors contributing to this lack of care.
+While the confidence intervals for the estimates from 2008 and 2019/2020 overlap, the increase highlights the sustained suboptimal preventive care for a subset of adults with diabetes.
+
+A1C testing and influenza vaccinations were the only two preventive services that showed increases either among the overall population or various subgroups which may be linked with the increase in health care service usage [@myerson2019].
+A1C increased among: adults age 45 -- 65, 65 -- 74, > 75 years, Hispanic adults, non-Hispanic White adults, adults on Medicare only, and adults in the > 400% poverty income ratio group.
+Influenza vaccine increased among: non-Hispanic White adults, adult females, adult males, adults in the 200% -- 399% poverty income ratio group, and adults in the > 400% poverty income ratio group.
+These services can be administered at the point-of-care during regular physician visits, whereas a dilated eye exam or dental visit require separate appointments.
+Lack of access to specialists, limited provider acceptance of public insurance options like Medicare, and inadequate care coordination may further complicate access to dilated eye exams or dentist visits and may explain why, for most groups, we observed no change or a decrease in the receipt of these services [@chen2020; @eppley2019; @fathy2016].
+
+Other studies on trends in preventive care using different data sources report some conflicting findings.
+A study using NHANES data from 2005 to 2018 found increases in the proportion of adults with diabetes who reported: having a primary care doctor, receiving an annual check-up with a physician, having had at least two A1C tests in a year, having their cholesterol levels tested, and having an annual foot exam by a doctor @shin2021.
+Another study that reported on data from NHANES, NHIS, and BRFSS found that foot exams, influenza vaccinations, and A1C testing increased from 1999 to 2016, although dilated eye exams stayed roughly constant @fang2020.
+Data from BRFSS showed that adults with diabetes had reported decreasing dentist visits from 2004 to 2014 [@luo2018], while patient-reported dilated eye examinations increased briefly following Medicaid expansion in 2014 and then decreased [@chen2020].
+In contrast, a study using NHANES data found that dilated eye exams for adults with diabetes did not increase from 2005 to 2016 [@eppley2019].
+A study using NHIS data reported no change in influenza vaccination rates from 2007 to 2018 for the overall population of adults with diabetes [@hung2020].
+Differences in these survey results may be due to differences in how questions are phrased and differences in the population being surveyed.
+Additionally, it is difficult to compare trends for overlapping time periods of different lengths, so caution should be used when interpreting these differences; when possible, trends should be compared over similar, longer time periods [@cusser2021; @bahlai2021].
+
+## Limitations
+
+The responses from MEPS were self-reported which may introduce bias.
+The study group was also cross-sectional and does not provide insight into how past receipt of preventive services may affect future receipt.
+In 2013, MEPS implemented efforts to improve collection of complete information by using field interviewers, with the goal of improving under reporting.
+This effort may have improved data quality after 2014 and could have impacted our trend analyses.
+
+We are unable to identify factors that are causally linked to the changes in trends.
+Additionally, there has been a steadily declining response rate for both MEPS and DCS from a peak during the studied time period from 59.3% and 92.4%, respectively in 2008 to 39.5% and 65.8%, respectively, in 2019 and 27.6% and 59.3%, respectively in 2020.
+Although weights for these data were adjusted for non-response, the direction of bias due to non-response cannot be known.
+Furthermore, we were unable to distinguish between type 1 and type 2 diabetes in these data.
+Because of the greater proportion of type 2 diabetes (90% -- 95%), the trends we report likely are more reflective of type 2 diabetes than type 1 diabetes.
+
+# Conclusions
+
+In summary, with the exception of influenza vaccination, the overall receipt of preventive care for diabetes from 2008 to 2019 was flat.
+The trend pattern in subgroups was heterogeneous.
+This work highlights services and subgroups with low or declining receipt of these services that could be targeted to improve preventive care.
+Declining trends in preventive care may lead to increased diabetes complications, thereby increasing morbidity as well as cost of diabetes care.
+
+# Acknowledgements
+
+*Funding:* The authors report no funding sources.
+
+*Conflict of Interest:* The authors of this study declare no conflicts of interest.
+
+*Author Contributions and Guarantor Statement:* J.T.W., K.M.B., S.R.B.
+conceptualized the study and contributed to discussion.
+J.T.W.
+curated and analyzed data, and wrote the first draft of the manuscript.
+K.M.B.
+and S.R.B.
+reviewed the manuscript, and all authors edited the manuscript.
+J.T.W.
+is the guarantor of this work and, as such, had full access to all the data in the study and takes responsibility for the integrity of the data and the accuracy of the data analysis.
+
+# References
+
+::: {#refs}
+:::
+
+\pagebreak
+
+::: landscape
+# Tables
+
+```{r}
+#| tbl-cap: Age-adjusted trends in proportions of U.S.
+adults with diabetes who report receiving at least three of six recommended care services—at least one dental visit, one dilated eye exam, one foot exam, two or more A1C tests, cholesterol level tested, and an influenza vaccine.
+
+proportion_table_sans_2020 %>% 
+  tab_header("Table 1—Age-adjusted trends in proportions of U.S.
+adults with diabetes that report receiving recommended care services - at least one dental visit, one dilated eye exam, one foot exam, two or more A1C tests, cholesterol level tested, and receiving an influenza vaccine.")
+```
+
+\pagebreak
+
+# Figures
+
+```{r}
+#| label: fig-exams
+#| fig-cap: Age-adjusted trends in proportions of U.S.
+adults with diabetes who reported receiving recommended medical examinations from 2008 to 2019.
+The dashed black line is the overall trend, while dots represent percentages for 2020.
+Data from 2020 were not included in the trend analysis.
+#| fig-width: 8
+
+all_exam_plots_sans_2020
+```
+
+\pagebreak
+
+```{r}
+#| label: fig-tests
+#| fig-cap: Age-adjusted trends in proportions of U.S.
+adults with diabetes who reported receiving recommended lab tests and vaccinations.
+The dashed black line is the overall trend, while dots represent percentages for 2020.
+Data from 2020 were not included in the trend analysis.
+#| fig-width: 10
+
+all_test_plots_sans_2020
+```
+
+\pagebreak
+
+# Figure Legends
+
+Figure 1—Age-adjusted trends in proportions of U.S.
+adults with diabetes who reported receiving recommended medical examinations from 2008 to 2019.
+The dashed black line is the overall trend, while dots represent percentages for 2020.
+Data from 2020 were not included in the trend analysis.
+
+Figure 2—Age-adjusted trends in proportions of U.S.
+adults with diabetes who reported receiving recommended lab tests and vaccinations.
+The dashed black line is the overall trend, while dots represent percentages for 2020.
+Data from 2020 were not included in the trend analysis.
+
+# Supplement
+
+```{r}
+
+supplement_prop_tab %>% 
+  tab_header('Age-adjusted trends in proportions of U.S.
+adults with diabetes, overall and by subgroup, who report receiving six recommended care services—at least one dental visit, one dilated eye exam, one foot exam, two or more A1C tests, cholesterol level tested, and an influenza vaccine.')
+```
+
+```{r}
+#| include: false
+#| echo: false
+# Create plots with actual proportions and standard errors
+supp_dat <- age_adjusted_stats %>%
+      filter(strata != 'Total') %>%
+      filter(stratifier != 'overall') %>% 
+      filter(strata != 'Not available') %>%
+      filter(strata != 'Other Race/not Hispanic') %>%
+      filter(strata != 'Other') %>% 
+      mutate(variable_text = case_when(variable == 'a1c' ~ '2 or more A1C tests',
+                                       variable == 'CHOL_all' ~ 'Cholesterol tested',
+                                       variable == 'DENT_all' ~ '1 or more dentist visits',
+                                       variable == 'eye-exam' ~ 'Dilated eye exam',
+                                       variable == 'flu' ~ 'Received influenza vaccine',
+                                       variable == 'foot' ~ 'Foot examination'),
+             strata = case_when(strata == 'stat_0' ~ 'Overall',
+                                TRUE ~ strata)) %>%
+      mutate(strata = as.factor(strata),
+             year_adj = year - 2007) %>%  
+  mutate(strata = as.factor(strata)) %>% 
+  split(., f = .$stratifier)
+
+supp_dat <- map(supp_dat, function(.x) {
+  .x %>% 
+    mutate(strata = fct_drop(strata))
+})
+
+supp_dat$poverty$strata <-
+  factor(
+    supp_dat$poverty$strata,
+    levels = c('Poor/Negative', 'Low income', 'Middle income', 'High income'), 
+    labels = c(
+      'd< 100%',
+      'c100%—199%',
+      'b200%—399%',
+      'a> 400% '
+    ),
+    ordered = TRUE
+  )
+
+supplemental_test_plots <-
   map(
-    ~ ggplot(filter(.x, variable %!in% c('a1c', 'CHOL_all', 'flu', 'foot')),
+    supp_dat,
+    ~ ggplot(
+      filter(.x, variable %in% c('a1c', 'CHOL_all', 'flu')),
       aes(
@@
         color = strata
-    )) +
-      #geom_point() +
-      geom_line(aes(x = year, y = model, group = strata, color = strata)) +
-      geom_line(data = filter(overall_data, variable %!in% c('a1c', 'CHOL_all', 'flu', 'foot')),
-                  aes(x = year, y = model),
-                  color = 'black',
-                  linetype = 'dashed') +
-      facet_wrap( ~ variable_text, ncol = 3) +
+      )
+    ) +
+      geom_point() +
+      geom_errorbar(
+        aes(ymin = p - 1.96 * (p.std.error * 100),
+            ymax = p + 1.96 * (p.std.error * 100))
+      ) +
+      facet_wrap(~ variable_text, ncol = 3, scales = 'free_y') +
       theme_classic() +
-      scale_y_continuous(
-        limits = c(  0, 100),
-        breaks = seq(0, 100, 25),
-        labels = seq(0, 100, 25)
-      ) +
       scale_x_continuous(
-        limits = c(2008, 2020),
+        limits = c(2007.5, 2020.5),
         breaks = seq(2008, 2020, 2),
-        labels = seq(2008, 2020, 2)
-      ) +
-      scale_color_brewer(type = 'qual', palette = 'Set2') +
-      theme(axis.text = element_text(color = 'black'),
-            axis.text.x = element_text(angle = 45, hjust = 0.9, vjust = 0.95),
-            legend.title = element_text(size = 8),
-            legend.text = element_text(size = 6)) +
+        labels = c(2008, "", 2012, "", 2016, "", 2020)
+      ) +
+      theme(
+        axis.text = element_text(color = 'black'),
+        #axis.text.x = element_text(angle = 45, hjust = 0.9, vjust = 0.95),
+        legend.title = element_text(size = 11),
+        legend.text = element_text(size = 9)
+      ) +
       labs(x = 'Year', y = 'Percentage')
-  )
-
-exam_plots1[[1]] <- exam_plots1[[1]] + labs(color = 'Age (grouped)') +
-  theme(axis.title.x = element_blank())
-exam_plots1[[2]] <-
-  exam_plots1[[2]] + labs(color = 'Highest degree \nobtained') + theme(
+
+  )
+
+supplemental_exam_plots <-
+  map(
+    supp_dat,
+    ~ ggplot(
+      filter(.x, variable %!in% c('a1c', 'CHOL_all', 'flu')),
+      aes(
+        x = year,
+        y = p,
+        group = strata,
+        color = strata
+      )
+    ) +
+      geom_point() +
+      geom_errorbar(
+        aes(ymin = p - 1.96 * (p.std.error * 100),
+            ymax = p + 1.96 * (p.std.error * 100))
+      ) +
+      facet_wrap(~ variable_text, ncol = 3, scales = 'free_y') +
+      theme_classic() +
+      scale_x_continuous(
+        limits = c(2007.5, 2020.5),
+        breaks = seq(2008, 2020, 2),
+        labels = c(2008, "", 2012, "", 2016, "", 2020)
+      ) +
+      theme(
+        axis.text = element_text(color = 'black'),
+        #axis.text.x = element_text(angle = 45, hjust = 0.9, vjust = 0.95),
+        legend.title = element_text(size = 11),
+        legend.text = element_text(size = 9)
+      ) +
+      labs(x = 'Year', y = 'Percentage')
+
+  )
+
+supplemental_test_plots[[1]] <-
+  supplemental_test_plots[[1]] +
+  theme(axis.title.x = element_blank()) +
+  scale_color_manual(
+    name = 'Age (grouped)',
+    values = c(
+     '18 to 44' = color_pal[1],
+     '45 to 64'  = color_pal[2],
+     '65 to 74' = color_pal[3],
+     '75+' = color_pal[4]
+    ),
+    labels = c('18 to 44' = '18 to 44',
+               '45 to 64' = '45 to 64',
+               '65 to 74' = '65 to 74',
+               '75+'      = '75+')
+  )
+
+supplemental_test_plots[[2]] <-
+  supplemental_test_plots[[2]] +
+  theme(
     strip.background =  element_blank(),
@@
     axis.title.x = element_blank()
-  )
-exam_plots1[[3]] <-
-  exam_plots1[[3]] + labs(color = "Insurance") + theme(
+  ) +
+  scale_color_manual(
+    name = 'Highest degree obtained',
+    labels = c('Greater than HS'       = 'Greater than HS',
+               'High school'           = 'High school',
+               'Less than high school' = 'Less than HS'),
+    values = c(
+     'Greater than HS' = color_pal[1],
+     'High school' = color_pal[2],
+     'Less than high school'  = color_pal[3]
+    )
+  )
+
+supplemental_test_plots[[3]] <-
+  supplemental_test_plots[[3]] +
+  theme(
     strip.background =  element_blank(),
@@
     axis.title.x = element_blank()
-  )
-exam_plots1[[4]] <-
-  exam_plots1[[4]] + labs(color = 'Poverty income ratio') + theme(
-    strip.background =  element_blank(),
-    strip.text = element_blank()
-  )
-exam_plots1[[5]] <-
-  exam_plots1[[5]] + labs(color = 'Race & Ethnicity') + theme(
+  ) +
+  scale_color_manual(
+    name = 'Insurance',
+    values = c(
+      'Medicaid' = color_pal[1],
+      'Medicare only' = color_pal[2],
+      'Private only' = color_pal[3],
+      'Uninsured' = color_pal[4]
+    ),   labels = c(
+      'Medicaid'      = 'Medicaid',
+      'Medicare only' = 'Medicare only',
+      'Private only'  = 'Private only',
+      'Uninsured'     = 'Uninsured'
+    )
+  )
+
+supplemental_test_plots[[4]] <-
+  supplemental_test_plots[[4]] +
+  theme(strip.background =  element_blank(),
+        strip.text = element_blank()) +
+  scale_color_manual(
+    name = 'Poverty income ratio',
+    labels = c('a> 400% '     = '> 400%',
+               'b200%—399%' = '200%—399%',
+               'c100%—199%' = '100%—199%',
+               'd< 100%'      = '< 100%'),
+
+    values = c(
+      'a> 400% ' = color_pal[1],
+      'b200%—399%' = color_pal[2],
+      'c100%—199%' = color_pal[3],
+      'd< 100%' = color_pal[4]
+    )
+  )
+
+supplemental_test_plots[[5]] <-
+  supplemental_test_plots[[5]] + theme(
     strip.background =  element_blank(),
@@
     axis.title.x = element_blank()
-  )
-exam_plots1[[6]] <-
-  exam_plots1[[6]] + labs(color = 'Sex') + theme(strip.background =  element_blank(),
+  ) +
+  scale_color_manual(
+    name = 'Race & Ethnicity',
+    labels = c(
+     'Asian/not Hispanic' = 'Asian/not Hispanic',
+     'Black/not Hispanic' = 'Black/not Hispanic',
+     'Hispanic'           = 'Hispanic',
+     'White/not Hispanic' = 'White/not Hispanic'
+    ),
+    values = c(
+     'Asian/not Hispanic' = color_pal[1],
+     'Black/not Hispanic'  = color_pal[2],
+     'Hispanic' = color_pal[3],
+     'White/not Hispanic' = color_pal[4]
+    )
+  )
+supplemental_test_plots[[6]] <-
+  supplemental_test_plots[[6]] +
+  theme(
+    strip.background =  element_blank(),
     strip.text = element_blank(),
-    axis.title.x = element_blank())
-exam_plots1 <- list(
-  exam_plots1[[1]],
-  exam_plots1[[6]],
-  exam_plots1[[5]],
-  exam_plots1[[2]],
-  exam_plots1[[3]],
-  exam_plots1[[4]]
-)
+    axis.title.x = element_blank()
+  ) +
+  scale_color_manual(
+    name = 'Sex',
+    labels = c('Female'  = 'Female',
+               'Male'    = 'Male'),
+    values = c(
+     'Female' = color_pal[1],
+     'Male'  = color_pal[2]
+    )
+  ) 
+supplemental_test_plots <- list(
+  supplemental_test_plots[[1]],
+  supplemental_test_plots[[6]],
+  supplemental_test_plots[[5]],
+  supplemental_test_plots[[2]],
+  supplemental_test_plots[[3]],
+  supplemental_test_plots[[4]]
+)
+
+# Set up legends on all plots
+supplemental_exam_plots[[1]] <- supplemental_exam_plots[[1]] +
+  theme(axis.title.x = element_blank()) +
+  scale_color_manual(
+    name = 'Age (grouped)',
+    labels = c('18 to 44' = '18 to 44',
+               '45 to 64' = '45 to 64',
+               '65 to 74' = '65 to 74',
+               '75+'      = '75+'),
+    values =   c(
+      '18 to 44' = color_pal[1],
+      '45 to 64' = color_pal[2],
+      '65 to 74' = color_pal[3],
+      '75+'      = color_pal[4]
+    )
+  )
+
+supplemental_exam_plots[[2]] <-
+  supplemental_exam_plots[[2]] +
+  theme(
+    strip.background =  element_blank(),
+    strip.text = element_blank(),
+    axis.title.x = element_blank()
+  ) +
+  scale_color_manual(
+    name = 'Highest degree obtained',
+    labels = c('Greater than HS'       = 'Greater than HS',
+               'High school'           = 'High school',
+               'Less than high school' = 'Less than HS'),
+        values = c(
+      'Greater than HS'       = color_pal[1],
+      'High school'           = color_pal[2],
+      'Less than high school' = color_pal[3]
+    )
+  )
+
+supplemental_exam_plots[[3]] <-
+  supplemental_exam_plots[[3]] +
+  theme(
+    strip.background =  element_blank(),
+    strip.text = element_blank(),
+    axis.title.x = element_blank()
+  ) +
+  scale_color_manual(
+    name = 'Insurance',
+    labels = c(
+     'Medicaid'      =  'Medicaid',
+     'Medicare only' =  'Medicare only',
+     'Private only'  =  'Private only',
+     'Uninsured'     =  'Uninsured'
+    ),
+    values = c(
+      'Medicaid'      = color_pal[1],
+      'Medicare only' = color_pal[2],
+      'Private only'  = color_pal[3],
+      'Uninsured'     = color_pal[4]
+    )
+  )
+
+supplemental_exam_plots[[4]] <-
+  supplemental_exam_plots[[4]] +
+  theme(strip.background =  element_blank(),
+        strip.text = element_blank()) +
+  scale_color_manual(
+    name = 'Poverty income ratio',
+    labels = c('a> 400% '     = '> 400%',
+               'b200%—399%' = '200%—399%',
+               'c100%—199%' = '100%—199%',
+               'd< 100%'      = '< 100%'),
+    values = c(
+      'a> 400% '     = color_pal[1],
+      'b200%—399%' = color_pal[2],
+      'c100%—199%' = color_pal[3],
+      'd< 100%'      = color_pal[4]
+    )
+  )
+
+supplemental_exam_plots[[5]] <-
+  supplemental_exam_plots[[5]] +
+  theme(
+    strip.background =  element_blank(),
+    strip.text = element_blank(),
+    axis.title.x = element_blank()
+  ) +
+  scale_color_manual(
+    name = 'Race & Ethnicity',
+    labels = c(
+      'Asian/not Hispanic' = 'Asian/not Hispanic',
+      'Black/not Hispanic' = 'Black/not Hispanic',
+      'Hispanic'           = 'Hispanic',
+      'White/not Hispanic' = 'White/not Hispanic'
+    ),
+    values = c(
+      'Asian/not Hispanic' = color_pal[1],
+      'Black/not Hispanic' = color_pal[2],
+      'Hispanic'           = color_pal[3],
+      'White/not Hispanic' = color_pal[4]
+    )
+  )
+
+supplemental_exam_plots[[6]] <-
+  supplemental_exam_plots[[6]] +
+  theme(
+    strip.background =  element_blank(),
+    strip.text = element_blank(),
+    axis.title.x = element_blank()
+  ) +
+  scale_color_manual(
+    name = 'Sex',
+    labels = c('Female'  = 'Female',
+               'Male'    = 'Male'),
+    values = c(
+      'Female' = color_pal[1],
+      'Male'  = color_pal[2]
+    )
+  )
+
+supplemental_exam_plots <- list(
+  supplemental_exam_plots[[1]],
+  supplemental_exam_plots[[6]],
+  supplemental_exam_plots[[5]],
+  supplemental_exam_plots[[2]],
+  supplemental_exam_plots[[3]],
+  supplemental_exam_plots[[4]]
+)
+
+supplemental_all_exam <- supplemental_exam_plots %>% 
+  wrap_plots(nrow = 6) &
+  theme(plot.margin = margin(0.5, 0.5, 0.5, 0.5, 'pt'),
+        legend.justification = 'left',
+        plot.caption = element_text(hjust = 0)) &
+  guides(color = guide_legend(ncol = 2)) 
+supplemental_all_test <- supplemental_test_plots %>% 
+  wrap_plots(nrow = 6) &
+  theme(plot.margin = margin(0.5, 0.5, 0.5, 0.5, 'pt'),
+        legend.justification = 'left',
+         plot.caption = element_text(hjust = 0)) &
+  guides(color = guide_legend(ncol = 2))
+
+ggsave(plot = supplemental_all_exam,
+       filename = 'figures/supp_exam_plots.tiff',
+       dpi = 1200,
+       width = 10,
+       height = 6)
+ggsave(plot = supplemental_all_test,
+       filename = 'figures/supp_test_plots.tiff',
+       dpi = 1200,
+       width = 10,
+       height = 6)
 ```
@@
 ```{r}
-#| fig-height: 9
-#| fig-width: 6
-(all_exam_plots1 <- exam_plots1 %>% 
-  wrap_plots(nrow = 6) &
-  theme(plot.margin = margin(0.5, 0.5, 0.5, 0.5, 'pt')))
+#| include: FALSE
+#| fig-cap: Age-adjusted proportions with 95% confidence intervals of U.S. adults with diabetes who reported receiving recommended medical examinations from 2008 - 2020. 
+supplemental_all_exam
 ```
@@
 ```{r}
-#| fig-height: 9
-#| fig-width: 6
-
-(all_test_plots1 <- test_plots1 %>% 
-  wrap_plots(nrow = 6) &
-  theme(plot.margin = margin(0.5, 0.5, 0.5, 0.5, 'pt')))
+#| include: FALSE
+#| fig-cap: Age-adjusted proportions with 95% confidence intervals of U.S. adults with diabetes who reported receiving recommended lab tests and vaccinations from 2008 - 2020.
+supplemental_all_test
 ```
-
-```{r}
-#| fig-height: 9
-#| fig-width: 6
-
-(all_test_plots2 <- test_plots2 %>% 
-  wrap_plots(nrow = 6) &
-  theme(plot.margin = margin(0.5, 0.5, 0.5, 0.5, 'pt')))
-```
+:::

### 2023-06-14 _targets.R

@@ -92,7 +92,7 @@ list(
   ),
   tar_target(
     diab_dat,
-    cumulativePractices(diab_dat_sub)
+    cumulativeServices(diab_dat_sub)
   ),
   tar_target(diab_list,
              diab_dat %>% group_split(year),
@@ -549,7 +549,7 @@ list(
         'Once a year or more'
       )
       ) %>%
-      filter(strata %!in% c('Not available', 'Other Race/Not Hispanic'))
+      filter(strata %!in% c('Not available', 'Other Race/not Hispanic'))
   ),
   tar_target(
     stats_table,
@@ -657,7 +657,7 @@ list(
   #                              'YES'
   #                            ))),
 
-# Age adjust preventive practices ------------------------------------
+# Age adjust preventive services ------------------------------------
   tar_target(
     overall_preventive,
     diab_list %>%
@@ -668,7 +668,7 @@ list(
         nest = TRUE
       ) %>%
       svystandardize(., ~ AGE_all, ~1, population = c(0.530535, 0.299194, 0.088967, 0.081304)) %>%
-      preventivePractice(., by = NULL, diab_list) %>%
+      preventiveService(., by = NULL, diab_list) %>%
       makePreventiveTablesLonger(),
     pattern = map(diab_list)
   ),
@@ -682,7 +682,7 @@ list(
         nest = TRUE
       ) %>%
       svystandardize(., ~ AGE_all, ~1, population = c(0.530535, 0.299194, 0.088967, 0.081304)) %>%
-      preventivePractice(., by = 'SEX', diab_list) %>%
+      preventiveService(., by = 'SEX', diab_list) %>%
       makePreventiveTablesLonger(),
     pattern = map(diab_list)
   ),
@@ -696,7 +696,7 @@ list(
         nest = TRUE
       ) %>%
       svystandardize(., ~ AGE_all, ~1, population = c(0.530535, 0.299194, 0.088967, 0.081304)) %>%
-      preventivePractice(., by = 'RACE_all', diab_list) %>%
+      preventiveService(., by = 'RACE_all', diab_list) %>%
       makePreventiveTablesLonger(),
     pattern = map(diab_list)
   ),
@@ -710,7 +710,7 @@ list(
         nest = TRUE
       ) %>%
       svystandardize(., ~ AGE_all, ~1, population = c(0.530535, 0.299194, 0.088967, 0.081304)) %>%
-      preventivePractice(., by = 'HIDEG_all', diab_list) %>%
[…]

### 2023-06-14 scripts/functions.R

@@ -332,17 +332,17 @@ cleanMepsData <- function(dat) {
       RACETHNX = recode_factor(
         RACETHNX,
         `1` = 'Hispanic',
-        `2` = 'Black/Not Hispanic',
-        `3` = 'Asian/Not Hispanic',
-        `4` = 'Other Race/Not Hispanic',
-      ) %>% fct_expand('White/Not Hispanic'),
+        `2` = 'Black/not Hispanic',
+        `3` = 'Asian/not Hispanic',
+        `4` = 'Other Race/not Hispanic',
+      ) %>% fct_expand('White/not Hispanic'),
       RACETHX = recode_factor(
         RACETHX,
         `1` = 'Hispanic',
-        `2` = 'White/Not Hispanic',
-        `3` = 'Black/Not Hispanic',
-        `4` = 'Asian/Not Hispanic',
-        `5` = 'Other Race/Not Hispanic',
+        `2` = 'White/not Hispanic',
+        `3` = 'Black/not Hispanic',
+        `4` = 'Asian/not Hispanic',
+        `5` = 'Other Race/not Hispanic',
       ),
       # USBORN42 = recode_factor(
       #   USBORN42,
@@ -442,7 +442,7 @@ cleanMepsData <- function(dat) {
 
     )
 
-  temp_dat$RACETHNX[temp_dat$RACEX == 'White'] <- 'White/Not Hispanic'
+  temp_dat$RACETHNX[temp_dat$RACEX == 'White'] <- 'White/not Hispanic'
   return(temp_dat)
 }
 
@@ -534,7 +534,7 @@ relevelFactors <- function(dat) {
 }
 
 # This function calculates proportion of individuals following prventive
-# care practices in each year and for the different strata.
+# care services in each year and for the different strata.
 calcProp <- function(data, year, variable = NULL) {
   if (is.character(variable)) {
     vari <- enquo(variable)
@@ -637,9 +637,9 @@ combineRace <- function(meps_data, dash_data) {
       ),
       RACE_all = case_when(
         RACE_all == 'Hispanic' ~ 'hispanic',
-        RACE_all == 'Black/Not Hispanic' ~ 'black',
-        RACE_all == 'White/Not Hispanic' ~ 'white',
-        RACE_all == 'Asian/Not Hispanic' ~ 'asian',
+        RACE_all == 'Black/not Hispanic' ~ 'black',
+        RACE_all == 'White/not Hispanic' ~ 'white',
[…]

### 2023-08-31 scripts/manuscript/manuscript_draft.qmd
Revisions submitted

@@
 bibliography: references.bib
+citation-abbreviations: medline-abbreviations.json
 csl: diabetes-care2.csl
@@
 ---
+
+```{r}
+# Remove figures from final doc
+# Fix hyphens
+# Change supplemental table name in separate file
+
+```
 
@@
 }
+
+# sample size
+# tar_load(diab_list)
+# bind_rows(diab_list) %>% filter(DIABW != 0, RACE_all != 'Other Race/not Hispanic')
+n <- 25616
+
+dcs_response_rates <- tibble(
+  year = c(2008, 2009, 2010, 2011, 2012, 2013, 2014, 2015, 2016, 2017, 2018, 2019, 2020),
+  rate = c(92.4, 93.2, 90.1, 90.1, 90.1, 88.1, 88.4, 85.9, 83.7, 81.0, 75.4, 65.8, 57.1)
+)
 
@@
                           TRUE ~ NA_character_)) %>%
-  select(stratifier, strata, AAPC)
+  select(stratifier, strata, variable = service, AAPC)
 
@@
   # or a joinpoint (segment_end != 2020)
-  pivot_wider(id_cols = c(stratifier, strata, model),
+  pivot_wider(id_cols = c(stratifier, service, strata, model),
               names_from = segment,
@@
   ) %>%
-  select(stratifier, strata, segment, starts_with('APC '))
+  select(stratifier, strata, variable = service, segment, starts_with('APC '))
 
@@
   # Filter to just the >=3 services
-  filter(variable == 'zero_services') %>% 
+  filter(variable == 'zero_services' | variable == 'atleast_six_services') %>% 
   # Filter down to every other year
@@
   # Join with AAPC table
-  left_join(cleaned_jp_aapc, by = c('stratifier', 'strata'))
-
-cleaned_preventive_df <- left_join(clean_age_adjusted, cleaned_jp_apc, by = c('stratifier', 'strata')) %>% 
+  left_join(cleaned_jp_aapc, by = c('stratifier', 'strata', 'variable'))
+
+cleaned_preventive_df <- left_join(clean_age_adjusted, cleaned_jp_apc, by = c('stratifier', 'strata', 'variable')) %>% 
   mutate(AAPC = case_when(is.na(AAPC) & is.na(`APC Period 2`) ~ `APC Period 1`,
@@
   group_by(stratifier) %>%
-  select(stratifier, ` ` = strata, `2008`:`2020`, `Percent Change (95% CI)`, `Joinpoint Year` = segment,
+  select(stratifier,` ` = strata, variable, `2008`:`2020`, `Percent Change (95% CI)`, `Joinpoint Year` = segment,
          `APC Period 1`, `APC Period 2`, `AAPC`) %>%
   mutate(stratifier = case_when(as.character(stratifier) == 'Poverty level' ~ 'Poverty income ratio',
-                                TRUE ~ as.character(stratifier))) %>% 
+                                TRUE ~ as.character(stratifier)),
+         variable = case_when(variable == "zero_services" ~ 'Zero services',
+                              variable == 'atleast_six_services' ~ 'All services')) %>% 
   # Rename some columns to add () info
-  rename(`2008 (SE)` = `2008`,
+  rename(`Number of services` = variable,
+         `2008 (SE)` = `2008`,
          `2009 (SE)` = `2009`,
@@
 # Reorganize insurance variables
-preventive_service_table$`_data` <- preventive_service_table$`_data`[c(1:14, 15, 18, 16, 17, 19:22), ]
+preventive_service_table$`_data` <- preventive_service_table$`_data`[c(1:28, 29, 32, 30, 31, 33, 36, 34, 35, 37:44), ]
 tab1 <- preventive_service_table$`_data`
@@
   # or a joinpoint (segment_end != 2019)
-  pivot_wider(id_cols = c(stratifier, strata, model),
+  pivot_wider(id_cols = c(stratifier, strata, service, model),
               names_from = segment,
@@
   # Join with AAPC table
-  left_join(cleaned_jp_aapc_sans_2020, by = c('stratifier', 'strata'))
-
-cleaned_preventive_df_sans_2020 <- left_join(clean_age_adjusted, cleaned_jp_apc_sans_2020, by = c('stratifier', 'strata')) %>% 
+  left_join(cleaned_jp_aapc_sans_2020, by = c('stratifier', 'strata', 'variable'))
+
+cleaned_preventive_df_sans_2020 <- left_join(clean_age_adjusted, cleaned_jp_apc_sans_2020, by = c('stratifier', 'strata', 'variable')) %>% 
   mutate(AAPC = case_when(is.na(AAPC) & is.na(`APC Period 2`) ~ `APC Period 1`,
@@
   group_by(stratifier) %>%
-  select(stratifier, ` ` = strata, `2008`:`2020`, `Percent Change (95% CI)`, `Joinpoint Year` = segment,
+  select(stratifier, ` ` = strata, variable, `2008`:`2020`, `Percent Change (95% CI)`, `Joinpoint Year` = segment,
          `APC Period 1`, `APC Period 2`, `AAPC`) %>%
 mutate(stratifier = case_when(as.character(stratifier) == 'Poverty level' ~ 'Poverty income ratio',
-                                TRUE ~ as.character(stratifier))) %>% 
+                                TRUE ~ as.character(stratifier)),
+         variable = case_when(variable == "zero_services" ~ 'Zero services',
+                              variable == 'atleast_six_services' ~ 'All services')) %>% 
   # Rename some columns to add () info
-  rename(`2008 (SE)` = `2008`,
+  rename(`Number of services` = variable,
+         `2008 (SE)` = `2008`,
          `2009 (SE)` = `2009`,
@@
     locations = cells_column_labels(
-      columns = c(`Percent Change (95% CI)`,
+      columns = c(
+      `Percent Change (95% CI)`,
       `APC Period 1 (95% CI)`,
@@
   ) %>% 
-  tab_options(footnotes.marks = "a")
+  tab_footnote(
+    footnote = "Years identified as Joinpoint years.",
+    locations = cells_column_labels(
+      columns = c(`Joinpoint Year`)
+    )
+  ) %>% 
+  tab_footnote(
+    footnote = 'Annual percent change: the slope of the line in each period demarcated by a Joinpoint year.
+If two Joinpoint years are identified, there will be three different annual percent changes.
+Joinpoint years are identified by permutation test, whereas the test of significance for APC is an asymptotic t-test.
+Due to the omnibus nature of the permutation test and the use of all the data in identifying the Joinpoints, the permutation tests are more powerful.
+In some cases, Joinpoint years are identified but the corresponding intervals for the APC will overlap zero due to this power difference.',
+    locations = cells_column_labels(
+      columns = c(`APC Period 1 (95% CI)`, `APC Period 2 (95% CI)`)
+    )
+  ) %>% 
+  tab_footnote(
+    footnote = 'Average annual percent change: the slope of the line over the entire study period.',
+    locations = cells_column_labels(
+      columns = c(`AAPC (95% CI)`)
+    )
+  ) %>% 
+  tab_footnote(
+    footnote = 'Percent change: the percent change in the proportion from 2008 to 2019.',
+    locations = cells_column_labels(
+      columns = c(`Percent Change (95% CI)`)
+    )
+  ) %>% 
+  tab_options(footnotes.marks = c("*", "†", "‡", "§", "||", "¶", "#", "**", "††", "‡‡"),
+              table.font.names = 'Times New Roman',
+              table.font.size = 12)
 # Reorganize insurance variables
- preventive_service_table_sans_2020$`_data` <- preventive_service_table_sans_2020$`_data`[c(1:14, 15, 18, 16, 17, 19:22), ]
+ preventive_service_table_sans_2020$`_data` <- preventive_service_table_sans_2020$`_data`[c(1:28, 29, 32, 30, 31, 33, 36, 34, 35, 37:44), ]
 
 tab_sans_2020 <- preventive_service_table_sans_2020$`_data`
-
+in_text_preventive_services_aggregate <- rename(tab_sans_2020,
+                                     num_services = `Number of services`,
+                                     stratifier_column = ` `,
+                                     apc_period_1_95_percent_ci = `APC Period 1 (95% CI)`,
+                                     apc_period_2_95_percent_ci = `APC Period 2 (95% CI)`,
+                                     aapc_95_percent_ci = `AAPC (95% CI)`)
 ```
@@
   ) %>% 
-  tab_options(footnotes.marks = "*",
+  tab_footnote(
+    footnote = "Years identified as Joinpoint years.",
+    locations = cells_column_labels(
+      columns = c(`Joinpoint Year`)
+    )
+  ) %>% 
+  tab_footnote(
+    footnote = 'Annual percent change: the slope of the line in each period demarcated by a Joinpoint year.
+If two Joinpoint years are identified, there will be three different annual percent changes.
+Joinpoint years are identified by permutation test, whereas the test of significance for APC is an asymptotic t-test.
+Due to the omnibus nature of the permutation test and the use of all the data in identifying the Joinpoints, the permutation tests are more powerful.
+In some cases, Joinpoint years are identified but the corresponding intervals for the APC will overlap zero due to this power difference.',
+    locations = cells_column_labels(
+      columns = c(`APC (95% CI)`)
+    )
+  ) %>% 
+  tab_footnote(
+    footnote = 'Average annual percent change: the slope of the line over the entire study period.',
+    locations = cells_column_labels(
+      columns = c(`AAPC (95% CI)`)
+    )
+  ) %>% 
+  tab_footnote(
+    footnote = 'Percent change: the percent change in the proportion from 2008 to 2019.',
+    locations = cells_column_labels(
+      columns = c(`Percent Change (95% CI)`)
+    )
+  ) %>% 
+  tab_options(footnotes.marks = c("*", "†", "‡", "§", "||", "¶", "#", "**", "††", "‡‡"),
               table.font.names = 'Times New Roman',
@@
 color_pal <- RColorBrewer::brewer.pal(n = 4, 'Set2')
+graphical_abstract_color_pal <- RColorBrewer::brewer.pal(n = 6, 'Set2')
+graphical_abstract_color_pal[6] <- '#806a0d'
 # Get the p for 2020 but remove the join point stuff so the line doesn't plot
@@
         width = 0.22,
-        height = 0.005
+        height = 0.005,
+        show.legend = FALSE
       ) +
@@
         aes(x = year, y = p, color = strata),
-        inherit.aes = FALSE
+        inherit.aes = FALSE,
+        show.legend = FALSE
       ) +
@@
         #color = 'black',
-        inherit.aes = FALSE
+        inherit.aes = FALSE,
+        show.legend = FALSE
       ) +
@@
         plot.caption = element_text(hjust = 0)) &
-  guides(color = guide_legend(ncol = 2)) 
+  guides(color = guide_legend(ncol = 2)) &
+  labs(y = '%')
 all_test_plots_sans_2020 <- test_plots_sans_2020 %>% 
@@
          plot.caption = element_text(hjust = 0)) &
-  guides(color = guide_legend(ncol = 2))
+  guides(color = guide_legend(ncol = 2)) &
+  labs(y = '%')
 ```
 
-```{r}
+```{r graphical-abstract, include = FALSE}
+graphical_abstract <- ggplot(
+  filter(overall_data, year != 2020),
+  aes(
+    x = year,
+    y = p,
+    group = variable_text,
+    color = variable_text
+  )
+) +
+  geom_line(show.legend = FALSE, linewidth = 0.1) +
+  geom_point(data = filter(overall_data,
+                           year == 2020),
+             show.legend = FALSE, size = 0.1) +
+  # geom_label_repel(
+  #   data = filter(overall_data,
+  #                 year == 2020),
+  #   aes(label = variable_text)
+  # ) +
+  theme_classic() +
+  scale_y_continuous(
+    limits = c(0, 100),
+    breaks = seq(0, 100, 25),
+    labels = seq(0, 100, 25),
+    sec.axis = dup_axis(
+      breaks = overall_data$p[overall_data$year == 2020] + c(6, 10, -10, -2, -6, 2),
+      labels = unique(overall_data$variable_text),
+      name = NULL
+    )
+  ) +
+  scale_x_continuous(
+    limits = c(2008, 2020),
+    breaks = seq(2008, 2020, 2),
+    labels = c(2008, "", 2012, "", 2016, "", 2020)
+  ) +
+  # I had to use ggrepel to figure out what order the colors needed to go in
+  # to match the colors on the secondary y-axis
+  scale_color_manual(
+    labels = c(
+      'Cholesterol tested' = 'Cholesterol tested',
+      'Two or more A1C tests' = 'Two or more A1c tests',
+      'Foot examination' = 'Foot examination',
+      'Dilated eye exam' = 'Dilated eye exam',
+      'Received influenza vaccine' = 'Received influenza vaccine',
+      'One or more dentist visits' = 'One or more dentist visits'
+    ),
+
+    values = c(
+      'Cholesterol tested' = graphical_abstract_color_pal[2],
+      'Two or more A1C tests' = graphical_abstract_color_pal[1],
+      'Foot examination' = graphical_abstract_color_pal[6],
+      'Dilated eye exam' = graphical_abstract_color_pal[4],
+      'Received influenza vaccine' = graphical_abstract_color_pal[5],
+      'One or more dentist visits' = graphical_abstract_color_pal[3]
+    )
+  ) +
+  theme(axis.text.y.left = element_text(color = 'black'),
+        axis.text.x = element_text(color = 'black'),
+        axis.line.y.right = element_blank(),
+        axis.ticks.y.right = element_blank(),
+        axis.text.y.right = element_text(margin = margin(0, 0, 0, 0),
+                                         color = graphical_abstract_color_pal),
+        legend.position = 'none',
+        plot.margin = margin(1, 5, 1, 1, unit = 'pt')) +
+  # labs(title = 'From 2008 to 2019, overall trends in the proportion of US adults with diabetes receiving six preventive services were stable, with the exception of an increase in the receipt of influenza vaccines.') +
+  labs(x = 'Year', y = '%')
+graphical_abstract_300dpi <- ggplot(
+  filter(overall_data, year != 2020),
+  aes(
+    x = year,
+    y = p,
+    group = variable_text,
+    color = variable_text
+  )
+) +
+  geom_line(show.legend = FALSE) +
+  geom_point(data = filter(overall_data,
+                           year == 2020),
+             show.legend = FALSE) +
+  # geom_label_repel(
+  #   data = filter(overall_data,
+  #                 year == 2020),
+  #   aes(label = variable_text)
+  # ) +
+  theme_classic() +
+  scale_y_continuous(
+    limits = c(0, 100),
+    breaks = seq(0, 100, 25),
+    labels = seq(0, 100, 25),
+    sec.axis = dup_axis(
+      breaks = overall_data$p[overall_data$year == 2020],
+      labels = unique(overall_data$variable_text),
+      name = NULL
+    )
+  ) +
+  scale_x_continuous(
+    limits = c(2008, 2020),
+    breaks = seq(2008, 2020, 2),
+    labels = c(2008, "", 2012, "", 2016, "", 2020)
+  ) +
+  # I had to use ggrepel to figure out what order the colors needed to go in
+  # to match the colors on the secondary y-axis
+  scale_color_manual(
+    labels = c(
+      'Cholesterol tested' = 'Cholesterol tested',
+      'Two or more A1C tests' = 'Two or more A1c tests',
+      'Foot examination' = 'Foot examination',
+      'Dilated eye exam' = 'Dilated eye exam',
+      'Received influenza vaccine' = 'Received influenza vaccine',
+      'One or more dentist visits' = 'One or more dentist visits'
+    ),
+
+    values = c(
+      'Cholesterol tested' = graphical_abstract_color_pal[2],
+      'Two or more A1C tests' = graphical_abstract_color_pal[1],
+      'Foot examination' = graphical_abstract_color_pal[6],
+      'Dilated eye exam' = graphical_abstract_color_pal[4],
+      'Received influenza vaccine' = graphical_abstract_color_pal[5],
+      'One or more dentist visits' = graphical_abstract_color_pal[3]
+    )
+  ) +
+  theme(axis.text.y.left = element_text(color = 'black'),
+        axis.text.x = element_text(color = 'black'),
+        axis.line.y.right = element_blank(),
+        axis.ticks.y.right = element_blank(),
+        axis.text.y.right = element_text(margin = margin(0, 0, 0, 0),
+                                         color = graphical_abstract_color_pal),
+        legend.position = 'none',
+        plot.margin = margin(1, 5, 1, 1, unit = 'pt')) +
+  # labs(title = 'From 2008 to 2019, overall trends in the proportion of US adults with diabetes receiving six preventive services were stable, with the exception of an increase in the receipt of influenza vaccines.') +
+  labs(x = 'Year', y = '%')
+```
+
+```{r save-tables-and-figs}
 #| include: false
@@
   gtsave('supplemental_table1.docx')
+preventive_service_table_sans_2020 %>% 
+  tab_header('Age-adjusted trends in proportions of U.S.
+adults with diagnosed diabetes, overall and by subgroup, who report receiving either none of six recommended care services or all six recommended care services—at least one dental visit, one dilated eye exam, one foot exam, two or more A1C tests, cholesterol level tested, and an influenza vaccine.') %>%
+  gtsave('supplemental_table2.docx')
 preventive_service_table %>%
@@
        filename = 'figures/figure1.tiff',
-       dpi = 1200,
-       width = 10,
-       height = 6)
+       dpi = 300,
+       width = 11.3,
+       height = 6.08)
 ggsave(plot = all_test_plots_sans_2020,
        filename = 'figures/figure2.tiff',
-       dpi = 1200,
-       width = 10,
-       height = 6)
+       dpi = 300,
+       width = 11.3,
+       height = 6.08)
+# Have to save this manually at 500 x 200 px
+(graphical_abstract <- graphical_abstract +
+  theme(plot.title = element_text(size = 8),
+        axis.text = element_text(size = 8),
+        axis.title = element_text(size = 8),
+        axis.line = element_line(linewidth = 0.1),
+        axis.ticks = element_line(linewidth = 0.1)))
+(graphical_abstract_300dpi <- graphical_abstract_300dpi +
+  theme(plot.title = element_text(size = 12),
+        axis.text = element_text(size = 10),
+        axis.title = element_text(size = 10)))
+ggsave(plot = graphical_abstract_300dpi,
+       filename = 'figures/graphical_abstract_300dpi.tiff',
+       dpi = 300,
+       width = 11.3,
+       height = 4.52)
+
 # ggsave(plot = all_exam_plots,
@@
 
-*Target Journal: Diabetes Care*
-
 **Trends in Preventive Care Services among U.S. Adults with Diagnosed Diabetes, 2008--2020**
@@
 
-Corresponding Author: Jacob T. Wittman, ugv4\@cdc.gov
+Corresponding Author: Jacob T. Wittman, ugv4\@cdc.gov, 770-488-3533
 
@@
 
-Twitter Summary: We report trends of six ADA recommended preventive care services 2008 –- 2020.
-Other than flu vaccination, we saw no improvement in receipt of preventive care services for US adults with diabetes.
-
-Word Count:
+Keywords: preventive services, Medical Expenditure Panel Survey, trends, joinpoint
+
+Word Count: 3213
 
@@
 
+Twitter Summary:
+
+We report trends of six recommended preventive care services from 2008 -- 2020. Other than flu vaccination, we saw no improvement in preventive care service utilization for US adults with diabetes.
+
+\pagebreak
+
 # Abstract (250 words, current 250)
@@
 **Objective:** Preventive care services are important to prevent or delay complications associated with diabetes.
-We reported trends in receipt of six American Diabetes Association recommended preventive care services during 2008 -- 2020.
+We reported trends in receipt of six American Diabetes Association recommended preventive care services during 2008--2020.
 
 **Research Design and Methods:** We used 2008--2020 data from the cross-sectional Medical Expenditures Panel Survey to calculate the proportion of U.S.
-adults ≥ 18 years of age with diagnosed diabetes that reported receiving preventive care services, overall and for subpopulations.
-We used Joinpoint regression to identify trends during 2008 -- 2019.
-The six services in the past year included at least one dental examination, a dilated eye examination, foot examination, ≥ 2 A1C tests, a cholesterol test, and receipt of an influenza vaccine.
+adults ≥18 years of age with diagnosed diabetes that reported receiving preventive care services, overall and by subpopulation (n = 25,616).
+We used Joinpoint regression to identify trends during 2008--2019.
+The six services completed in the past year included ≥1 dental examination, dilated eye examination, foot examination, ≥2 A1C tests, cholesterol test, and receipt of an influenza vaccine.
 
@@
 adults with diabetes receiving any individual preventive care service ranged from 32.6% to 89.9%.
-From 2008--2019, overall trends in preventive services among these adults were stable except for an increase in receipt of influenza vaccines (average annual percent change: `r pullNumber2(in_text_prop_tab_sans_2020, 'aapc_95_percent_ci', brackets = TRUE, CI = FALSE, stratifier_column == 'Overall', preventive_service == 'Received influenza vaccine')`).
-Trend analysis at the subgroup level was heterogeneous: influenza vaccination, A1C testing, and dental visits tended to improve while, among the uninsured, foot exams, cholesterol testing, and dental visits tended to decline.
-In 2020, 8.2% (4.5%, 11.9%) received none of the six recommended preventive care services.
-
-**Conclusions:** Other than influenza vaccination, we observed no improvement in receipt of preventive care services among U.S.
+From 2008--2019, overall trends in preventive services among these adults were flat except for an increase in influenza vaccination (average annual percent change: `r pullNumber2(in_text_prop_tab_sans_2020, 'aapc_95_percent_ci', brackets = TRUE, CI = TRUE, stratifier_column == 'Overall', preventive_service == 'Received influenza vaccine')`).
+Trend analysis of subgroups was heterogeneous: influenza vaccination and A1C testing showed improvements among several subgroups, while cholesterol testing (45-64 year age, \< high school education, Medicaid insurance) and dental visits (uninsured) declined.
+In 2020, 8.2% (4.5%, 11.9%) of those with diabetes received none of the recommended preventive care services.
+
+**Conclusions:** Other than influenza vaccination, we observed no improvement in preventive care service utilization among U.S.
 adults with diabetes.
@@
 
-# Article Highlights (75 - 100 words, current: 99)
+# Article Highlights (75 - 100 words, current: 92)
 
@@
 Diabetes is a chronic disease that affects 11.3% of the adult population, or 37.1 million adults, in the United States @nationalreport.
-Diabetes is also costly: total direct and indirect costs are estimated at \$327 billion @economic2018.
+Diabetes is also costly: total direct and indirect costs in 2017 were estimated at \$327 billion @economic2018.
 The prevalence of diabetes in the U.S.
@@
 
-Access to preventive services is important to minimize diabetes-related complications and reduce rates of hospitalization.
+Complications of diabetes include both microvascular (retinopathy, neuropathy, and diabetic nephropathy) and macrovascular complications (coronary artery disease, peripheral arterial disease, and stroke) [@ElSayed2023f; @fowler2008].
+Access to preventive services to control glycemia, lipids, and blood pressure and the early identification of diabetic retinopathy and foot lesions is important to minimize diabetes-related complications and reduce rates of hospitalization [@ElSayed2023f; @kent2013; @gregg2014].
 Other studies have reported on trends in receipt of some preventive services in the 2000s using data from various surveys, such as the Behavioral Risk Factor Surveillance System (BRFSS) and the National Health and Nutrition Examination Survey (NHANES) [@monnette2020; @luo2019; @shin2021; @fang2020; @eppley2019].
 To our knowledge, the proportion and trend of receipt of preventive services addressed in the Medical Expenditure Panel Survey (MEPS) has not been reported.
-We reported the proportion of and trends in the receipt of six preventive care services recommended by the American Diabetes Association (ADA) overall and among subgroups.
-These data are valuable for identifying groups that may be under-utilizing health care services, examining any effects the COVID-19 pandemic may have had on receipt of these services, and providing benchmarks for future studies.
+Analysis of MEPS data provides advantages over other surveys, as it is nationally representative and available yearly.
+Meanwhile, NHANES is not annual and has smaller sample sizes; BRFSS is administered at the state level, and the diabetes module is not available in every state in every year.
+We reported the proportion of and trends in the receipt of six preventive care services recommended by the American Diabetes Association (ADA) overall and among subgroups [@ElSayed2023f].
+These data are valuable for identifying groups that may be under-utilizing health care services, examining any effects the start of the COVID-19 pandemic may have had on receipt of these services, and providing benchmarks for future studies.
 
@@
 We used data from the 2008 -- 2020 MEPS, a household survey of U.S.
-noninstitutionalized populations administered and maintained by the Agency for Healthcare Research and Quality since 1996.
+noninstitutionalized populations administered and maintained by the Agency for Healthcare Research and Quality since 1996 [@MEPSdocumentation].
 The set of households surveyed for MEPS is a subsample of those surveyed in the National Health Interview Survey (NHIS).
-We chose the years 2008 to 2020 due to method changes in MEPS starting in 2008, and the consistency of questions related to preventive care during that time period.
+We chose the years 2008 to 2020 due to consistency of questions related to preventive care during that time period starting in 2008.
 Data from MEPS were collected through a combination of computer-assisted personal interviewing and pencil-and-paper surveys.
+In 2020, the computer-assisted personal interviews were changed from in-person to phone interviews due to the COVID-19 pandemic.
 MEPS provides national and regional estimates of health care use, expenditures, sources of payment and health insurance coverage.
 This survey also contains information on patient demographics, socioeconomic characteristics, and, via the Diabetes Care Survey (DCS), information on diabetes preventive care services.
-The DCS is a self-administered paper-and-pencil questionnaire that is provided to MEPS respondents who indicate that they have been told by a doctor or health care professional that they have diabetes.
-In this analysis, we used data from the full-year consolidated MEPS files with an average annual number of 32,170 individual respondents over the 13-year period and response rates from 59.3% in 2008 to 27.6% in 2020.
+The DCS is a self-administered paper-and-pencil questionnaire that is mailed to MEPS respondents who indicate that they have been told by a doctor or health care professional that they have diabetes.
+In this analysis, we used data from the full-year consolidated MEPS files for adults with diagnosed diabetes that responded to the DCS survey (*n =* 25,616).
+Response rates for the DCS survey ranged from 92.4% in 2008 to 57.1% in 2020.
 
@@
 Respondents were asked about receiving each of these services in a given year (e.g., "Did you receive an influenza vaccine in 2013?").
-We also created a binary variable classifying adults with diabetes who received none of the recommended preventive care services, although these results are presented only for the overall population due to small sample sizes in many of the examined subgroups.
+We also created binary variables classifying adults with diabetes who received none of the recommended preventive care services or all of the recommended services, although these results were presented only for the overall population due the unreliability of estimates of some sub-populations in some years [@parker2017national].
 
@@
 
-Our analysis accounts for the complex survey design used, including clustering and stratification.
+Our analysis accounts for the complex survey design used, including clustering and stratification, using the weights provided for the DCS [@MEPSdocumentation].
 Reported values were age-adjusted using the direct method, standardized to the 2000 U.S.
@@
 Medical care utilization decreased as a result of the COVID-19 pandemic starting in early 2020 @cantor2022.
-We reported the estimated proportions for 2020 in Table 1 and as points in @fig-exams and @fig-tests, but 2020 was excluded from trend analysis because of the decreased medical care utilization associated with the COVID-19 pandemic.
+We excluded 2020 from the trend analysis because of the decreased medical care utilization associated with the COVID-19 pandemic.
+However, we presented the estimated proportions for 2020 in the results to show how the onset of the pandemic affected the reported receipt of preventive services.
 Trends were analyzed using Joinpoint Command Line Software @joinpoint with R via the R package nih.joinpoint @nihjoinpoint.
@@
 Joinpoint regression uses permutation tests to detect statistically significant changes at a pre-specified alpha of 0.05 in direction or magnitude of trends @kim2000permutation.
-The Joinpoint software also provided estimates of the annual percent change (APC) for each trend segment and the average annual percent change (AAPC) for the entire trend.
+The Joinpoint software also provided estimates of the annual percent change (APC), or slope, for each trend segment and the average annual percent change (AAPC), or overall slope, for the entire trend.
+The test of significance for APC is an asymptotic t-test.
+Due to the omnibus nature of the permutation test used to identify Joinpoint years and the use of all the data in identifying those years, the permutation tests are more powerful [@kim2000permutation].
+In some cases, Joinpoint years are identified but the corresponding intervals for the APC will overlap zero due to this power difference.
 
@@
 All values pertaining to individual preventive practices presented here, as well as those that are not described, can be found in Supplemental Table 1.
+Figures 1 and 2 display trends, overall and by subgroup.
+
+## Dilated Eye Exam
+
+The overall proportion receiving dilated eye exams was stable during 2008--2019 (Table 1, Figure 1).
+This proportion averaged 55.5% (95% CI: 54.0%, 57.0%) over this period.
+Similarly, for males, we observed stable trends from 2008 to 2011 but a significant decrease after 2011 (APC `r pullNumber2(in_text_prop_tab_sans_2020, 'apc_period_2_95_percent_ci', brackets = TRUE, CI = FALSE, stratifier_column == 'Sex: Male', preventive_service == 'Dilated eye exam')`) (Figure 1).
+Uninsured adults with diabetes had average annual increase from 2008 to 2019 in the receipt of dilated eye exams of `r pullNumber2(in_text_prop_tab_sans_2020, 'aapc_95_percent_ci', brackets = FALSE, CI = FALSE, stratifier_column == 'Insurance coverage: Uninsured', preventive_service == 'Dilated eye exam')` (Figure 1).
+Adults with diabetes in the highest income group (poverty income ratio \> 400%) had a flat trend in dilated eye examinations until 2013, after which the proportion significantly decreased (APC `r pullNumber2(in_text_prop_tab_sans_2020, 'apc_period_2_95_percent_ci', brackets = TRUE, CI = FALSE, stratifier_column == 'Poverty income ratio: > 400%', preventive_service == 'Dilated eye exam')`).
+
+## Foot Exam
+
+The average proportion of U.S.
+adults with diabetes receiving a foot exam over the study period was 61.4% (95% CI: 60.0%, 62.8%) (Table 1).
+The trend for foot exams for the overall adult population with diabetes was flat until 2011, after which it decreased (APC `r pullNumber2(in_text_prop_tab_sans_2020, 'apc_period_2_95_percent_ci', brackets = TRUE, CI = FALSE, stratifier_column == 'Overall', preventive_service == 'Foot examination')`, Table 1, Figure 1).
+We found an increase in foot exams among adults with diabetes age 65--74 years until 2014 (APC `r pullNumber2(in_text_prop_tab_sans_2020, 'apc_period_1_95_percent_ci', brackets = TRUE, CI = FALSE, stratifier_column == 'Age: 65 to 74', preventive_service == 'Foot examination')`), and the trend was flat thereafter (Figure 1).
+
+## One or More Dentist Visits
+
+The trend for dentist visits for the overall adult population with diabetes was stable over the study period, averaging 35.7% (34.2%, 37.2%) (Table 1).
+Adults age 65--74 and ≥75 years had average annual percent increases of `r pullNumber2(in_text_prop_tab_sans_2020, 'aapc_95_percent_ci', brackets = FALSE, CI = FALSE, stratifier_column == 'Age: 65 to 74', preventive_service == 'One or more dentist visits')` and `r pullNumber2(in_text_prop_tab_sans_2020, 'apc_period_1_95_percent_ci', brackets = FALSE, CI = FALSE, stratifier_column == 'Age: 75+', preventive_service == 'One or more dentist visits')`, respectively.
+Non-Hispanic White adults with diabetes had an average annual percent increase of `r pullNumber2(in_text_prop_tab_sans_2020, 'aapc_95_percent_ci', brackets = FALSE, CI = FALSE, stratifier_column == 'Race/Ethnicity: White/not Hispanic', preventive_service == 'One or more dentist visits')`.
+Among those with private insurance, we found decreasing proportions visiting the dentist during 2008--2015 (APC `r pullNumber2(in_text_prop_tab_sans_2020, 'apc_period_1_95_percent_ci', brackets = TRUE, CI = FALSE, stratifier_column == 'Insurance coverage: Private only', preventive_service == 'One or more dentist visits')`), followed by an increase after 2015 (APC `r pullNumber2(in_text_prop_tab_sans_2020, 'apc_period_2_95_percent_ci', brackets = TRUE, CI = FALSE, stratifier_column == 'Insurance coverage: Private only', preventive_service == 'One or more dentist visits')`.
+The trends for adults with diabetes in the poverty income ratio group \< 100% and those with a high school education had multiple changes upward and downward during the study period.
 
@@
 
-From 2008 to 2019, receipt of influenza vaccines increased at an AAPC of `r pullNumber2(in_text_prop_tab_sans_2020, 'aapc_95_percent_ci', brackets = FALSE, CI = FALSE, stratifier_column == 'Overall', preventive_service == 'Received influenza vaccine')`.
+From 2008 to 2019, receipt of influenza vaccines increased at an AAPC of `r pullNumber2(in_text_prop_tab_sans_2020, 'aapc_95_percent_ci', brackets = FALSE, CI = FALSE, stratifier_column == 'Overall', preventive_service == 'Received influenza vaccine')` (Table 1, Figure 2).
 The average proportion of adults with diabetes receiving an influenza vaccine over the study period was 41.8% (39.6%, 44.0%).
@@
 
-## One or More Dentist Visits
-
-The trend for dentist visits for the overall adult population with diabetes was stable over the study period, averaging 35.7% (34.2%, 37.2%) (Table 1).
-Adults age 65--74 and ≥75 years had average annual percent increases of `r pullNumber2(in_text_prop_tab_sans_2020, 'aapc_95_percent_ci', brackets = FALSE, CI = FALSE, stratifier_column == 'Age: 65 to 74', preventive_service == 'One or more dentist visits')` and `r pullNumber2(in_text_prop_tab_sans_2020, 'apc_period_1_95_percent_ci', brackets = FALSE, CI = FALSE, stratifier_column == 'Age: 75+', preventive_service == 'One or more dentist visits')`, respectively.
-Non-Hispanic White adults with diabetes had an average annual percent increase of `r pullNumber2(in_text_prop_tab_sans_2020, 'aapc_95_percent_ci', brackets = FALSE, CI = FALSE, stratifier_column == 'Race/Ethnicity: White/not Hispanic', preventive_service == 'One or more dentist visits')`.
-Among those with private insurance, we found decreasing proportions visiting the dentist during 2008--2015 (APC `r pullNumber2(in_text_prop_tab_sans_2020, 'apc_period_1_95_percent_ci', brackets = TRUE, CI = FALSE, stratifier_column == 'Insurance coverage: Private only', preventive_service == 'One or more dentist visits')`), followed by an increase after 2015 (APC `r pullNumber2(in_text_prop_tab_sans_2020, 'apc_period_2_95_percent_ci', brackets = TRUE, CI = FALSE, stratifier_column == 'Insurance coverage: Private only', preventive_service == 'One or more dentist visits')`.
-The trends for adults with diabetes in the poverty income ratio group \< 100% and those with a high school education had multiple changes upward and downward during the study period.
-
 ## A1C Tests
@@
 
-## Dilated Eye Exam
-
-The overall proportion receiving dilated eye exams was stable during 2008--2019 (Table 1).
-This proportion averaged 55.5% (95% CI: 54.0%, 57.0%) over this period.
-Similarly, for males, we observed stable trends from 2008 to 2011 but a significant decrease after 2011 (APC `r pullNumber2(in_text_prop_tab_sans_2020, 'apc_period_2_95_percent_ci', brackets = FALSE, CI = FALSE, stratifier_column == 'Sex: Male', preventive_service == 'Dilated eye exam')`).
-Uninsured adults with diabetes had average annual increase from 2008 to 2019 in the receipt of dilated eye exams of `r pullNumber2(in_text_prop_tab_sans_2020, 'aapc_95_percent_ci', brackets = FALSE, CI = FALSE, stratifier_column == 'Insurance coverage: Uninsured', preventive_service == 'Dilated eye exam')`.
-Adults with diabetes in the highest income group (poverty income ratio \> 400%) had a flat trend in dilated eye examinations until 2013, after which the proportion significantly decreased (APC `r pullNumber2(in_text_prop_tab_sans_2020, 'apc_period_2_95_percent_ci', brackets = TRUE, CI = FALSE, stratifier_column == 'Poverty income ratio: > 400%', preventive_service == 'Dilated eye exam')`).
-
-## Foot Exam
-
-The average proportion of U.S.
-adults with diabetes receiving a foot exam over the study period was 61.4% (95% CI: 60.0%, 62.8%).
-The trend for foot exams for the overall adult population with diabetes was flat until 2011, after which it decreased (APC `r pullNumber2(in_text_prop_tab_sans_2020, 'apc_period_2_95_percent_ci', brackets = TRUE, CI = FALSE, stratifier_column == 'Overall', preventive_service == 'Foot examination')`, Table 1).
-We found an increase in foot exams among adults with diabetes age 65--74 years until 2014 (APC `r pullNumber2(in_text_prop_tab_sans_2020, 'apc_period_1_95_percent_ci', brackets = TRUE, CI = FALSE, stratifier_column == 'Age: 65 to 74', preventive_service == 'Foot examination')`), and the trend was flat thereafter.
-
-## Absence of Preventive Care Services
-
-In 2008, 5.1% (95% CI: 2.7%, 7.5%) of adults with diabetes reported receiving none of the six recommended care services.
-In 2019, this estimate was 6.1% (3.7%, 8.5%) and in 2020 it was 8.2% (4.5%, 11.9%).
+## Aggregate Preventive Care Services
+
+For both adults with diabetes that reported receiving none of the six recommended preventive services and adults reporting receiving all of them, trends were flat from 2008 to 2019 (zero services: `r pullNumber2(in_text_preventive_services_aggregate, 'aapc_95_percent_ci', brackets = TRUE, CI = TRUE, stratifier_column == '-', num_services == 'Zero services')`; all services: `r pullNumber2(in_text_preventive_services_aggregate, 'aapc_95_percent_ci', brackets = TRUE, CI = FALSE, stratifier_column == '-', num_services == 'All services')`; Supplemental Table 2).
+In 2008, 5.1% (2.7%, 7.5%) of adults with diabetes reported receiving none of the six recommended care services (Supplemental Table 2).
+In 2019, this estimate was 6.1% (3.7%, 8.5%) and in 2020 it was 8.2% (4.5%, 11.9%; Supplemental Table 2).
+The percentage of adults that reported receiving all six preventive services in 2008 was 7.1% (4.5%, 9.6%), 10.8% (7.4%, 14.1%) in 2019 and 7.9% (5.3%, 10.5%) in 2020 (Supplemental Table 2).
 
@@
 
+Influenza vaccination was the only preventive service that increased significantly during 2008--2019 overall.
+Among most subgroups, influenza vaccine uptake, A1C testing, and dental visits tended to improve.
+However, foot exams, cholesterol testing, and dental visits among the uninsured tended to decline.
 The passing of the Affordable Care Act (ACA) in 2010 and subsequent Medicaid expansion has been seen as a mechanism to increase the receipt of preventive services [@luo2019]; however, we found no significant change over time in five out of the six preventive care services for the overall U.S.
 adult population with diagnosed diabetes from 2008 to 2019.
-Influenza vaccination was the only preventive service that increased significantly during 2008--2019 overall.
-Among subgroups, influenza vaccine uptake, A1C testing, and dental visits tended to improve.
-However, foot exams, cholesterol testing, and dental visits among the uninsured tended to decline.
-While the passing of the ACA led to an increase in the number of adults with diagnosed and undiagnosed diabetes who have health insurance, and an increase in their use of health care services [@myerson2019; @simon2017], detecting corresponding increases in the receipt of preventive care has proved more elusive.
-As of 2019, 6.1% of adults with diabetes had not received any of the six preventive services, and this percentage grew to 8.2% in 2020 during the onset of the COVID-19 pandemic.
+While the passing of the ACA led to an increase in the number of adults with diagnosed and undiagnosed diabetes who have health insurance, and an increase in their access to health care [@myerson2019; @simon2017], detecting corresponding increases in the receipt of preventive care has proved more elusive.
+As of 2019, 6.1% of adults with diabetes had not received any of the six preventive services, and this percentage was 8.2% in 2020 during the onset of the COVID-19 pandemic.
+Continued monitoring will help to understand the extent to which the pandemic interrupted preventive care service utilization.
 
@@
 A1C testing and influenza vaccinations were the only two preventive services that showed increases either among the overall population or various subgroups which may be linked with the increase in health care service usage [@myerson2019].
-A1C increased among: adults age 45 -- 65, 65 -- 74, > 75 years, Hispanic adults, non-Hispanic White adults, adults on Medicare only, and adults in the > 400% poverty income ratio group.
-Influenza vaccine increased among: non-Hispanic White adults, adult females, adult males, adults in the 200% -- 399% poverty income ratio group, and adults in the > 400% poverty income ratio group.
+A1C increased among: adults age 45 -- 65, 65 -- 74, \> 75 years, Hispanic adults, non-Hispanic White adults, adults on Medicare only, and adults in the \> 400% poverty income ratio group.
+Influenza vaccination increased among: non-Hispanic White adults, adult females, adult males, adults in the 200% -- 399% poverty income ratio group, and adults in the \> 400% poverty income ratio group.
 These services can be administered at the point-of-care during regular physician visits, whereas a dilated eye exam or dental visit require separate appointments.
@@
 Other studies on trends in preventive care using different data sources report some conflicting findings.
-A study using NHANES data from 2005 to 2018 found increases in the proportion of adults with diabetes who reported: having a primary care doctor, receiving an annual check-up with a physician, having had at least two A1C tests in a year, having their cholesterol levels tested, and having an annual foot exam by a doctor @shin2021.
-Another study that reported on data from NHANES, NHIS, and BRFSS found that foot exams, influenza vaccinations, and A1C testing increased from 1999 to 2016, although dilated eye exams stayed roughly constant @fang2020.
+A study using NHANES data from 2005 to 2018 found increases in the proportion of adults with diabetes who reported all of the following: having a primary care doctor, receiving an annual check-up with a physician, having had at least two A1C tests in a year, having their cholesterol levels tested, and having an annual foot exam by a doctor [@shin2021].
+However, when evaluated individually, only A1C testing increased, which is similar to our findings.
+Another study that reported on data from NHANES, NHIS, and BRFSS found that foot exams, influenza vaccinations, and two or more A1C tests in a year increased from 1999 to 2016, although dilated eye exams stayed roughly constant @fang2020.
 Data from BRFSS showed that adults with diabetes had reported decreasing dentist visits from 2004 to 2014 [@luo2018], while patient-reported dilated eye examinations increased briefly following Medicaid expansion in 2014 and then decreased [@chen2020].
@@
 A study using NHIS data reported no change in influenza vaccination rates from 2007 to 2018 for the overall population of adults with diabetes [@hung2020].
-Differences in these survey results may be due to differences in how questions are phrased and differences in the population being surveyed.
-Additionally, it is difficult to compare trends for overlapping time periods of different lengths, so caution should be used when interpreting these differences; when possible, trends should be compared over similar, longer time periods [@cusser2021; @bahlai2021].
+Our finding that A1C testing increased is consistent with what has been reported in other studies.
+Discrepancies with other survey results may be due to differences in how questions are phrased, differences in the population being surveyed and trend analysis of time periods of different length.
+Caution should be used when interpreting these differences; when possible, trends should be compared over similar and longer time periods [@cusser2021; @bahlai2021].
 
@@
 We are unable to identify factors that are causally linked to the changes in trends.
-Additionally, there has been a steadily declining response rate for both MEPS and DCS from a peak during the studied time period from 59.3% and 92.4%, respectively in 2008 to 39.5% and 65.8%, respectively, in 2019 and 27.6% and 59.3%, respectively in 2020.
+Additionally, there has been a steadily declining response rate for both MEPS and DCS.
+During the studied time period both MEPS and DCS response rates peaked in 2008 at 59.3% and 92.4%, respectively, fell to 39.5% and 65.8%, respectively, in 2019, and fell further to 27.6% and 57.1%, respectively, in 2020.
 Although weights for these data were adjusted for non-response, the direction of bias due to non-response cannot be known.
@@
 #| tbl-cap: Age-adjusted trends in proportions of U.S.
-adults with diabetes who report receiving at least three of six recommended care services—at least one dental visit, one dilated eye exam, one foot exam, two or more A1C tests, cholesterol level tested, and an influenza vaccine.
+adults with diagnosed diabetes who report receiving at least three of six recommended care services—at least one dental visit, one dilated eye exam, one foot exam, two or more A1C tests, cholesterol level tested, and an influenza vaccine.
 
@@
   tab_header("Table 1—Age-adjusted trends in proportions of U.S.
-adults with diabetes that report receiving recommended care services - at least one dental visit, one dilated eye exam, one foot exam, two or more A1C tests, cholesterol level tested, and receiving an influenza vaccine.")
+adults with diagnosed diabetes that report receiving recommended care services - at least one dental visit, one dilated eye exam, one foot exam, two or more A1C tests, cholesterol level tested, and receiving an influenza vaccine.")
 ```
@@
 #| fig-cap: Age-adjusted trends in proportions of U.S.
-adults with diabetes who reported receiving recommended medical examinations from 2008 to 2019.
+adults with diagnosed diabetes overall and by subgroup who reported receiving recommended medical examinations from 2008 to 2019.
 The dashed black line is the overall trend, while dots represent percentages for 2020.
@@
 #| fig-cap: Age-adjusted trends in proportions of U.S.
-adults with diabetes who reported receiving recommended lab tests and vaccinations.
+adults with diagnosed diabetes overall and by subgroup who reported receiving recommended lab tests and vaccinations.
 The dashed black line is the overall trend, while dots represent percentages for 2020.
@@
 
-Figure 1—Age-adjusted trends in proportions of U.S.
-adults with diabetes who reported receiving recommended medical examinations from 2008 to 2019.
+Figure 1---Age-adjusted trends in proportions of U.S.
+adults with diagnosed diabetes overall and by subgroup who reported receiving recommended medical examinations from 2008 to 2019.
 The dashed black line is the overall trend, while dots represent percentages for 2020.
@@
 
-Figure 2—Age-adjusted trends in proportions of U.S.
-adults with diabetes who reported receiving recommended lab tests and vaccinations.
+Figure 2---Age-adjusted trends in proportions of U.S.
+adults with diagnosed diabetes overall and by subgroup who reported receiving recommended lab tests and vaccinations.
 The dashed black line is the overall trend, while dots represent percentages for 2020.
@@
   tab_header('Age-adjusted trends in proportions of U.S.
-adults with diabetes, overall and by subgroup, who report receiving six recommended care services—at least one dental visit, one dilated eye exam, one foot exam, two or more A1C tests, cholesterol level tested, and an influenza vaccine.')
+adults with diagnosed diabetes, overall and by subgroup, who report receiving six recommended care services—at least one dental visit, one dilated eye exam, one foot exam, two or more A1C tests, cholesterol level tested, and an influenza vaccine.')
 ```
@@
 ```{r}
-#| include: false
-#| echo: false
-# Create plots with actual proportions and standard errors
-supp_dat <- age_adjusted_stats %>%
-      filter(strata != 'Total') %>%
-      filter(stratifier != 'overall') %>% 
-      filter(strata != 'Not available') %>%
-      filter(strata != 'Other Race/not Hispanic') %>%
-      filter(strata != 'Other') %>% 
-      mutate(variable_text = case_when(variable == 'a1c' ~ '2 or more A1C tests',
-                                       variable == 'CHOL_all' ~ 'Cholesterol tested',
-                                       variable == 'DENT_all' ~ '1 or more dentist visits',
-                                       variable == 'eye-exam' ~ 'Dilated eye exam',
-                                       variable == 'flu' ~ 'Received influenza vaccine',
-                                       variable == 'foot' ~ 'Foot examination'),
-             strata = case_when(strata == 'stat_0' ~ 'Overall',
-                                TRUE ~ strata)) %>%
-      mutate(strata = as.factor(strata),
-             year_adj = year - 2007) %>%  
-  mutate(strata = as.factor(strata)) %>% 
-  split(., f = .$stratifier)
-
-supp_dat <- map(supp_dat, function(.x) {
-  .x %>% 
-    mutate(strata = fct_drop(strata))
-})
-
-supp_dat$poverty$strata <-
-  factor(
-    supp_dat$poverty$strata,
-    levels = c('Poor/Negative', 'Low income', 'Middle income', 'High income'), 
-    labels = c(
-      'd< 100%',
-      'c100%—199%',
-      'b200%—399%',
-      'a> 400% '
-    ),
-    ordered = TRUE
-  )
-
-supplemental_test_plots <-
-  map(
-    supp_dat,
-    ~ ggplot(
-      filter(.x, variable %in% c('a1c', 'CHOL_all', 'flu')),
-      aes(
-        x = year,
-        y = p,
-        group = strata,
-        color = strata
-      )
-    ) +
-      geom_point() +
-      geom_errorbar(
-        aes(ymin = p - 1.96 * (p.std.error * 100),
-            ymax = p + 1.96 * (p.std.error * 100))
-      ) +
-      facet_wrap(~ variable_text, ncol = 3, scales = 'free_y') +
-      theme_classic() +
-      scale_x_continuous(
-        limits = c(2007.5, 2020.5),
-        breaks = seq(2008, 2020, 2),
-        labels = c(2008, "", 2012, "", 2016, "", 2020)
-      ) +
-      theme(
-        axis.text = element_text(color = 'black'),
-        #axis.text.x = element_text(angle = 45, hjust = 0.9, vjust = 0.95),
-        legend.title = element_text(size = 11),
-        legend.text = element_text(size = 9)
-      ) +
-      labs(x = 'Year', y = 'Percentage')
-
-  )
-
-supplemental_exam_plots <-
-  map(
-    supp_dat,
-    ~ ggplot(
-      filter(.x, variable %!in% c('a1c', 'CHOL_all', 'flu')),
-      aes(
-        x = year,
-        y = p,
-        group = strata,
-        color = strata
-      )
-    ) +
-      geom_point() +
-      geom_errorbar(
-        aes(ymin = p - 1.96 * (p.std.error * 100),
-            ymax = p + 1.96 * (p.std.error * 100))
-      ) +
-      facet_wrap(~ variable_text, ncol = 3, scales = 'free_y') +
-      theme_classic() +
-      scale_x_continuous(
-        limits = c(2007.5, 2020.5),
-        breaks = seq(2008, 2020, 2),
-        labels = c(2008, "", 2012, "", 2016, "", 2020)
-      ) +
-      theme(
-        axis.text = element_text(color = 'black'),
-        #axis.text.x = element_text(angle = 45, hjust = 0.9, vjust = 0.95),
-        legend.title = element_text(size = 11),
-        legend.text = element_text(size = 9)
-      ) +
-      labs(x = 'Year', y = 'Percentage')
-
-  )
-
-supplemental_test_plots[[1]] <-
-  supplemental_test_plots[[1]] +
-  theme(axis.title.x = element_blank()) +
-  scale_color_manual(
-    name = 'Age (grouped)',
-    values = c(
-     '18 to 44' = color_pal[1],
-     '45 to 64'  = color_pal[2],
-     '65 to 74' = color_pal[3],
-     '75+' = color_pal[4]
-    ),
-    labels = c('18 to 44' = '18 to 44',
-               '45 to 64' = '45 to 64',
-               '65 to 74' = '65 to 74',
-               '75+'      = '75+')
-  )
-
-supplemental_test_plots[[2]] <-
-  supplemental_test_plots[[2]] +
-  theme(
-    strip.background =  element_blank(),
-    strip.text = element_blank(),
-    axis.title.x = element_blank()
-  ) +
-  scale_color_manual(
-    name = 'Highest degree obtained',
-    labels = c('Greater than HS'       = 'Greater than HS',
-               'High school'           = 'High school',
-               'Less than high school' = 'Less than HS'),
-    values = c(
-     'Greater than HS' = color_pal[1],
-     'High school' = color_pal[2],
-     'Less than high school'  = color_pal[3]
-    )
-  )
-
-supplemental_test_plots[[3]] <-
-  supplemental_test_plots[[3]] +
-  theme(
-    strip.background =  element_blank(),
-    strip.text = element_blank(),
-    axis.title.x = element_blank()
-  ) +
-  scale_color_manual(
-    name = 'Insurance',
-    values = c(
-      'Medicaid' = color_pal[1],
-      'Medicare only' = color_pal[2],
-      'Private only' = color_pal[3],
-      'Uninsured' = color_pal[4]
-    ),   labels = c(
-      'Medicaid'      = 'Medicaid',
-      'Medicare only' = 'Medicare only',
-      'Private only'  = 'Private only',
-      'Uninsured'     = 'Uninsured'
-    )
-  )
-
-supplemental_test_plots[[4]] <-
-  supplemental_test_plots[[4]] +
-  theme(strip.background =  element_blank(),
-        strip.text = element_blank()) +
-  scale_color_manual(
-    name = 'Poverty income ratio',
-    labels = c('a> 400% '     = '> 400%',
-               'b200%—399%' = '200%—399%',
-               'c100%—199%' = '100%—199%',
-               'd< 100%'      = '< 100%'),
-
-    values = c(
-      'a> 400% ' = color_pal[1],
-      'b200%—399%' = color_pal[2],
-      'c100%—199%' = color_pal[3],
-      'd< 100%' = color_pal[4]
-    )
-  )
-
-supplemental_test_plots[[5]] <-
-  supplemental_test_plots[[5]] + theme(
-    strip.background =  element_blank(),
-    strip.text = element_blank(),
-    axis.title.x = element_blank()
-  ) +
-  scale_color_manual(
-    name = 'Race & Ethnicity',
-    labels = c(
-     'Asian/not Hispanic' = 'Asian/not Hispanic',
-     'Black/not Hispanic' = 'Black/not Hispanic',
-     'Hispanic'           = 'Hispanic',
-     'White/not Hispanic' = 'White/not Hispanic'
-    ),
-    values = c(
-     'Asian/not Hispanic' = color_pal[1],
-     'Black/not Hispanic'  = color_pal[2],
-     'Hispanic' = color_pal[3],
-     'White/not Hispanic' = color_pal[4]
-    )
-  )
-supplemental_test_plots[[6]] <-
-  supplemental_test_plots[[6]] +
-  theme(
-    strip.background =  element_blank(),
-    strip.text = element_blank(),
-    axis.title.x = element_blank()
-  ) +
-  scale_color_manual(
-    name = 'Sex',
-    labels = c('Female'  = 'Female',
-               'Male'    = 'Male'),
-    values = c(
-     'Female' = color_pal[1],
-     'Male'  = color_pal[2]
-    )
-  ) 
-supplemental_test_plots <- list(
-  supplemental_test_plots[[1]],
-  supplemental_test_plots[[6]],
-  supplemental_test_plots[[5]],
-  supplemental_test_plots[[2]],
-  supplemental_test_plots[[3]],
-  supplemental_test_plots[[4]]
-)
-
-# Set up legends on all plots
-supplemental_exam_plots[[1]] <- supplemental_exam_plots[[1]] +
-  theme(axis.title.x = element_blank()) +
-  scale_color_manual(
-    name = 'Age (grouped)',
-    labels = c('18 to 44' = '18 to 44',
-               '45 to 64' = '45 to 64',
-               '65 to 74' = '65 to 74',
-               '75+'      = '75+'),
-    values =   c(
-      '18 to 44' = color_pal[1],
-      '45 to 64' = color_pal[2],
-      '65 to 74' = color_pal[3],
-      '75+'      = color_pal[4]
-    )
-  )
-
-supplemental_exam_plots[[2]] <-
-  supplemental_exam_plots[[2]] +
-  theme(
-    strip.background =  element_blank(),
-    strip.text = element_blank(),
-    axis.title.x = element_blank()
-  ) +
-  scale_color_manual(
-    name = 'Highest degree obtained',
-    labels = c('Greater than HS'       = 'Greater than HS',
-               'High school'           = 'High school',
-               'Less than high school' = 'Less than HS'),
-        values = c(
-      'Greater than HS'       = color_pal[1],
-      'High school'           = color_pal[2],
-      'Less than high school' = color_pal[3]
-    )
-  )
-
-supplemental_exam_plots[[3]] <-
-  supplemental_exam_plots[[3]] +
-  theme(
-    strip.background =  element_blank(),
-    strip.text = element_blank(),
-    axis.title.x = element_blank()
-  ) +
-  scale_color_manual(
-    name = 'Insurance',
-    labels = c(
-     'Medicaid'      =  'Medicaid',
-     'Medicare only' =  'Medicare only',
-     'Private only'  =  'Private only',
-     'Uninsured'     =  'Uninsured'
-    ),
-    values = c(
-      'Medicaid'      = color_pal[1],
-      'Medicare only' = color_pal[2],
-      'Private only'  = color_pal[3],
-      'Uninsured'     = color_pal[4]
-    )
-  )
-
-supplemental_exam_plots[[4]] <-
-  supplemental_exam_plots[[4]] +
-  theme(strip.background =  element_blank(),
-        strip.text = element_blank()) +
-  scale_color_manual(
-    name = 'Poverty income ratio',
-    labels = c('a> 400% '     = '> 400%',
-               'b200%—399%' = '200%—399%',
-               'c100%—199%' = '100%—199%',
-               'd< 100%'      = '< 100%'),
-    values = c(
-      'a> 400% '     = color_pal[1],
-      'b200%—399%' = color_pal[2],
-      'c100%—199%' = color_pal[3],
-      'd< 100%'      = color_pal[4]
-    )
-  )
-
-supplemental_exam_plots[[5]] <-
-  supplemental_exam_plots[[5]] +
-  theme(
-    strip.background =  element_blank(),
-    strip.text = element_blank(),
-    axis.title.x = element_blank()
-  ) +
-  scale_color_manual(
-    name = 'Race & Ethnicity',
-    labels = c(
-      'Asian/not Hispanic' = 'Asian/not Hispanic',
-      'Black/not Hispanic' = 'Black/not Hispanic',
-      'Hispanic'           = 'Hispanic',
-      'White/not Hispanic' = 'White/not Hispanic'
-    ),
-    values = c(
-      'Asian/not Hispanic' = color_pal[1],
-      'Black/not Hispanic' = color_pal[2],
-      'Hispanic'           = color_pal[3],
-      'White/not Hispanic' = color_pal[4]
-    )
-  )
-
-supplemental_exam_plots[[6]] <-
-  supplemental_exam_plots[[6]] +
-  theme(
-    strip.background =  element_blank(),
-    strip.text = element_blank(),
-    axis.title.x = element_blank()
-  ) +
-  scale_color_manual(
-    name = 'Sex',
-    labels = c('Female'  = 'Female',
-               'Male'    = 'Male'),
-    values = c(
-      'Female' = color_pal[1],
-      'Male'  = color_pal[2]
-    )
-  )
-
-supplemental_exam_plots <- list(
-  supplemental_exam_plots[[1]],
-  supplemental_exam_plots[[6]],
-  supplemental_exam_plots[[5]],
-  supplemental_exam_plots[[2]],
-  supplemental_exam_plots[[3]],
-  supplemental_exam_plots[[4]]
-)
-
-supplemental_all_exam <- supplemental_exam_plots %>% 
-  wrap_plots(nrow = 6) &
-  theme(plot.margin = margin(0.5, 0.5, 0.5, 0.5, 'pt'),
-        legend.justification = 'left',
-        plot.caption = element_text(hjust = 0)) &
-  guides(color = guide_legend(ncol = 2)) 
-supplemental_all_test <- supplemental_test_plots %>% 
-  wrap_plots(nrow = 6) &
-  theme(plot.margin = margin(0.5, 0.5, 0.5, 0.5, 'pt'),
-        legend.justification = 'left',
-         plot.caption = element_text(hjust = 0)) &
-  guides(color = guide_legend(ncol = 2))
-
-ggsave(plot = supplemental_all_exam,
-       filename = 'figures/supp_exam_plots.tiff',
-       dpi = 1200,
-       width = 10,
-       height = 6)
-ggsave(plot = supplemental_all_test,
-       filename = 'figures/supp_test_plots.tiff',
-       dpi = 1200,
-       width = 10,
-       height = 6)
-```
-
-```{r}
-#| include: FALSE
-#| fig-cap: Age-adjusted proportions with 95% confidence intervals of U.S. adults with diabetes who reported receiving recommended medical examinations from 2008 - 2020. 
-supplemental_all_exam
-```
-
-```{r}
-#| include: FALSE
-#| fig-cap: Age-adjusted proportions with 95% confidence intervals of U.S. adults with diabetes who reported receiving recommended lab tests and vaccinations from 2008 - 2020.
-supplemental_all_test
+preventive_service_table_sans_2020 %>% 
+  tab_header('Age-adjusted trends in proportions of U.S.
+adults with diagnosed diabetes, overall and by subgroup, who report receiving either none of six recommended care services or all six recommended care services—at least one dental visit, one dilated eye exam, one foot exam, two or more A1C tests, cholesterol level tested, and an influenza vaccine.')
 ```

### 2023-08-31 _targets.R

@@ -848,7 +848,7 @@ list(
       .x$aapc
     }) %>%
       bind_rows(.id = 'group.service') %>%
-      filter(str_detect(group.service, 'atleast_three')) %>%
+      filter(str_detect(group.service, 'zero_services') | str_detect(group.service, 'atleast_six_services')) %>%
       separate(group.service, c('stratifier', 'service'), sep = '[.]') %>%
       mutate(strata = case_when(stratifier == 'overall' ~ 'stat_0',
                                 TRUE ~ strata)) %>%
@@ -875,7 +875,7 @@ tar_target(
     .x$apc
   }) %>%
     bind_rows(.id = 'group.service') %>%
-    filter(str_detect(group.service, 'atleast_three')) %>%
+    filter(str_detect(group.service, 'zero_services') | str_detect(group.service, 'atleast_six_services')) %>%
     separate(group.service, c('stratifier', 'service'), sep = '[.]') %>%
     mutate(strata = case_when(stratifier == 'overall' ~ 'stat_0',
                               TRUE ~ strata)) %>%
@@ -984,7 +984,7 @@ tar_target(
     .x$aapc
   }) %>%
     bind_rows(.id = 'group.service') %>%
-    filter(str_detect(group.service, 'atleast_three')) %>%
+    filter(str_detect(group.service, 'zero_services') | str_detect(group.service, 'atleast_six_services')) %>%
     separate(group.service, c('stratifier', 'service'), sep = '[.]') %>%
     mutate(strata = case_when(stratifier == 'overall' ~ 'stat_0',
                               TRUE ~ strata)) %>%
@@ -1011,7 +1011,7 @@ tar_target(
     .x$apc
   }) %>%
     bind_rows(.id = 'group.service') %>%
-    filter(str_detect(group.service, 'atleast_three')) %>%
+    filter(str_detect(group.service, 'zero_services') | str_detect(group.service, 'atleast_six_services')) %>%
     separate(group.service, c('stratifier', 'service'), sep = '[.]') %>%
     mutate(strata = case_when(stratifier == 'overall' ~ 'stat_0',
                               TRUE ~ strata)) %>%
